### 2020-04-06 paper/main.tex
init commit

\documentclass[9pt]{article}

% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2020

% ready for submission
% \usepackage{neurips_2020}

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
\usepackage[preprint]{neurips_2020}

% to compile a camera-ready version, add the [final] option, e.g.:
%     \usepackage[final]{neurips_2020}

% to avoid loading the natbib package, add option nonatbib:
%     \usepackage[nonatbib]{neurips_2020}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\usepackage{bm}
\usepackage{amsmath}
\usepackage{graphicx}

\graphicspath{{./../../plots/}}
\newcommand{\real}{\text{real}}

\title{Bayesian Neural Arithmetic Units -- Leveraging The Complex Plane}
\author{
  Niklas Heim,
  V\'aclav \v Sm\'idl,
  Tom\'a\v s Pevn\'y \\
  Artificial Intelligence Center\\
  Czech Technical University\\
  Prague, CZ 120 00\\
  \texttt{\{niklas.heim, vasek.smidl, tomas.pevny\}@aic.fel.cvut.cz}\\
}

\begin{document}

\maketitle

\begin{abstract}
  Common Neural Networks poorly approximate simple arithmetic operations.  The
  new Neural Arithmetic Units aim to overcome this difficulty, but are limited
  either limited to operate on positive numbers (NALU by
  \citet{trask_neural_2018}), or can only represent simple addition and
  multiplication (NAU & NMU by \citet{madsen_neural_2020}).
  We present the first Neural Arithmetic Unit that operates on the full domain
  of real numbers and is capable of learning arbitrary power functions.
  For a theoretically grounded sparsification of the units we employ Bayesian
  compression on the model weights via Automatic Relevance Determination.
\end{abstract}

\section{Introduction}%
\label{sec:introduction}

It is known that Neural Networks can approximate functions arbitrarily well but
do not necessarily generalize beyond the range inputs that were seen during
training. Neural Arithmetic Units can help to overcome this problem
\cite{trask_neural_2018,madsen_neural_2020}

\section{Introduction}%
\label{sec:introduction}

We fuse the ideas of the \emph{Neural Multiplication Unit} (NMU) by
\citet{madsen_neural_2020} and the \emph{Neural Arithmetic Logic Unit} (NALU)
by \citet{trask_neural_2018}.

The NALU in its original form is capable of addition, subtraction, and
multiplication of \textbf{positive}, high-dimensional vectors. However, for
small inputs convergence is complicated by the use of the logarithm in the
NALU. The logarithm further prevents the NALU of processing negative inputs
correctly.

The NMU fixes both the previous issues, but can only multiply two inputs, and
not represent arbitrary power functions.  Addition is taken care of by the
\emph{Neural Addition Unit} (NAU), which is essentially a dense layer without
bias. A chain of NAU and NMU can thus learn the task defined in
Eq.~\ref{eq:nmu_task}.

\begin{equation}
  \label{eq:nmu_task}
  y = (x_1 + x_2) \cdot (x_1 + x_2 + x_3 + x_4)
\end{equation}

\section{Complex Neural Multiplication Unit}%
\label{sec:complex_neural_multiplication_unit}

Our \emph{complex NMU} (NMUX) can learn arbitrary power functions while still
being able to correctly deal with negative inputs.
The NMUX layer is defined by
\begin{align}
  k_i &= \begin{cases}
     0  & x_i \leq 0 \\
    \pi & x_i > 0
  \end{cases} \\
  \bm r &= |\bm x| \\
  \bm m &= \exp(\bm M \log(\bm r)) \odot \cos(\bm M \bm k)
\end{align}
where $\bm k$ is a vector that is zero where $\bm x$ is positive and $\pi$
where it is negative, $\bm r$ is the elementwise absolute value, and $\bm M$
the multiplication matrix that we want to learn.

The NMUX is inspired by the multiplication part of the NALU, extended to
negative inputs by leveraging taking advantage of the complex logarithm.
The multiplication part of the NALU reads:
\begin{equation}
  \bm m = \exp(\bm M \log(|\bm x| + \epsilon)),
\end{equation}
where $\epsilon$ is a small constant that ensures positive inputs to the real
logarithm.  If use the complex logarithm, this constant becomes superfluous,
but we end up with a complex output in case of negative $x_i$.  In general, for
any complex number $z$\footnote{Note that complex numbers can be represented in
the polar, complex plane where $z=re^{i\varphi}$ with $r>0$ and $\varphi \in
(0,2\pi)$.}
\begin{align}
  \log(z) = \log\left(r\cdot e^{i\varphi}\right)
     = \log(r) + i\varphi.
\end{align}
However, as $z$ is assumed to be real, we can simplify as follows:
\begin{align}
  \log(z) = \log(r) + ik\pi,
\end{align}
where $k \in [0,1]$.

\begin{align}
  \bm m &= \exp(\bm M \log(\bm x)) \\
    &= \exp(\bm M ( \log(\bm r) + i\pi\bm k ))
\end{align}

\begin{align}
  \bm m_{\text{re}} &= \real(\exp(\bm M \log \bm r + i\pi\bm M\bm k)) \\
    &= \real(\exp(\bm M \log \bm r) \odot (\cos(\pi \bm M \bm k) + i \sin(\pi \bm M \bm k))) \\
    &= \exp(\bm M \log \bm r) \odot \cos(\pi \bm M \bm k)
\end{align}

\section{Experimetns}%
\label{sec:experimetns}

\subsection{10 param func}%
\label{sub:10_param_func}

% \begin{figure}
%   \centering
%   \includegraphics[width=0.8\linewidth]{10-param-func-task-nmu-paper.pdf}
%   \caption{MSE optimization result}%
%   \label{fig:10-param-func-task-nmu-paper}
% \end{figure}
% \begin{figure}
%   \centering
%   \includegraphics[width=0.8\linewidth]{10-param-func-bayes-task-nmu-paper.pdf}
%   \caption{ARD result with MSE starting point}%
%   \label{fig:10-param-func-bayes-task-nmu-paper}
% \end{figure}
% \begin{figure}
%   \centering
%   \includegraphics[width=0.8\linewidth]{10-param-func-bayes-task-nmu-paper-history.pdf}
%   \caption{ARD history}%
%   \label{fig:history}
% \end{figure}
% 
% \subsection{10 param func with sqrt and power}%
% \label{sub:10_param_func_with_sqrt_and_power}
% 
% \begin{figure}
%   \centering
%   \includegraphics[width=0.8\linewidth]{10-param-func-task-sqrt-power.pdf}
%   \caption{10-param-func-task-sqrt-Power}%
%   \label{fig:10-param-func-task-sqrt-power}
% \end{figure}
% \begin{figure}
%   \centering
%   \includegraphics[width=0.8\linewidth]{10-param-func-bayes-task-sqrt-power.pdf}
%   \caption{10-param-func-bayes-task-sqrt-Power}%
%   \label{fig:10-param-func-bayes-task-sqrt-power}
% \end{figure}
% \begin{figure}
%   \centering
%   \includegraphics[width=0.8\linewidth]{10-param-func-bayes-task-sqrt-power-history.pdf}
%   \caption{10-param-func-bayes-task-sqrt-Power-history}%
%   \label{fig:10-param-func-bayes-task-sqrt-power-history}
% \end{figure}

\subsection{Gradient surfaces}%
\label{sub:gradient_surfaces}

\bibliographystyle{plainnat}
\bibliography{refs}

\end{document}

### 2020-04-06 scripts/setup.jl

@@ -1,0 +1,60 @@
+function train!(loss, model, data, opt, history=MVHistory())
+    ps = params(model)
+    tot, llh, kld, lpλ = 0f0, 0f0, 0f0, 0f0
+
+    logging = Flux.throttle((i)->(@info "Step $i" [tot llh kld lpλ]), 1)
+    pushhist = Flux.throttle((i)->(
+            push!(history, :μz, i, copy(mean(model.encoder)));
+            push!(history, :σz, i, copy(var(model.encoder)));
+            push!(history, :λz, i, copy(var(model.prior)));
+            push!(history, :σx, i, copy(var(model.decoder,ones(1))));
+            push!(history, :loss, i, [tot, llh, kld, lpλ]);
+       ),
+    0.5)
+
+    i = haskey(history,:loss) ? get(history,:loss)[1][end]+1 : 1
+    for d in data
+        gs = gradient(ps) do
+            (tot, llh, kld, lpλ) = loss(d...)
+            return tot
+        end
+        logging(i)
+        pushhist(i)
+        Flux.Optimise.update!(opt, ps, gs)
+        i += 1
+    end
+
+    history
+end
+
+function notelbo(m::ARDNet, x, y; α0=1, β0=0, esamples=1)
+    llh = T(0)
+    for _ in 1:esamples
+        ps = reshape(rand(m.encoder),:)
+        llh += sum(logpdf(m.decoder, y, x, ps))
+    end
+    llh /= esamples
+    kld = sum(kl_divergence(m.encoder, m.prior))
+    lpλ = sum(logpdf(m.hyperprior, var(m.prior)))
+
+    _elbo = -llh + kld - lpλ
+    _elbo, -llh, kld, -lpλ
+end
+
+function run(d)
+    @unpack niters, batch, inlen, outlen, α0, β0, lr, esamples = d
+    e = Gaussian(μz, σz)
+    p = Gaussian(NoGradArray(zeros(T, zlen)), λz)
+    h = InverseGamma(α0,β0,zlen,true)
+    d = CMeanGaussian{ScalarVar}(FluxDecoder(net), σx, outlen)
+    model = ARDNet(p, h, e, d)
+
+
+    loss(x,y) = notelbo(model,x,y,α0=α0,β0=β0,esamples=esamples)
+
+    train_data = [generate() for _ in 1:niters]
+    opt = RMSProp(lr)
+    history = train!(loss, model, train_data, opt)
+
+    return @dict(model, history)
+end

### 2020-04-06 scripts/task-division-nmu-only.jl

@@ -1,0 +1,95 @@
+using DrWatson
+@quickactivate "arithmetic"
+
+using Flux
+using Plots
+using GenerativeModels
+using GMExtensions
+using NeuralArithmetic
+using Distributions: Uniform
+using Parameters
+using ValueHistories
+using LinearAlgebra
+
+include(srcdir("bayesnet.jl"))
+include(joinpath(@__DIR__, "setup.jl"))
+
+function perfect_nmu(T::Type, a::Int, b::Int)
+    if a == 1
+        m = zeros(T, a, b)
+        m[1] = T(1)
+        m[2] = T(-1)
+        return m
+    else
+        error("not sure how to create perfect NMU")
+    end
+end
+
+task = "task-division-nmu-only"
+T           = Float32
+batch       = 50
+inlen       = 4
+outlen      = 1
+niters      = 30000
+α0          = T(1)
+β0          = T(1)
+lr          = 0.003
+esamples    = 1
+r           = Uniform(-2,2)
+
+initf(s...) = rand(T, s...)
+
+setup = @dict(T, batch, inlen, outlen, niters, α0, β0, lr,
+              esamples, r, initf)
+
+net = Chain(ReNMUX(inlen, outlen, init=initf))
+
+zlen = length(Flux.destructure(net)[1])
+μz = Flux.destructure(net)[1]
+λz = ones(T,zlen)
+σz = ones(T,zlen)/10
+σx = ones(T,1)
+
+function f(x)
+    x1 = x[1,:]
+    x2 = x[2,:]
+    x3 = x[3,:]
+    x4 = x[4,:]
+    y = x1 ./ x2
+    reshape(y, 1, :)
+end
+
+function generate()
+    x = T.(rand(r, inlen, batch))
+    y = f(x)
+    (x,y)
+end
+
+file = produce_or_load(
+    datadir("10-param-func"),
+    setup,
+    prefix="bayes-$task",
+    run,
+    # force=true
+)
+
+pyplot()
+
+m = file[1][:model]
+h = file[1][:history]
+z = get(h, :μz)[2]
+p1 = plothistory(h)
+
+nmu = m.decoder.mapping.restructure(mean(m.encoder))
+(x,y) = generate()
+display(nmu(x))
+display(f(x))
+display(task)
+
+p2 = plot(
[…]

### 2020-04-06 scripts/task-division.jl

@@ -1,0 +1,116 @@
+using DrWatson
+@quickactivate "arithmetic"
+
+using Flux
+using Plots
+using GenerativeModels
+using GMExtensions
+using NeuralArithmetic
+using Distributions: Uniform
+using Parameters
+using ValueHistories
+using LinearAlgebra
+
+include(joinpath(@__DIR__, "setup.jl"))
+
+function perfect_nau(T::Type, a::Int, b::Int)
+    if a == b
+        m = zeros(T, a, b)
+        m[1,1] = T(1)
+        m[2,2] = T(1)
+        return m
+    else
+        error("not sure how to create perfect NAU")
+    end
+end
+
+function perfect_nmu(T::Type, a::Int, b::Int)
+    if a == 1
+        m = zeros(T, a, b)
+        m[1] = T(1)
+        m[2] = T(-1)
+        return m
+    else
+        error("not sure how to create perfect NMU")
+    end
+end
+
+task = "task-division"
+T           = Float32
+batch       = 50
+inlen       = 4
+outlen      = 1
+niters      = 30000
+α0          = T(1)
+β0          = T(1)
+lr          = 0.001
+esamples    = 1
+r           = Uniform(1,3)
+
+function init_nau(T, a::Int, b::Int)
+    m = zeros(T,a,b)
+    m[diagind(m,0)] .= T(1)
+    return m
+end
+
+init_nmu(T, a::Int, b::Int) = zeros(T, a, b)
+
+setup = @dict(T, batch, inlen, outlen, niters, α0, β0, lr,
+              esamples, r)
+ 
+net = Chain(
+            NAU(inlen, inlen, init=(s...)->init_nau(T,s...)),
+            ReNMUX(inlen, outlen, init=(s...)->init_nmu(T,s...))
+           )
+
+zlen = length(Flux.destructure(net)[1])
+μz = Flux.destructure(net)[1]
+λz = ones(T,zlen)/10
+σz = ones(T,zlen)/10
+σx = ones(T,1)
+
+function f(x)
+    x1 = x[1,:]
+    x2 = x[2,:]
+    y = x1 ./ x2
+    reshape(y, 1, :)
+end
+
+function generate()
+    x = T.(rand(r, inlen, batch))
+    y = f(x)
+    (x,y)
+end
+
+(x,y) = generate()
+
+file = produce_or_load(
[…]

### 2020-04-06 scripts/task-nmu-paper.jl

@@ -1,0 +1,89 @@
+using DrWatson
+@quickactivate "arithmetic"
+
+using Flux
+using Plots
+using GenerativeModels
+using GMExtensions
+using NeuralArithmetic
+using Distributions: Uniform
+using Parameters
+using ValueHistories
+using LinearAlgebra
+
+include(joinpath(@__DIR__, "setup.jl"))
+
+task = "task-nmu-paper"
+T           = Float32
+batch       = 50
+inlen       = 4
+outlen      = 1
+niters      = 30000
+α0          = T(1)
+β0          = T(1)
+lr          = 0.004
+esamples    = 1
+r           = Uniform(-2,2)
+
+initf(s...) = rand(T, s...)
+
+setup = @dict(T, batch, inlen, outlen, niters, α0, β0, lr,
+              esamples, r, initf)
+
+net = Chain(
+            NAU(inlen, inlen, init=initf),
+            ReNMUX(inlen, outlen, init=initf))
+
+zlen = length(Flux.destructure(net)[1])
+μz = Flux.destructure(net)[1]
+σz = ones(T,zlen)/2
+λz = ones(T,zlen)
+σx = ones(T,1)
+
+function f(x)
+    x1 = x[1,:]
+    x2 = x[2,:]
+    x3 = x[3,:]
+    x4 = x[4,:]
+    y = (x1 .+ x2) .* (x1 .+ x2 .+ x3 .+ x4)
+    reshape(y, 1, :)
+end
+
+rand_uniform(s...) = rand(r, s...)
+Flux.@nograd rand_uniform
+
+function generate()
+    x = T.(rand_uniform(inlen, batch))
+    y = f(x)
+    (x,y)
+end
+
+file = produce_or_load(
+    datadir("10-param-func"),
+    setup,
+    prefix="bayes-$task",
+    run,
+    # force=true
+)
+
+pyplot()
+
+m = file[1][:model]
+h = file[1][:history]
+z = get(h, :μz)[2]
+p1 = plothistory(h)
+
+nmu = m.decoder.mapping.restructure(mean(m.encoder))
+(x,y) = generate()
+display(nmu(x))
+display(f(x))
+display(task)
+
+p2 = plot(
+    annotatedheatmap(nmu[1].W[end:-1:1,:], c=:bluesreds, title="NAU", clim=(-1,1)),
[…]

### 2020-04-06 scripts/task-simple.jl

@@ -1,0 +1,20 @@
+T = Float32
+batch  = 50
+inlen  = 4
+outlen = 1
+r = Uniform(-2,2)
+
+function f(x)
+    x1 = x[1,:]
+    x2 = x[2,:]
+    x3 = x[3,:]
+    x4 = x[4,:]
+    y = (x1 .+ x2)
+    reshape(y, 1, :)
+end
+
+function generate()
+    x = Float32.(rand(r, inlen, batch))
+    y = f(x)
+    (x,y)
+end

### 2020-04-06 scripts/task-sqrt-power.jl

@@ -1,0 +1,87 @@
+using DrWatson
+@quickactivate "arithmetic"
+
+using Flux
+using Plots
+using GenerativeModels
+using GMExtensions
+using NeuralArithmetic
+using Distributions: Uniform
+using Parameters
+using ValueHistories
+using LinearAlgebra
+
+include(srcdir("bayesnet.jl"))
+include(joinpath(@__DIR__, "setup.jl"))
+
+task = "task-sqrt-power"
+T           = Float32
+batch       = 50
+inlen       = 4
+outlen      = 1
+niters      = 100000
+α0          = T(1)
+β0          = T(1)
+lr          = 0.004
+esamples    = 1
+r           = Uniform(0,2)
+
+initf(s...) = rand(T, s...)
+
+setup = @dict(T, batch, inlen, outlen, niters, α0, β0, lr,
+              esamples, r, initf)
+
+net = Chain(
+            NAU(inlen, inlen, init=initf),
+            ReNMUX(inlen, outlen, init=initf))
+
+zlen = length(Flux.destructure(net)[1])
+μz = Flux.destructure(net)[1]
+σz = ones(T,zlen)/2
+λz = ones(T,zlen)
+σx = ones(T,1)
+
+function f(x)
+    x1 = x[1,:]
+    x2 = x[2,:]
+    x3 = x[3,:]
+    x4 = x[4,:]
+    y = (x1 .+ x2).^2 .* sqrt.(x1 .+ x2 .+ x3 .+ x4)
+    reshape(y, 1, :)
+end
+
+function generate()
+    x = T.(rand(r, inlen, batch))
+    y = f(x)
+    (x,y)
+end
+
+file = produce_or_load(
+    datadir("10-param-func"),
+    setup,
+    prefix="bayes-$task",
+    run,
+    # force=true
+)
+
+pyplot()
+
+m = file[1][:model]
+h = file[1][:history]
+z = get(h, :μz)[2]
+p1 = plothistory(h)
+
+nmu = m.decoder.mapping.restructure(mean(m.encoder))
+(x,y) = generate()
+display(nmu(x))
+display(f(x))
+display(task)
+
+p2 = plot(
+    annotatedheatmap(nmu[1].W[end:-1:1,:], c=:bluesreds, title="NAU", clim=(-1,1)),
+    annotatedheatmap(nmu[2].M[end:-1:1,:], c=:bluesreds, title="ReNMUX", clim=(-1,1)),
[…]

### 2020-04-06 src/bayesnet.jl

@@ -1,0 +1,35 @@
+using GenerativeModels: AbstractGM
+using ConditionalDists: ACGaussian
+
+include(srcdir("flux_decoder.jl"))
+
+FDCMeanGaussian = CMeanGaussian{V,<:FluxDecoder} where V
+
+struct BayesNet{P<:Gaussian, E<:Gaussian, D<:CMeanGaussian} <: AbstractGM
+    prior::P
+    encoder::E
+    decoder::D
+end
+
+Flux.@functor BayesNet
+
+function ConditionalDists.logpdf(p::ACGaussian, x::AbstractArray{T}, z::AbstractArray{T},
+                                 ps::AbstractVector{T}) where T
+    μ = mean(p, z, ps)
+    σ2 = var(p, z)
+    d = x - μ
+    y = d .* d
+    y = (1 ./ σ2) .* y .+ log.(σ2) .+ T(log(2π))
+    -sum(y, dims=1) / 2
+end
+
+function GenerativeModels.mean(p::FDCMeanGaussian, z::AbstractArray, ps::AbstractVector)
+    p.mapping(z, ps)
+end
+
+function elbo(m::BayesNet, x, y; β=1)
+    ps = reshape(rand(m.encoder),:)
+    llh = sum(logpdf(m.decoder, y, x, ps))
+    kld = sum(kl_divergence(m.encoder, m.prior))
+    llh - β*kld
+end

### 2020-04-06 src/flux_decoder.jl

@@ -1,0 +1,9 @@
+struct FluxDecoder{M}
+    model::M
+    restructure::Function
+end
+
+FluxDecoder(m) = FluxDecoder(m, Flux.destructure(m)[2])
+
+(d::FluxDecoder)(x::AbstractMatrix, ps::AbstractVector) = d.restructure(ps)(x)
+(d::FluxDecoder)(x::AbstractMatrix) = d.model(x)

### 2020-04-07 paper/main.tex
cite diffeq+flux

@@
   \citet{trask_neural_2018}), or can only represent simple addition and
-  multiplication (NAU & NMU by \citet{madsen_neural_2020}).
+  multiplication (NAU \& NMU by \citet{madsen_neural_2020}).
   We present the first Neural Arithmetic Unit that operates on the full domain
@@
 \cite{trask_neural_2018,madsen_neural_2020}
+
+% TODO: put this in acknowledgements %
+all the results in this paper were create with the help of the following Julia
+packages: \cite{rackauckas_differentialequationsjl_2017} + (Flux.jl)
 

### 2020-04-13 scripts/division/plots.jl
plots.jl fixes

@@ -1,4 +1,6 @@
 
+using DrWatson
+using Plots
 using DataFrames
 using Statistics
 using ValueHistories
@@ -10,6 +12,7 @@ using ProgressMeter
 using LinearAlgebra
 using Parameters
 using Distributions: Uniform
+using GMExtensions
 
 include(joinpath(@__DIR__, "utils.jl"))
 include(joinpath(@__DIR__, "ard_utils.jl"))
@@ -79,7 +82,7 @@ function aggregateruns(runs::DataFrame)
         σL2=std(r.L2),
         loss_func=r.loss_func[1])
    end
-end
+end;
 
 
 force  = false

### 2020-04-22 paper/main.tex
start writing

@@
 \usepackage{microtype}      % microtypography
+
+\usepackage{todonotes}
 
@@
 
-It is known that Neural Networks can approximate functions arbitrarily well but
-do not necessarily generalize beyond the range inputs that were seen during
-training. Neural Arithmetic Units can help to overcome this problem
-\cite{trask_neural_2018,madsen_neural_2020}
+It is known that Neural Networks can approximate functions arbitrarily
+well\todo{cite universal approx}.  However, this strength of approximation
+often comes at the cost of generalization beyond the training data manifold.
+\citet{trask_neural_2018} have demonstrated how severe this problem is even for
+the simplest arithmetic operations, such as summing or multiplying two numbers.
+In order to increase the power of abstraction of Neural Networks they propose a
+\emph{Neural Arithmetic Logic Unit} (NALU) which can help to overcome this problem
+\cite{trask_neural_2018} and is capable of learning the arithmetic addition
+$+$, subtraction $-$, multiplication $\times$, and division
+$\{+,-,\times,\div\}$ with stunning extrapolation accuracy.
+However, the NALU comes with the severe limitation not being able to handle negative
+inputs due to the logarithm in the multiplication part of the NALU:
+\begin{align}
+  \label{eq:nalu}
+  \text{Addition: }       & \bm a = \bm W \bm x                  
+                          & \bm W& = \tanh(\hat{\bm W}) \odot \sigma(\hat{\bm M}) \\
+  \text{Multiplication: } & \bm m = \exp \bm W(\log(|\bm x|+\epsilon)) & &\\
+  \text{Output: }         & \bm y = \bm a \odot \bm g + \bm m \odot (1-\bm g) 
+                          & \bm g& = \sigma(\bm G\bm x)
+\end{align}
 
-% TODO: put this in acknowledgements %
+A multiplication layer that can handle negative inputs was introduced by \citet{madsen_neural_2020}.
+The \emph{Neural Multiplication Unit} (NMU) is defined by
+\begin{align}
+  \text{NMU: } y_j = \prod_i W_{ij} z_{i} + 1 - W_{ij} \hskip .2\textwidth W_{ij}=\min(\max(W_{ij}, 0), 1)
+\end{align}
+
+\todo{put this in acknowledgements
 all the results in this paper were create with the help of the following Julia
-packages: \cite{rackauckas_differentialequationsjl_2017} + (Flux.jl)
+packages: \cite{rackauckas_differentialequationsjl_2017} + (Flux.jl)}
 

### 2020-04-22 scripts/arithmetic/addition_npu_ard.jl
ard with gamma opt woooooorks

@@ -21,32 +21,32 @@ include(srcdir("arithmetic_ard_models.jl"))
 @with_kw struct AddARDConfig
     batch::Int      = 128
     inlen::Int      = 10
-    niters::Int     = 50000
-    lr::Real        = 0.001
-    lowlim::Real    = 1
+    niters::Int     = 300000
+    lr::Real        = 0.0005
+    lowlim::Real    = -2
     uplim::Real     = 2
-    α0              = Float32(1e-5)
-    β0              = Float32(1e-5)
+    α0              = Float32(1e0)
+    β0              = Float32(1e0)
     fstinit::String = "glorotuniform"
     sndinit::String = "glorotuniform"
     model::String   = "npu"
-    subset::Real    = 0.5f0
-    overlap::Real   = 0.25f0
+    subset::Real    = 0.3f0
+    overlap::Real   = 0.0f0
 end
 
 
 function run(c::AddARDConfig)
-    generate = arithmetic_dataset(+, c.inlen,
+    generate = arithmetic_dataset(*, c.inlen,
         d=Uniform(c.lowlim,c.uplim),
         subset=c.subset,
         overlap=c.overlap)
-    test_generate = arithmetic_dataset(+, c.inlen,
+    test_generate = arithmetic_dataset(*, c.inlen,
         d=Uniform(c.lowlim-4,c.uplim+4),
         subset=c.subset,
         overlap=c.overlap)
 
     net   = get_model(c.model, c.inlen, c.fstinit, c.sndinit)
-    model = ardnet(net, c.α0, c.β0, 1)
+    model = ardnet_αβ(net, c.α0, c.β0, 1)
     loss  = (x,y) -> notelbo(model,x,y)
 
     data     = (generate(c.batch) for _ in 1:c.niters)
@@ -61,7 +61,7 @@ end
 pattern = basename(splitext(@__FILE__)[1])
 config = AddARDConfig()
 outdir  = datadir("tests", pattern)
-res, fname = produce_or_load(outdir, config, run, force=false)
+res, fname = produce_or_load(outdir, config, run, force=true)
 
 m = res[:model]
 h = res[:history]
@@ -72,10 +72,11 @@ include(srcdir("plots.jl"))
 
 pyplot()
 p1 = plot(h,logscale=false)
+#p1 = plothistory(h)
 net = get_mapping(m)
[…]

### 2020-04-22 src/arithmetic_ard_models.jl

@@ -12,6 +12,21 @@ function ardnet(mapping, α0, β0, out)
     ARDNet(h, p, e, d)
 end
 
+function ardnet_αβ(mapping, α0, β0, out)
+    μz = Flux.destructure(mapping)[1]
+    zlen = length(μz)
+    λz = ones(Float32,zlen)/10
+    σz = ones(Float32,zlen)/10
+    σx = ones(Float32,1)
+
+    e = Gaussian(μz, σz)
+    p = Gaussian(NoGradArray(zeros(Float32,zlen)), λz)
+    h = InverseGamma(α0,β0,zlen)
+    d = CMeanGaussian{ScalarVar}(FluxDecoder(mapping), σx, out)
+    a = ARDNet(h, p, e, d)
+end
+
+
 function train!(loss, model::ARDNet, data, val_data, opt, history=MVHistory())
     ps = params(model)
     tot, llh, kld, lpλ, tot_val = 0f0, 0f0, 0f0, 0f0, 0f0
@@ -22,6 +37,7 @@ function train!(loss, model::ARDNet, data, val_data, opt, history=MVHistory())
             push!(history, :σz, i, copy(var(model.encoder)));
             push!(history, :λz, i, copy(var(model.prior)));
             push!(history, :σx, i, copy(var(model.decoder,ones(1))));
+            push!(history, :αβ, i, copy([model.hyperprior.α[1], model.hyperprior.β[1]]));
             tot_val = loss(val_data...);
             push!(history, :loss, i, [tot, llh, kld, lpλ, tot_val]);
        ),

### 2020-04-22 src/arithmetic_dataset.jl

@@ -14,7 +14,7 @@ function arithmetic_dataset(op::Function, xlen::Int; d::Uniform=Uniform(-2,2),
     len = round(Int, xlen*subset)
     ovl = round(Int, len*overlap)
     ii = 1:len
-    jj = (len-ovl):(2len-ovl)
+    jj = (len-ovl+1):(2len-ovl)
     @info "Arithmetic dataset sum indices: a=$ii b=$jj"
 
     function generate(batch::Int)

### 2020-04-22 src/arithmetic_models.jl

@@ -10,7 +10,7 @@ function initf(s::String)
     elseif s == "glorotuniform"
         return (a,b) -> Flux.glorot_uniform(a,b)
     elseif s == "rand"
-        return (a,b) -> rand(Float32,a,b)
+        return (a,b) -> rand(Float32,a,b)/10
     elseif s == "randn"
         return (a,b) -> randn(Float32,a,b)
     elseif s == "zero"

### 2020-04-22 src/plots.jl

@@ -15,5 +15,6 @@ function Plots.plot(h::MVHistory; logscale=true)
 
     ps = reduce(hcat, get(h, :μz)[2])'
     p2 = plot(idx, ps, legend=false, lw=2)
+
     plot(p1,p2,layout=(2,1))
 end

### 2020-04-22 paper/main.tex

@@
 often comes at the cost of generalization beyond the training data manifold.
+\todo{mention ODEs as use case}
+
+\section{Related Work}%
+\label{sec:related_work}
+
 \citet{trask_neural_2018} have demonstrated how severe this problem is even for
@@
 In order to increase the power of abstraction of Neural Networks they propose a
-\emph{Neural Arithmetic Logic Unit} (NALU) which can help to overcome this problem
-\cite{trask_neural_2018} and is capable of learning the arithmetic addition
-$+$, subtraction $-$, multiplication $\times$, and division
-$\{+,-,\times,\div\}$ with stunning extrapolation accuracy.
-However, the NALU comes with the severe limitation not being able to handle negative
+\emph{Neural Arithmetic Logic Unit} (NALU) which can help to overcome this
+problem \cite{trask_neural_2018} and is capable of learning the arithmetic
+addition, subtraction, multiplication, and division
+$\{+,-,\times,\div\}$ with stunning extrapolation accuracy.  However,
+the NALU comes with the severe limitation not being able to handle negative
 inputs due to the logarithm in the multiplication part of the NALU:
+
 \begin{align}
-  \label{eq:nalu}
+  \label{eq:nalu_add}
   \text{Addition: }       & \bm a = \bm W \bm x
                           & \bm W& = \tanh(\hat{\bm W}) \odot \sigma(\hat{\bm M}) \\
+  \label{eq:nalu_mult}
   \text{Multiplication: } & \bm m = \exp \bm W(\log(|\bm x|+\epsilon)) & &\\
@@
 A multiplication layer that can handle negative inputs was introduced by \citet{madsen_neural_2020}.
-The \emph{Neural Multiplication Unit} (NMU) is defined by
+The \emph{Neural Multiplication Unit} (NMU) is defined by Eq.~\ref{eq:nmu} and is typically used in
+conjunction with the so-called \emph{Neural Addition Unit} (NAU) in Eq.~\ref{eq:nau}.
 \begin{align}
-  \text{NMU: } y_j = \prod_i W_{ij} z_{i} + 1 - W_{ij} \hskip .2\textwidth W_{ij}=\min(\max(W_{ij}, 0), 1)
+  \label{eq:nmu}
+  \text{NMU: } &y_j = \prod_i M_{ij} z_{i} + 1 - M_{ij}  &M_{ij}=\min(\max(M_{ij}, 0), 1)\\
+  \label{eq:nau}
+  \text{NAU: } &\bm y = \bm A \bm x &A_{ij}=\min(\max(A_{ij}, 0), 1)
 \end{align}
+In both NMU and NAU the weights are clipped to $[0,1]$, and typically regularized
+with $\mathcal{R}$:
+\begin{align}
+  \label{eq:rsparse}
+  \mathcal{R} = \sum_{ij} \min(W_{ij}, 1-W_{ij})
+\end{align}
+
+The combination of NAU and NMU can thus learn $\{+,-,\times\}$, but no division.
 
@@
 
-\section{Introduction}%
-\label{sec:introduction}
+\section{Neural Power Unit}%
+\label{sec:neural_power_unit}
 
-We fuse the ideas of the \emph{Neural Multiplication Unit} (NMU) by
-\citet{madsen_neural_2020} and the \emph{Neural Arithmetic Logic Unit} (NALU)
-by \citet{trask_neural_2018}.
-
-The NALU in its original form is capable of addition, subtraction, and
-multiplication of \textbf{positive}, high-dimensional vectors. However, for
-small inputs convergence is complicated by the use of the logarithm in the
-NALU. The logarithm further prevents the NALU of processing negative inputs
-correctly.
-
-The NMU fixes both the previous issues, but can only multiply two inputs, and
-not represent arbitrary power functions.  Addition is taken care of by the
-\emph{Neural Addition Unit} (NAU), which is essentially a dense layer without
-bias. A chain of NAU and NMU can thus learn the task defined in
-Eq.~\ref{eq:nmu_task}.
-
-\begin{equation}
-  \label{eq:nmu_task}
-  y = (x_1 + x_2) \cdot (x_1 + x_2 + x_3 + x_4)
-\end{equation}
-
-\section{Complex Neural Multiplication Unit}%
-\label{sec:complex_neural_multiplication_unit}
-
-Our \emph{complex NMU} (NMUX) can learn arbitrary power functions while still
-being able to correctly deal with negative inputs.
-The NMUX layer is defined by
+Our \emph{Neural Power Unit} (NPU) can learn arbitrary power functions (which
+includes division) while still being able to correctly deal with negative
+inputs.  The NPU layer is defined by
 \begin{align}
@@
 
-The NMUX is inspired by the multiplication part of the NALU, extended to
-negative inputs by leveraging taking advantage of the complex logarithm.
-The multiplication part of the NALU reads:
-\begin{equation}
-  \bm m = \exp(\bm M \log(|\bm x| + \epsilon)),
-\end{equation}
-where $\epsilon$ is a small constant that ensures positive inputs to the real
-logarithm.  If use the complex logarithm, this constant becomes superfluous,
-but we end up with a complex output in case of negative $x_i$.  In general, for
-any complex number $z$\footnote{Note that complex numbers can be represented in
-the polar, complex plane where $z=re^{i\varphi}$ with $r>0$ and $\varphi \in
-(0,2\pi)$.}
+The NPU is inspired by the multiplication part of the NALU
+Eq.~\ref{eq:nalu_mult}, extended to negative inputs by taking advantage of the
+complex logarithm. In general, for any complex number $z$\footnote{Note that
+complex numbers can be represented in the polar, complex plane where
+$z=re^{i\varphi}$ with $r>0$ and $\varphi \in (0,2\pi)$.}
 \begin{align}
@@
 \end{align}
-where $k \in [0,1]$.
+where $k \in [0,1]$ is zero for positive inputs and one for negative inputs $z$.
 

### 2020-05-15 paper/main.tex
commit before starting to write

@@
 
-\title{Bayesian Neural Arithmetic Units -- Leveraging The Complex Plane}
+\title{Neural Power Unit \\-- A Bayesian Approach To Neural Arithmetic}
 \author{
@@
 often comes at the cost of generalization beyond the training data manifold.
+This lack of generalization of traditional network architectures becomes 
+The inability to generalize to unseen inputs is an indicator for a lack of
+abstraction of the task at hand. The model merely sort of memorized the inputs.
+Neural Arithmetic Units aim to
+
 \todo{mention ODEs as use case}
@@
 
-\citet{trask_neural_2018} have demonstrated how severe this problem is even for
+\citet{trask_neural_2018} have demonstrated how severe the extrapolation problem is even for
 the simplest arithmetic operations, such as summing or multiplying two numbers.
@@
 \label{sub:gradient_surfaces}
+\begin{figure}
+  \centering
+  %\includegraphics[width=0.8\linewidth]{../plots/test.pgf}
+  \input{../plots/test.tikz.tex}
+  \caption{Test}%
+  \label{fig:test}
+\end{figure}
 

### 2020-05-15 experiments/gated-npu.jl

@@ -46,10 +46,10 @@ end
 @with_kw struct Config
     batch::Int      = 128
     niters::Int     = 5000
-    lr::Real        = 1e-2
+    lr::Real        = 5e-3
 
-    lowlim::Real    = -1
-    uplim::Real     = 1
+    lowlim::Real    = 0
+    uplim::Real     = 3
     subset::Real    = 0.5f0
     overlap::Real   = 0.25f0
 
@@ -60,15 +60,15 @@ end
 c = Config()
 d = c.inlen
 init(a,b) = rand(Float32,a,b)/10
-#init(a,b) = Flux.glorot_uniform(a,b)
+init(a,b) = Flux.glorot_uniform(a,b)
 model = Chain(NAU(d,d,init=init), GatedNPU(d,1,init=init))
 #model = Chain(NAU(d,d,init=init), NPU(d,1,init=init))
 
-generate = arithmetic_dataset(*, c.inlen,
+generate = arithmetic_dataset(/, c.inlen,
     d=Uniform(c.lowlim,c.uplim),
     subset=c.subset,
     overlap=c.overlap)
-test_generate = arithmetic_dataset(*, c.inlen,
+test_generate = arithmetic_dataset(/, c.inlen,
     d=Uniform(c.lowlim-4,c.uplim+4),
     subset=c.subset,
     overlap=c.overlap)
@@ -78,10 +78,10 @@ ps = Flux.params(model)
 function loss(x,y)
     mse = Flux.mse(model(x),y)
     l1  = norm(ps, 1)
-    mse + 0.1l1
+    mse + 0.0001l1
     # st  = -logSt(ps, 0.5f0, 1f0)
     # mse + st
-    # mse
+    #mse
 end
 
 data     = (generate(c.batch) for _ in 1:c.niters)

### 2020-05-15 jmds/mult.jl

@@ -1,0 +1,124 @@
+
+using DrWatson
+@quickactivate "NIPS_2020_NMUX"
+
+using LinearAlgebra
+using Flux
+using NeuralArithmetic
+using Distributions: Uniform
+using Plots
+# pyplot()
+plotly()
+
+include(srcdir("arithmetic_st_models.jl"))
+
+
+w1 = Float32.(-1:0.04:1)
+w2 = Float32.(-1:0.04:1)
+r  = Uniform(-3,3)
+
+X  = Float32.(rand(r, 4, 300))
+
+function f(x::Vector)
+    x1 = x[1]
+    x2 = x[2]
+    x3 = x[3]
+    x4 = x[4]
+    (x1 + x2) * (x1 + x2 + x3 + x4)
+end;
+
+
+nacplus(x::Matrix{T}, w::Matrix{T}) where T = w*x
+function nacplus(x::Matrix{T}, w::T) where T
+    W = [w w T(0) T(0);
+         w w w w]
+    nacplus(x, W)
+end
+
+nacmult(x::Matrix{T}, w::Matrix{T}; ϵ=T(1e-8)) where T = exp.(w * log.(abs.(x) .+ ϵ))
+nacmult(x::Matrix{T}, w::T) where T = nacmult(x, [w w]);
+
+nalu(x::Matrix{T}, w1::T, w2::T) where T = nacmult(nacplus(x, w1), w2)
+
+
+function mse(model::Function, x::Matrix{T}, w1::T, w2::T; zmin=0, zmax=1000) where T
+    y = mapslices(f, x, dims=1)
+    ŷ = model(x, w1, w2)
+    max(min(Flux.mse(y,ŷ), zmax), zmin)
+end
+
+# p1 = surface(w1, w2, (w1,w2)-> mse(nalu,X,w1,w2),
+#     title="NALU", xlabel="w1", ylabel="w2")
+# display(p1)
+
+
+function nmu(x::Vector{T}, W::Matrix{T}) where T
+    z = W .* reshape(x,1,:) .+ 1 .- W
+    dropdims(prod(z, dims=2), dims=2)
+end
+function nmu(x::AbstractMatrix, W::Matrix{T}) where T
+    buf = zeros(size(W,1), size(x,2))
+    for i in 1:size(x,2)
+        buf[:,i] = nmu(x[:,i], W)
+    end
+    return buf
+end
[…]

### 2020-05-15 jmds/npu-gradient.jl

@@ -1,0 +1,84 @@
+
+using DrWatson
+@quickactivate "NIPS_2020_NMUX"
+
+using Plots
+using Zygote
+using Distributions
+pyplot()
+
+meshgrid(x, y) = (repeat(x, outer=length(y)), repeat(y, inner=length(x)))
+
+
+nacmult(x,w;ϵ=1f-7) = exp(w * log(abs(x + ϵ)))
+
+function npu(x::T, w::T; e::T=T(1e-7)) where T
+    r = abs(x) + e
+    k = T(x < 0 ? pi : 0.0)
+    # if r < e && abs(w) < e
+    #     T(1)
+    # else
+    #     return exp(w * log(r)) * cos(w*k)
+    # end
+    return exp(w * log(r)) * cos(w*k)
+end;
+
+
+id_mse(x,w) = abs(x - npu(x,w))
+
+dx(x,w) = -Zygote.gradient(x->id_mse(x,w), x)[1]
+dw(x,w) = -Zygote.gradient(w->id_mse(x,w), w)[1]
+
+x = -1:0.1:2
+w = -1:0.1:2
+x,w = meshgrid(x,w)
+u = dx.(x,w)
+v = dw.(x,w)
+r = sqrt.(u.^2 + v.^2) * 10
+u = u ./ r
+v = v ./ r
+
+# p1 = heatmap(x, w, (x,w)->dx(x,w), clim=(-10,10))
+# p2 = heatmap(x, w, (x,w)->dw(x,w), clim=(-10,10))
+# plot(p1,p2,size=(1000,500))
+plt = heatmap(x, w, id_mse, clim=(0,2), c=:viridis)
+quiver!(plt, x, w, quiver=(u,v), c=:white)
+
+
+function nmu(x::Vector, W::Matrix)
+     z = W .* reshape(x,1,:) .+ 1 .- W
+    dropdims(prod(z, dims=2), dims=2)
+end
+nmu(X::Matrix, W::Matrix) = vec(mapslices(x->nmu(x,W), X, dims=1))
+
+function npu(x::Vector{T}, W::Matrix{T}) where T
+    r = abs.(x) .+ eps(T)
+    k = map(i -> T(i < 0 ? pi : 0.0), x)
+    exp.(W * log.(r)) .* cos.(W*k)
+end
[…]

### 2020-05-15 scripts/loss-plots/div-loss.jl

@@ -1,0 +1,60 @@
+using DrWatson
+@quickactivate "NIPS_2020_NMUX"
+
+using Plots
+using Zygote
+using Distributions
+using LaTeXStrings
+#pgfplotsx()
+pyplot()
+
+include(srcdir("turbocmap.jl"))
+
+function nmu(x::Vector, W::Matrix)
+     z = W .* reshape(x,1,:) .+ 1 .- W
+    dropdims(prod(z, dims=2), dims=2)
+end
+nmu(X::Matrix, W::Matrix) = vec(mapslices(x->nmu(x,W), X, dims=1))
+
+function npu(x::AbstractArray{T}, W::Matrix{T}) where T
+    r = abs.(x) .+ eps(T)
+    k = max.(-sign.(x), 0) .* T(pi)
+    z = exp.(W * log.(r)) .* cos.(W*k)
+end
+#npu(X::Matrix, W::Matrix) = vec(mapslices(x->npu(x,W), X, dims=1))
+
+function gatednpu(x::AbstractArray{T}, W::AbstractMatrix{T}, g::AbstractVector{T}) where T
+    g = min.(max.(g, 0), 1)
+    r = abs.(x) .+ eps(T)
+    r = g .* r .+ (1 .- g) .* T(1)
+    k = max.(-sign.(x), 0) .* T(pi)
+    z = exp.(W * log.(r)) .* cos.(W*k)
+end
+
+batch = 500
+X = Array{Float64,2}(undef,2,batch)
+X[1,:] .= rand(Uniform(-3,3),batch)
+X[2,:] .= rand(Uniform(-0.05,0.05),batch)
+# X[1,:] .= rand(Uniform(-3,3),batch)
+# X[2,:] .= rand(Uniform(-0.001,0.001), batch)
+
+
+npuloss(w1,w2) = mean(abs2, vec(npu(X, [w1 w2])) .- X[1,:])
+nmuloss(w1,w2) = mean(abs2, vec(nmu(X, [w1 w2])) .- X[1,:])
+gatednpuloss(w1,w2,g) = mean(abs2, vec(gatednpu(X, [w1 w2], [g,g])) .- X[1,:])
+# gatednpuloss_zero(w1,w2) = mean(abs2, gatednpu(X, [w1 w2], zeros(2)) .- X[1,:])
+
+w1 = -1:0.05:1
+w2 = -1:0.05:1
+
+zlim = clim = (0,4.2)
[…]

### 2020-05-15 scripts/loss-plots/id-loss.jl

@@ -1,0 +1,74 @@
+using DrWatson
+@quickactivate "NIPS_2020_NMUX"
+
+using Plots
+using Zygote
+using Distributions
+using LaTeXStrings
+#pgfplotsx()
+pyplot()
+
+include(srcdir("turbocmap.jl"))
+
+function nmu(x::Vector, W::Matrix)
+     z = W .* reshape(x,1,:) .+ 1 .- W
+    dropdims(prod(z, dims=2), dims=2)
+end
+nmu(X::Matrix, W::Matrix) = vec(mapslices(x->nmu(x,W), X, dims=1))
+
+function npu(x::AbstractArray{T}, W::Matrix{T}) where T
+    r = abs.(x) .+ eps(T)
+    k = max.(-sign.(x), 0) .* T(pi)
+    z = exp.(W * log.(r)) .* cos.(W*k)
+end
+#npu(X::Matrix, W::Matrix) = vec(mapslices(x->npu(x,W), X, dims=1))
+
+function gatednpu(x::AbstractArray{T}, W::AbstractMatrix{T}, g::AbstractVector{T}) where T
+    g = min.(max.(g, 0), 1)
+
+    r = abs.(x) .+ eps(T)
+    r = g .* r .+ (1 .- g) .* T(1)
+
+    k = max.(-sign.(x), 0) .* T(pi)
+    k = g .* k .+ (1 .- g) .* T(0)
+
+    z = exp.(W * log.(r)) .* cos.(W*k)
+end
+
+batch = 500
+X = Array{Float64,2}(undef,2,batch)
+X[1,:] .= rand(Uniform(0,2),batch)
+X[2,:] .= rand(Uniform(-0.05,0.05),batch)
+# X[1,:] .= rand(Uniform(-3,3),batch)
+# X[2,:] .= rand(Uniform(-0.001,0.001), batch)
+
+
+npuloss(w1,w2) = mean(abs2, vec(npu(X, [w1 w2])) .- X[1,:])
+nmuloss(w1,w2) = mean(abs2, vec(nmu(X, [w1 w2])) .- X[1,:])
+gatednpuloss(w1,w2,g1,g2) = mean(abs2, vec(gatednpu(X, [w1 w2], [g1,g2])) .- X[1,:])
+gatednpuloss(w1,w2,g) = gatednpuloss(w1,w2,g,g)
[…]

### 2020-05-15 scripts/loss-plots/mult-loss.jl

@@ -1,0 +1,60 @@
+using DrWatson
+@quickactivate "NIPS_2020_NMUX"
+
+using Plots
+using Zygote
+using Distributions
+using LaTeXStrings
+#pgfplotsx()
+pyplot()
+
+include(srcdir("turbocmap.jl"))
+
+function nmu(x::Vector, W::Matrix)
+     z = W .* reshape(x,1,:) .+ 1 .- W
+    dropdims(prod(z, dims=2), dims=2)
+end
+nmu(X::Matrix, W::Matrix) = vec(mapslices(x->nmu(x,W), X, dims=1))
+
+function npu(x::AbstractArray{T}, W::Matrix{T}) where T
+    r = abs.(x) .+ eps(T)
+    k = max.(-sign.(x), 0) .* T(pi)
+    z = exp.(W * log.(r)) .* cos.(W*k)
+end
+#npu(X::Matrix, W::Matrix) = vec(mapslices(x->npu(x,W), X, dims=1))
+
+function gatednpu(x::AbstractArray{T}, W::AbstractMatrix{T}, g::AbstractVector{T}) where T
+    g = min.(max.(g, 0), 1)
+    r = abs.(x) .+ eps(T)
+    r = g .* r .+ (1 .- g) .* T(1)
+    k = max.(-sign.(x), 0) .* T(pi)
+    z = exp.(W * log.(r)) .* cos.(W*k)
+end
+
+batch = 500
+X = Array{Float64,2}(undef,2,batch)
+X[1,:] .= rand(Uniform(-3,3),batch)
+X[2,:] .= rand(Uniform(-0.05,0.05),batch)
+# X[1,:] .= rand(Uniform(-3,3),batch)
+# X[2,:] .= rand(Uniform(-0.001,0.001), batch)
+
+
+npuloss(w1,w2) = mean(abs2, vec(npu(X, [w1 w2])) .- X[1,:] .* X[2,:])
+nmuloss(w1,w2) = mean(abs2, vec(nmu(X, [w1 w2])) .- X[1,:] .* X[2,:])
+gatednpuloss(w1,w2,g) = mean(abs2, vec(gatednpu(X, [w1 w2], [g,g])) .- X[1,:] .* X[2,:])
+# gatednpuloss_zero(w1,w2) = mean(abs2, gatednpu(X, [w1 w2], zeros(2)) .- X[1,:])
+
+w1 = -1:0.05:1
+w2 = -1:0.05:1
+
+zlim = clim = (0,4.2)
[…]

### 2020-05-15 scripts/loss-plots/npu-quiver.jl

@@ -1,0 +1,38 @@
+meshgrid(x, y) = (repeat(x, outer=length(y)), repeat(y, inner=length(x)))
+
+
+nacmult(x,w;ϵ=1f-7) = exp(w * log(abs(x + ϵ)))
+
+function npu(x::T, w::T; e::T=T(1e-7)) where T
+    r = abs(x) + e
+    k = T(x < 0 ? pi : 0.0)
+    # if r < e && abs(w) < e
+    #     T(1)
+    # else
+    #     return exp(w * log(r)) * cos(w*k)
+    # end
+    return exp(w * log(r)) * cos(w*k)
+end;
+
+
+id_mse(x,w) = abs(x - npu(x,w))
+
+dx(x,w) = -Zygote.gradient(x->id_mse(x,w), x)[1]
+dw(x,w) = -Zygote.gradient(w->id_mse(x,w), w)[1]
+
+x = -1:0.1:2
+w = -1:0.1:2
+x,w = meshgrid(x,w)
+u = dx.(x,w)
+v = dw.(x,w)
+r = sqrt.(u.^2 + v.^2) * 10
+u = u ./ r
+v = v ./ r
+
+# p1 = heatmap(x, w, (x,w)->dx(x,w), clim=(-10,10))
+# p2 = heatmap(x, w, (x,w)->dw(x,w), clim=(-10,10))
+# plot(p1,p2,size=(1000,500))
+plt = heatmap(x, w, id_mse, clim=(0,2), c=:viridis)
+quiver!(plt, x, w, quiver=(u,v), c=:white)
+
+

### 2020-05-15 papers/main.tex
paper update

--- 2020-05-15 paper/main.tex
@@
 
+\usepackage{booktabs}
+\renewcommand{\arraystretch}{1.2}
+
 \title{Neural Power Unit \\-- A Bayesian Approach To Neural Arithmetic}
@@
 \begin{abstract}
-  Common Neural Networks poorly approximate simple arithmetic operations.  The
-  new Neural Arithmetic Units aim to overcome this difficulty, but are limited
-  either limited to operate on positive numbers (NALU by
+  Common Neural Networks can approximate simple arithmetic operations, but fail
+  to generalize well beyond the training manifold. A new class of units called
+  \emph{Neural Arithmetic Units} aim to overcome this difficulty, but are limited
+  either to operate on positive numbers (NALU by
   \citet{trask_neural_2018}), or can only represent simple addition and
@@
   of real numbers and is capable of learning arbitrary power functions.
-  For a theoretically grounded sparsification of the units we employ Bayesian
-  compression on the model weights via Automatic Relevance Determination.
 \end{abstract}
@@
 
-It is known that Neural Networks can approximate functions arbitrarily
-well\todo{cite universal approx}.  However, this strength of approximation
-often comes at the cost of generalization beyond the training data manifold.
-This lack of generalization of traditional network architectures becomes 
-The inability to generalize to unseen inputs is an indicator for a lack of
-abstraction of the task at hand. The model merely sort of memorized the inputs.
-Neural Arithmetic Units aim to
+Neural Networks (NN) have proven to perform exceptionally well at function
+approximation tasks\todo{cite universal approx}. The great approximation
+performance unfortunately come at the cost of generalization beyond the
+training domain\todo{cite something?}.  The inability to generalize to unseen
+inputs is a fundamental problem that hints at a lack of \emph{understanding} of
+the given task. The model merely memorizes the seen inputs and fails to
+abstract the true learning task.
 
+Neural Arithmetic Units aim to overcome this problem with units that are able
+to represent simple arithmetic operations exactly. By composition of these
+units it becomes possible to learn e.g. exponentials, sinus functions,
+logarithms, etc. This promises to improve on the extrapolation capabilities of
+NNs even on tasks that are beyond artificial arithmetic tasks such as learning
+multiplication, or a certain power function \todo{cite some examples}.
 \todo{mention ODEs as use case}
@@
 
-\citet{trask_neural_2018} have demonstrated how severe the extrapolation problem is even for
-the simplest arithmetic operations, such as summing or multiplying two numbers.
-In order to increase the power of abstraction of Neural Networks they propose a
-\emph{Neural Arithmetic Logic Unit} (NALU) which can help to overcome this
-problem \cite{trask_neural_2018} and is capable of learning the arithmetic
-addition, subtraction, multiplication, and division
-$\{+,-,\times,\div\}$ with stunning extrapolation accuracy.  However,
-the NALU comes with the severe limitation not being able to handle negative
-inputs due to the logarithm in the multiplication part of the NALU:
+\citet{trask_neural_2018} have demonstrated how severe the extrapolation
+problem is even for the simplest arithmetic operations, such as summing or
+multiplying two numbers.  In order to increase the power of abstraction of NNs
+they propose a \emph{Neural Arithmetic Logic Unit} (NALU) which is capable of
+learning arithmetic addition, subtraction, multiplication, and division
+$\{+,-,\times,\div\}$ with stunning extrapolation accuracy.  However, the NALU
+comes with the severe limitation not being able to handle negative inputs due
+to the logarithm in the multiplication part of the NALU:
 
@@
 packages: \cite{rackauckas_differentialequationsjl_2017} + (Flux.jl)}
+
+\begin{table}
+  \centering
+  \caption{Comparison of different $2\times2$ layers on the task $(x,y)\rightarrow(xy,\frac{x}{y})$.
+  $(x,y) \in \mathcal U^2(-2,2)$}
+  \label{tab:label}
+  \input{table_x*y_xdivy.tex}
+\end{table}
 
@@
 \label{sub:gradient_surfaces}
-\begin{figure}
-  \centering
-  %\includegraphics[width=0.8\linewidth]{../plots/test.pgf}
-  \input{../plots/test.tikz.tex}
-  \caption{Test}%
-  \label{fig:test}
-\end{figure}
+% \begin{figure}
+%   \centering
+%   %\includegraphics[width=0.8\linewidth]{../plots/test.pgf}
+%   \input{../plots/test.tikz.tex}
+%   \caption{Test}%
+%   \label{fig:test}
+% \end{figure}
 

### 2020-05-15 scripts/compare-npu-nmu-nalu-xy-xdivy.jl

@@ -1,0 +1,159 @@
+using DrWatson
+@quickactivate "NIPS_2020_NMUX"
+
+using Flux
+using LinearAlgebra
+using NeuralArithmetic
+
+f(x::Array) = cat(reshape(x[1,:] .* x[2,:], 1, :),
+                  reshape(x[1,:] ./ x[2,:], 1, :),
+                  dims=1)
+
+function generate()
+    x = rand(Float32, 2, 100) .* 4 .- 2
+    y = f(x)
+    (x,y)
+end
+
+function test_generate()
+    x = rand(Float32, 2, 1000) .* 8 .- 4
+    y = f(x)
+    (x,y)
+end
+
+function run_npu(c::Dict)
+    model = GatedNPUX(2,2,initRe=(s...)->rand(Float32,s...)/10)
+    ps = params(model)
+    opt = RMSProp(c[:lr])
+    data = (generate() for _ in 1:c[:niters])
+    loss(x,y) = Flux.mse(model(x),y) + c[:βl1]*norm(model.Im, 1) #+ 0.1norm(model.Im,1)
+    (x,y) = generate()
+    cb = Flux.throttle(() -> (@info loss(x,y)), 0.1)
+    Flux.train!(loss, ps, data, opt, cb=cb)
+    return Dict(:model=>model, :config=>c)
+end
+
+function run_nmu(c::Dict)
+    model = NMU(2,2)
+    ps = params(model)
+    opt = RMSProp(c[:lr])
+    data = (generate() for _ in 1:c[:niters])
+    loss(x,y) = Flux.mse(model(x),y)
+    (x,y) = generate()
+    cb = Flux.throttle(() -> (@info loss(x,y)), 0.1)
+    Flux.train!(loss, ps, data, opt, cb=cb)
+    return Dict(:model=>model, :config=>c)
+end
+
+function run_nalu(c::Dict)
+    model = NALU(2,2)
+    ps = params(model)
+    opt = RMSProp(c[:lr])
+    data = (generate() for _ in 1:c[:niters])
+    loss(x,y) = Flux.mse(model(x),y)
+    (x,y) = generate()
+    cb = Flux.throttle(() -> (@info loss(x,y)), 0.1)
+    Flux.train!(loss, ps, data, opt, cb=cb)
+    return Dict(:model=>model, :config=>c)
+end
+
+res, _ = produce_or_load(datadir("layercomparison"),
[…]

### 2020-05-15 papers/main.tex
some plots

@@
 Neural Networks (NN) have proven to perform exceptionally well at function
-approximation tasks\todo{cite universal approx}. The great approximation
-performance unfortunately come at the cost of generalization beyond the
+approximation tasks\todo{cite universal approx}. This great approximation
+performance unfortunately comes at the cost of generalization beyond the
 training domain\todo{cite something?}.  The inability to generalize to unseen
@@
 abstract the true learning task.
+This can be demonstrated by training a traditional, dense NN to approximate
+three functions
+\begin{align}
+  \label{eq:approx_tasks}
+  f(x) = e^x, && g(x) = \log(x), && h(x) = \sin(x)
+\end{align}
+
+\begin{figure}
+  \centering
+  \input{../plots/exp_log_sin/dense_exp.tex}
+  \caption{}%
+  \label{fig:}
+\end{figure}
 
@@
 to represent simple arithmetic operations exactly. By composition of these
-units it becomes possible to learn e.g. exponentials, sinus functions,
-logarithms, etc. This promises to improve on the extrapolation capabilities of
-NNs even on tasks that are beyond artificial arithmetic tasks such as learning
+units it becomes possible to learn e.g. exponentials, logarithms, and power
+functions. This promises to improve on the extrapolation capabilities of NNs
+even on tasks that are beyond artificial arithmetic tasks such as learning
 multiplication, or a certain power function \todo{cite some examples}.
@@
 packages: \cite{rackauckas_differentialequationsjl_2017} + (Flux.jl)}
-
+\todo{add sqrt and positive range to table~\ref{tab:compare_npu_npu_nalu}?}
 \begin{table}
   \centering
-  \caption{Comparison of different $2\times2$ layers on the task $(x,y)\rightarrow(xy,\frac{x}{y})$.
-  $(x,y) \in \mathcal U^2(-2,2)$}
-  \label{tab:label}
+  \caption{Comparison of different $2\times2$ layers on the task
+  $(x,y)\rightarrow(xy,\frac{x}{y})$.  $(x,y) \in \mathcal U^2(-2,2)$.}
+  \label{tab:compare_npu_npu_nalu}
   \input{table_x*y_xdivy.tex}

### 2020-05-15 scripts/compare-npu-nmu-nalu-xy-xdivy.jl

@@ -15,6 +15,12 @@ function generate()
     (x,y)
 end
 
+function generate_pos()
+    x = rand(Float32, 2, 100) .* 2
+    y = f(x)
+    (x,y)
+end
+
 function test_generate()
     x = rand(Float32, 2, 1000) .* 8 .- 4
     y = f(x)

### 2020-05-15 scripts/taylor/dense_exp_log_sin.jl

@@ -1,0 +1,74 @@
+using DrWatson
+@quickactivate "NIPS_2020_NMUX"
+
+using Flux
+using Parameters
+using LinearAlgebra
+using NeuralArithmetic
+using Plots
+pyplot()
+
+
+function run(c::Dict, f::Function)
+    @unpack dim, lowlim, uplim, niter = c
+    x = Float32.(reshape(lowlim:0.1:uplim, 1, :))
+    y = f.(x)
+
+    data = Iterators.repeated((x,y), niter)
+    opt = ADAM(1e-2)
+    model = Chain(Dense(1,dim,σ),Dense(dim,dim,σ),Dense(dim,1))
+    ps = params(model)
+    loss(x,y) = sum(abs2, model(x) .- y)
+
+    cb = [Flux.throttle(()->(
+               xt = Float32.(reshape((lowlim*2):0.5:(uplim*2),1,:));
+               yt = f.(xt);
+               p1 = plot(vec(xt), vec(yt));
+               plot!(p1, vec(xt), vec(model(xt)));
+               display(p1);
+               @info loss(x,y) loss(xt,yt)
+              ), 1)
+         ]
+    Flux.train!(loss, ps, data, opt, cb=cb)
+    return Dict(:model=>model, :config=>c)
+end
+
+expres, _ = produce_or_load(datadir("exp_log_sin"),
+                         Dict(:lowlim=>-5, :uplim=>5, :dim=>10, :niter=>10000),
+                         c -> run(c, exp),
+                         prefix="dense_exp",
+                         force=false)
+
+logres, _ = produce_or_load(datadir("exp_log_sin"),
+                         Dict(:lowlim=>0.1, :uplim=>2, :dim=>10, :niter=>10000),
+                         c -> run(c, log),
+                         prefix="dense_log",
+                         force=false)
+
+pgfplotsx()
+expmodel = expres[:model]
+c = expres[:config]
+@unpack dim, lowlim, uplim, niter = c
+
+xt = collect((lowlim*2):0.5:(uplim*2))
+yt = exp.(xt)
+
+p1 = plot(xt, yt, label="Exp", yscale=:log10, lw=2, ls=:dash)
+plot!(p1, xt, vec(expmodel(reshape(xt,1,:))), lw=2, label="Dense NN", size=(300,200))
[…]

### 2020-05-15 scripts/taylor/gatednpux_exp_log_sin.jl

@@ -1,0 +1,73 @@
+using DrWatson
+@quickactivate "NIPS_2020_NMUX"
+
+using Flux
+using Parameters
+using LinearAlgebra
+using NeuralArithmetic
+using Plots
+pyplot()
+
+
+function run(c::Dict, f::Function)
+    @unpack dim, lowlim, uplim, niter = c
+    x = Float32.(reshape(lowlim:0.1:uplim, 1, :))
+    y = f.(x)
+
+    data = Iterators.repeated((x,y), niter)
+    opt = ADAM(1e-3)
+    model = Chain(GatedNPUX(1,dim), NAU(dim,1))
+    ps = params(model)
+    loss(x,y) = sum(abs2, model(x) .- y) #+ βl1*norm(model[1].Im)
+
+    cb = [Flux.throttle(()->(
+               xt = Float32.(reshape((lowlim*2):0.5:(uplim*1.5),1,:));
+               yt = f.(xt);
+               p1 = plot(vec(xt), vec(yt), yscale=:log10);
+               plot!(p1, vec(xt), abs.(vec(model(xt))));
+               display(p1);
+               @info loss(x,y) loss(xt,yt)
+              ), 1)
+         ]
+    Flux.train!(loss, ps, data, opt, cb=cb)
+    return Dict(:model=>model, :config=>c)
+end
+
+expres, _ = produce_or_load(datadir("exp_log_sin"),
+                         Dict(:lowlim=>-5, :uplim=>5, :dim=>10, :niter=>50000),
+                         c -> run(c, exp),
+                         prefix="gatednpux_exp",
+                         force=false)
+
+logres, _ = produce_or_load(datadir("exp_log_sin"),
+                         Dict(:lowlim=>0.1, :uplim=>2, :dim=>10, :niter=>50000),
+                         c -> run(c, log),
+                         prefix="gatednpux_log",
+                         force=false)
+
+pgfplotsx()
+expmodel = expres[:model]
+c = expres[:config]
+@unpack dim, lowlim, uplim, niter = c
+
+xt = Float32.(collect((lowlim*2):0.5:(uplim*2)))
+yt = exp.(xt)
+
+p1 = plot(xt, yt, label="Exp", yscale=:log10, lw=2, ls=:dash)
[…]

### 2020-05-15 scripts/taylor/nalu_exp_log_sin.jl

@@ -1,0 +1,73 @@
+using DrWatson
+@quickactivate "NIPS_2020_NMUX"
+
+using Flux
+using Parameters
+using LinearAlgebra
+using NeuralArithmetic
+using Plots
+pyplot()
+
+
+function run(c::Dict, f::Function)
+    @unpack dim, lowlim, uplim, niter = c
+    x = Float32.(reshape(lowlim:0.1:uplim, 1, :))
+    y = f.(x)
+
+    data = Iterators.repeated((x,y), niter)
+    opt = ADAM(1e-3)
+    model = Chain(NALU(1,dim), NALU(dim,1))
+    ps = params(model)
+    loss(x,y) = sum(abs2, model(x) .- y) #+ βl1*norm(model[1].Im)
+
+    cb = [Flux.throttle(()->(
+               xt = Float32.(reshape((lowlim*2):0.5:(uplim*1.5),1,:));
+               yt = f.(xt);
+               p1 = plot(vec(xt), vec(yt), yscale=:log10);
+               plot!(p1, vec(xt), abs.(vec(model(xt))));
+               display(p1);
+               @info loss(x,y) loss(xt,yt)
+              ), 1)
+         ]
+    Flux.train!(loss, ps, data, opt, cb=cb)
+    return Dict(:model=>model, :config=>c)
+end
+
+expres, _ = produce_or_load(datadir("exp_log_sin"),
+                         Dict(:lowlim=>-5, :uplim=>5, :dim=>10, :niter=>50000),
+                         c -> run(c, exp),
+                         prefix="nalu_exp",
+                         force=false)
+
+logres, _ = produce_or_load(datadir("exp_log_sin"),
+                         Dict(:lowlim=>0.1, :uplim=>2, :dim=>10, :niter=>50000),
+                         c -> run(c, log),
+                         prefix="nalu_log",
+                         force=false)
+
+pgfplotsx()
+expmodel = expres[:model]
+c = expres[:config]
+@unpack dim, lowlim, uplim, niter = c
+
+xt = Float32.(collect((lowlim*2):0.5:(uplim*2)))
+yt = exp.(xt)
+
+p1 = plot(xt, yt, label="Exp", yscale=:log10, lw=2, ls=:dash)
[…]

### 2020-05-15 scripts/taylor/nmu_exp_log_sin.jl

@@ -1,0 +1,73 @@
+using DrWatson
+@quickactivate "NIPS_2020_NMUX"
+
+using Flux
+using Parameters
+using LinearAlgebra
+using NeuralArithmetic
+using Plots
+pyplot()
+
+
+function run(c::Dict, f::Function)
+    @unpack dim, lowlim, uplim, niter = c
+    x = Float32.(reshape(lowlim:0.1:uplim, 1, :))
+    y = f.(x)
+
+    data = Iterators.repeated((x,y), niter)
+    opt = ADAM(1e-4)
+    model = Chain(NMU(1,dim), NAU(dim,1))
+    ps = params(model)
+    loss(x,y) = sum(abs2, model(x) .- y) #+ βl1*norm(model[1].Im)
+
+    cb = [Flux.throttle(()->(
+               xt = Float32.(reshape((lowlim*2):0.5:(uplim*1.5),1,:));
+               yt = f.(xt);
+               p1 = plot(vec(xt), vec(yt), yscale=:log10);
+               plot!(p1, vec(xt), abs.(vec(model(xt))));
+               #display(p1);
+               @info loss(x,y) loss(xt,yt)
+              ), 1)
+         ]
+    Flux.train!(loss, ps, data, opt, cb=cb)
+    return Dict(:model=>model, :config=>c)
+end
+
+expres, _ = produce_or_load(datadir("exp_log_sin"),
+                         Dict(:lowlim=>-5, :uplim=>5, :dim=>100, :niter=>50000),
+                         c -> run(c, exp),
+                         prefix="nmu_exp",
+                         force=false)
+
+logres, _ = produce_or_load(datadir("exp_log_sin"),
+                         Dict(:lowlim=>0.1, :uplim=>2, :dim=>100, :niter=>50000),
+                         c -> run(c, log),
+                         prefix="nmu_log",
+                         force=false)
+
+pgfplotsx()
+expmodel = expres[:model]
+c = expres[:config]
+@unpack dim, lowlim, uplim, niter = c
+
+xt = Float32.(collect((lowlim*2):0.5:(uplim*2)))
+yt = exp.(xt)
+
+p1 = plot(xt, yt, label="Exp", yscale=:log10, lw=2, ls=:dash)
[…]

### 2020-05-16 papers/main.tex
plots and tables

@@
 
+% figures
+\usepackage{tikz}
+\usetikzlibrary{arrows,backgrounds,positioning,intersections}
+\usepackage{pgfplots}
+\pgfplotsset{compat=newest}
+\usepgfplotslibrary{groupplots}
+\usepgfplotslibrary{polar}
+\usepgfplotslibrary{smithchart}
+\usepgfplotslibrary{statistics}
+\usepgfplotslibrary{dateplot}
 \graphicspath{{./../../plots/}}
@@
 
+% tables
 \usepackage{booktabs}
@@
 
-Neural Networks (NN) have proven to perform exceptionally well at function
-approximation tasks\todo{cite universal approx}. This great approximation
-performance unfortunately comes at the cost of generalization beyond the
-training domain\todo{cite something?}.  The inability to generalize to unseen
-inputs is a fundamental problem that hints at a lack of \emph{understanding} of
-the given task. The model merely memorizes the seen inputs and fails to
-abstract the true learning task.
-This can be demonstrated by training a traditional, dense NN to approximate
-three functions
+Numbers and simple algebra are essential not only to human intelligence but also
+to the survival of many other
+species~\citep{dehaene_number_2011,gallistel_finding_2018}.  This can be taken
+as a hint that arithmetic is an important ingredient to a successful,
+intelligent agent.  State of the art neural networks are capable of learning
+simple arithmetic, but they fail to extrapolate beyond the ranges seen during
+training~\citep{suzgun_evaluating_2018,lake_generalization_2018}.
+The inability to generalize to unseen inputs is a fundamental problem that
+hints at a lack of \emph{understanding} of the given task. The model merely
+memorizes the seen inputs and fails to abstract the true learning task.
+The failure of numerical extrapolation on simple arithmetic tasks has been shown
+by~\cite{trask_neural_2018},
+who also introduce a new class of \emph{Neural Arithmetic Units}
+that show exceptional extrapolation performance on most arithmetic tasks.
+...now explain drawbacks of NALU and NMU...
+...we introduce blah...
+
+  This
+can be demonstrated by training a traditional, dense NN to approximate three
+functions
 \begin{align}
@@
   \centering
-  \input{../plots/exp_log_sin/dense_exp.tex}
+  \input{../plots/exp_log_sin/gatednpux_exp.tikz}
   \caption{}%
@@
 \todo{mention ODEs as use case}
+\todo{mention explainability}
 

### 2020-05-16 scripts/compare-npu-nmu-nalu-xy-xdivy.jl

@@ -9,22 +9,35 @@ f(x::Array) = cat(reshape(x[1,:] .* x[2,:], 1, :),
                   reshape(x[1,:] ./ x[2,:], 1, :),
                   dims=1)
 
-function generate()
+
+train_range = "pos-neg"
+
+function generate_pos_neg()
     x = rand(Float32, 2, 100) .* 4 .- 2
     y = f(x)
     (x,y)
 end
 
 function generate_pos()
-    x = rand(Float32, 2, 100) .* 2
+    x = rand(Float32, 2, 100) .* 2 .+ 0.1f0
     y = f(x)
     (x,y)
 end
 
 function test_generate()
-    x = rand(Float32, 2, 1000) .* 8 .- 4
+    x = rand(Float32, 2, 10000) .* 8 .- 4
     y = f(x)
     (x,y)
+end
+
+function generate()
+    if train_range == "pos-neg"
+        return generate_pos_neg()
+    elseif train_range == "pos"
+        return generate_pos()
+    else
+        error("Unknown train range: $train_range")
+    end
 end
 
 function run_npu(c::Dict)
@@ -52,7 +65,7 @@ function run_nmu(c::Dict)
 end
 
 function run_nalu(c::Dict)
-    model = NALU(2,2)
+    model = Chain(NALU(2,2))
     ps = params(model)
     opt = RMSProp(c[:lr])
     data = (generate() for _ in 1:c[:niters])
@@ -63,24 +76,44 @@ function run_nalu(c::Dict)
     return Dict(:model=>model, :config=>c)
 end
 
+function run_dense(c::Dict)
+    model = Chain(Dense(2,10,σ),Dense(10,10,σ),Dense(10,2))
+    ps = params(model)
+    opt = RMSProp(c[:lr])
+    data = (generate() for _ in 1:c[:niters])
+    loss(x,y) = Flux.mse(model(x),y)
+    (x,y) = generate()
+    cb = Flux.throttle(() -> (@info loss(x,y)), 0.1)
+    Flux.train!(loss, ps, data, opt, cb=cb)
+    return Dict(:model=>model, :config=>c)
+end
+
+
 res, _ = produce_or_load(datadir("layercomparison"),
                          Dict(:niters=>40000, :βl1=>0.1, :lr=>0.002),
[…]

### 2020-05-16 scripts/taylor/dense_exp_log_sin.jl

@@ -45,6 +45,12 @@ logres, _ = produce_or_load(datadir("exp_log_sin"),
                          prefix="dense_log",
                          force=false)
 
+sinres, _ = produce_or_load(datadir("exp_log_sin"),
+                         Dict(:lowlim=>-5, :uplim=>5, :dim=>10, :niter=>50000),
+                         c -> run(c, sin),
+                         prefix="dense_sin",
+                         force=false)
+
 pgfplotsx()
 expmodel = expres[:model]
 c = expres[:config]
@@ -54,7 +60,7 @@ xt = collect((lowlim*2):0.5:(uplim*2))
 yt = exp.(xt)
 
 p1 = plot(xt, yt, label="Exp", yscale=:log10, lw=2, ls=:dash)
-plot!(p1, xt, vec(expmodel(reshape(xt,1,:))), lw=2, label="Dense NN", size=(300,200))
+plot!(p1, xt, vec(expmodel(reshape(xt,1,:))), lw=2, label="Dense", size=(300,200))
 vline!(p1, [lowlim, uplim], lw=2, c=:gray, label="Train range")
 savefig(p1, plotsdir("exp_log_sin", "dense_exp.tikz"))
 display(p1)
@@ -68,7 +74,19 @@ xt = collect((lowlim*2):0.1:(uplim*4))
 yt = log.(xt)
 
 p2 = plot(xt, yt, label="Log", lw=2, ls=:dash)
-plot!(p2, xt, vec(logmodel(reshape(xt,1,:))), lw=2, label="Dense NN", size=(300,200))
+plot!(p2, xt, vec(logmodel(reshape(xt,1,:))), lw=2, label="Dense", size=(300,200))
 vline!(p2, [lowlim, uplim], lw=2, c=:gray, label="Train range")
 savefig(p2, plotsdir("exp_log_sin", "dense_log.tikz"))
 display(p2)
+
+sinmodel = sinres[:model]
+c = sinres[:config]
+@unpack dim, lowlim, uplim, niter = c
+xt = Float32.(collect((lowlim*2):0.1:(uplim*2)))
+yt = sin.(xt)
+
+p3 = plot(xt, yt, label="Sin", lw=2, ls=:dash)
+plot!(p3, xt, vec(sinmodel(reshape(xt,1,:))), lw=2, label="Dense", size=(300,200))
+vline!(p3, [lowlim, uplim], lw=2, c=:gray, label="Train range")
[…]

### 2020-05-16 scripts/taylor/gatednpux_exp_log_sin.jl

@@ -10,21 +10,22 @@ pyplot()
 
 
 function run(c::Dict, f::Function)
-    @unpack dim, lowlim, uplim, niter = c
+    #@unpack dim, lowlim, uplim, niter, lr = c
+    @unpack dim, lowlim, uplim, niter, lr, βl1 = c
     x = Float32.(reshape(lowlim:0.1:uplim, 1, :))
     y = f.(x)
 
     data = Iterators.repeated((x,y), niter)
-    opt = ADAM(1e-3)
+    opt = ADAM(lr)
     model = Chain(GatedNPUX(1,dim), NAU(dim,1))
     ps = params(model)
-    loss(x,y) = sum(abs2, model(x) .- y) #+ βl1*norm(model[1].Im)
+    loss(x,y) = sum(abs2, model(x) .- y) + βl1*norm(model[1].Im)
 
     cb = [Flux.throttle(()->(
                xt = Float32.(reshape((lowlim*2):0.5:(uplim*1.5),1,:));
                yt = f.(xt);
-               p1 = plot(vec(xt), vec(yt), yscale=:log10);
-               plot!(p1, vec(xt), abs.(vec(model(xt))));
+               p1 = plot(vec(xt), vec(yt));
+               plot!(p1, vec(xt), vec(model(xt)));
                display(p1);
                @info loss(x,y) loss(xt,yt)
               ), 1)
@@ -34,18 +35,24 @@ function run(c::Dict, f::Function)
 end
 
 expres, _ = produce_or_load(datadir("exp_log_sin"),
-                         Dict(:lowlim=>-5, :uplim=>5, :dim=>10, :niter=>50000),
+                         Dict(:lowlim=>-5, :uplim=>5, :dim=>10, :niter=>50000, :lr=>1e-3),
                          c -> run(c, exp),
                          prefix="gatednpux_exp",
                          force=false)
 
 logres, _ = produce_or_load(datadir("exp_log_sin"),
-                         Dict(:lowlim=>0.1, :uplim=>2, :dim=>10, :niter=>50000),
+                         Dict(:lowlim=>0.1, :uplim=>2, :dim=>10, :niter=>50000, :lr=>1e-3),
                          c -> run(c, log),
                          prefix="gatednpux_log",
[…]

### 2020-05-16 scripts/taylor/taylor_series.jl

@@ -9,7 +9,8 @@ global_logger(TerminalLogger(right_justify=80))
 using Flux
 using LinearAlgebra
 using NeuralArithmetic
-using UnicodePlots
+using Plots
+unicodeplots()
 
 
 _sine_taylor(x,n) = (-1)^n * x^(2n+1) / factorial(2n+1)
@@ -24,26 +25,26 @@ log_taylor(x,n) = _sum_taylor(_log_taylor,x,n,n0=1)
 
 x = -3:0.1:3
 
-plt = lineplot(x,exp_taylor.(x,0))
+plt = plot(x,exp_taylor.(x,0))
 for n in 1:6
-    lineplot!(plt,x,exp_taylor.(x,n))
+    plot!(plt,x,exp_taylor.(x,n))
 end
 
 
 x = 0.1:0.1:3
 
-plt = lineplot(x,log_taylor.(x,1))
+plt = plot(x,log_taylor.(x,1))
 for n in 2:6
-    lineplot!(plt,x,log_taylor.(x,n))
+    plot!(plt,x,log_taylor.(x,n))
 end
 display(plt)
 
 
 x = Float32.(reshape(-5:0.1:5, 1, :))
-f(x) = sine_taylor.(x,4)
+f(x) = sine_taylor.(x,2)
 #f(x) = exp_taylor.(x,3)
 #f(x) = exp.(x)
-f(x) = sin.(x)
+#f(x) = sin.(x)
 
 
 # x = Float32.(reshape(0.1:0.1:3, 1, :))
@@ -54,11 +55,11 @@ dim = 10
 
 data = Iterators.repeated((x,y), 100000)
 opt = ADAM(1e-2)
-model = Chain(NPU(1,dim), NAU(dim,1))
-model = Chain(NPUX(1,dim), NAU(dim,1))
+#model = Chain(NPU(1,dim), NAU(dim,1))
+#model = Chain(NPUX(1,dim), NAU(dim,1))
 #model = Chain(GatedNPU(1,dim), NAU(dim,1))
-#model = Chain(GatedNPUX(1,dim), NAU(dim,1))
-model = Chain(NALU(1,dim), NALU(dim,1))
+model = Chain(GatedNPUX(1,dim), NAU(dim,1))
+#model = Chain(NALU(1,dim), NALU(dim,1))
 #model = Chain(NMU(1,dim), NAU(dim,1))
[…]

### 2020-05-16 papers/main.tex
update plots packages; figure fuzzing

@@
 \usepgfplotslibrary{dateplot}
-\graphicspath{{./../../plots/}}
+\graphicspath{{./../plots/}}
 \newcommand{\real}{\text{real}}
@@
   Common Neural Networks can approximate simple arithmetic operations, but fail
-  to generalize well beyond the training manifold. A new class of units called
-  \emph{Neural Arithmetic Units} aim to overcome this difficulty, but are limited
-  either to operate on positive numbers (NALU by
+  to generalize beyond the range of numbers that were seen during training. A
+  new class of units called \emph{Neural Arithmetic Units} aim to overcome this
+  difficulty, but are limited either to operate on positive numbers (NALU by
   \citet{trask_neural_2018}), or can only represent simple addition and
-  multiplication (NAU \& NMU by \citet{madsen_neural_2020}).
-  We present the first Neural Arithmetic Unit that operates on the full domain
-  of real numbers and is capable of learning arbitrary power functions.
+  multiplication (NAU \& NMU by \citet{madsen_neural_2020}).  We introduce a
+  Neural Arithmetic Unit that operates on the full domain of real numbers and
+  is capable of learning arbitrary power functions called \emph{Neural Power
+  Unit} (NPU). The NPU enables not only the learning simple arithmetic
+  operations, but is also capable of learning e.g. Taylor expansions with very
+  few parameters, which makes the NPU highly explainable.
+  \footnote{Implementation of neural arithmetic units:
+  \url{https://github.com/nmheim/NeuralArithmetic.jl}}.
 \end{abstract}
@@
 
-Numbers and simple algebra are essential not only to human intelligence but also
-to the survival of many other
+Numbers and simple algebra are essential not only to human intelligence but
+also to the survival of many other
 species~\citep{dehaene_number_2011,gallistel_finding_2018}.  This can be taken
@@
 simple arithmetic, but they fail to extrapolate beyond the ranges seen during
-training~\citep{suzgun_evaluating_2018,lake_generalization_2018}.
-The inability to generalize to unseen inputs is a fundamental problem that
-hints at a lack of \emph{understanding} of the given task. The model merely
-memorizes the seen inputs and fails to abstract the true learning task.
-The failure of numerical extrapolation on simple arithmetic tasks has been shown
-by~\cite{trask_neural_2018},
-who also introduce a new class of \emph{Neural Arithmetic Units}
-that show exceptional extrapolation performance on most arithmetic tasks.
-...now explain drawbacks of NALU and NMU...
-...we introduce blah...
+training~\citep{suzgun_evaluating_2018,lake_generalization_2018}.  The
+inability to generalize to unseen inputs is a fundamental problem that hints at
+a lack of \emph{understanding} of the given task. The model merely memorizes
+the seen inputs and fails to abstract the true learning task.  The failure of
+numerical extrapolation on simple arithmetic tasks has been shown
+by~\cite{trask_neural_2018}, who also introduce a new class of \emph{Neural
+Arithmetic Units} that show good extrapolation performance on some arithmetic
+tasks.
 
-  This
-can be demonstrated by training a traditional, dense NN to approximate three
-functions
-\begin{align}
-  \label{eq:approx_tasks}
-  f(x) = e^x, && g(x) = \log(x), && h(x) = \sin(x)
-\end{align}
+The \emph{Neural Arithmetic Logic Unit} (NALU) can learn addition,
+subtraction, multiplication, and division with two severe limitations: the
+inputs that the NALU is trained with have to be positive, and should be
+significantly larger than zero, otherwise the layer will not converge to
+a correct solution.
+
+\cite{madsen_neural_2020} introduce two new arithmetic layers, the \emph{Neural
+Addition Unit} (NAU) and the \emph{Neural Multiplication Unit} (NMU).
+Stacked, they can learn addition, subtraction, and multiplication and they converge
+for any input range. However, the NMU cannot learn division.
+
+\subsection*{Our Contribution}%
+\label{sub:our_contribution}
+
+We introduce a new arithmetic layer called the \emph{Neural Power Unit} (NPU)
+which is capable of learning addition, subtraction, and arbitrary power
+functions, which includes multiplication and division.
+Our approach is inspired by the NALU, but overcomes its limitations to
+non-small positive numbers by leveraging the complex plane.
 
@@
   \centering
-  \input{../plots/exp_log_sin/gatednpux_exp.tikz}
-  \caption{}%
-  \label{fig:}
+  %\includegraphics[width=0.8\linewidth]{compare-npu-nmu-nalu-xy-xdivy.tikz}
+  \input{../plots/compare-npu-nmu-nalu-xy-xdivy.tex}
+  \caption{Comparison of different models learning the function
+  $(x,y)\rightarrow(xy,\frac{x}{y})$ with $(x,y)\in\mathcal U^2(0.1,2)$.  Each
+  plot shows the mean-squared error on a logarithmic color scale ($\hat{\bm
+  t}=\text{model}(\bm x)$).  The Dense network learns both multiplication and
+  division, but fails to extrapolate. NALU learns both tasks perfectly, but
+  completely fails if one of the inputs is negative.  The NMU successfully
+  learns multiplication, but not division. Only the NPU learns both tasks and
+  can extrapolate with an error that is less than $0.01$ in most places.}%
+  \label{fig:compare-npu-nmu-nalu-xy-xdivy}
 \end{figure}
-
-Neural Arithmetic Units aim to overcome this problem with units that are able
-to represent simple arithmetic operations exactly. By composition of these
-units it becomes possible to learn e.g. exponentials, logarithms, and power
-functions. This promises to improve on the extrapolation capabilities of NNs
-even on tasks that are beyond artificial arithmetic tasks such as learning
-multiplication, or a certain power function \todo{cite some examples}.
-\todo{mention ODEs as use case}
-\todo{mention explainability}
 
@@
 \label{sec:related_work}
+
+\subsection{Neural Arithmetic Logic Unit}%
+\label{sub:neural_arithmetic_logic_unit}
 
@@
 \end{align}
+Additionally the NALU has severe convergence problems for small inputs due to
+a non-smooth loss surface close to zero, as shown by \cite{madsen_neural_2020}.
 
-A multiplication layer that can handle negative inputs was introduced by \citet{madsen_neural_2020}.
-The \emph{Neural Multiplication Unit} (NMU) is defined by Eq.~\ref{eq:nmu} and is typically used in
-conjunction with the so-called \emph{Neural Addition Unit} (NAU) in Eq.~\ref{eq:nau}.
+\subsection{Neural Multiplication Unit}%
+\label{sub:neural_multiplication_unit}
+
+A multiplication layer that can handle small and negative inputs was introduced
+by \citet{madsen_neural_2020}.  The \emph{Neural Multiplication Unit} (NMU) is
+defined by Eq.~\ref{eq:nmu} and is typically used in conjunction with the
+so-called \emph{Neural Addition Unit} (NAU) in Eq.~\ref{eq:nau}.
 \begin{align}
@@
   \label{tab:compare_npu_npu_nalu}
-  \input{table_x*y_xdivy.tex}
+  \input{table-x*y-xdivy-pos-neg.tex}
 \end{table}
@@
 \label{sec:experimetns}
+This can be demonstrated by training a traditional, dense NN to approximate
+three functions
+\begin{align}
+  \label{eq:approx_tasks}
+  f(x) = e^x, && g(x) = \log(x), && h(x) = \sin(x)
+\end{align}
+
+Neural Arithmetic Units aim to overcome this problem with units that are able
+to represent simple arithmetic operations exactly. By composition of these
+units it becomes possible to learn e.g. exponentials, logarithms, and power
+functions. This promises to improve on the extrapolation capabilities of NNs
+even on tasks that are beyond artificial arithmetic tasks such as learning
+multiplication, or a certain power function \todo{cite some examples}.
+\todo{mention ODEs as use case}
+\todo{mention explainability}
 

### 2020-05-16 scripts/compare-npu-nmu-nalu-xy-xdivy.jl

@@ -3,14 +3,18 @@ using DrWatson
 
 using Flux
 using LinearAlgebra
+using Random
+using DataFrames
 using NeuralArithmetic
+
+Random.seed!(0)
 
 f(x::Array) = cat(reshape(x[1,:] .* x[2,:], 1, :),
                   reshape(x[1,:] ./ x[2,:], 1, :),
                   dims=1)
 
 
-train_range = "pos-neg"
+train_range = "pos"
 
 function generate_pos_neg()
     x = rand(Float32, 2, 100) .* 4 .- 2
@@ -79,7 +83,7 @@ end
 function run_dense(c::Dict)
     model = Chain(Dense(2,10,σ),Dense(10,10,σ),Dense(10,2))
     ps = params(model)
-    opt = RMSProp(c[:lr])
+    opt = ADAM(c[:lr])
     data = (generate() for _ in 1:c[:niters])
     loss(x,y) = Flux.mse(model(x),y)
     (x,y) = generate()
@@ -109,14 +113,13 @@ res, _ = produce_or_load(datadir("layercomparison"),
 nalu = res[:model]
 
 res, _ = produce_or_load(datadir("layercomparison"),
-                         Dict(:niters=>40000, :lr=>0.001),
+                         Dict(:niters=>40000, :lr=>0.01),
                          run_dense,
                          prefix="$train_range-dense", force=false)
 dense = res[:model]
 
 
 
-using DataFrames
 
 multloss(model,x::Real,y::Real) = abs(model([x,y])[1] - f([x,y])[1])
 multloss(model,x::Array,y::Array) = Flux.mse(model(x)[1,:], y[1,:])
@@ -163,37 +166,54 @@ raw"""\bottomrule
 
 display(df)
 fname = papersdir("table-x*y-xdivy-$train_range.tex")
-open(fname, "w") do file
-    @info "Writing dataframe to $fname"
-    #latex_str = repr(MIME("text/latex"), df)
-    write(file, latex_str)
-end
+# open(fname, "w") do file
+#     @info "Writing dataframe to $fname"
+#     write(file, latex_str)
+# end
 
 using Plots
+using LaTeXStrings
[…]

### 2020-05-18 papers/main.tex
fuzz fuzz

@@
 % figures
+\graphicspath{{./../plots/}}
 \usepackage{tikz}
@@
 \usepgfplotslibrary{dateplot}
-\graphicspath{{./../plots/}}
+
 \newcommand{\real}{\text{real}}
@@
 
+Including Neural Arithmetic Units in common neural networks, apart from the
+potential increase in extrapolation capabilities, has additional advantages.
+They promise to reduce the amount of parameters that are needed for a given
+task, can drastically improve the explainability of our models (more on the
+explainability of the NPU in Sec.~\ref{sec:neural_power_unit}).  Additionally,
+the field of Scientific Machine Learning, which, in part, is concerned with
+learning differential equations~\citep{rackauckas_universal_2020} could benefit
+from the inductive bias neural arithmetic.
+
 \subsection*{Our Contribution}%
@@
 non-small positive numbers by leveraging the complex plane.
-
-\begin{figure}
-  \centering
-  %\includegraphics[width=0.8\linewidth]{compare-npu-nmu-nalu-xy-xdivy.tikz}
-  \input{../plots/compare-npu-nmu-nalu-xy-xdivy.tex}
-  \caption{Comparison of different models learning the function
-  $(x,y)\rightarrow(xy,\frac{x}{y})$ with $(x,y)\in\mathcal U^2(0.1,2)$.  Each
-  plot shows the mean-squared error on a logarithmic color scale ($\hat{\bm
-  t}=\text{model}(\bm x)$).  The Dense network learns both multiplication and
-  division, but fails to extrapolate. NALU learns both tasks perfectly, but
-  completely fails if one of the inputs is negative.  The NMU successfully
-  learns multiplication, but not division. Only the NPU learns both tasks and
-  can extrapolate with an error that is less than $0.01$ in most places.}%
-  \label{fig:compare-npu-nmu-nalu-xy-xdivy}
-\end{figure}
 
@@
 
+\todo{should this be here already?}
+With the simple exemplary task of learning a function $f:\mathbb R^2 \rightarrow \mathbb R^2$
+\begin{equation}
+  \label{eq:xx_xdivy}
+  f(\bm x) = f(x,y) = [xy,x/y] = \bm t
+\end{equation}
+we can demonstrate the strengths and weaknesses of the NALU.  The NALU only
+learns successfully if it is trained on positive numbers, so we train with
+samples from $\bm x \in \mathcal U^2(0.1,2)$ and plot the error $\epsilon =
+|\bm t - \hat{\bm t}|^2$ in Fig.~\ref{fig:compare_npu_nmu_nalu_xy_xdivy}.
+
 \subsection{Neural Multiplication Unit}%
@@
 The combination of NAU and NMU can thus learn $\{+,-,\times\}$, but no division.
+This is shown in Fig.~\ref{fig:compare_npu_nmu_nalu_xy_xdivy} as well. The NMU
+can perfectly represent the multiplication of the two inputs, but fails at
+learning division.
 
@@
 packages: \cite{rackauckas_differentialequationsjl_2017} + (Flux.jl)}
-\todo{add sqrt and positive range to table~\ref{tab:compare_npu_npu_nalu}?}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\linewidth]{compare-npu-nmu-nalu-xy-xdivy.png}
+  \caption{Comparison of different models learning the function
+  $(x,y)\rightarrow(xy,x/y)$ with $(x,y)\in\mathcal U^2(0.1,2)$.  Each
+  plot shows the mean-squared error on a logarithmic color scale ($\hat{\bm
+  t}=\text{model}(\bm x)$).  The Dense network learns both multiplication and
+  division, but fails to extrapolate. NALU learns both tasks perfectly, but
+  completely fails if one of the inputs is negative.  The NMU successfully
+  learns multiplication, but not division. Only the NPU learns both tasks and
+  can extrapolate with an error that is less than $0.01$ in most places.}%
+  \label{fig:compare_npu_nmu_nalu_xy_xdivy}
+\end{figure}
+\todo{add in depth experiment desc. of fig.~\ref{fig:compare_npu_nmu_nalu_xy_xdivy} in appendix}
+\todo{add sqrt to table~\ref{tab:compare_npu_npu_nalu}?}
 \begin{table}
@@
   \label{tab:compare_npu_npu_nalu}
-  \input{table-x*y-xdivy-pos-neg.tex}
+  \input{table-x*y-xdivy-pos.tex}
 \end{table}
@@
 \label{sec:neural_power_unit}
+
+Eq.~\ref{eq:nalu_mult} enables the NALU to learn multiplication. If the weight
+matrix $\bm W$ would not be restricted to values in the range $(-1,1)$ it could
+in principle learn arbitrary power functions, because
+\begin{align}
+  z = \exp(w\log x) = x^w \text{ for } x>0.
+\end{align}
+However, this would complicate the convergence issues of the NALU even more.
+We therefore suggest to leverage the power of the complex plane, by using the
+complex logarithm and by promoting $w$ to a complex number.  This will enable
+us not only to lift the positivity constraint on $x$, but also provides and
+additional dimension that helps to avoid regions with an uninformative gradient
+signal\todo{rephrase this. do we have an educating example where it is obvious
+that complex plane helps? the stuff in fig.1 does not work as well with
+non-complex NPU, but I have not idea how to plot that}.
+Introducing a complex weight matrix somewhere in a larger network would mean that
+the gradients in other layers would potentially become complex as well, which
+would result in converting the whole network to complex numbers.
+This seems like a high price to pay, but fortunately there is a way around this.
+We can output only the real part of the result $z$, but still maintain a complex $w$.
+
+\newcommand{\wre}{w_{\text{re}}}
+\newcommand{\wim}{w_{\text{im}}}
+\begin{align}
+  \real(z) &= \real(\exp(w\log x)) \\
+    &= \real(\exp((\wre + i\wim) (\log r + ik\pi))) \\
+    &= \exp(\wre\log r - \wim k\pi) \real(\exp(i\wim\log r + ik\pi\wre)) \\
+    &= \exp(\wre\log r - \wim k\pi) \cos(\wim\log r + k\pi\wre)
+\end{align}
+\todo{explicitly compute gradients?}
 
@@
 multiplication, or a certain power function \todo{cite some examples}.
-\todo{mention ODEs as use case}
-\todo{mention explainability}
 

### 2020-05-18 scripts/compare-npu-nmu-nalu-xy-xdivy.jl

@@ -94,7 +94,7 @@ end
 
 
 res, _ = produce_or_load(datadir("layercomparison"),
-                         Dict(:niters=>40000, :βl1=>0.1, :lr=>0.002),
+                         Dict(:niters=>50000, :βl1=>0.1, :lr=>0.0001),
                          run_npu,
                          prefix="$train_range-gatednpux",
                          force=false, digits=6)
@@ -113,7 +113,7 @@ res, _ = produce_or_load(datadir("layercomparison"),
 nalu = res[:model]
 
 res, _ = produce_or_load(datadir("layercomparison"),
-                         Dict(:niters=>40000, :lr=>0.01),
+                         Dict(:niters=>50000, :lr=>0.001),
                          run_dense,
                          prefix="$train_range-dense", force=false)
 dense = res[:model]
@@ -145,7 +145,7 @@ push!(df, ("Dense", multloss(dense,x,y), divloss(dense,x,y),
            multloss(dense,xt,yt), divloss(dense,xt,yt)))
 
 for col in ["mult_trn", "div_trn", "mult_val", "div_val"]
-    df[!,col] = round.(df[!,col], digits=4)
+    df[!,col] = round.(df[!,col], digits=6)
 end
 
 latex_str = (
@@ -166,16 +166,16 @@ raw"""\bottomrule
 
 display(df)
 fname = papersdir("table-x*y-xdivy-$train_range.tex")
-# open(fname, "w") do file
-#     @info "Writing dataframe to $fname"
-#     write(file, latex_str)
-# end
+open(fname, "w") do file
+    @info "Writing dataframe to $fname"
+    write(file, latex_str)
+end
 
 using Plots
 using LaTeXStrings
 include(srcdir("turbocmap.jl"))
-pgfplotsx()
-#pyplot()
+#pgfplotsx()
+pyplot()
 
 x = Float32.(collect(-4:0.1:4))
 y = Float32.(collect(-4:0.1:4))
@@ -192,27 +192,34 @@ function inftoextreme(z)
 end
 rminvalid = nantozero ∘ inftoextreme
 
+@info "Plotting NPU..."
 func(x,y) = rminvalid(log10(multloss(npu,x,y)))
[…]

### 2020-05-18 scripts/complex-log-grad.jl

@@ -1,0 +1,10 @@
+using Flux
+using Plots
+pyplot()
+
+
+f(x, w) = exp(w*log(x))
+
+loss(x,w) = abs2(f(x,w) - x^2)
+
+Flux.gradient(loss, 3, 1)

### 2020-05-20 papers/main.tex
paper/taylor updates

@@
 
-\newcommand{\real}{\text{real}}
+\newcommand{\real}{\text{Re}}
+\newcommand{\imag}{\text{Im}}
+\newcommand{\wre}{w_{r}}
+\newcommand{\wim}{w_{i}}
+\newcommand{\Wre}{\bm W_{r}}
+\newcommand{\Wim}{\bm W_{i}}
 
@@
 \todo{add in depth experiment desc. of fig.~\ref{fig:compare_npu_nmu_nalu_xy_xdivy} in appendix}
-\todo{add sqrt to table~\ref{tab:compare_npu_npu_nalu}?}
-\begin{table}
-  \centering
-  \caption{Comparison of different $2\times2$ layers on the task
-  $(x,y)\rightarrow(xy,\frac{x}{y})$.  $(x,y) \in \mathcal U^2(-2,2)$.}
-  \label{tab:compare_npu_npu_nalu}
-  \input{table-x*y-xdivy-pos.tex}
-\end{table}
 
-\section{Neural Power Unit}%
+\section{Neural Power Units}%
 \label{sec:neural_power_unit}
@@
 \end{align}
+
 However, this would complicate the convergence issues of the NALU even more.
@@
 that complex plane helps? the stuff in fig.1 does not work as well with
-non-complex NPU, but I have not idea how to plot that}.
-Introducing a complex weight matrix somewhere in a larger network would mean that
-the gradients in other layers would potentially become complex as well, which
-would result in converting the whole network to complex numbers.
-This seems like a high price to pay, but fortunately there is a way around this.
-We can output only the real part of the result $z$, but still maintain a complex $w$.
-
-\newcommand{\wre}{w_{\text{re}}}
-\newcommand{\wim}{w_{\text{im}}}
+non-complex NPU, but I have not idea how to plot that}.  Introducing a complex
+weight matrix somewhere in a larger network would mean that the gradients in
+other layers would potentially become complex as well, which would result in
+converting the whole network to complex numbers.  This seems like a high price
+to pay, but fortunately there is a way around this.  We can output only the
+real part of the result $\real(z)$, but still maintain a complex $w$ by
+treating it as a sum of real and imaginary part $w=\wre+i\wim$. We are thus
+interested in
 \begin{align}
-  \real(z) &= \real(\exp(w\log x)) \\
-    &= \real(\exp((\wre + i\wim) (\log r + ik\pi))) \\
-    &= \exp(\wre\log r - \wim k\pi) \real(\exp(i\wim\log r + ik\pi\wre)) \\
-    &= \exp(\wre\log r - \wim k\pi) \cos(\wim\log r + k\pi\wre)
+  \label{eq:exp_w_log_complex}
+  \real(z) &= \real(\exp(w\log x)),
 \end{align}
+with a real input $x$. The complex logarithm is defined as $\log z=\log r +
+i\theta$, which, for real inputs $x$, can be simplified to $\log z = \log r +
+ik\pi$, where $k\in \{0,1\}$. With that Eq.~\ref{eq:exp_w_log_complex} can be
+rewritten to
+\begin{align}
+  \real(z) &= \real(\exp((\wre + i\wim) (\log r + ik\pi))) \\
+    &= \exp(\wre\log r - \wim k\pi) \cos(\wim\log r + k\pi\wre),
+\end{align}
+where we used Euler's formula\footnote{Euler's formula states that for any real
+number $x$: $re^{ix} = \cos x + i\sin x$}.
 \todo{explicitly compute gradients?}
 
-Our \emph{Neural Power Unit} (NPU) can learn arbitrary power functions (which
-includes division) while still being able to correctly deal with negative
-inputs.  The NPU layer is defined by
+\subsection{Neural Power Unit (NPU)}%
+\label{sub:neural_power_unit_npu_}
+
+\begin{figure}
+  \centering
+  \resizebox{.3\textwidth}{!}{\input{../plots/exp_log_sin/log_comp.tikz.tex}}
+  \resizebox{.3\textwidth}{!}{\input{../plots/exp_log_sin/exp_comp.tikz.tex}}
+  \resizebox{.3\textwidth}{!}{\input{../plots/exp_log_sin/sin_comp.tikz.tex}}
+  \caption{Function learning comparison of different layers.}%
+  \label{fig:sin_comp}
+\end{figure}
+
+The \emph{Neural Power Unit} (NPU) with two weight matrices $\Wre$ and $\Wim$
+then reads
 \begin{align}
-  k_i &= \begin{cases}
+  \bm r = |\bm x|,
+  \hspace{1cm}
+  & k_i = \begin{cases}
      0  & x_i \leq 0 \\
     \pi & x_i > 0
-  \end{cases} \\
-  \bm r &= |\bm x| \\
-  \bm m &= \exp(\bm M \log(\bm r)) \odot \cos(\bm M \bm k)
+  \end{cases}
+\end{align}
+\begin{align}
+  \bm z &= \exp(\Wre \log\bm r - \Wim\bm k) \odot \cos(\Wim\log \bm r + \Wre\bm k)
 \end{align}
 where $\bm k$ is a vector that is zero where $\bm x$ is positive and $\pi$
-where it is negative, $\bm r$ is the elementwise absolute value, and $\bm M$
-the multiplication matrix that we want to learn.
+where it is negative, $\bm r$ is the element-wise absolute value.
+In the final network we are only interested in real powers, so we recommend to
+strongly regularize the imaginary part of the weights $\Wim$.
 
-The NPU is inspired by the multiplication part of the NALU
-Eq.~\ref{eq:nalu_mult}, extended to negative inputs by taking advantage of the
-complex logarithm. In general, for any complex number $z$\footnote{Note that
-complex numbers can be represented in the polar, complex plane where
-$z=re^{i\varphi}$ with $r>0$ and $\varphi \in (0,2\pi)$.}
-\begin{align}
-  \log(z) = \log\left(r\cdot e^{i\varphi}\right)
-     = \log(r) + i\varphi.
-\end{align}
-However, as $z$ is assumed to be real, we can simplify as follows:
-\begin{align}
-  \log(z) = \log(r) + ik\pi,
-\end{align}
-where $k \in [0,1]$ is zero for positive inputs and one for negative inputs $z$.
+\subsection{Gated NPU}%
+\label{sub:gated_npu}
+As pointed out by \cite{madsen_neural_2020}, the loss surface of the NALU, and
+thus also the NPU, is not always smooth. For some input and weight combinations
+it can happen that the loss close to zero becomes very large as shown in
+Fig.~\ref{fig:task_loss_npu_nmu}.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\linewidth]{task_loss_npu_nmu.pdf}
+  \caption{asdf}%
+  \label{fig:task_loss_npu_nmu}
+\end{figure}
+However, most applications are dealing with batches of data which average out
+these cases, as shown in Fig.~\ref{fig:task_loss_npu_nmu_average} for a batch
+size of 32.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\linewidth]{task_loss_npu_nmu_average.pdf}
+  \caption{asdfadsf}%
+  \label{fig:task_loss_npu_nmu_average}
+\end{figure}
 
-\begin{align}
-  \bm m &= \exp(\bm M \log(\bm x)) \\
-    &= \exp(\bm M ( \log(\bm r) + i\pi\bm k ))
-\end{align}
-
-\begin{align}
-  \bm m_{\text{re}} &= \real(\exp(\bm M \log \bm r + i\pi\bm M\bm k)) \\
-    &= \real(\exp(\bm M \log \bm r) \odot (\cos(\pi \bm M \bm k) + i \sin(\pi \bm M \bm k))) \\
-    &= \exp(\bm M \log \bm r) \odot \cos(\pi \bm M \bm k)
-\end{align}
+In practice we encountered difficulties of obtaining sparse solutions with the
+NPU. If the inputs to an NPU unit are small, the gradient becomes practically
+zero, as we can see in Fig.~\ref{fig:id_loss_npu_nmu}
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\linewidth]{id_loss_npu_nmu.pdf}
+  \caption{learning identity with small inputs}%
+  \label{fig:id_loss_npu_nmu}
+\end{figure}
 
@@
 
+\appendix
+\section*{Appendix A}%
+\label{sec:appendix_a}
+
+\todo{add sqrt to table~\ref{tab:compare_npu_npu_nalu}?}
+\begin{table}[h]
+  \centering
+  \caption{Comparison of different $2\times2$ layers on the task
+  $(x,y)\rightarrow(xy,\frac{x}{y})$.  $(x,y) \in \mathcal U^2(-2,2)$.}
+  \label{tab:compare_npu_npu_nalu}
+  \input{table-xy-xdivy-pos.tex}
+\end{table}
+
 \bibliographystyle{plainnat}

### 2020-05-20 scripts/loss-plots/div-loss.jl

@@ -2,7 +2,6 @@ using DrWatson
 @quickactivate "NIPS_2020_NMUX"
 
 using Plots
-using Zygote
 using Distributions
 using LaTeXStrings
 #pgfplotsx()

### 2020-05-20 scripts/taylor/dense_exp_log_sin.jl

@@ -10,7 +10,7 @@ pyplot()
 
 
 function run(c::Dict, f::Function)
-    @unpack dim, lowlim, uplim, niter = c
+    @unpack dim, lr, lowlim, uplim, niter = c
     x = Float32.(reshape(lowlim:0.1:uplim, 1, :))
     y = f.(x)
 
@@ -23,8 +23,10 @@ function run(c::Dict, f::Function)
     cb = [Flux.throttle(()->(
                xt = Float32.(reshape((lowlim*2):0.5:(uplim*2),1,:));
                yt = f.(xt);
-               p1 = plot(vec(xt), vec(yt));
-               plot!(p1, vec(xt), vec(model(xt)));
+               p1 = plot(vec(xt), vec(yt), yscale=:log10);
+               plot!(p1, vec(xt), abs.(vec(model(xt))));
+               # p1 = plot(vec(xt), vec(yt));
+               # plot!(p1, vec(xt), vec(model(xt)));
                display(p1);
                @info loss(x,y) loss(xt,yt)
               ), 1)
@@ -34,19 +36,19 @@ function run(c::Dict, f::Function)
 end
 
 expres, _ = produce_or_load(datadir("exp_log_sin"),
-                         Dict(:lowlim=>-5, :uplim=>5, :dim=>10, :niter=>10000),
+                         Dict(:lowlim=>-5, :uplim=>5, :dim=>10, :niter=>100000, :lr=>1e-3),
                          c -> run(c, exp),
                          prefix="dense_exp",
-                         force=false)
+                         force=false, digits=6)
 
 logres, _ = produce_or_load(datadir("exp_log_sin"),
-                         Dict(:lowlim=>0.1, :uplim=>2, :dim=>10, :niter=>10000),
+                         Dict(:lowlim=>0.1, :uplim=>2, :dim=>10, :niter=>50000, :lr=>1e-3),
                          c -> run(c, log),
                          prefix="dense_log",
                          force=false)
 
 sinres, _ = produce_or_load(datadir("exp_log_sin"),
-                         Dict(:lowlim=>-5, :uplim=>5, :dim=>10, :niter=>50000),
+                         Dict(:lowlim=>-5, :uplim=>5, :dim=>4, :niter=>50000, :lr=>1e-3),
                          c -> run(c, sin),
                          prefix="dense_sin",
                          force=false)

### 2020-05-20 scripts/taylor/exp_log_sin.jl

@@ -1,0 +1,76 @@
+using DrWatson
+@quickactivate "NIPS_2020_NPUX"
+
+using Flux
+using Parameters
+using NeuralArithmetic
+using ValueHistories
+using Plots
+
+expconfig = Dict(:lowlim=>-5, :uplim=>5, :dim=>10, :niter=>100000, :lr=>1e-3, :βl1=>0.1)
+logconfig = Dict(:lowlim=>0.1, :uplim=>2, :dim=>10, :niter=>50000, :lr=>1e-3, :βl1=>0.01)
+sinconfig = Dict(:lowlim=>-5, :uplim=>5, :dim=>4, :niter=>50000, :lr=>1e-3, :βl1=>0.1)
+
+function loadmodels(prefixes::Vector, config::Dict, problem::String)
+    map(prefixes) do prefix
+        igs = occursin("npux", prefix) ? [] : [:βl1]
+        name = savename(config, ignores=igs, digits=9)
+        res = load(datadir("exp_log_sin", "$(prefix)_$(problem)_$(name).bson"))
+        res[:model]
+    end
+end
+
+expmodels = loadmodels(["npu","npux","gatednpux","dense","nalu"], expconfig, "exp")
+logmodels = loadmodels(["npu","npux","gatednpux","dense","nalu"], logconfig, "log")
+sinmodels = loadmodels(["npu","npux","gatednpux","dense","nalu"], sinconfig, "sin")
+
+name(l) = summary(l)
+name(l::GatedNPUX) = "GatedNPUX"
+name(l::Dense) = "Dense"
+name(m::Chain) = name(m[1])
+
+pgfplotsx()
+linewidth = 1.4
+linestyles = Iterators.cycle([:dash, :dashdot, :solid, :dot])
+
+@unpack lowlim, uplim, niter = expconfig
+xt = Float32.(collect((lowlim*2):0.5:(uplim*2)))
+yt = exp.(xt)
+
+p1 = plot(xt, yt, label="Exp", lw=linewidth, ls=:dash, yscale=:log10, ylim=[1e-4,1e4])
+for (m, ls) in zip(expmodels, linestyles)
+    plot!(p1, xt, abs.(vec(m(reshape(xt,1,:)))),
+          lw=linewidth, label=name(m), size=(300,200), legend=false, ls=ls)
+end
+plot!(p1, [lowlim, lowlim], [1e-5, 1e5], c=:gray, label=false)
[…]

### 2020-05-20 scripts/taylor/gatednpu_exp_log_sin.jl

@@ -7,18 +7,7 @@ using LinearAlgebra
 using NeuralArithmetic
 using ValueHistories
 using Plots
-pyplot()
-
-_sine_taylor(x,n) = (-1)^n * x^(2n+1) / factorial(2n+1)
-_sum_taylor(f,x,n;n0=0) = sum(map(i->f(x,i),n0:n))
-sine_taylor(x,n) = _sum_taylor(_sine_taylor,x,n)
-
-_exp_taylor(x,n) = x^n/factorial(n)
-exp_taylor(x,n) = _sum_taylor(_exp_taylor,x,n)
-
-_log_taylor(x,n) = (-1)^(n+1) * x^n/n
-log_taylor(x,n) = _sum_taylor(_log_taylor,x,n,n0=1)
-
+unicodeplots()
 
 
 function run(c::Dict, f::Function)
@@ -32,14 +21,14 @@ function run(c::Dict, f::Function)
     h = MVHistory()
     data = Iterators.repeated((x,y), niter)
     opt = ADAM(lr)
-    model = Chain(NALU(1,dim), NALU(dim,1))
+    model = Chain(GatedNPU(1,dim), NAU(dim,1))
     ps = params(model)
     mse(x,y) = sum(abs2, model(x) .- y)
     loss(x,y) = mse(x,y)
 
     cb = [Flux.throttle(()->(
-               #p1 = plot(vec(xt), vec(yt), yscale=:log10);
-               #plot!(p1, vec(xt), abs.(vec(model(xt))));
+               # p1 = plot(vec(xt), vec(yt), yscale=:log10);
+               # plot!(p1, vec(xt), abs.(vec(model(xt))));
                p1 = plot(vec(xt), vec(yt));
                plot!(p1, vec(xt), vec(model(xt)));
                display(p1);
@@ -52,22 +41,22 @@ function run(c::Dict, f::Function)
     return Dict(:model=>model, :config=>c, :history=>h)
 end
 
-expres, expfile = produce_or_load(datadir("exp_log_sin"),
-                         Dict(:lowlim=>-5, :uplim=>5, :dim=>10, :niter=>100000, :lr=>1e-3),
+expres, _ = produce_or_load(datadir("exp_log_sin"),
+                         Dict(:lowlim=>-5, :uplim=>5, :dim=>10, :niter=>100000, :lr=>2e-4),
                          c -> run(c, exp),
-                         prefix="nalu_exp",
[…]

### 2020-05-20 scripts/taylor/gatednpux_exp_log_sin.jl

@@ -5,6 +5,7 @@ using Flux
 using Parameters
 using LinearAlgebra
 using NeuralArithmetic
+using ValueHistories
 using Plots
 pyplot()
 
@@ -14,45 +15,51 @@ function run(c::Dict, f::Function)
     @unpack dim, lowlim, uplim, niter, lr, βl1 = c
     x = Float32.(reshape(lowlim:0.1:uplim, 1, :))
     y = f.(x)
+    xt = Float32.(reshape((lowlim*2):0.2:(uplim*1.5),1,:))
+    yt = f.(xt)
 
+    h = MVHistory()
     data = Iterators.repeated((x,y), niter)
     opt = ADAM(lr)
     model = Chain(GatedNPUX(1,dim), NAU(dim,1))
     ps = params(model)
-    loss(x,y) = sum(abs2, model(x) .- y) + βl1*norm(model[1].Im)
+    mse(x,y) = sum(abs2, model(x) .- y)
+    loss(x,y) = mse(x,y) + βl1*norm(model[1].Im)
 
     cb = [Flux.throttle(()->(
-               xt = Float32.(reshape((lowlim*2):0.5:(uplim*1.5),1,:));
-               yt = f.(xt);
-               p1 = plot(vec(xt), vec(yt));
-               plot!(p1, vec(xt), vec(model(xt)));
+               p1 = plot(vec(xt), vec(yt), yscale=:log10);
+               plot!(p1, vec(xt), abs.(vec(model(xt))));
+               # p1 = plot(vec(xt), vec(yt));
+               # plot!(p1, vec(xt), vec(model(xt)));
                display(p1);
                @info loss(x,y) loss(xt,yt)
-              ), 1)
+              ), 1),
+          Flux.throttle(() -> (push!(h, :μz, Flux.destructure(model)[1]);
+                               push!(h, :mse, mse(xt,yt))), 0.1)
          ]
     Flux.train!(loss, ps, data, opt, cb=cb)
-    return Dict(:model=>model, :config=>c)
+    return Dict(:model=>model, :config=>c, :history=>h)
 end
 
 expres, _ = produce_or_load(datadir("exp_log_sin"),
-                         Dict(:lowlim=>-5, :uplim=>5, :dim=>10, :niter=>50000, :lr=>1e-3),
[…]

### 2020-05-20 scripts/taylor/nmu_exp_log_sin.jl

@@ -5,44 +5,69 @@ using Flux
 using Parameters
 using LinearAlgebra
 using NeuralArithmetic
+using ValueHistories
 using Plots
-pyplot()
+unicodeplots()
+
+_sine_taylor(x,n) = (-1)^n * x^(2n+1) / factorial(2n+1)
+_sum_taylor(f,x,n;n0=0) = sum(map(i->f(x,i),n0:n))
+sine_taylor(x,n) = _sum_taylor(_sine_taylor,x,n)
+
+_exp_taylor(x,n) = x^n/factorial(n)
+exp_taylor(x,n) = _sum_taylor(_exp_taylor,x,n)
+
+_log_taylor(x,n) = (-1)^(n+1) * x^n/n
+log_taylor(x,n) = _sum_taylor(_log_taylor,x,n,n0=1)
+
 
 
 function run(c::Dict, f::Function)
-    @unpack dim, lowlim, uplim, niter = c
+    #@unpack dim, lowlim, uplim, niter, lr = c
+    @unpack dim, lowlim, uplim, niter, lr = c
     x = Float32.(reshape(lowlim:0.1:uplim, 1, :))
     y = f.(x)
+    xt = Float32.(reshape((lowlim*2):0.2:(uplim*1.5),1,:))
+    yt = f.(xt)
 
+    h = MVHistory()
     data = Iterators.repeated((x,y), niter)
-    opt = ADAM(1e-4)
+    opt = ADAM(lr)
     model = Chain(NMU(1,dim), NAU(dim,1))
     ps = params(model)
-    loss(x,y) = sum(abs2, model(x) .- y) #+ βl1*norm(model[1].Im)
+    mse(x,y) = sum(abs2, model(x) .- y)
+    loss(x,y) = mse(x,y)
 
     cb = [Flux.throttle(()->(
-               xt = Float32.(reshape((lowlim*2):0.5:(uplim*1.5),1,:));
-               yt = f.(xt);
-               p1 = plot(vec(xt), vec(yt), yscale=:log10);
-               plot!(p1, vec(xt), abs.(vec(model(xt))));
-               #display(p1);
+               # p1 = plot(vec(xt), vec(yt), yscale=:log10);
+               # plot!(p1, vec(xt), abs.(vec(model(xt))));
+               p1 = plot(vec(xt), vec(yt));
+               plot!(p1, vec(xt), vec(model(xt)));
+               display(p1);
                @info loss(x,y) loss(xt,yt)
-              ), 1)
+              ), 1),
[…]

### 2020-05-20 scripts/taylor/npu_exp_log_sin.jl

@@ -32,16 +32,16 @@ function run(c::Dict, f::Function)
     h = MVHistory()
     data = Iterators.repeated((x,y), niter)
     opt = ADAM(lr)
-    model = Chain(NALU(1,dim), NALU(dim,1))
+    model = Chain(NPU(1,dim), NAU(dim,1))
     ps = params(model)
     mse(x,y) = sum(abs2, model(x) .- y)
     loss(x,y) = mse(x,y)
 
     cb = [Flux.throttle(()->(
-               #p1 = plot(vec(xt), vec(yt), yscale=:log10);
-               #plot!(p1, vec(xt), abs.(vec(model(xt))));
-               p1 = plot(vec(xt), vec(yt));
-               plot!(p1, vec(xt), vec(model(xt)));
+               p1 = plot(vec(xt), vec(yt), yscale=:log10);
+               plot!(p1, vec(xt), abs.(vec(model(xt))));
+               # p1 = plot(vec(xt), vec(yt));
+               # plot!(p1, vec(xt), vec(model(xt)));
                display(p1);
                @info loss(x,y) loss(xt,yt)
               ), 1),
@@ -55,19 +55,19 @@ end
 expres, expfile = produce_or_load(datadir("exp_log_sin"),
                          Dict(:lowlim=>-5, :uplim=>5, :dim=>10, :niter=>100000, :lr=>1e-3),
                          c -> run(c, exp),
-                         prefix="nalu_exp",
-                         force=false, digits=8)
+                         prefix="npu_exp",
+                         force=true, digits=8)
 
 logres, logfile = produce_or_load(datadir("exp_log_sin"),
                          Dict(:lowlim=>0.1, :uplim=>2, :dim=>10, :niter=>50000, :lr=>1e-3),
                          c -> run(c, log),
-                         prefix="nalu_log",
+                         prefix="npu_log",
                          force=false)
 
 sinres, sinfile = produce_or_load(datadir("exp_log_sin"),
                          Dict(:lowlim=>-5, :uplim=>5, :dim=>4, :niter=>50000, :lr=>1e-3),
                          c -> run(c, sin),
[…]

### 2020-05-20 scripts/taylor/npux_exp_log_sin.jl

@@ -9,21 +9,10 @@ using ValueHistories
 using Plots
 pyplot()
 
-_sine_taylor(x,n) = (-1)^n * x^(2n+1) / factorial(2n+1)
-_sum_taylor(f,x,n;n0=0) = sum(map(i->f(x,i),n0:n))
-sine_taylor(x,n) = _sum_taylor(_sine_taylor,x,n)
-
-_exp_taylor(x,n) = x^n/factorial(n)
-exp_taylor(x,n) = _sum_taylor(_exp_taylor,x,n)
-
-_log_taylor(x,n) = (-1)^(n+1) * x^n/n
-log_taylor(x,n) = _sum_taylor(_log_taylor,x,n,n0=1)
-
-
 
 function run(c::Dict, f::Function)
     #@unpack dim, lowlim, uplim, niter, lr = c
-    @unpack dim, lowlim, uplim, niter, lr = c
+    @unpack dim, lowlim, uplim, niter, lr, βl1 = c
     x = Float32.(reshape(lowlim:0.1:uplim, 1, :))
     y = f.(x)
     xt = Float32.(reshape((lowlim*2):0.2:(uplim*1.5),1,:))
@@ -32,16 +21,16 @@ function run(c::Dict, f::Function)
     h = MVHistory()
     data = Iterators.repeated((x,y), niter)
     opt = ADAM(lr)
-    model = Chain(NALU(1,dim), NALU(dim,1))
+    model = Chain(NPUX(1,dim), NAU(dim,1))
     ps = params(model)
     mse(x,y) = sum(abs2, model(x) .- y)
-    loss(x,y) = mse(x,y)
+    loss(x,y) = mse(x,y) + βl1*norm(model[1].Im)
 
     cb = [Flux.throttle(()->(
-               #p1 = plot(vec(xt), vec(yt), yscale=:log10);
-               #plot!(p1, vec(xt), abs.(vec(model(xt))));
-               p1 = plot(vec(xt), vec(yt));
-               plot!(p1, vec(xt), vec(model(xt)));
+               p1 = plot(vec(xt), vec(yt), yscale=:log10);
+               plot!(p1, vec(xt), abs.(vec(model(xt))));
+               # p1 = plot(vec(xt), vec(yt));
+               # plot!(p1, vec(xt), vec(model(xt)));
                display(p1);
                @info loss(x,y) loss(xt,yt)
               ), 1),
@@ -52,25 +41,25 @@ function run(c::Dict, f::Function)
[…]

### 2020-05-20 experiments/gated-npu-ode.jl
eval updates

@@ -74,7 +74,7 @@ function predict_n_ode(p)
   n_ode(u0,p)
 end
 
-reg_loss(p) = 1e-4*norm(p,1)
+reg_loss(p) = 1e-5*norm(p,1)
 mse_loss(pred) = sum(abs2, ode_data .- pred)
 img_loss(p) = 1e-3*norm(p[hdim*2+1:hdim*4],1)
 
@@ -87,15 +87,15 @@ end
 function plot_chain(p)
     npuw = p[1:(hdim*4)]
     nauw = p[(hdim*4+1+2):end]
-    UnicodePlots.heatmap(reshape(vcat(npuw,nauw), hdim, 6))
+    UnicodePlots.heatmap(reshape(vcat(npuw,nauw), hdim, 6), height=hdim)
 end
 
 
 cb = function (p,l,pred;doplot=false) #callback function to observe training
   # plot current prediction against data
   #@info l mse_loss(pred) reg_loss(p)
-  # plot_chain(p)
   if doplot
+    display(plot_chain(p))
     pl = scatter(t,ode_data[1,:],label="data")
     scatter!(pl,t,ode_data[2,:],label="data")
     plot!(pl,t,pred[1,:],label="prediction")
@@ -109,14 +109,14 @@ end
 # Display the ODE with the initial parameter values.
 cb(n_ode.p,loss_n_ode(n_ode.p)...)
 
-res1 = DiffEqFlux.sciml_train(loss_n_ode, n_ode.p, RMSProp(0.005), cb = cb, maxiters = 3000)
+res1 = DiffEqFlux.sciml_train(loss_n_ode, n_ode.p, RMSProp(0.005), cb = cb, maxiters = 5000)
 cb(res1.minimizer,loss_n_ode(res1.minimizer)...;doplot=true)
 
 # res2 = DiffEqFlux.sciml_train(loss_n_ode, res1.minimizer, RMSProp(0.0005), cb = cb, maxiters = 2000)
 # cb(res2.minimizer,loss_n_ode(res2.minimizer)...;doplot=true)
 
 using Optim
-res2 = DiffEqFlux.sciml_train(loss_n_ode, res1.minimizer, LBFGS(), cb = cb, maxiters=300)
+res2 = DiffEqFlux.sciml_train(loss_n_ode, res1.minimizer, LBFGS(), cb = cb)
 cb(res2.minimizer,loss_n_ode(res2.minimizer)...;doplot=true)
 
 # result is res2 as an Optim.jl object

### 2020-05-20 scripts/arithmetic/configs.jl

@@ -3,7 +3,7 @@ using Parameters
 @with_kw struct AddL1SearchConfig
     batch::Int      = 128
     niters::Int     = 1e5
-    lr::Real        = 5e-3
+    lr::Real        = 1e-2
 
     βstart::Real    = 1f-5
     βend::Real      = 1f-2
@@ -49,10 +49,10 @@ end
 @with_kw struct DivL1SearchConfig
     batch::Int      = 128
     niters::Int     = 1e5
-    lr::Real        = 2e-3
+    lr::Real        = 5e-3
 
-    βstart::Real    = 1f-7
-    βend::Real      = 1f-6
+    βstart::Real    = 1f-9
+    βend::Real      = 1f-7
     βgrowth::Real   = 10f0
     βstep::Int      = 10000
 
@@ -72,10 +72,10 @@ end
 @with_kw struct SqrtL1SearchConfig
     batch::Int      = 128
     niters::Int     = 1e5
-    lr::Real        = 1e-2
+    lr::Real        = 5e-3
 
-    βstart::Real    = 1f-5
-    βend::Real      = 1f-2
+    βstart::Real    = 1f-7
+    βend::Real      = 1f-5
     βgrowth::Real   = 10f0
     βstep::Int      = 10000
 

### 2020-05-20 scripts/arithmetic/div_npu_l1.jl

@@ -21,10 +21,10 @@ include(srcdir("arithmetic_models.jl"))
 @with_kw struct DivL1Config
     batch::Int      = 128
     niters::Int     = 1e5
-    lr::Real        = 2e-3
+    lr::Real        = 5e-3
 
-    βstart::Real    = 1f-7
-    βend::Real      = 1f-6
+    βstart::Real    = 1f-9
+    βend::Real      = 1f-7
     βgrowth::Real   = 10f0
     βstep::Int      = 10000
 

### 2020-05-20 scripts/arithmetic/div_npu_l1_search.jl

@@ -8,13 +8,12 @@ global_logger(TerminalLogger(right_justify=80))
 
 using Parameters
 using UnicodePlots
+using ValueHistories
 
 using Flux
 using LinearAlgebra
 using NeuralArithmetic
 
-include(srcdir("history.jl"))
-include(srcdir("mvhistory.jl"))
 include(srcdir("schedules.jl"))
 include(srcdir("arithmetic_dataset.jl"))
 include(srcdir("arithmetic_models.jl"))
@@ -56,7 +55,7 @@ end
 
 
 # set up dict which will be permuted to yield all config combinations
-config_dicts = Dict(:βend => 10f0 .^ (-7f0:-5f0),
+config_dicts = Dict(:βend => 10f0 .^ (-8f0:-7f0),
                     :init => [("rand","rand"),
                               ("glorotuniform", "glorotuniform")],
                     :model => ["gatednpu", "gatednpux", "nmu", "nalu"])
@@ -71,9 +70,8 @@ config_dicts = map(dict_list(config_dicts)) do config
     d
 end
 
-using Distributed
-pmap(config_dicts) do d
-    config = DivL1SearchConfig(βstart=1f-8)
+@progress name="Div Search: " for d in config_dicts
+    config = DivL1SearchConfig()
     for nr in 1:5
         d[:run] = nr
         config = reconstruct(config, d)

### 2020-05-20 scripts/arithmetic/mult_npu_l1_search.jl

@@ -69,8 +69,7 @@ config_dicts = map(dict_list(config_dicts)) do config
     d
 end
 
-using Distributed
-pmap(config_dicts) do d
+@progress name="Mult Search: " for d in config_dicts
     config = MultL1SearchConfig()
     for nr in 1:5
         d[:run] = nr

### 2020-05-20 scripts/arithmetic/results_table.jl

@@ -20,7 +20,9 @@ function aggregateruns(df::DataFrame)
          μval = mean(df.val),
          σval = std(df.val),
          fstinit = first(df.fstinit),
-         sndinit = first(df.sndinit))
+         sndinit = first(df.sndinit),
+         model = first(df.model),
+         task = first(df.task))
     end
 end
 
@@ -48,37 +50,98 @@ end
 Base.last(h::MVHistory, k::Symbol) = get(h,k)[2][end]
 
 
+function collect_all_results!(folders)
+    df = map(folders) do folder
+        _df = collect_results!(datadir(folder), white_list=[],
+                              special_list=[:trn => data -> last(data[:history], :loss)[1],
+                                            :mse => data -> last(data[:history], :loss)[2],
+                                            :reg => data -> last(data[:history], :loss)[3],
+                                            :val => data -> last(data[:history], :loss)[4],
+                                            :config => data -> data[:c],
+                                            :hash => data -> hash(delete!(struct2dict(data[:c]),:run)),
+                                            :task => data -> split(basename(folder),"_")[1],
+                                           ],
+                             )
+        expand_config!(_df)
+        return _df
+    end
+    vcat(df...)
+end
+
+function best_models_for_tasks(df::DataFrame, key::String)
+    best = combine(groupby(df,"model")) do modeldf
+        combine(groupby(modeldf, "task")) do taskdf
+            tdf = sort!(DataFrame(taskdf[1,:]), key)
+            tdf[1,:]
+        end
+    end
+
+    best = select(best, "model", "task", key)
+    tasks = unique(best, "task").task
+    models = unique(best, "model").model
+
+    result = DataFrame(Union{Float64,Missing}, length(tasks), length(models)+1)
+    rename!(result, vcat(["task"], models))
+    result[!,1] = tasks
+
+    #result.models = models
+    for m in models
+        mdf = filter(:model=>model->model==m, best)
+        for (i,t) in zip(1:length(tasks), tasks)
+            mtdf = filter(:task=>task->task==t, mdf)
+            if size(mtdf) == (1,3)
+                v = mtdf[1,key]
+                @info m,t,v
+                result[i,m] = v
+            elseif size(mtdf) == (0,3)
+                result[i,m] = missing
+            else
+                error("Expected single row no row.")
+            end
+        end
+    end
+    return result
+end
+
[…]

### 2020-05-20 scripts/arithmetic/sqrt_npu_l1.jl

@@ -21,10 +21,10 @@ include(srcdir("arithmetic_models.jl"))
 @with_kw struct SqrtL1Config
     batch::Int      = 128
     niters::Int     = 50000
-    lr::Real        = 1e-2
+    lr::Real        = 5e-3
 
-    βstart::Real    = 1f-4
-    βend::Real      = 1f-2
+    βstart::Real    = 1f-7
+    βend::Real      = 1f-5
     βgrowth::Real   = 10f0
     βstep::Int      = 10000
 
@@ -33,7 +33,7 @@ include(srcdir("arithmetic_models.jl"))
     subset::Real    = 0.5f0
     overlap::Real   = 0.25f0
 
-    inlen::Int      = 20
+    inlen::Int      = 100
     fstinit::String = "glorotuniform"
     sndinit::String = "glorotuniform"
     model::String   = "gatednpu"

### 2020-05-20 scripts/arithmetic/sqrt_npu_l1_search.jl

@@ -53,7 +53,7 @@ function run(c::SqrtL1SearchConfig)
 end
 
 # set up dict which will be permuted to yield all config combinations
-config_dicts = Dict(:βend => 10f0 .^ (-4f0:-2f0),
+config_dicts = Dict(:βend => 10f0 .^ (-6f0:-4f0),
                     :init => [("rand","rand"),
                               ("glorotuniform", "glorotuniform")],
                     :model => ["gatednpu", "gatednpux", "nmu", "nalu"])
@@ -68,7 +68,7 @@ config_dicts = map(dict_list(config_dicts)) do config
     d
 end
 
-for d in config_dicts
+@progress name="Sqrt Search: " for d in config_dicts
     config = SqrtL1SearchConfig()
     for nr in 1:5
         d[:run] = nr

### 2020-05-20 src/arithmetic_models.jl

@@ -56,11 +56,11 @@ function get_model(model::String, inlen::Int, fstinit::String, sndinit::String)
         return Chain(NALU(inlen, inlen,
                           initNAC=initf(fstinit),
                           initG=initf(fstinit),
-                          initb=initf(fstinit)),
+                          initb=Flux.zeros),
                      NALU(inlen, 1,
                           initNAC=initf(sndinit),
                           initG=initf(sndinit),
-                          initb=initf(sndinit)))
+                          initb=Flux.zeros))
     elseif model == "npux"
         return Chain(Flux.fmap(ComplexMatrix, NAU(inlen,inlen,init=initf(fstinit))),
                      NPU(inlen, 1, init=initf(sndinit)))

### 2020-05-22 papers/main.tex
simple function table

@@
 samples from $\bm x \in \mathcal U^2(0.1,2)$ and plot the error $\epsilon =
-|\bm t - \hat{\bm t}|^2$ in Fig.~\ref{fig:compare_npu_nmu_nalu_xy_xdivy}.
+|\bm t - \hat{\bm t}|^2$ in Fig.~\ref{fig:simple_err}.
 
@@
 The combination of NAU and NMU can thus learn $\{+,-,\times\}$, but no division.
-This is shown in Fig.~\ref{fig:compare_npu_nmu_nalu_xy_xdivy} as well. The NMU
+This is shown in Fig.~\ref{fig:simple_err} as well. The NMU
 can perfectly represent the multiplication of the two inputs, but fails at
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{compare-npu-nmu-nalu-xy-xdivy.png}
+  \includegraphics[width=0.245\linewidth]{simple_err_add.pdf}
+  \includegraphics[width=0.245\linewidth]{simple_err_mult.pdf}
+  \includegraphics[width=0.245\linewidth]{simple_err_div.pdf}
+  \includegraphics[width=0.245\linewidth]{simple_err_sqrt.pdf}
   \caption{Comparison of different models learning the function
@@
   can extrapolate with an error that is less than $0.01$ in most places.}%
-  \label{fig:compare_npu_nmu_nalu_xy_xdivy}
+  \label{fig:simple_err}
 \end{figure}
-\todo{add in depth experiment desc. of fig.~\ref{fig:compare_npu_nmu_nalu_xy_xdivy} in appendix}
+\todo{add in depth experiment desc. of fig.~\ref{fig:simple_err} in appendix}
+\begin{table}
+  \centering
+  \caption{Comparison of different $2\times2$ layers on the task
+  $(x,y)\rightarrow(xy,\frac{x}{y})$.  $(x,y) \in \mathcal U^2(-2,2)$.}
+  \label{tab:simple_err}
+  \input{simple_err.tex}
+\end{table}
 
@@
 
-\appendix
-\section*{Appendix A}%
-\label{sec:appendix_a}
-
-\todo{add sqrt to table~\ref{tab:compare_npu_npu_nalu}?}
-\begin{table}[h]
-  \centering
-  \caption{Comparison of different $2\times2$ layers on the task
-  $(x,y)\rightarrow(xy,\frac{x}{y})$.  $(x,y) \in \mathcal U^2(-2,2)$.}
-  \label{tab:compare_npu_npu_nalu}
-  \input{table-xy-xdivy-pos.tex}
-\end{table}
-
 \bibliographystyle{plainnat}

### 2020-05-22 scripts/compare-npu-nmu-nalu-xy-xdivy.jl

@@ -10,7 +10,6 @@ using NeuralArithmetic
 Random.seed!(0)
 
 f1(x::Array) = reshape(x[1,:] .+ x[2,:], 1, :)
-f1(x::Array) = reshape(x[1,:], 1, :)
 f2(x::Array) = reshape(x[1,:] .* x[2,:], 1, :)
 f3(x::Array) = reshape(x[1,:] ./ x[2,:], 1, :)
 f4(x::Array) = reshape(sqrt.(x[1,:]), 1, :)
@@ -25,7 +24,9 @@ function generate_pos_neg()
 end
 
 function generate_pos()
-    x = rand(Float32, 2, 100) .* 2 .+ 0.01f0
+    #x = rand(Float32, 2, 100) .* 2 .+ 0.01f0
+    x = rand(Float32, 2, 100) .* 2 .+ 0.1f0
+    #x = rand(Float32, 2, 100) .+ 1
     y = f(x)
     (x,y)
 end
@@ -47,20 +48,12 @@ function generate()
 end
 
 function run_npu(c::Dict)
-    # model = Chain(NAU(2,4),
-    #               #GatedNPUX(4,4,initRe=(s...)->rand(Float32,s...)/10))
-    #               GatedNPUX(4,4))
-    #model = GatedNPUX(2,4)
     hdim = 6
     model = Chain(GatedNPUX(2,hdim),NAU(hdim,4))
-    #model = Chain(NAU(2,hdim),GatedNPUX(hdim,4))
-    #model = GatedNPUX(2,4,initRe=(s...)->rand(Float32,s...)/10)
-    #model = NPU(2,4)
-    #model = GatedNPUX(2,4)
     ps = params(model)
     opt = ADAM(c[:lr])
     data = (generate() for _ in 1:c[:niters])
-    loss(x,y) = Flux.mse(model(x),y) #+ c[:βl1]*norm(ps, 1) #+ 0.1norm(model.Im,1)
+    loss(x,y) = Flux.mse(model(x),y) + c[:βl1]*norm(ps, 1) #+ 0.1norm(model.Im,1)
     (x,y) = generate()
     cb = Flux.throttle(() -> (@info loss(x,y)), 0.1)
     Flux.train!(loss, ps, data, opt, cb=cb)
@@ -70,7 +63,7 @@ end
 function run_nmu(c::Dict)
     model = NMU(2,4)
     ps = params(model)
-    opt = RMSProp(c[:lr])
[…]

### 2020-05-22 scripts/simple/dataset.jl

@@ -1,0 +1,30 @@
+f1(x::Array) = reshape(x[1,:] .+ x[2,:], 1, :)
+f2(x::Array) = reshape(x[1,:] .* x[2,:], 1, :)
+f3(x::Array) = reshape(x[1,:] ./ x[2,:], 1, :)
+f4(x::Array) = reshape(sqrt.(x[1,:]), 1, :)
+f(x::Array) = cat(f1(x),f2(x),f3(x),f4(x),dims=1)
+
+function generate_pos_neg()
+    x = rand(Float32, 2, 100) .* 4 .- 2
+    y = f(x)
+    (x,y)
+end
+
+function generate_pos()
+    #x = rand(Float32, 2, 100) .* 2 .+ 0.01f0
+    x = rand(Float32, 2, 100) .* 2 .+ 0.1f0
+    #x = rand(Float32, 2, 100) .+ 1
+    y = f(x)
+    (x,y)
+end
+
+function test_generate()
+    x = rand(Float32, 2, 10000) .* 6
+    y = f(x)
+    (x,y)
+end
+
+addloss(model,x::Real,y::Real)  = abs(model([x,y])[1] - f1([x,y])[1])
+multloss(model,x::Real,y::Real) = abs(model([x,y])[2] - f2([x,y])[1])
+divloss(model,x::Real,y::Real)  = abs(model([x,y])[3] - f3([x,y])[1])
+sqrtloss(model,x::Real,y::Real) = abs(model([x,y])[4] - f4([x,y])[1])

### 2020-05-22 scripts/simple/plots.jl

@@ -1,0 +1,127 @@
+using DrWatson
+@quickactivate "NIPS_2020_NMUX"
+
+using Flux
+using LinearAlgebra
+using NeuralArithmetic
+using DataFrames
+using Plots
+using LaTeXStrings
+
+
+include(srcdir("turbocmap.jl"))
+include(joinpath(@__DIR__, "dataset.jl"))
+#pgfplotsx()
+
+nantozero(z) = isnan(z) ? 0 : z
+function inftoextreme(z)
+    if isinf(z)
+        m = maxintfloat(typeof(z))
+        return z<0 ? -m : m
+    else
+        return z
+    end
+end
+
+folder = datadir("simple")
+run = 2
+npu = load(joinpath(folder, "pos-gatednpux_lr=0.005_niters=20000_run=$(run)_βl1=1e-5.bson"))[:model]
+run = 4
+nalu = load(joinpath(folder, "pos-nalu_lr=0.005_niters=20000_run=$(run).bson"))[:model]
+run = 8
+nmu = load(joinpath(folder, "pos-nmu_lr=0.005_niters=20000_run=$(run).bson"))[:model]
+run = 11
+dense = load(joinpath(folder, "pos-dense_lr=0.005_niters=20000_run=$(run).bson"))[:model]
+
+
+posnegx = Float32.(collect(-4:0.1:4))
+posnegy = Float32.(collect(-4:0.1:4))
+posx = Float32.(collect(0.1:0.1:4))
+posy = Float32.(collect(0.1:0.1:4))
+
+plotsize = (400,400)
+cmap = :inferno
+clim = (-3,2)
+clip(x) = max(min(x,clim[2]),clim[1])
+levels = range(clim..., length=10)
+rminvalid = clip ∘ nantozero ∘ inftoextreme
+
+pyplot()
+@info "Plotting Addition..."
+func(model,x,y) = rminvalid(log10(addloss(model,x,y)))
+s1 = contour(posnegx, posnegy, (x,y)->func(npu,x,y),
+             c=cmap, clim=clim, title="NPU Add", ylabel="y",
+             levels=levels, fill=true, colorbar=false, aspect_ratio=:equal)
+
+s2 = contour(posnegx, posnegy, (x,y)->func(nalu,x,y),
+             c=cmap, clim=clim, title="NALU Add",
+             levels=levels, fill=true, colorbar=false, aspect_ratio=:equal)
+
+s3 = contour(posnegx, posnegy, (x,y)->func(nmu,x,y),
[…]

### 2020-05-22 scripts/simple/results_table.jl

@@ -1,0 +1,158 @@
+using DrWatson
+@quickactivate "NIPS_2020_NPUX"
+
+using DataFrames
+using Statistics
+using Flux
+using NeuralArithmetic
+using PrettyTables
+include(joinpath(@__DIR__, "dataset.jl"))
+
+train_range = "pos"
+function generate()
+    if train_range == "pos-neg"
+        return generate_pos_neg()
+    elseif train_range == "pos"
+        return generate_pos()
+    else
+        error("Unknown train range: $train_range")
+    end
+end
+
+function aggregateruns(dataframe::DataFrame)
+    gdf = groupby(dataframe, :hash)
+    combine(gdf) do df
+        (μmse  = mean(df.mse),
+         σmse  = std(df.mse),
+         μval  = mean(df.val),
+         σval  = std(df.val),
+         μadd  = mean(df.add_val),
+         μmult = mean(df.mult_val),
+         μdiv  = mean(df.div_val),
+         μsqrt = mean(df.sqrt_val),
+         model = first(df.model))
+    end
+end
+
+function find_best(df::DataFrame, key::String)
+    combine(groupby(df,"model")) do sdf
+        filter(r->r[key]==minimum(sdf[!,key]), sdf)
+    end
+end
+
+function delete_from_savename(path,key)
+    (dir,dict,_) = parse_savename(path)
+    delete!(dict, key)
+    joinpath(dir, savename(dict,digits=20))
+end
+
+name(m::GatedNPUX) = "GatedNPU"
+name(m::Dense) = "Dense"
+name(m::NALU) = "NALU"
+name(m::NMU) = "NMU"
+name(m::Chain) = name(m[1])
+
+function collect_folder!(folder::String)
+    sum_val(data) = sum([data[:add_val], data[:mult_val],
+                         data[:div_val], data[:sqrt_val]])
+    _df = collect_results!(datadir(folder), black_list=[:model,:val],
+                           special_list=[:model=>data->name(data[:model]),
+                                         :val  =>data->sum_val(data)])
+    _df.hash = delete_from_savename.(_df.path, "run")
+    return _df
+end
+
+"""
+Creates table like this:
+| task | npu | npux | ... |
+"""
+function table_models_tasks(df::DataFrame)
[…]

### 2020-05-22 scripts/simple/run.jl

@@ -1,0 +1,140 @@
+using DrWatson
+@quickactivate "NIPS_2020_NMUX"
+
+using Logging
+using TerminalLoggers
+using ProgressLogging
+global_logger(TerminalLogger(right_justify=80))
+
+using Flux
+using LinearAlgebra
+using Statistics
+using NeuralArithmetic
+
+include(joinpath(@__DIR__, "dataset.jl"))
+
+train_range = "pos"
+nr_runs = 20
+
+
+function generate()
+    if train_range == "pos-neg"
+        return generate_pos_neg()
+    elseif train_range == "pos"
+        return generate_pos()
+    else
+        error("Unknown train range: $train_range")
+    end
+end
+
+function result_dict(model::Chain, config::Dict)
+    res = Dict{Symbol,Any}([(k,v) for (k,v) in config])
+    res[:model] = model
+
+    (x,y) = generate()
+    res[:mse] = Flux.mse(model(x),y)
+
+    (xt,yt) = test_generate()
+    res[:val] = Flux.mse(model(xt),yt)
+
+    # training error
+    x = 0.1f0:0.1f0:2
+    y = 0.1f0:0.1f0:2
+    xy = reduce(hcat, map(t->[t...], Iterators.product(x,y)))
+    t = model(xy)
+    res[:add_trn]  = mean(abs, t[1,:] - vec(f1(xy)))
+    res[:mult_trn] = mean(abs, t[2,:] - vec(f2(xy)))
+    res[:div_trn]  = mean(abs, t[3,:] - vec(f3(xy)))
+    res[:sqrt_trn] = mean(abs, t[4,:] - vec(f4(xy)))
+
+
+    # validation error
+    x = -4.1f0:0.2f0:4f0
+    y = -4.1f0:0.2f0:4f0
+    xy = reduce(hcat, map(t->[t...], Iterators.product(x,y)))
+    t = model(xy)
+    res[:add_val]  = mean(abs, t[1,:] - vec(f1(xy)))
+    res[:mult_val] = mean(abs, t[2,:] - vec(f2(xy)))
+    res[:div_val]  = mean(abs, t[3,:] - vec(f3(xy)))
+
+    x = 0.1f0:0.1f0:4
+    y = 0.1f0:0.1f0:4
+    xy = reduce(hcat, map(t->[t...], Iterators.product(x,y)))
+    t = model(xy)
[…]

### 2020-05-23 papers/main.tex
fuzz fuzz

@@
   \caption{Comparison of different models learning the function
-  $(x,y)\rightarrow(xy,x/y)$ with $(x,y)\in\mathcal U^2(0.1,2)$.  Each
-  plot shows the mean-squared error on a logarithmic color scale ($\hat{\bm
-  t}=\text{model}(\bm x)$).  The Dense network learns both multiplication and
-  division, but fails to extrapolate. NALU learns both tasks perfectly, but
-  completely fails if one of the inputs is negative.  The NMU successfully
-  learns multiplication, but not division. Only the NPU learns both tasks and
-  can extrapolate with an error that is less than $0.01$ in most places.}%
+  $(x,y)\rightarrow(x+y,xy,x/y,\sqrt(x))$ with $(x,y)\in\mathcal U^2(0.1,2)$.
+  Each plot shows the mean-squared error on a logarithmic color scale
+  ($\hat{\bm t}=\text{model}(\bm x)$) of the best model of 20 runs.
+  The Dense network learns all tasks, but fails to extrapolate. NALU is
+  slightly better at extrapolating to positive numbers, but fails if one of the
+  inputs is negative.  The NMU successfully learns addition and multiplication,
+  but not division and the square-root.  Only the NPU learns all tasks and can
+  extrapolate both to positive and negative numbers.}%
   \label{fig:simple_err}
@@
   \centering
-  \caption{Comparison of different $2\times2$ layers on the task
-  $(x,y)\rightarrow(xy,\frac{x}{y})$.  $(x,y) \in \mathcal U^2(-2,2)$.}
+  \caption{Validation error of different models learning the function
+  $(x,y)\rightarrow(x+y,xy,x/y,\sqrt(x))$ with $(x,y)\in\mathcal U^2(0.1,2)$.
+  The validation ranges are $(x,y) \in -4.1:0.2:4$ for addition, multiplication,
+  and division, and $(x,y) \in 0.1:0.2:4$ for the square-root.
+  Each value is the averaged absolute of 20 models.
+  }
   \label{tab:simple_err}

### 2020-05-23 experiments/lhs_vs_rand.jl

@@ -1,0 +1,35 @@
+using DrWatson
+@quickactivate "NIPS_2020_NMUX"
+
+using Plots
+using LatinHypercubeSampling
+
+pyplot()
+
+
+n = 1000
+x = rand(n)
+y = rand(n)
+
+
+@info "creating plan"
+plan, _ = LHCoptim(300,2,1000)
+@info "scaling plan"
+scaled_plan = scaleLHC(plan,[(-5.0,5.0),(-5.0,5.0)])
+
+rosenbrock_2D(x) = (1.0 - x[1])^2 + 100.0 * (x[2] - x[1]^2)^2
+#samples = mapslices(rosenbrock_2D,scaled_plan; dims=2)
+
+(x,y) = eachcol(scaled_plan)
+# x = -5:0.2:5
+# y = -5:0.2:5
+
+@info "plotting"
+heatmap(x,y,(x,y)->log10(rosenbrock_2D([x,y])))
+
+# (hx,hy) = eachcol(cube)
+# 
+# p1 = scatter(x,y)
+# p2 = scatter(hx,hy)
+# 
+# plot(p1,p2)

### 2020-05-23 scripts/arithmetic/results_table.jl

@@ -226,6 +226,12 @@ print_table(table_best_models_tasks(clean_adf,"μ$key"))
 
 using UnicodePlots
 row = find_best(df,"gatednpu","div",key)
-model = load(row.path)[:model]
+@unpack history,model = load(row.path)
 display(row.config)
 heat(model)
+
+using Plots
+pyplot()
+z = reduce(hcat, get(history, :μz)[2])[1:100,:]
+plot(z',legend=false)
+

### 2020-05-23 scripts/arithmetic/validation.jl

@@ -12,6 +12,7 @@ using ValueHistories
 using UnicodePlots
 using DataFrames
 using PrettyTables
+using Sobol
 
 include(joinpath(@__DIR__, "configs.jl"))
 include(srcdir("unicodeheat.jl"))
@@ -80,7 +81,7 @@ function validation_samples(c,xs)
 end
 
 validation_samples(c::Union{MultL1SearchConfig,AddL1SearchConfig,DivL1SearchConfig}) =
-    validation_samples(c,[-4.5f0,-2.5f0,-1.5f0,-0.3f0,-0.2f0,0.1f0, 1f0,2f0,3f0,10f0])
+    validation_samples(c,[-4.5f0,-2.5f0,-1.5f0,-0.3f0,-0.2f0,-0.01f0,0.1f0, 1f0,2f0,3f0,10f0])
 
     # validation_samples(c,[ 1f0, 2f0, 3f0, 4f0, 0.1f0, 0.2f0,
     #                       -1f0,-2f0,-3f0,-4f0,-0.1f0,-0.2f0])
@@ -90,11 +91,11 @@ validation_samples(c::SqrtL1SearchConfig) =
 
 function sobol_samples(c)
     s = SobolSeq(c.inlen)
+    # discard first zero sample
+    next!(s)
     x = reduce(hcat, [next!(s) for i = 1:100000])
     xs = c.uplim * 2
     xe = c.lowlim * 2
-    xs = 0
-    xe = 2
     Float32.(x .* (xs - xe) .+ xe)
 end
 
@@ -149,8 +150,8 @@ end
 key = "val"
 print_table(table_models_tasks(bestmodels,key))
 @progress for row in eachrow(bestmodels)
-    #x = sobol_samples(row.config)
-    x = validation_samples(row.config)
+    x = sobol_samples(row.config)
+    #x = validation_samples(row.config)
     y = task(x,row.config)
     m = load(row.path)[:model]
     row.val = Flux.mse(m(x),y)

### 2020-05-23 scripts/polynomial/gatednpux.jl

@@ -1,0 +1,139 @@
+using DrWatson
+@quickactivate "NIPS_2020_NMUX"
+
+using Flux
+using Parameters
+using LinearAlgebra
+using NeuralArithmetic
+using ValueHistories
+using Plots
+#unicodeplots()
+pyplot()
+
+f(x) = x^2
+f(x) = x^4/10 + x^3/10 - (13x^2)/10 - x/10 + 6/5
+f(x) = (x^3-2x)/2(x^2-5)
+#f(x) = (x-2)/(x-3)
+
+function validationplot(xt,yt,tt,lowlim,uplim)
+    p1 = plot(vec(xt), vec(yt))
+    plot!(p1, vec(xt), vec(tt))
+    vline!([lowlim,uplim],c=:gray)
+end
+
+
+
+function run(c::Dict, f::Function)
+    @unpack dim, lowlim, uplim, niter, lr, βpsl1, βiml1 = c
+    x = Float32.(reshape(lowlim:0.1:uplim, 1, :))
+    y = f.(x)
+    xt = Float32.(reshape((lowlim*1.1):0.1:(uplim*1.1),1,:))
+    yt = f.(xt)
+
+    h = MVHistory()
+    data = Iterators.repeated((x,y), niter)
+    opt = ADAM(lr)
+    #model = Chain(NAU(1,dim), GatedNPUX(dim,dim), NAU(dim,1))
+    model = Chain(GatedNPUX(1,dim), NAU(dim,dim), GatedNPUX(dim,1))
+    iml1(model::GatedNPUX) = norm(model.Im,1)
+    iml1(model::NAU) = 0
+    iml1(model::Chain) = sum(iml1, model)
+    #model = Chain(NALU(1,dim), NALU(dim,1))
+    ps = params(model)
+    mse(x,y) = sum(abs2, model(x) .- y)
+    iml1() = βiml1*iml1(model)
+    psl1() = βpsl1*norm(ps,1)
+    loss(x,y) = mse(x,y) #+ iml1() + psl1()
+
+    cb = [Flux.throttle(()->(
+               p1 = validationplot(xt,yt,model(xt),lowlim,uplim);
+               display(p1);
+               @info loss(x,y) loss(xt,yt)
+              ), 1),
+          Flux.throttle(() -> (push!(h, :μz, Flux.destructure(model)[1]);
+                               push!(h, :mse, mse(xt,yt))), 0.1)
+         ]
+    Flux.train!(loss, ps, data, opt, cb=cb)
[…]

### 2020-06-02 scripts/arithmetic/pareto.jl
merge plotting scripts

@@ -8,99 +8,109 @@ global_logger(TerminalLogger(right_justify=80))
 
 using Plots
 using LaTeXStrings
+using DataFrames
+using Flux
+using NeuralArithmetic
 pgfplotsx()
+#pyplot()
 
 include(joinpath(@__DIR__, "sobolconfigs.jl"))
 include(srcdir("arithmetic_dataset.jl"))
 
 res = load(datadir("pareto","thresh=1e-5.bson"))
 df = combine(groupby(res[:df], ["model","task"])) do gdf
+    gdf = sort(DataFrame(gdf),"val")
     gdf[1:min(10,size(gdf,1)),:]
 end
+df.nrps = zeros(length(df.model))
+ϵ = 1e-2
+for row in eachrow(df)
+    row.nrps = sum(abs.(Flux.destructure(row.modelps)[1]) .> ϵ)
+end
 
-models = Dict("npux"=>"NPU",
-              "gatednpux"=>"GatedNPU",
+models = Dict("npux"=>"NaiveNPU",
+              "gatednpux"=>"NPU",
               "nalu"=>"NALU",
               "nmu"=>"NMU")
 ms     = 4
 alpha  = 0.7
 xscale = :log10
 yscale = :log10
-plotmodels = ["gatednpux","nalu","nmu","npux"]
+plotmodels = [(:circle,"gatednpux"),(:pentagon,"nalu"),(:diamond,"nmu"),(:utriangle,"npux")]
 #plotmodels = ["gatednpux","nalu","nmu"]
 
-s1 = plot(title="Addition +")
+s1,s2,s3,s4=plot(),plot(),plot(),plot()
 pdf  = filter(row->row.task=="add", df)
-for m in plotmodels
-    mdf = filter(row->row.model==m, pdf)
-    scatter!(s1, mdf.reg, mdf.val,
-             label=models[m], yscale=yscale, xscale=xscale, alpha=alpha, ms=ms,
-             ylabel="Validation MSE", legend=false)
+for (marker,model) in plotmodels
+    mdf = filter(row->row.model==model, pdf)
+    scatter!(s1, mdf.nrps, mdf.val, marker=marker,
+             label=models[model], yscale=yscale, xscale=xscale, alpha=alpha, ms=ms,
+             ylabel="Testing MSE", legend=false, xlabel="Nr. Parameters")
 end
 
-s2 = plot(title="Multiplication \$\\times\$")
 pdf  = filter(row->row.task=="mult", df)
-for m in plotmodels
[…]

### 2020-06-02 scripts/arithmetic/revalidate.jl

@@ -111,8 +111,8 @@ function latex_table(results::DataFrame)
 
     function latex_row(row)
         vals = convert(Vector, row[2:end])
-        i  = findmin(vals)[2]
-        ss = map(x->string(round(x,digits=3)), vals)
+        i  = findmin(map(x->isinf(x) ? 1e30 : x,vals))[2]
+        ss = map(x->string(round(x,digits=7)), vals)
         ss = map(s->replace(s,"±"=>"\$\\pm\$"), ss)
         ss[i] = "\\textbf{$(ss[i])}"
         srow = DataFrame(Dict(zip(names(row[2:end]),ss)))
@@ -127,7 +127,7 @@ function latex_table(results::DataFrame)
 raw"""
 \begin{tabular}{lcccc}
 \toprule
-Task & GatedNPU & NALU & NMU & NPU (real)\\
+Task & NPU & NALU & NMU & NaiveNPU\\
 \midrule
 """ *
 "Add  & $(r1[1,:gatednpux]) & $(r1[1,:nalu]) & $(r1[1,:nmu]) & $(r1[1,:npux]) \\\\\n" *

### 2020-06-02 scripts/fracode/model-ps.jl

@@ -1,0 +1,62 @@
+using DrWatson
+@quickactivate "NIPS_2020_NMUX"
+
+using Plots
+using LaTeXStrings
+
+using Flux
+using NeuralArithmetic
+using RecursiveArrayTools
+using DiffEqFlux
+
+include(srcdir("annotatedheatmap.jl"))
+
+fname = "gatednpu_hdim=6_lr=0.005_niters=3000_run=4_αinit=0.2_βim=0_βps=1.bson"
+# fname = "gatednpux_hdim=6_lr=0.005_niters=3000_run=4_αinit=0.2_βim=0.1_βps=0.1.bson"
+# fname = "gatednpux_hdim=6_lr=0.005_niters=3000_run=3_αinit=0.2_βim=1_βps=1.bson"
+# fname = "gatednpux_hdim=15_lr=0.005_niters=3000_run=5_αinit=0.2_βim=1_βps=1.bson"
+# fname = "gatednpux_hdim=6_lr=0.005_niters=3000_run=4_αinit=0.2_βim=0.1_βps=0.1.bson"
+# fname = "gatednpux_hdim=9_lr=0.005_niters=3000_run=4_αinit=0.2_βim=0.1_βps=0.1.bson"
+res = load(datadir("fracsir",fname))
+
+nonfast(m::FastNAU) = NAU(m.in,m.out)
+nonfast(m::FastGatedNPU) = GatedNPU(m.in,m.out)
+nonfast(m::FastGatedNPUX) = GatedNPUX(m.in,m.out)
+nonfast(m::FastChain) = Chain(map(nonfast, m.layers)...)
+name(m::NAU) = "NAU"
+name(m::GatedNPU) = "NPU (real)"
+name(m::GatedNPUX) = "NPU"
+
+@unpack dudt, ps = res
+m = Flux._restructure(nonfast(dudt),ps)
+
+
+fontsize=11
+pyplot()
+cmap = :balance
+p0 = annotatedheatmap(zeros(3,1), annotationtexts=[L"0.09I-"*"\n"*L"0.15R^{0.6}",
+                                                   L"0.11r"*"\n"*L"-0.1R",
+                                                   L"-0.12r"*"\n"*L"+0.13I"],
+                      annotationargs=(:black,fontsize),
+                      c=cmap, clim=(-1,1), aspect_ratio=:equal, title="Output")
+
+p1 = annotatedheatmap(m[2].W[end:-1:1,:], title="$(name(m[2]))\nLayer 2",
[…]

### 2020-06-02 scripts/fracode/pareto-sir.jl

@@ -1,0 +1,115 @@
+using DrWatson
+@quickactivate "NIPS_2020_NMUX"
+
+using DataFrames
+using Plots
+using LaTeXStrings
+using OrdinaryDiffEq
+using QHull
+
+include(joinpath(@__DIR__, "odedata.jl"))
+include(srcdir("annotatedheatmap.jl"))
+
+#for loading the dataframe
+using NeuralArithmetic
+using RecursiveArrayTools
+using Flux
+using DiffEqFlux
+
+function delete_from_savename(path,key)
+    (dir,dict,_) = parse_savename(path)
+    delete!(dict, key)
+    joinpath(dir, savename(dict,digits=20))
+end
+
+@unpack df = load(datadir("results_fracsir.bson"))
+df.hash = delete_from_savename.(df.path, "run")
+
+function Plots.rotate(x::Vector,n::Int)
+    if n==0
+        return x
+    else
+        rotate(vcat(x[2:end],x[1:1]), n-1)
+    end
+end
+
+function hull(nrps::Vector, mse::Vector)
+    ch = chull(Array{Float64}(hcat(nrps, mse)))
+    return ch.vertices
+end
+
+gdf = filter(r->r.model=="FastGatedNPUX", df)
+npux_nrps = Array{Float64}(gdf.nrps)
+npux_mse  = Array{Float64}(gdf.mse)
+npux_idx  = rotate(hull(gdf.nrps, min.(gdf.mse, 1e5)), 0)[1:end-3]
+
+gdf = filter(r->r.model=="FastGatedNPU", df)
+npu_nrps = gdf.nrps
+npu_mse  = gdf.mse
+npu_idx  = rotate(hull(gdf.nrps, min.(gdf.mse, 1e5)), 3)[1:end-1]
+
+gdf = filter(r->r.model=="FastDense", df)
+dense_nrps = gdf.nrps
+dense_mse  = gdf.mse
+dense_idx  = rotate(hull(gdf.nrps, gdf.mse), 1)[4:end]
+ 
+# xbins = 0:7:200
+# ybins = 10. .^(-2.2:0.3:3)
+# 
+# npux_hist = fit(Histogram, (npux_nrps,min.(npux_mse,ybins[end])), (xbins, ybins))
+# npu_hist = fit(Histogram, (npu_nrps,min.(npu_mse,1e5)), (xbins, ybins))
[…]

### 2020-06-02 scripts/id-loss.jl

@@ -1,0 +1,136 @@
+using DrWatson
+@quickactivate "NIPS_2020_NMUX"
+
+using Plots
+using Distributions
+using LaTeXStrings
+using Random
+Random.seed!(2)
+#pgfplotsx()
+pyplot()
+
+include(srcdir("turbocmap.jl"))
+
+function nmu(x::Vector, W::Matrix)
+     z = W .* reshape(x,1,:) .+ 1 .- W
+    dropdims(prod(z, dims=2), dims=2)
+end
+nmu(X::Matrix, W::Matrix) = vec(mapslices(x->nmu(x,W), X, dims=1))
+
+function npu(x::AbstractArray{T}, W::Matrix{T}) where T
+    r = abs.(x) .+ eps(T)
+    k = max.(-sign.(x), 0) .* T(pi)
+    z = exp.(W * log.(r)) .* cos.(W*k)
+end
+#npu(X::Matrix, W::Matrix) = vec(mapslices(x->npu(x,W), X, dims=1))
+
+function gatednpu(x::AbstractArray{T}, W::AbstractMatrix{T}, g::AbstractVector{T}) where T
+    g = min.(max.(g, 0), 1)
+
+    r = abs.(x) .+ eps(T)
+    r = g .* r .+ (1 .- g)
+
+    k = max.(-sign.(x), 0) .* T(pi)
+    k = g .* k
+
+    z = exp.(W * log.(r)) .* cos.(W*k)
+end
+
+function gatednpux(x::AbstractArray{T}, Re::AbstractMatrix{T}, Im::AbstractMatrix{T}, g::AbstractVector{T}) where T
+    g = min.(max.(g, 0), 1)
+
+    r = abs.(x) .+ eps(T)
+    r = g .* r .+ (1 .- g)
+
+    k = max.(-sign.(x), 0) .* T(pi)
+    k = g .* k
+
+    exp.(Re*log.(r) - Im*k) .* cos.(Re*k + Im*log.(r))
+end
+
+
+batch = 32
+X = Array{Float64,2}(undef,2,batch)
+X[1,:] .= rand(Uniform(0,2),batch)
+X[2,:] .= rand(Uniform(-0.05,0.05),batch)
+# X[1,:] .= rand(Uniform(-3,3),batch)
+# X[2,:] .= rand(Uniform(-0.001,0.001), batch)
+
+
[…]

### 2020-06-02 scripts/simple/plots.jl

@@ -1,5 +1,5 @@
 using DrWatson
-@quickactivate "NIPS_2020_NMUX"
+@quickactivate "npu"
 
 using Flux
 using LinearAlgebra
@@ -24,104 +24,157 @@ function inftoextreme(z)
 end
 
 folder = datadir("simple")
-run = 2
-npu = load(joinpath(folder, "pos-gatednpux_lr=0.005_niters=20000_run=$(run)_βl1=1e-5.bson"))[:model]
-run = 4
+run = 19
+npu = load(joinpath(folder, "pos-gatednpux_lr=0.005_niters=20000_run=10_βl1=0.bson"))[:model]
+run = 8
 nalu = load(joinpath(folder, "pos-nalu_lr=0.005_niters=20000_run=$(run).bson"))[:model]
+run = 4
+inalu = load(joinpath(folder, "pos-inalu_lr=0.001_niters=20000_run=$(run).bson"))[:model]
 run = 8
 nmu = load(joinpath(folder, "pos-nmu_lr=0.005_niters=20000_run=$(run).bson"))[:model]
-run = 11
+run = 1
 dense = load(joinpath(folder, "pos-dense_lr=0.005_niters=20000_run=$(run).bson"))[:model]
 
 
-posnegx = Float32.(collect(-4:0.1:4))
-posnegy = Float32.(collect(-4:0.1:4))
-posx = Float32.(collect(0.1:0.1:4))
-posy = Float32.(collect(0.1:0.1:4))
+posnegx = Float32.(collect(-4.1:0.2:4))
+posnegy = Float32.(collect(-4.1:0.2:4))
+posx = Float32.(collect(0.1:0.1:5))
+posy = Float32.(collect(0.1:0.1:5))
 
-plotsize = (400,400)
-cmap = :inferno
+plotsize = (800,200)
+layout = grid(1,4,widths=[0.23,0.23,0.23,0.25])
+cmap = cgrad(:inferno, rev=true)
+
 clim = (-3,2)
 clip(x) = max(min(x,clim[2]),clim[1])
 levels = range(clim..., length=10)
 rminvalid = clip ∘ nantozero ∘ inftoextreme
 
+npu_addloss(x,y)    = rminvalid(log10(addloss(npu,x,y)))
+npu_multloss(x,y)   = rminvalid(log10(multloss(npu,x,y)))
[…]

### 2020-06-02 scripts/simple/results_table.jl

@@ -25,27 +25,16 @@ function aggregateruns(dataframe::DataFrame)
     combine(gdf) do df
         (μmse  = mean(df.mse),
          μval  = mean(df.val),
+         μadd  = mean(df.add_val),
+         μmult = mean(df.mult_val),
+         μdiv  = mean(df.div_val),
+         μsqrt = mean(df.sqrt_val),
          σmse  = std(df.mse),
          σval  = std(df.val),
-
-         μval_add  = mean(df.add_val),
-         μval_mult = mean(df.mult_val),
-         μval_div  = mean(df.div_val),
-         μval_sqrt = mean(df.sqrt_val),
-         σval_add  = std(df.add_val),
-         σval_mult = std(df.mult_val),
-         σval_div  = std(df.div_val),
-         σval_sqrt = std(df.sqrt_val),
-
-         μmse_add  = mean(df.add_trn),
-         μmse_mult = mean(df.mult_trn),
-         μmse_div  = mean(df.div_trn),
-         μmse_sqrt = mean(df.sqrt_trn),
-         σmse_add  = std(df.add_trn),
-         σmse_mult = std(df.mult_trn),
-         σmse_div  = std(df.div_trn),
-         σmse_sqrt = std(df.sqrt_trn),
-
+         σadd  = std(df.add_val),
+         σmult = std(df.mult_val),
+         σdiv  = std(df.div_val),
+         σsqrt = std(df.sqrt_val),
          nr    = length(df.model),
          model = first(df.model))
     end
@@ -63,7 +52,7 @@ function delete_from_savename(path,key)
     joinpath(dir, savename(dict,digits=20))
 end
 
-name(m::GatedNPUX) = "GatedNPU"
+name(m::GatedNPUX) = "NPU"
 name(m::Dense) = "Dense"
 name(m::NALU) = "NALU"
 name(m::NMU) = "NMU"
@@ -84,16 +73,16 @@ end
 Creates table like this:
 | task | npu | npux | ... |
 """
-function table_models_tasks(df::DataFrame, key)
+function table_models_tasks(df::DataFrame)
[…]

### 2020-06-02 papers/main.tex
clean up; get tikz

--- 2020-05-22 papers/main.tex
@@
 % [preprint] option:
-\usepackage[preprint]{neurips_2020}
+\usepackage{neurips_2020}
 
@@
 \usepackage{amsfonts}       % blackboard math symbols
+\usepackage{amsthm}         % definitions
 \usepackage{nicefrac}       % compact symbols for 1/2, etc.
 \usepackage{microtype}      % microtypography
+\usepackage{caption}
+\usepackage{mathtools}
+
+\newtheorem*{definition}{Definition}
 
@@
 
-% figures
+% tikz
+\usepackage{tikz}
+\usetikzlibrary{%
+  arrows,%
+  backgrounds,
+  intersections,
+  shapes,
+  shapes.misc,% wg. rounded rectangle
+  shapes.arrows,%
+  chains,%
+  matrix,%
+  positioning,% wg. " of "
+  scopes,%
+  decorations.pathmorphing,% /pgf/decoration/random steps | erste Graphik
+  shadows,%
+  patterns% for hatched rect
+}
+
+% plots
 \graphicspath{{./../plots/}}
-\usepackage{tikz}
-\usetikzlibrary{arrows,backgrounds,positioning,intersections}
 \usepackage{pgfplots}
@@
 \newcommand{\Wim}{\bm W_{i}}
+\newcommand{\npu}{\text{NPU}}
+\newcommand{\naivenpu}{\text{NaiveNPU}}
+\newcommand{\nau}{\text{NAU}}
+\newcommand{\nmu}{\text{NMU}}
+\newcommand{\nalu}{\text{NALU}}
+\newcommand{\inalu}{\text{iNALU}}
+\newcommand{\dense}{\text{Dense}}
+\newcommand{\chain}{\text{Chain}}
 
@@
 
-\title{Neural Power Unit \\-- A Bayesian Approach To Neural Arithmetic}
+\title{Neural Power Units}
 \author{
   Niklas Heim,
-  V\'aclav \v Sm\'idl,
-  Tom\'a\v s Pevn\'y \\
+  Tom\'a\v s Pevn\'y,
+  V\'aclav \v Sm\'idl\\
   Artificial Intelligence Center\\
@@
 \begin{abstract}
-  Common Neural Networks can approximate simple arithmetic operations, but fail
-  to generalize beyond the range of numbers that were seen during training. A
-  new class of units called \emph{Neural Arithmetic Units} aim to overcome this
-  difficulty, but are limited either to operate on positive numbers (NALU by
-  \citet{trask_neural_2018}), or can only represent simple addition and
-  multiplication (NAU \& NMU by \citet{madsen_neural_2020}).  We introduce a
-  Neural Arithmetic Unit that operates on the full domain of real numbers and
-  is capable of learning arbitrary power functions called \emph{Neural Power
-  Unit} (NPU). The NPU enables not only the learning simple arithmetic
-  operations, but is also capable of learning e.g. Taylor expansions with very
-  few parameters, which makes the NPU highly explainable.
-  \footnote{Implementation of neural arithmetic units:
-  \url{https://github.com/nmheim/NeuralArithmetic.jl}}.
+  Conventional Neural Networks can approximate simple arithmetic operations, but fail
+  to generalize beyond the range of numbers that were seen during training.
+  \emph{Neural Arithmetic Units} aim to overcome this difficulty, but current
+  arithmetic units are either limited to operate on positive numbers or can
+  only represent a subset of arithmetic operations. We introduce the \emph{Neural
+  Power Unit} (NPU) that operates on the
+  \emph{full domain of real numbers} and is capable of \emph{learning
+  arbitrary power functions} in a single layer.
+  The NPU thus fixes the shortcomings of existing arithmetic units and extends
+  their expressivity. This is achieved by using formulas from complex arithmetics
+  without requiring a conversion of the network to complex numbers.
+  We show where the NPU outperforms its
+  competitors in terms of accuracy and sparsity on artificial arithmetic
+  datasets. Additionally, we demonstrate how the NPU can be used as a highly
+  interpretable model to discover the generating equation of a dynamical system
+  purely from the data.
 \end{abstract}
@@
 also to the survival of many other
-species~\citep{dehaene_number_2011,gallistel_finding_2018}.  This can be taken
-as a hint that arithmetic is an important ingredient to a successful,
-intelligent agent.  State of the art neural networks are capable of learning
-simple arithmetic, but they fail to extrapolate beyond the ranges seen during
+species~\citep{dehaene_number_2011,gallistel_finding_2018}. A successful,
+intelligent agent should therefore be able to perform simple arithmetic.  State
+of the art neural networks are capable of learning arithmetic, but they
+fail to extrapolate beyond the ranges seen during
 training~\citep{suzgun_evaluating_2018,lake_generalization_2018}.  The
@@
 
-The \emph{Neural Arithmetic Logic Unit} (NALU) can learn addition,
-subtraction, multiplication, and division with two severe limitations: the
-inputs that the NALU is trained with have to be positive, and should be
-significantly larger than zero, otherwise the layer will not converge to
-a correct solution.
+Including Neural Arithmetic Units in common neural networks, promises to
+significantly increase their extrapolation capabilities due to their inductive
+bias towards numerical computation. This is especially true for tasks in which
+the data contains mathematical relationships.  Additionally, they promise to
+reduce the amount of parameters that are needed for a given task, and can
+therefore drastically improve the explainability of the model.  We demonstrate
+how neural arithmetic units as part of a \emph{Neural Ordinary Differential
+Equation} (NODE, \cite{chen_neural_2019}) can outperform a dense network with
+significantly fewer parameters in Sec.~\ref{sub:fractional_sir_model}.  In
+fact, our NPU can be used to directly read out the correct generating ODE from
+the fitted model.  This is inline with recent efforts to build
+\emph{interpretable} models instead of \emph{explaining} black box models
+\citep{rudin_stop_2019}, like conventional neural networks.
 
-\cite{madsen_neural_2020} introduce two new arithmetic layers, the \emph{Neural
-Addition Unit} (NAU) and the \emph{Neural Multiplication Unit} (NMU).
-Stacked, they can learn addition, subtraction, and multiplication and they converge
-for any input range. However, the NMU cannot learn division.
+The currently available arithmetic units all have different strengths and
+weaknesses, but none of them solve simple arithmetic completely.
+The \emph{Neural Arithmetic Logic Unit} (NALU) by \cite{trask_neural_2018},
+chronologically, was the first arithmetic unit. It can solve
+addition ($+$, including subtraction), multiplication ($\times$), and division
+($\div$), but is limited to positive inputs. The convergence of the
+NALU is quite fragile due to an internal gating mechanism between addition and
+multiplication paths as well as the use of a logarithm which is problematic for
+small inputs.  Recently, \cite{schlor_inalu_2020} introduced the \emph{improved NALU} (iNALU,
+to fix the NALU's shortcomings. However, it significantly increases its complexity and we
+observe only a slight improvement in performance.\\
+\cite{madsen_neural_2020} solve ($+,\times$) with two new units: the
+\emph{Neural Addition Unit} (NAU), and the \emph{Neural Multiplication Unit}
+(NMU). Instead of gating between addition and multiplication paths, they are
+separate units that can be stacked. They can work with the full range real
+numbers, converge much more reliably, but are not capable of representing
+division.
 
-Including Neural Arithmetic Units in common neural networks, apart from the
-potential increase in extrapolation capabilities, has additional advantages.
-They promise to reduce the amount of parameters that are needed for a given
-task, can drastically improve the explainability of our models (more on the
-explainability of the NPU in Sec.~\ref{sec:neural_power_unit}).  Additionally,
-the field of Scientific Machine Learning, which, in part, is concerned with
-learning differential equations~\citep{rackauckas_universal_2020} could benefit
-from the inductive bias neural arithmetic.
-
-\subsection*{Our Contribution}%
+\subsection*{Our Contributions}%
 \label{sub:our_contribution}
 
-We introduce a new arithmetic layer called the \emph{Neural Power Unit} (NPU)
-which is capable of learning addition, subtraction, and arbitrary power
-functions, which includes multiplication and division.
-Our approach is inspired by the NALU, but overcomes its limitations to
-non-small positive numbers by leveraging the complex plane.
+\textbf{Neural Power Unit.}
+We introduce a new arithmetic layer (NPU,
+Sec.~\ref{sec:neural_power_unit}) which is capable of learning power
+functions $(\prod x_{i}^{w_i})$ for arbitrary real input $x_i$ and power $w_i$ thus including multiplication ($x_1\times x_2 = x_1^1 x_2^1$) as well as division $(x_1\div x_2=x_1^{1}x_2^{-1})$ .
+This is achieved by using formulas from complex arithmetics (Sec.~\ref{sub:naive_npu}).
+Stacks of NAUs and NPUs can thus learn the full spectrum of simple arithmetic operations.
+
+\textbf{Convergence improvement.}
+We address the known convergence issues of neural arithmetic units by introducing a
+\emph{relevance gate} that smooths out the loss surface of the NPU
+(Sec.~\ref{sub:npu}). With the relevance gate the NPU reaches extrapolation and
+sparsity errors that are on par with the NMU on ($\times$) and outperform NALU
+on ($\div,\sqrt{\cdot}$).
+
+\textbf{Interpretability.}
+We show how the NPU can be used as a highly interpretable model for discovery of epidemiological models. 
+Specifically, we demontrate its ability to provide a model that can be interpreted as fractional SIR model (Sec.~\ref{sub:fractional_sir_model})
+that was used to fit the COVID-19 outbreak in various countries
+\citep{taghvaei_fractional_2020}.
 
@@
 
-\subsection{Neural Arithmetic Logic Unit}%
+A number of different approaches to automatically solve arithmetic tasks have
+been studied in the recent years. Approaches include Neural GPUs
+\citep{kaiser_neural_2016}, Grid LSTMs \citep{kalchbrenner_grid_2016}, Neural
+Turing Machines \citep{graves_neural_2014}, and Neural Random Access Machines
+\citep{kurach_neural_2016}. They solve tasks like binary addition and
+multiplication, or single digit arithmetic. The Neural Status Register
+\citep{faber_neural_2020} focusses on control flow.  The Neural Arithmetic
+Expression Calculator \citep{chen_neural_2018}, a hierarchical reinforcement
+learner is the only method that solves the division problem, but it operates on
+character sequences of arithmetic expressions. Related is symbolic integration
+with transformers \citep{lample_deep_2019}. Unfortunately, most of the named models
+have severe problems with extrapolation \citep{madsen_measuring_2019,saxton_analysing_2019}.
+A solution to the extrapolation problem could be Neural Arithmetic Units. They are
+designed with an inductive bias towards systematic, arithmetic computation.
+However, currently they are limited in their capabilities of expressing the full
+range of simple arithmetic operations ($+,\times,\div$).
+In the following two sections we briefly describe the currently available
+arithmetic layers including their advantages and drawbacks.
+
+\subsection{Neural Arithmetic Logic Units}%
 \label{sub:neural_arithmetic_logic_unit}
 
-\citet{trask_neural_2018} have demonstrated how severe the extrapolation
-problem is even for the simplest arithmetic operations, such as summing or
-multiplying two numbers.  In order to increase the power of abstraction of NNs
-they propose a \emph{Neural Arithmetic Logic Unit} (NALU) which is capable of
-learning arithmetic addition, subtraction, multiplication, and division
-$\{+,-,\times,\div\}$ with stunning extrapolation accuracy.  However, the NALU
-comes with the severe limitation not being able to handle negative inputs due
-to the logarithm in the multiplication part of the NALU:
-
+\citet{trask_neural_2018} have demonstrated the severity of the extrapolation
+problem of dense networks for even the simplest arithmetic operations, such as
+summing or multiplying two numbers.  In order to increase the power of
+abstraction to for arithmetic tasks they propose the \emph{Neural Arithmetic
+Logic Unit} (NALU) which is capable of learning ($+,\times,\div$).  However,
+the NALU cannot handle negative inputs correctly due to the logarithm in
+Eq.~\ref{eq:nalu_mult}:
+\begin{definition}[{\bf NALU}]
+  The NALU consits of a ($+$) and a ($\times$) path that share their weights $\bm{\hat{W}}$ and $\bm{\hat{M}}$.
 \begin{align}
@@
   \text{Addition: }       & \bm a = \bm W \bm x
-                          & \bm W& = \tanh(\hat{\bm W}) \odot \sigma(\hat{\bm M}) \\
+                          & \bm{\hat W}& = \tanh(\bm{W}) \odot \sigma(\bm{M}) \\
   \label{eq:nalu_mult}
-  \text{Multiplication: } & \bm m = \exp \bm W(\log(|\bm x|+\epsilon)) & &\\
+  \text{Multiplication: } & \bm m = \exp \bm{\hat W}(\log(|\bm x|+\epsilon)) & &\\
   \text{Output: }         & \bm y = \bm a \odot \bm g + \bm m \odot (1-\bm g) 
@@
 \end{align}
-Additionally the NALU has severe convergence problems for small inputs due to
-a non-smooth loss surface close to zero, as shown by \cite{madsen_neural_2020}.
+\end{definition}
+Additionally, the logarithm destabilizes training to an extent that the chance of success
+can drop below 20\% for ($+,\times$), it becomes practically impossible to
+learn ($\div$), and difficult to learn from small inputs in general
+\citep{madsen_measuring_2019}.
+\cite{schlor_inalu_2020} provide a detailed description of the shortcomings of
+the NALU and they suggest an \emph{improved NALU} (iNALU).  The iNALU addresses
+the NALU's problems through a number of mechanisms.  It has independent
+addition and multiplication weights for Eq.~\ref{eq:nalu_add} and
+Eq.~\ref{eq:nalu_mult}, clips weights and gradients to improve training
+stability, regularizes the weights to push them away from zero, and, most
+importantly, introduces a mechanism to recover the sign that is lost due to the
+absolute value in the logarithm. Additionally, the authors propose to
+reinitialize the network if its loss is not improving during training.  We
+include the iNALU in one of our experiments and find that it only slightly
+improves the NALU's performance (Sec.~\ref{sub:simple_arithmetic_task}) at the
+cost of a significantly more complicated unit. Our NPU avoids all these mechanisms
+by internally using complex arithmetics.
 
-\todo{should this be here already?}
-With the simple exemplary task of learning a function $f:\mathbb R^2 \rightarrow \mathbb R^2$
-\begin{equation}
-  \label{eq:xx_xdivy}
-  f(\bm x) = f(x,y) = [xy,x/y] = \bm t
-\end{equation}
-we can demonstrate the strengths and weaknesses of the NALU.  The NALU only
-learns successfully if it is trained on positive numbers, so we train with
-samples from $\bm x \in \mathcal U^2(0.1,2)$ and plot the error $\epsilon =
-|\bm t - \hat{\bm t}|^2$ in Fig.~\ref{fig:simple_err}.
-
-\subsection{Neural Multiplication Unit}%
+\subsection{Neural Multiplication Unit \& Neural Addition Unit}%
 \label{sub:neural_multiplication_unit}
 
-A multiplication layer that can handle small and negative inputs was introduced
-by \citet{madsen_neural_2020}.  The \emph{Neural Multiplication Unit} (NMU) is
+Instead of trying to fix the NALU's convergence issues
+\cite{madsen_neural_2020} propose a new unit for ($\times$) only.
+The \emph{Neural Multiplication Unit} (NMU) uses explicit multiplications and learns
+to gate between identity and ($\times$) of inputs. The NMU is
 defined by Eq.~\ref{eq:nmu} and is typically used in conjunction with the
 so-called \emph{Neural Addition Unit} (NAU) in Eq.~\ref{eq:nau}.
+\begin{definition}[{\bf NMU \& NAU}]
+  NMU and NAU are two units that can be stacked to model ($+,\times$).
 \begin{align}
   \label{eq:nmu}
-  \text{NMU: } &y_j = \prod_i M_{ij} z_{i} + 1 - M_{ij}  &M_{ij}=\min(\max(M_{ij}, 0), 1)\\
+  \text{NMU: } &y_j = \prod_i \hat M_{ij} z_{i} + 1 - \hat M_{ij}  & \hat M_{ij}=\min(\max(M_{ij}, 0), 1)\\
   \label{eq:nau}
-  \text{NAU: } &\bm y = \bm A \bm x &A_{ij}=\min(\max(A_{ij}, 0), 1)
+  \text{NAU: } &\bm y = \bm{\hat{A}} \bm x & \hat A_{ij}=\min(\max(A_{ij}, -1), 1)
 \end{align}
-In both NMU and NAU the weights are clipped to $[0,1]$, and typically regularized
-with $\mathcal{R}$:
-\begin{align}
-  \label{eq:rsparse}
-  \mathcal{R} = \sum_{ij} \min(W_{ij}, 1-W_{ij})
-\end{align}
-
-The combination of NAU and NMU can thus learn $\{+,-,\times\}$, but no division.
-This is shown in Fig.~\ref{fig:simple_err} as well. The NMU
-can perfectly represent the multiplication of the two inputs, but fails at
-learning division.
-
-\todo{put this in acknowledgements
-all the results in this paper were create with the help of the following Julia
-packages: \cite{rackauckas_differentialequationsjl_2017} + (Flux.jl)}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.245\linewidth]{simple_err_add.pdf}
-  \includegraphics[width=0.245\linewidth]{simple_err_mult.pdf}
-  \includegraphics[width=0.245\linewidth]{simple_err_div.pdf}
-  \includegraphics[width=0.245\linewidth]{simple_err_sqrt.pdf}
-  \caption{Comparison of different models learning the function
-  $(x,y)\rightarrow(xy,x/y)$ with $(x,y)\in\mathcal U^2(0.1,2)$.  Each
-  plot shows the mean-squared error on a logarithmic color scale ($\hat{\bm
-  t}=\text{model}(\bm x)$).  The Dense network learns both multiplication and
-  division, but fails to extrapolate. NALU learns both tasks perfectly, but
-  completely fails if one of the inputs is negative.  The NMU successfully
-  learns multiplication, but not division. Only the NPU learns both tasks and
-  can extrapolate with an error that is less than $0.01$ in most places.}%
-  \label{fig:simple_err}
-\end{figure}
-\todo{add in depth experiment desc. of fig.~\ref{fig:simple_err} in appendix}
-\begin{table}
-  \centering
-  \caption{Comparison of different $2\times2$ layers on the task
-  $(x,y)\rightarrow(xy,\frac{x}{y})$.  $(x,y) \in \mathcal U^2(-2,2)$.}
-  \label{tab:simple_err}
-  \input{simple_err.tex}
-\end{table}
+\end{definition}
+Both NMU and NAU are regularized with $\mathcal{R} = \sum_{ij} \min(|W_{ij}|,
+|1-W_{ij}|)$ and their weights are clipped, which biases them towards learning
+an operation or pruning it completely.  The combination of NAU and NMU can thus
+learn $(+,\times)$ for both positive and negative inputs. Training NAU and NMU
+is stable and succeeds much more frequently than with the NALU, but they cannot
+represent ($\div$), which we address with our NPU.
 
@@
 
-Eq.~\ref{eq:nalu_mult} enables the NALU to learn multiplication. If the weight
-matrix $\bm W$ would not be restricted to values in the range $(-1,1)$ it could
-in principle learn arbitrary power functions, because
+To fix the deficiencies of current arithmetic units, we propose a new
+arithmetic unit (inspired by NALU) that can learn arbitrary power functions $(x^w)$ (including
+$\times,\div$) for positive and negative numbers, and still train well.
+Combined with the NAU we solve the full range of arithmetic operations.
+This is possible through a simple modification of the ($\times$)-path of the
+NALU (Eq.~\ref{eq:nalu_mult_2}).  We suggest to use the complex logarithm and
+to allow $\bm W$ to become complex.  The complex logarithm is also defined for
+negative inputs and a complex $\bm W$ aides convergence (see
+Sec.~\ref{sub:fractional_sir_model}). The improvement during training might be
+explained by the additional imaginary parameters that make it possible to avoid
+regions with an uninformative gradient signal.
+
+\subsection{Naive Neural Power Unit -- NaiveNPU}%
+\label{sub:naive_npu}
+
+With the modifications introduced above we can extend the multiplication path
+of the NALU from
 \begin{align}
-  z = \exp(w\log x) = x^w \text{ for } x>0.
+  \label{eq:nalu_mult_2}
+  \bm m = \exp \bm W(\log_{\text{real}}(|\bm x|+\epsilon))
 \end{align}
+to use the complex logarithm ($\log\coloneqq\log_{\text{complex}}$) and a
+complex weight $\bm W$ to
+\begin{align}
+  \label{eq:1}
+  \bm z = \exp(\bm W\log \bm x) = \exp\left((\bm \Wre + i\Wim) \log\bm x\right).
+\end{align}
+The complex log in Eq.~\ref{eq:1} lifts the positivity constraint on $\bm x$ resulting
+in a layer that can process both positive and negative numbers correctly.  A complex
+weight matrix $\bm W$ somewhere in a larger network would result in complex
+gradients in other layers.  This would effectively result in doubling the
+number of parameters of the whole network. As we are only interested in real
+networks outputs, we can avoid this doubling by considering only the real part
+of the output $\bm z$:
+\begin{align}
+  \real(\bm z) &= \real(\exp((\Wre + i\Wim)(\log\bm r + i\pi\bm k))) \\
+    \label{eq:npumult}
+    &= \exp(\Wre\log\bm r - \pi\Wim\bm k) \odot \cos(\Wim\log\bm r + \pi\Wre\bm k).
+\end{align}
+Above we have used Euler's formula\footnote{Euler's formula states that for any
+real number $x$: $e^{ix} = \cos x + i\sin x$} and the fact that the complex
+logarithm for real valued inputs is
+\begin{align}
+  \log x = \log r + i\theta = \log r + ik\pi,
+\end{align}
+where $k=0$ if $r\geq0$ and $k=1$ if $r<0$.
+A diagram of the NaiveNPU is shown in Fig.~\ref{fig:npu_diagram}.
+\begin{definition}[{\bf NaiveNPU}]
+  The Naive Neural Power Unit with matrices $\Wre$ and
+  $\Wim$ representing real and imaginary part of the complex numbers defined as
+  \begin{gather}
+    \label{eq:naivenpu_def}
+    \bm z = \exp(\Wre \log\bm r - \Wim\bm k) \odot \cos(\Wim\log \bm r + \Wre\bm k), \text{ where }\\
+    \nonumber
+    \bm r = |\bm x|,
+    \quad
+    k_i = \begin{cases}
+       0  & x_i \leq 0 \\
+       \pi & x_i > 0
+    \end{cases}
+  \end{gather}
+\end{definition}
 
-However, this would complicate the convergence issues of the NALU even more.
-We therefore suggest to leverage the power of the complex plane, by using the
-complex logarithm and by promoting $w$ to a complex number.  This will enable
-us not only to lift the positivity constraint on $x$, but also provides and
-additional dimension that helps to avoid regions with an uninformative gradient
-signal\todo{rephrase this. do we have an educating example where it is obvious
-that complex plane helps? the stuff in fig.1 does not work as well with
-non-complex NPU, but I have not idea how to plot that}.  Introducing a complex
-weight matrix somewhere in a larger network would mean that the gradients in
-other layers would potentially become complex as well, which would result in
-converting the whole network to complex numbers.  This seems like a high price
-to pay, but fortunately there is a way around this.  We can output only the
-real part of the result $\real(z)$, but still maintain a complex $w$ by
-treating it as a sum of real and imaginary part $w=\wre+i\wim$. We are thus
-interested in
+\begin{figure}
+  \begin{minipage}{.45\textwidth}
+      \resizebox{0.9\textwidth}{!}{\input{../tikz/npu-diagram.tex}}
+      \captionof{figure}{NaiveNPU diagram, with input $\bm x$ and output $\bm y$.
+      Vectors in green, trainables in orange, functions in blue.}
+      \label{fig:npu_diagram}
+  \end{minipage}
+  \hspace{0.01\textwidth}
+  \begin{minipage}{0.54\textwidth}
+    \resizebox{\textwidth}{!}{\input{../tikz/gatednpu-diagram.tex}}
+    \captionof{figure}{NPU diagram. The NPU has a relevance gate $\bm g$
+    (hatched background) in front of the input to the actual unit to prevent
+    vanishing gradients.}
+    \label{fig:gatednpu_diagram}
+  \end{minipage}
+\end{figure}
+
+\subsection{The Relevance Gate -- NPU}%
+\label{sub:npu}
+
+The NaiveNPU has difficulties to converge on large scale tasks, and to reach
+sparse results in cases where the input to a given row is small. We
+demonstrate this on a toy example of learning the identity on one of two inputs
+(neglecting the second one):
 \begin{align}
-  \label{eq:exp_w_log_complex}
-  \real(z) &= \real(\exp(w\log x)),
+  \nonumber
+  \mathcal{L} &= |\text{m}(x_1,x_2) - x_1|, \quad \text{where}
+  & \text{m} = \npu(2,1), \quad
+  &x_1 \sim \mathcal U(0,2), \quad x_2 \sim \mathcal U(0,0.05).
 \end{align}
-with a real input $x$. The complex logarithm is defined as $\log z=\log r +
-i\theta$, which, for real inputs $x$, can be simplified to $\log z = \log r +
-ik\pi$, where $k\in \{0,1\}$. With that Eq.~\ref{eq:exp_w_log_complex} can be
-rewritten to
+The left plot in Fig.~\ref{fig:id_loss} depicts
+the the norm of gradient of a batch of two dimensional inputs, one of which is small and
+irrelevant. It is clearly visible that even for this simple example, a large
+part of the gradient surface of the NaiveNPU is zero.  This vanishing gradient can be explained
+as follows. One row of NaiveNPU weights effectively raises each input to a power and
+multiplies them: $x_1^{w_1} x_2^{w_2} \dots x_n^{w_n}$. If a single input $x_i$
+is constantly close to zero (i.e. irrelevant), the whole row will be zero, no
+matter what its weights are and the gradient information on all other weights
+is lost.  We therefore introduce a gate on the input of the NPU that can turn
+irrelevant inputs into 1s.
+A diagram of the NPU is shown in Fig.~\ref{fig:gatednpu_diagram}.
+\begin{definition}[{\bf NPU}]
+  The NPU extends the NaiveNPU by the relevance gate $\bm g$ on the input $\bm x$.
+   \begin{gather}
+    \label{eq:gatednpu_def}
+    \bm z = \exp(\Wre \log\bm r - \Wim\bm k) 
+          \odot \cos(\Wim\log \bm r + \Wre\bm k), \text{ where } \\
+    \bm r = \bm{\hat g} \odot |\bm x| + (1-\bm{\hat g}),
+    \quad
+    k_i = \begin{cases}
+       0  & x_i \leq 0 \\
+      \hat g_i\pi & x_i > 0
+    \end{cases},
+    \quad
+    \hat g_i = \min(\max(g_i,0),1)
+  \end{gather}
+\end{definition}
+\begin{figure}
+  \centering
+  \begin{minipage}{0.55\textwidth}
+    \includegraphics[width=\textwidth]{npu_gatednpu_id_grad.pdf}
+  \end{minipage}
+  \begin{minipage}{0.42\textwidth}
+  \end{minipage}
+  \caption{Absolute value of a gradient of NaiveNPU and NPU for the task
+  of learning the identity on $x_1$. Inputs and
+  loss are defined on the right, gradient surfaces on the left
+  (black areas are beyond the color scale). The correct solution is
+  $w_1=1$ and $w_2=0$.  The NaiveNPU has a large zero gradient region for
+  $w_2>0.75$, while the NPU's surface is much more informative. The gates
+  for central plot are fixed at $g_1=g_2=0.5$ which corresponds to the initial
+  gate parameters. During training they will adjust as needed, in this case to
+  $g_1=1$ and $g_2=0$. $\bm W_i$ is set to zero in all plots.
+  }%
+  \label{fig:id_loss}
+\end{figure}
+The central plot of Fig.~\ref{fig:id_loss} shows the gradient of the NPU
+on the identity task with its initial gate setting of $g_1=g_2=0.5$. The
+large zero-gradient region of the NaiveNPU is gone. The last plot shows the
+same loss for $g_1=1$ and $g_2=0$, which corresponds to the correct gates at
+the end of NPU training. The gradient is independent of $w_2$, which
+means that it can easily be pruned by a simple regularization such as L1.  In
+Sec.~\ref{sub:large_scale_arithmetic_task} we show how important the relevance
+gating mechanism is for the convergence and sparsity of large models.  Sparsity
+is especially important in order to use the NPU as an interpretable model.
+
+\subsection{Initialization}%
+\label{sub:initialization}
+We recommend to initialize the NPU with a Glorot Uniform distribution on the
+real weights $\Wre$. The imaginary weights $\Wim$ can be initialized to zeros,
+so they will only be used where necessary, and the gate $\bm g$ with 0.5, so
+the NPU can choose to output 1.
+\todo{should this be longer? or not a section at all?}
+
+\section{Experiments}%
+\label{sec:experiments}
+
+In Sec.~\ref{sub:fractional_sir_model} we show how the NPU can be used as a
+highly interpretable model which can extract the generating equation of an ODE
+that contains fractional powers.
+In Sec.~\ref{sub:simple_arithmetic_task}\,\&\,\ref{sub:large_scale_arithmetic_task}
+we provide experiments on standard arithmetic tasks in which the NPU outperforms
+the NALU in all tasks.
+
+\subsection{Equation Discovery of an Epidemiological Model}%
+\label{sub:fractional_sir_model}
+\todo{other titles: Discovering the Equations of an Epidemic}
+
+Data-driven models such as \emph{SINDy}~\citep{champion_data-driven_2019} or
+\emph{Neural Ordinary Differential Equations} (NODE, \cite{chen_neural_2019})
+are used more and more in scientific applications.
+Recently, \emph{Universal Differential Equations} (UDEs,
+\cite{rackauckas_universal_2020}) were introduced which aim to combine
+data-driven models with physically informed differential equations to maximize
+explainability of the resulting models.
+NODEs and UDEs can be tricky to fit, because they run into the same
+difficulties as RNNs like vanishing gradients and bifurcations. With this
+experiment we want to demonstrate that the NPU works reliably in such settings,
+despite the convergence issues that its predecessor (the NALU) has -
+even for non-sequential tasks.
+If an ODE contains parameters that cannot easily be modelled by dense layers,
+the NPU can be a good choice because of its ability to learn any power
+function.  Additionally, if interpretability of the result is important, the
+NPU can be used recover the generating ODE because of its interpretable design,
+instead of trying to explain a black box model in retrospect.
+
+An example of an ODE that contains powers is the fractional SIR model (fSIR,
+\cite{taghvaei_fractional_2020}).  The classical SIR model is built from three
+quantities of interest: $S$ (susceptible), $I$ (infectious), and $R$
+(recovered/removed).  Arguably the most important part of the model is the
+transmission rate $r$, which is typically taken to be proportional to the
+product of $S$ and $I$.  \citet{taghvaei_fractional_2020} argue that,
+especially in the initial phase of an epidemic, the boundary areas of infected
+and susceptible cells scale with a fractional power, which leads to
+Eq.~\ref{eq:fracsir_r}:
 \begin{align}
-  \real(z) &= \real(\exp((\wre + i\wim) (\log r + ik\pi))) \\
-    &= \exp(\wre\log r - \wim k\pi) \cos(\wim\log r + k\pi\wre),
+  \label{eq:fracsir}
+  \frac{dS}{dt} &= -r(t) + \eta R(t), &
+  \frac{dI}{dt} &=  r(t) - \alpha I(t), &
+  \frac{dR}{dt} &= \alpha I(t) - \eta R(t),\\
+  \label{eq:fracsir_r}
+  & & r(t) &= \beta I(t)^\gamma S(t)^\kappa,
 \end{align}
-where we used Euler's formula\footnote{Euler's formula states that for any real
-number $x$: $re^{ix} = \cos x + i\sin x$}.
-\todo{explicitly compute gradients?}
+We solve the fSIR model numerically with the parameters $\alpha=0.05$,
+$\beta=0.06$, $\eta=0.01$, $\gamma=\kappa=0.5$, and 40 datapoints that are
+equally spaced in the time interval $T=(0,200)$. The initial conditions are set
+to $S_0=100$, $I_0=0.01$, and $R_0=0$.
 
-\subsection{Neural Power Unit (NPU)}%
-\label{sub:neural_power_unit_npu_}
+We fit the fSIR model with three different model types: a dense network, the
+NPU, and an NPU with imaginary weights fixed to zero (further referred to as
+\emph{real NPU}). An exemplary model is: $\npu=\chain(\npu(3,h),\nau(h,3))$
+with variable hidden size $h$.  The detailed models are defined in
+Tab.~\ref{tab:fsir_models}. The training objective is the loss $\mathcal{L}$
+with L1 regularization.
+\begin{align}
+  \label{eq:sir_loss}
+  \mathcal{L} = \text{MSE}(\bm t,\text{model}(\bm u_0)) + \beta||\bm\theta||_1.
+\end{align}
+We train each model for 3000 steps with the ADAM optimizer and a learning rate
+of 0.005, and after that with LBFGS until convergence (or for maximum 1000
+steps).  For each model type we run a small grid search to build a Pareto front
+with $h\in \{6,9,12,15,20\}$ and $\beta\in\{0,0.01,0.1,1\}$, where each
+hyper-parameter pair is run five times. The resulting Pareto front is shown on
+the left of Fig.~\ref{fig:pareto_sir}. The NPU clearly reaches much sparser and
+better solutions than the dense network.
+The real NPU has problems to converge in the majority of cases.
+However, there are a few models in the bottom left that
+reach a very low MSE and have very few parameters. The best these models is
+shown in Fig.~\ref{fig:sir_gatednpu_modelps}.  It looks strikingly similar to
+the fSIR model in matrix from:
+\renewcommand*{\arraystretch}{1.3}
+\begin{equation}
+  \begin{bmatrix}
+    \dot S \\ \dot I \\ \dot R
+  \end{bmatrix}
+  =
+  \begin{bmatrix}
+    -\beta & 0 & \eta \\
+    \beta & -\alpha & 0 \\
+    0 & \alpha & \eta
+  \end{bmatrix}
+  \begin{bmatrix}
+    I^\gamma S^\kappa \\ I \\ R
+  \end{bmatrix}.
+\end{equation}
+Reading Fig.~\ref{fig:sir_gatednpu_modelps} from right to left, we can extract
+the ODE that the real NPU represents.  It identified the transmission rate
+correctly as a product of two fractional powers $r = I^\gamma S^\kappa$ with
+$\kappa=0.57$ and $\gamma=0.62$, which is close to the true values
+$\gamma=\kappa=0.5$.  In the second layer the NAU combines the correct hidden
+outputs from the NPU such that $\dot S$ is composed of the negative
+transmission rate $r$ and positive $R$.  $\dot I$ and $\dot R$ are also
+composed from the correct hidden variables, with the parameters
+$\alpha,\beta,\eta$ being not far off from the truth.
+We conclude that even with this very naive approach the real NPU is able to
+recover a fractional SIR model.
+\begin{figure}
+  \centering
+  \resizebox{.7\textwidth}{!}{\input{../plots/pareto_sir.tex}}
+  \caption{Pareto fronts of the dense network, the NPU, and the NPU
+  with imaginary weights fixed to zero. The NPU reaches solutions with lower
+  MSE and fewer parameters than the dense net. The real NPU mostly yields
+  worse results than the NPU, just in a few cases it converges to very sparse
+  models with good MSE.}%
+  \label{fig:pareto_sir}
+\end{figure}
+\begin{figure}
+  \centering
+  \includegraphics[width=.6\linewidth]{../plots/sir_gatednpu_modelps.pdf}
+  \captionof{figure}{Visualization of the best real NPU. Reading from right
+  to left, it takes the SIR variables as an input, then applies the NPU and
+  the NAU.  It correctly identifies $r$ as a fractional product in the NPU,
+  and gets the rest of the fSIR parameters almost right in the NAU.}%
+  \label{fig:sir_gatednpu_modelps}
+\end{figure}
+\\
+In summary, the NPU clearly works well in sequential tasks, and we have shown
+that we can reach highly interpretable results with the real NPU, but in practice,
+using the real NPU might be difficult due to its lower success rate. With a more
+elaborate analysis it might be possible to reach the same solutions with the
+full NPU and e.g. a strong regularization of its imaginary parameters.
+
+\subsection{Simple Arithmetic Task}%
+\label{sub:simple_arithmetic_task}
+
+In this experiment we demonstrate the capabilities of five different
+layers (NPU, NMU, NALU, iNALU, Dense) on a small problem with two inputs
+and four outputs. The objective is to learn the function $f: \mathbb{R}^2
+\rightarrow \mathbb{R}^4$ with a standard MSE loss:
+\begin{align}
+  \label{eq:simple_f}
+  f(x,y) &= (x+y,\, xy,\, x/y,\, \sqrt{x} \text{  })^T \eqqcolon \bm t, \\
+  \mathcal L &= \frac{1}{4} \sum_{i=1}^{n=4}\left(\text{model}(x,y)_i - f(x,y)_i\right)
+             = \text{MSE}(\bm{\hat t}, \bm t).
+\end{align}
+Each model has two layers with a hidden dimension $h=6$.  E.g. the NPU model is
+defined by $\npu=\chain(\npu(2,6),\nau(6,4))$.  The remaining models that are
+used in the tables and plots are given in Tab.~\ref{tab:models_simple_task}.
+To obtain valid results in case of division we train on positive, non-zero
+inputs, but test on negative, non-zero numbers (except for test inputs to the
+square-root):
+\begin{align}
+  \label{eq:simple_train}
+  (x_{\text{train}}, y_{\text{train}}) &\sim \mathcal{U}(0.1,2) &
+  (x_{\text{test}}, y_{\text{test}}) &\sim \mathcal{R}(\text{-4.1:0.2:4}) &
+  (x_{\text{test,\,sqrt}}, y_{\text{test,\,sqrt}}) &\sim \mathcal{R}(\text{0.1:0.1:4})
+\end{align}
+where $\mathcal{R}$ denotes a \emph{range} with start, step, and end.
+We train each model for 20\,000 steps with the ADAM optimizer, a learning rate of
+0.001, and a batch size of 100. The input samples are generated on the fly
+during training. Fig.~\ref{fig:simple_err} shows the error surface of the best
+of 20 models on each task. Tab.~\ref{tab:simple_err} lists the corresponding
+averaged testing errors of all 20 models.
+
+The NPU successfully learns ($+,\times,\div,\sqrt{\cdot}$) and clearly
+outperforms NALU and iNALU on all tasks.  The NPU is on par with the NMU for
+($+$), but the NMU is better at ($\times$) due to its inductive bias. The NMU
+cannot learn ($\div,\sqrt{\cdot}$). The NPU excels at extrapolation on all tasks.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\linewidth]{simple_err.pdf}
+  \caption{Comparison of different models learning Eq.~\ref{eq:simple_f}. Each
+  column represents the best model of 20 runs.  The dense network learns all
+  tasks, but fails to extrapolate. NALU and iNALU are better at extrapolating
+  to positive numbers, but fail if one of the inputs is negative.  The NMU
+  successfully learns ($+,\times$), but not ($\div,\sqrt{\cdot}\,$). Only the NPU
+  learns all tasks and can extrapolate both to positive and negative numbers.
+  }%
+  \label{fig:simple_err}
+\end{figure}
+
+\subsection{Large Scale Arithmetic Task}%
+\label{sub:large_scale_arithmetic_task}
+
+One of the most important properties of a layer in a neural network is its
+ability to scale. With the large scale arithmetic task we show that the NPU
+works reliably on many-input tasks that are heavily over-parametrized.  In this
+section we compare NALU, NMU, NPU, and the NaiveNPU on a task that is identical
+to the `arithmetic task' that \cite{madsen_neural_2020} and
+\cite{trask_neural_2018} analyse as well.
+The goal is to sum two subsets of a 100 dimensional vector and
+apply an operation (like $\times$) to the two summed subsets.  The dataset
+generation is defined in the set of Eq.~\ref{eq:large_scale_def}, with the
+parameters from Tab.~\ref{tab:dataset_params_large_scale}.
+\begin{align}
+  \label{eq:large_scale_def}
+  a = \sum_{i=s_{1,\text{start}}}^{s_{1,\text{end}}} x_i, &&
+  b = \sum_{i=s_{2,\text{start}}}^{s_{2,\text{end}}} x_i, &&
+  t_{\text{add}} = a + b, && t_{\text{mul}} = a \times b, &&
+  t_{\text{div}} = 1 / a, && t_{\text{sqrt}} = \sqrt{a},
+\end{align}
+where starting and
+ending values $s_{i,\text{start}},s_{i,\text{end}}$ of the summations are chosen
+such that $a$ and $b$ come from subsets of the input vector $\bm x$ with a
+given overlap.  Specifics of the used models are defined in
+Tab.~\ref{tab:models_large_task}.  \cite{madsen_neural_2020} perform an
+extensive analysis of this task with different subset and overlap ratios,
+varying model and input sizes, and much more, establishing that the combination
+of NAU/NMU outperforms the NALU. We focus on the
+comparison of NPU, NMU, and NALU on the default parameters of
+\cite{madsen_neural_2020} which sets the subset ratio to 0.5 and the overlap
+ratio to 0.25 (details in Tab.~\ref{tab:dataset_params_large_scale}).
+We also compare to the NaiveNPU (without the relevance gate) to show
+how important the gating mechanism is for both sparsity and overall
+performance.
+
+Fig.~\ref{fig:pareto} plots training and testing errors over the number of
+non-zero parameters for all models and tasks.
+The addition column shows that all models except NaiveNPU learn ($+$) on the
+training set, with the NMU converging to the sparsest models. The NMU also
+performs best on the testing set, with the NPU as a close second.\\
+On ($\times$), the best NMU models also outperform the NPU, but some of
+them do not converge at all, which is why the NPU has a better testing MSE on
+average (see also Tab.~\ref{tab:arithmetic100_val}). The testing MSE of the
+NALU is so large that is excluded from the plot.\\
+On ($\div,\sqrt{\cdot}$) the NPU clearly outperforms all other layers
+in MSE and sparsity. Generally, the difference between the NaiveNPU and the NPU
+is very significant and demonstrates how important the relevance gate is both
+for convergence and sparsity. The NPU effectively converts irrelevant inputs
+to 1s, while the NaiveNPU is stuck on the zero gradient plateau.
 
@@
   \centering
-  \resizebox{.3\textwidth}{!}{\input{../plots/exp_log_sin/log_comp.tikz.tex}}
-  \resizebox{.3\textwidth}{!}{\input{../plots/exp_log_sin/exp_comp.tikz.tex}}
-  \resizebox{.3\textwidth}{!}{\input{../plots/exp_log_sin/sin_comp.tikz.tex}}
-  \caption{Function learning comparison of different layers.}%
-  \label{fig:sin_comp}
+  \resizebox{\textwidth}{!}{\input{../plots/pareto.tex}}
+  \caption{Validation MSE over number of non-zero parameters ($w_i > 0.001$) of the large scale
+  arithmetic task.  Again, the NMU outperforms the NPU on its
+  native tasks, addition and multiplication. The NPU is the best at division
+  and square-root.  The NaiveNPU without the relevance gate is far off, because
+  it does not have the necessary gradient signal to converge, as discussed in
+  Sec.~\ref{sub:npu}}%
+  \label{fig:pareto}
 \end{figure}
 
-The \emph{Neural Power Unit} (NPU) with two weight matrices $\Wre$ and $\Wim$
-then reads
-\begin{align}
-  \bm r = |\bm x|,
-  \hspace{1cm}
-  & k_i = \begin{cases}
-     0  & x_i \leq 0 \\
-    \pi & x_i > 0
-  \end{cases}
-\end{align}
-\begin{align}
-  \bm z &= \exp(\Wre \log\bm r - \Wim\bm k) \odot \cos(\Wim\log \bm r + \Wre\bm k)
-\end{align}
-where $\bm k$ is a vector that is zero where $\bm x$ is positive and $\pi$
-where it is negative, $\bm r$ is the element-wise absolute value.
-In the final network we are only interested in real powers, so we recommend to
-strongly regularize the imaginary part of the weights $\Wim$.
+\begin{table}
+  \centering
+  \caption{Testing errors of the large scale arithmetic task.}
+  \label{tab:arithmetic100_val}
+  \input{../plots/arithmetic100_val.tex}
+\end{table}
 
-\subsection{Gated NPU}%
-\label{sub:gated_npu}
-As pointed out by \cite{madsen_neural_2020}, the loss surface of the NALU, and
-thus also the NPU, is not always smooth. For some input and weight combinations
-it can happen that the loss close to zero becomes very large as shown in
-Fig.~\ref{fig:task_loss_npu_nmu}.
-\begin{figure}
-  \centering
-  \includegraphics[width=0.8\linewidth]{task_loss_npu_nmu.pdf}
-  \caption{asdf}%
-  \label{fig:task_loss_npu_nmu}
-\end{figure}
-However, most applications are dealing with batches of data which average out
-these cases, as shown in Fig.~\ref{fig:task_loss_npu_nmu_average} for a batch
-size of 32.
-\begin{figure}
-  \centering
-  \includegraphics[width=0.8\linewidth]{task_loss_npu_nmu_average.pdf}
-  \caption{asdfadsf}%
-  \label{fig:task_loss_npu_nmu_average}
-\end{figure}
+\section{Conclusion}%
+\label{sec:conclusion}
 
-In practice we encountered difficulties of obtaining sparse solutions with the
-NPU. If the inputs to an NPU unit are small, the gradient becomes practically
-zero, as we can see in Fig.~\ref{fig:id_loss_npu_nmu}
-\begin{figure}
-  \centering
-  \includegraphics[width=0.8\linewidth]{id_loss_npu_nmu.pdf}
-  \caption{learning identity with small inputs}%
-  \label{fig:id_loss_npu_nmu}
-\end{figure}
+We introduced the \emph{Neural Arithmetic Unit} that addresses the deficiencies
+of current arithmetic units: it can learn arbitrary power functions for
+positive, negative, and small numbers. We showed that the NPU outperforms its
+main competitor (NALU) and reaches performance that is on par with the
+multiplication specialist NMU.  For tasks that are known to contain only
+addition and multiplication a stack of NAU and NMU can be a better choice than
+the NPU, because they might be easier to train. For more complicated problems
+that involve division or power functions, the NPU is the better choice.
 
-\section{Experimetns}%
-\label{sec:experimetns}
-This can be demonstrated by training a traditional, dense NN to approximate
-three functions
-\begin{align}
-  \label{eq:approx_tasks}
-  f(x) = e^x, && g(x) = \log(x), && h(x) = \sin(x)
-\end{align}
+Additionally we have demonstrated how the NPU can be used as an interpretable
+model that can recover governing equations of dynamical systems purely from
+data.
 
-Neural Arithmetic Units aim to overcome this problem with units that are able
-to represent simple arithmetic operations exactly. By composition of these
-units it becomes possible to learn e.g. exponentials, logarithms, and power
-functions. This promises to improve on the extrapolation capabilities of NNs
-even on tasks that are beyond artificial arithmetic tasks such as learning
-multiplication, or a certain power function \todo{cite some examples}.
+\section{Statement of Broader Impact}%
+\label{sec:statement_of_broader_impact}
 
-\subsection{10 param func}%
-\label{sub:10_param_func}
+Current neural network architectures can be problematic because they are black
+box models that are difficult to interpret. This becomes highly problematic if
+ML models are involved in high stakes decisions in e.g. criminal justice,
+healthcare, or control systems that affect lives.  With the NPU we hope to
+contribute to the broad topic of interpretable machine learning, with a focus
+on scientific applications.
 
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.8\linewidth]{10-param-func-task-nmu-paper.pdf}
-%   \caption{MSE optimization result}%
-%   \label{fig:10-param-func-task-nmu-paper}
-% \end{figure}
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.8\linewidth]{10-param-func-bayes-task-nmu-paper.pdf}
-%   \caption{ARD result with MSE starting point}%
-%   \label{fig:10-param-func-bayes-task-nmu-paper}
-% \end{figure}
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.8\linewidth]{10-param-func-bayes-task-nmu-paper-history.pdf}
-%   \caption{ARD history}%
-%   \label{fig:history}
-% \end{figure}
-% 
-% \subsection{10 param func with sqrt and power}%
-% \label{sub:10_param_func_with_sqrt_and_power}
-% 
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.8\linewidth]{10-param-func-task-sqrt-power.pdf}
-%   \caption{10-param-func-task-sqrt-Power}%
-%   \label{fig:10-param-func-task-sqrt-power}
-% \end{figure}
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.8\linewidth]{10-param-func-bayes-task-sqrt-power.pdf}
-%   \caption{10-param-func-bayes-task-sqrt-Power}%
-%   \label{fig:10-param-func-bayes-task-sqrt-power}
-% \end{figure}
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.8\linewidth]{10-param-func-bayes-task-sqrt-power-history.pdf}
-%   \caption{10-param-func-bayes-task-sqrt-Power-history}%
-%   \label{fig:10-param-func-bayes-task-sqrt-power-history}
-% \end{figure}
+Additionally, learning to abstract (mathematical) ideas and extrapolate is a
+fundamental goal that might contribute to more reliable machine learning
+systems.
 
-\subsection{Gradient surfaces}%
-\label{sub:gradient_surfaces}
-% \begin{figure}
-%   \centering
-%   %\includegraphics[width=0.8\linewidth]{../plots/test.pgf}
-%   \input{../plots/test.tikz.tex}
-%   \caption{Test}%
-%   \label{fig:test}
-% \end{figure}
+\section{Acknowledgements}%
+\label{sec:acknowledgements}
+
+We thank the authors of the Julia packages
+Flux.jl~\citep{innes_fashionable_2018} and
+DifferentialEquations.jl~\citep{rackauckas_differentialequationsjl_2017}).
 
@@
 
+\appendix
+\section*{Appendix}%
+\label{sec:appendix}
+
+\setcounter{table}{0}
+\renewcommand{\thetable}{A\arabic{table}}
+
+\begin{table}[h]
+  \centering
+  \caption{Validation error of the different models (i.e. mean of each heatmap
+  in Fig.~\ref{fig:simple_err}). Each value is obtained by averaging the error
+  of 20 models.
+  }
+  \label{tab:simple_err}
+  \input{../plots/simple_err.tex}
+\end{table}
+
+\begin{table}[h]
+  \centering
+  \caption{Model definitions for the simple arithmetic task}
+  \label{tab:models_simple_task}
+  \begin{tabular}{llll}
+    \toprule
+    Model & Layer 1 & Layer 2 & Layer 3 \\
+    \midrule
+    NPU & NAU(2,\,6) & NPU(6,\,2) & -- \\
+    NMU & NAU(2,\,6) & NMU(6,\,2) & -- \\
+    NALU & NALU(2,\,6) & NALU(6,\,2) & -- \\
+    iNALU & iNALU(2,\,6) & iNALU(6,\,2) & -- \\
+    Dense & Dense(2,\,10,\,\sigma) & Dense(10,\,10,\,\sigma) & Dense(10,\,2) \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\begin{table}[h]
+  \caption{Model definitions for the large scale arithmetic task}
+  \label{tab:models_large_task}
+  \begin{tabular}{llll}
+    \toprule
+    Model & Layer 1 & Layer 2\\
+    \midrule
+    NPU & NAU(100,\,100) & NPU(100,\,1) \\
+    NPU & NAU(100,\,100) & NPU(100,\,1) \\
+    NMU & NAU(100,\,100) & NMU(100,\,1) \\
+    NALU & NALU(100,\,100) & NALU(100,\,1) \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\begin{table}[h]
+  \centering
+  \caption{Dataset parameters for the large scale arithmetic task.}
+  \label{tab:dataset_params_large_scale}
+  \begin{tabular}{lccccc}
+    \toprule
+    Task & Input size & Subset ratio & Overlap ratio & Training range  & Validation range\\
+    \midrule
+    Add  & 100        & 0.5          & 0.25          & Sobol(-1,1)     & Sobol(-4,4) \\
+    Mult & 100        & 0.5          & 0.25          & Sobol(-1,1)     & Sobol(-4,4)\\
+    Div  & 100        & 0.5          & --            & Sobol(0,0.5)    & Sobol(-0.5,0.5) \\
+    Sqrt & 100        & 0.5          & --            & Sobol(0,2)      & Sobol(0,4) \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\begin{table}[h]
+  \centering
+  \caption{fSIR model definitions}
+  \label{tab:fsir_models}
+  \begin{tabular}{llll}
+    \toprule
+    Model & Layer 1 & Layer 2 & Layer 3 \\
+    \midrule
+    NPU & $\npu(3,\,h)$ & $\nau(h,\,3)$ & -- \\
+    NPU & NPU$_{\text{real}}(3,\,h)$ & $\nau(h,\,3)$ & -- \\
+    Dense & $\dense(2,\,h,\sigma)$ & $\dense(h,\,h,\,\sigma)$ & $\dense(h,\,3)$ \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
 \end{document}

### 2020-06-02 papers/main.tex
pdflatex

@@
     iNALU & iNALU(2,\,6) & iNALU(6,\,2) & -- \\
-    Dense & Dense(2,\,10,\,\sigma) & Dense(10,\,10,\,\sigma) & Dense(10,\,2) \\
+    Dense & Dense(2,\,10,\,$\sigma$) & Dense(10,\,10,\,$\sigma$) & Dense(10,\,2) \\
     \bottomrule

### 2020-06-02 plots/pareto.tex
plots

\begin{tikzpicture}[/tikz/background rectangle/.style={fill={rgb,1:red,1.0;green,1.0;blue,1.0}, draw opacity={1.0}}, show background rectangle]
\begin{axis}[point meta max={nan}, point meta min={nan}, legend cell align={left}, title={}, title style={at={{(0.5,1)}}, anchor={south}, font={{\fontsize{14 pt}{18.2 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, legend style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid, fill={rgb,1:red,1.0;green,1.0;blue,1.0}, fill opacity={1.0}, text opacity={1.0}, font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, at={(1.02, 1)}, anchor={north west}}, axis background/.style={fill={rgb,1:red,1.0;green,1.0;blue,1.0}, opacity={1.0}}, anchor={north west}, xshift={1.0mm}, yshift={-1.0mm}, width={55.15mm}, height={48.8mm}, scaled x ticks={false}, xlabel={Nr. Parameters}, x tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, x tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, xlabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, xmode={log}, log basis x={10}, xmajorgrids={true}, xmin={76.74464101797544}, xmax={14403.350974579345}, xtick={{100.0,316.22776601683796,1000.0,3162.2776601683795,10000.0}}, xticklabels={{$10^{2.0}$,$10^{2.5}$,$10^{3.0}$,$10^{3.5}$,$10^{4.0}$}}, xtick align={inside}, xticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, x grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis x line*={left}, x axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}, scaled y ticks={false}, ylabel={Testing MSE}, y tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, y tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, ylabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, ymode={log}, log basis y={10}, ymajorgrids={true}, ymin={0.0005672734950819899}, ymax={291455.14136474277}, ytick={{0.01,1.0,100.0,10000.0}}, yticklabels={{$10^{-2}$,$10^{0}$,$10^{2}$,$10^{4}$}}, ytick align={inside}, yticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, y grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis y line*={left}, y axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}]
    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={8432bdbe-b384-493b-a894-2ca9aed19dd4}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
        coordinates {
            (1212.0,0.0044327993)
            (633.0,0.025323598)
            (2198.0,0.07513304)
            (1414.0,0.07950895)
            (1045.0,0.08757629)
            (423.0,0.09544645)
            (172.0,0.12249249)
            (1131.0,0.12339931)
            (976.0,0.148304)
            (1970.0,0.14878139)
        }
        ;
    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={19c422f2-2c28-4773-bff4-dbd0b472008a}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
        coordinates {
            (10169.0,398.8512385486777)
            (10217.0,416.529448488352)
            (10157.0,429.61028780569137)
            (12420.0,487.83743759498134)
            (10159.0,621.4133164105747)
            (10246.0,858.7089297238343)
            (11411.0,1077.5153824358792)
            (10300.0,1486.1756888766222)
            (10184.0,1651.9431386116044)
            (11284.0,9942.065087422989)
        }
        ;
    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={2a7cf6d3-80f4-4533-929d-ea31232589ab}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
        coordinates {
            (4109.0,0.0010007463)
            (89.0,0.0036541214)
            (90.0,0.0039218063)
            (89.0,0.005820834)
            (90.0,0.00598223)
            (189.0,0.006059413)
            (91.0,0.006182335)
            (90.0,0.006198649)
            (3228.0,0.006199132)
            (90.0,0.043522302)
        }
        ;
    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={b82a4fdf-f8e3-4a56-bc52-e5e1e40eaa88}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
        coordinates {
            (9878.0,161.49628)
            (9879.0,161.5955)
            (9852.0,161.59552)
            (9837.0,161.59552)
            (9836.0,161.59557)
            (9944.0,161.70662)
            (9854.0,186.75471)
            (9861.0,250.42944)
            (9933.0,388.22473)
            (9870.0,165211.48)
        }
        ;
\end{axis}
\begin{axis}[point meta max={nan}, point meta min={nan}, legend cell align={left}, title={}, title style={at={{(0.5,1)}}, anchor={south}, font={{\fontsize{14 pt}{18.2 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, legend style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid, fill={rgb,1:red,1.0;green,1.0;blue,1.0}, fill opacity={1.0}, text opacity={1.0}, font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, at={(1.02, 1)}, anchor={north west}}, axis background/.style={fill={rgb,1:red,1.0;green,1.0;blue,1.0}, opacity={1.0}}, anchor={north west}, xshift={58.15mm}, yshift={-1.0mm}, width={55.15mm}, height={48.8mm}, scaled x ticks={false}, xlabel={Nr. Parameters}, x tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, x tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, xlabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, xmode={log}, log basis x={10}, xmajorgrids={true}, xmin={89.49402359104843}, xmax={35417.024208050476}, xtick={{100.0,316.22776601683796,1000.0,3162.2776601683795,10000.0,31622.776601683792}}, xticklabels={{$10^{2.0}$,$10^{2.5}$,$10^{3.0}$,$10^{3.5}$,$10^{4.0}$,$10^{4.5}$}}, xtick align={inside}, xticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, x grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis x line*={left}, x axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}, scaled y ticks={false}, ylabel={}, y tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, y tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, ylabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, ymode={log}, log basis y={10}, ymajorgrids={true}, ymin={0.1}, ymax={100000.0}, ytick={{0.1,1.0,10.0,100.0,1000.0,10000.0,100000.0}}, yticklabels={{$10^{-1}$,$10^{0}$,$10^{1}$,$10^{2}$,$10^{3}$,$10^{4}$,$10^{5}$}}, ytick align={inside}, yticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, y grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis y line*={left}, y axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}]
    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={ca743fe9-f865-4257-9e33-032174efb577}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
        coordinates {
            (1947.0,3.119196)
            (1912.0,3.1269026)
            (1934.0,3.200298)
            (1314.0,3.550602)
            (2021.0,3.9671524)
            (2036.0,4.5925226)
            (2517.0,4.6573997)
            (1865.0,4.9660153)
            (1928.0,7.385417)
            (2304.0,8.159821)
        }
        ;
    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={718cbf1c-0e6b-42da-8705-e6a8efb5b5de}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
        coordinates {
            (27266.0,6.056448979580512e57)
            (27271.0,1.1270697569661482e67)
            (29240.0,6.670123662775398e74)
            (29769.0,2.3908233870509967e81)
            (29902.0,5.73026454938337e83)
            (29723.0,5.578735868305779e84)
            (29719.0,6.47201021019638e89)
            (29857.0,3.343027269532066e95)
        }
        ;
    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={3adb2d3b-7fa3-4ded-a575-cc69f8a5d964}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
        coordinates {
            (1432.0,0.22429785)
            (3584.0,0.35476318)
            (106.0,0.50807154)
            (5648.0,0.5131744)
            (109.0,0.597559)
            (8249.0,2.7305448)
            (8075.0,20011.611)
            (383.0,27771.52)
            (383.0,27781.611)
            (385.0,27991.143)
        }
        ;
    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={1b311080-2e2a-4c14-b593-bbd939282850}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
        coordinates {
            (9938.0,687.11816)
            (9950.0,1251.8556)
            (9983.0,2757.291)
            (9962.0,3324.5964)
            (10018.0,4169.526)
            (9966.0,4312.167)
            (10049.0,4416.4814)
            (10071.0,4609.3774)
            (10056.0,4618.8584)
            (9946.0,5408.8984)
        }
        ;
\end{axis}
\begin{axis}[point meta max={nan}, point meta min={nan}, legend cell align={left}, title={}, title style={at={{(0.5,1)}}, anchor={south}, font={{\fontsize{14 pt}{18.2 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, legend style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid, fill={rgb,1:red,1.0;green,1.0;blue,1.0}, fill opacity={1.0}, text opacity={1.0}, font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, at={(1.02, 1)}, anchor={north west}}, axis background/.style={fill={rgb,1:red,1.0;green,1.0;blue,1.0}, opacity={1.0}}, anchor={north west}, xshift={115.3mm}, yshift={-1.0mm}, width={55.15mm}, height={48.8mm}, scaled x ticks={false}, xlabel={Nr. Parameters}, x tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, x tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, xlabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, xmode={log}, log basis x={10}, xmajorgrids={true}, xmin={43.480244741743846}, xmax={24215.503069354898}, xtick={{100.0,316.22776601683796,1000.0,3162.2776601683795,10000.0}}, xticklabels={{$10^{2.0}$,$10^{2.5}$,$10^{3.0}$,$10^{3.5}$,$10^{4.0}$}}, xtick align={inside}, xticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, x grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis x line*={left}, x axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}, scaled y ticks={false}, ylabel={}, y tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, y tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, ylabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, ymode={log}, log basis y={10}, ymajorgrids={true}, ymin={3.003128636465643e-10}, ymax={1.0476863806782078e31}, ytick={{1.0,1.0e10,1.0e20,1.0e30}}, yticklabels={{$10^{0}$,$10^{10}$,$10^{20}$,$10^{30}$}}, ytick align={inside}, yticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, y grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis y line*={left}, y axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}]
    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={25c6bfe2-b14c-4d58-812c-34611c63a621}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
        coordinates {
            (52.0,4.217039e-9)
            (155.0,4.6643503e-8)
            (204.0,5.3117162e-8)
            (102.0,5.7346426e-8)
            (102.0,9.8668096e-8)
            (154.0,1.7296065e-7)
            (102.0,2.6649218e-7)
            (102.0,3.3172265e-7)
            (102.0,3.909838e-7)
            (102.0,4.380334e-7)
        }
        ;
    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={35cbff1c-ba07-48c9-bd21-cbf564ba8620}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
        coordinates {
            (18994.0,0.006679143442147095)
            (20248.0,300.5367981426397)
            (18253.0,420.4417069693)
            (18484.0,462.16137066417264)
            (19124.0,506.4912807643721)
            (19352.0,550.5197097967591)
            (18115.0,699.409735838578)
            (19284.0,806.9032735843994)
            (18698.0,1548.9257860967384)
            (19035.0,2074.445574153203)
        }
        ;
    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={364b3eb2-628a-44de-a4b5-f6fca4d5743c}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
        coordinates {
            (801.0,1.3877087)
            (749.0,1.5402892)
            (757.0,1.5402905)
            (742.0,1.5402931)
            (757.0,1.5402986)
            (692.0,1.7030367)
            (693.0,1.7030562)
            (864.0,1.7975432)
            (791.0,1.9803718)
            (715.0,2.169463)
        }
        ;
    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={e362d5ba-5d53-4952-9528-3385a563c01a}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
        coordinates {
            (9845.0,2.0357272e7)
            (9810.0,4.9806867e8)
            (9970.0,6.223722e13)
            (10082.0,7.144208e14)
            (9868.0,7.4999905e15)
            (9765.0,1.0666438e18)
            (9927.0,2.085579e20)
            (9760.0,7.4610096e29)
        }
        ;
\end{axis}
\begin{axis}[point meta max={nan}, point meta min={nan}, legend cell align={left}, title={}, title style={at={{(0.5,1)}}, anchor={south}, font={{\fontsize{14 pt}{18.2 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, legend style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid, fill={rgb,1:red,1.0;green,1.0;blue,1.0}, fill opacity={1.0}, text opacity={1.0}, font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, at={(1.02, 1)}, anchor={north west}}, axis background/.style={fill={rgb,1:red,1.0;green,1.0;blue,1.0}, opacity={1.0}}, anchor={north west}, xshift={172.45mm}, yshift={-1.0mm}, width={55.15mm}, height={48.8mm}, scaled x ticks={false}, xlabel={Nr. Parameters}, x tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, x tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, xlabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, xmode={log}, log basis x={10}, xmajorgrids={true}, xmin={86.16627370302126}, xmax={33416.29939718559}, xtick={{100.0,316.22776601683796,1000.0,3162.2776601683795,10000.0,31622.776601683792}}, xticklabels={{$10^{2.0}$,$10^{2.5}$,$10^{3.0}$,$10^{3.5}$,$10^{4.0}$,$10^{4.5}$}}, xtick align={inside}, xticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, x grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis x line*={left}, x axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}, scaled y ticks={false}, ylabel={}, y tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, y tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, ylabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, ymode={log}, log basis y={10}, ymajorgrids={true}, ymin={0.0014075044814322237}, ymax={2.162048835278372e21}, ytick={{1.0,100000.0,1.0e10,1.0e15,1.0e20}}, yticklabels={{$10^{0}$,$10^{5}$,$10^{10}$,$10^{15}$,$10^{20}$}}, ytick align={inside}, yticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, y grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis y line*={left}, y axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}]
    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={ebdc7105-4d92-4a3f-95d2-02699858279c}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
        coordinates {
            (103.0,0.006807239)
            (103.0,0.036651038)
            (103.0,0.040400617)
            (103.0,0.052491613)
            (102.0,0.053030577)
            (102.0,0.054934423)
            (103.0,0.05519525)
            (104.0,0.05592795)
            (103.0,0.27859107)
            (103.0,0.28152826)
        }
        ;
    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={554d6241-181a-4734-8d6d-49428305bc1c}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
        coordinates {
            (25002.0,110.9731299000638)
            (24711.0,139.27110419326715)
            (23060.0,259.65656416957603)
            (24543.0,883.9527082423043)
            (23574.0,2017.814681341383)
            (28229.0,12599.269355463382)
            (27241.0,19142.912878289713)
            (20686.0,42905.89328481797)
            (27171.0,91624.4060802308)
            (20707.0,3.556283999184454e7)
        }
        ;
    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={55056117-138d-4bdc-a592-4d4fe5a3384e}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
        coordinates {
            (7201.0,9.486513)
            (6707.0,9.52155)
            (188.0,9.844871)
            (6927.0,9.845515)
            (1701.0,10.554757)
            (1101.0,11.371628)
            (10001.0,11.378366)
            (5902.0,11.498858)
            (8701.0,11.621315)
            (10001.0,13.208106)
        }
        ;
    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={f886d280-b26f-49cb-9603-d33a459d2008}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
        coordinates {
            (7992.0,0.23132631)
            (9564.0,99.999794)
            (7554.0,99.999794)
            (8926.0,100.0038)
            (7772.0,100.0563)
            (4221.0,1.8681482e9)
            (6967.0,3.5018813e10)
            (6613.0,1.2335086e12)
            (6682.0,4.4703785e20)
        }
        ;
\end{axis}
\end{tikzpicture}

### 2020-06-02 plots/pareto_sir.tex
plots

\begin{tikzpicture}[/tikz/background rectangle/.style={fill={rgb,1:red,1.0;green,1.0;blue,1.0}, draw opacity={1.0}}, show background rectangle]
\begin{axis}[point meta max={nan}, point meta min={nan}, legend cell align={left}, title={Pareto}, title style={at={{(0.5,1)}}, anchor={south}, font={{\fontsize{14 pt}{18.2 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, legend style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid, fill={rgb,1:red,1.0;green,1.0;blue,1.0}, fill opacity={1.0}, text opacity={1.0}, font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, at={(0.98, 0.98)}, anchor={north east}}, axis background/.style={fill={rgb,1:red,1.0;green,1.0;blue,1.0}, opacity={1.0}}, anchor={north west}, xshift={1.0mm}, yshift={-1.0mm}, width={112.3mm}, height={74.2mm}, scaled x ticks={false}, xlabel={Nr. Paramters}, x tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, x tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, xlabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, xmode={log}, log basis x={10}, xmajorgrids={true}, xmin={15.305486448632008}, xmax={625.3313171144225}, xtick={{15.848931924611142,25.11886431509581,39.810717055349734,63.09573444801933,100.0,158.48931924611142,251.18864315095823,398.1071705534973}}, xticklabels={{$10^{1.2}$,$10^{1.4}$,$10^{1.6}$,$10^{1.8}$,$10^{2.0}$,$10^{2.2}$,$10^{2.4}$,$10^{2.6}$}}, xtick align={inside}, xticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, x grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis x line*={left}, x axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}, scaled y ticks={false}, ylabel={MSE}, y tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, y tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, ylabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, ymode={log}, log basis y={10}, ymajorgrids={true}, ymin={0.005}, ymax={10000.0}, ytick={{0.01,0.1,1.0,10.0,100.0,1000.0,10000.0}}, yticklabels={{$10^{-2}$,$10^{-1}$,$10^{0}$,$10^{1}$,$10^{2}$,$10^{3}$,$10^{4}$}}, ytick align={inside}, yticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, y grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis y line*={left}, y axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}]
    \addplot[color={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, name path={c6416611-1574-49a0-9ea4-91e50a33118b}, draw opacity={0.25}, line width={0}, solid, mark={*}, mark size={3.75 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.25}, fill={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, fill opacity={0.25}, line width={0.75}, rotate={0}, solid}, only marks, forget plot]
        coordinates {
            (105.0,0.05584966441816506)
            (102.0,0.04975238296092152)
            (109.0,0.05940020202500067)
            (89.0,2.294967031333799)
            (109.0,0.01674682323492209)
            (103.0,0.10720479779621425)
            (111.0,0.047378610574098125)
            (91.0,0.10379493048125163)
            (110.0,2.513624607833005)
            (104.0,0.05086478924822935)
            (109.0,0.11351618280207543)
            (108.0,0.4020253123624037)
            (110.0,0.07446102987541804)
            (105.0,0.11535032606585913)
            (111.0,0.18480906070431535)
            (98.0,0.20276032629175944)
            (107.0,0.08951349573643062)
            (102.0,0.04128707134536484)
            (111.0,0.08564751808207169)
            (101.0,0.3024196229705965)
            (134.0,0.0625994120602839)
            (123.0,0.07725887987692295)
            (137.0,0.0446213228734711)
            (133.0,0.3084188318399655)
            (133.0,0.01962266981062221)
            (134.0,0.10146607016990984)
            (138.0,0.06814314041036643)
            (126.0,0.1400125295960749)
            (138.0,467.4741755918939)
            (127.0,1.1166477896146412)
            (138.0,0.17714972309111646)
            (19.0,0.11922132709056152)
            (133.0,0.08769252229223219)
            (130.0,0.07793316024608679)
            (137.0,0.1718723416265335)
            (125.0,0.33914255094342527)
            (136.0,0.015348260495236497)
            (131.0,0.14565843998621403)
            (137.0,0.19446231157170504)
            (123.0,0.26589194567164826)
            (178.0,0.13602372744489552)
            (164.0,1.3096147548790622)
            (183.0,1.2001412178607553)
            (20.0,0.13777438440294185)
            (181.0,0.8479907542370899)
            (183.0,0.0950066129025234)
            (182.0,0.0973834969835291)
            (140.0,4.6045371868841265)
            (181.0,0.08489426529555413)
            (171.0,1.434207428800683)
            (182.0,0.03715339077893962)
            (172.0,0.22976469267521113)
            (179.0,0.021032926937894693)
            (174.0,0.12032695402812911)
            (183.0,0.1184679992516246)
            (167.0,0.19684607920197908)
            (179.0,0.07686867922650574)
            (173.0,2.5546282892181007)
            (182.0,2.568218715361108)
            (20.0,0.14201835288630793)
            (57.0,0.034130835764939665)
            (57.0,0.08573571106663361)
            (57.0,0.027468464787432298)
            (53.0,0.1845821255465333)
            (57.0,0.3145059229030894)
            (50.0,0.03924953982860379)
            (57.0,0.06856875980583756)
            (18.0,0.13408208779207065)
            (57.0,0.246120844440766)
            (57.0,0.04960174895763792)
            (57.0,2.4305662054492216e9)
            (49.0,0.19845525108383108)
            (57.0,0.10124427200601582)
            (57.0,723.2519398047787)
            (57.0,0.04868286562065639)
            (21.0,0.09182349525167144)
            (57.0,2.72184197085509)
            (57.0,0.02883792885224287)
            (57.0,0.05463115607163071)
            (47.0,3.4065463877724946)
            (83.0,0.0897939767464811)
            (73.0,0.13931869624662485)
            (82.0,0.2953775450777107)
            (78.0,0.18845400004232993)
            (83.0,0.03326786171772812)
            (81.0,0.03346088666911155)
            (84.0,0.021920164977564584)
            (29.0,0.13107584979633108)
            (83.0,0.025448977666601213)
            (83.0,0.052182247335789286)
            (84.0,0.03318537664315938)
            (19.0,0.11324273930491076)
            (83.0,0.049563710942017516)
            (82.0,0.05229073956836107)
            (84.0,0.936285586965232)
            (79.0,0.36352072822414827)
            (84.0,0.06743210142176875)
            (83.0,0.06069929189699635)
            (84.0,1.0402239808527012)
            (20.0,0.0863532735177328)
        }
        ;
    \addplot[color={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, name path={0b6b36d8-c846-4873-8ad0-9609ab2cf7aa}, draw opacity={0.25}, line width={0}, solid, mark={pentagon*}, mark size={3.75 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.25}, fill={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, fill opacity={0.25}, line width={0.75}, rotate={0}, solid}, only marks, forget plot]
        coordinates {
            (235.0,0.13357198945321846)
            (70.0,0.04461548817109118)
            (240.0,0.27826514621649645)
            (55.0,0.40610599113961626)
            (231.0,0.16842724844486784)
            (183.0,0.053126061241543406)
            (243.0,0.09279724868377123)
            (44.0,0.6219680679576621)
            (224.0,0.14673187421056033)
            (222.0,0.17126303810452492)
            (242.0,0.26732925740823366)
            (72.0,0.40406046468282036)
            (239.0,0.27881283308599)
            (215.0,0.08349271759735011)
            (242.0,0.2125101399226415)
            (32.0,0.5513286633867127)
            (235.0,0.22568337408398828)
            (206.0,0.09258343306049661)
            (243.0,0.20454040997137593)
            (26.0,0.5107297023521244)
            (323.0,0.3667902032609065)
            (106.0,0.04378510564953422)
            (346.0,0.16065746518529136)
            (41.0,0.4591112638861731)
            (338.0,0.16645620302038866)
            (329.0,0.0837772625628679)
            (343.0,0.14366152756083547)
            (43.0,0.6024946038819587)
            (331.0,0.18929036413010172)
            (287.0,0.33185148527249725)
            (348.0,0.04576725492168219)
            (40.0,0.5307735589972514)
            (333.0,0.25561466836673213)
            (267.0,0.08139063563463969)
            (348.0,0.2603533867117459)
            (42.0,0.485145599462851)
            (324.0,0.06458173214154204)
            (150.0,0.03822594080269291)
            (346.0,0.22772148021684693)
            (38.0,0.5349911168200644)
            (529.0,0.09246980203670312)
            (76.0,0.032150726839285076)
            (561.0,0.2953731709925806)
            (42.0,0.42435150858456305)
            (551.0,0.5658710399734437)
            (172.0,0.03671331385133575)
            (562.0,0.2247420272307935)
            (39.0,0.6093866677344313)
            (552.0,0.42285681275210707)
            (338.0,0.07585812329891815)
            (561.0,0.16916001531239544)
            (39.0,0.4801687797714871)
            (536.0,0.1460284576306947)
            (519.0,0.1674664372593216)
            (563.0,0.07034107539784748)
            (36.0,0.6153149633129895)
            (538.0,0.2901270824759899)
            (314.0,0.0894523538965804)
            (561.0,0.9493069230558913)
            (43.0,0.45231290229037063)
            (86.0,0.19904079876071654)
            (86.0,0.2474597369029254)
            (87.0,0.9661924012140722)
            (52.0,0.5183448216596367)
            (83.0,0.41163416709756745)
            (86.0,0.2018533637471545)
            (87.0,0.7338740990737738)
            (29.0,0.502255804939499)
            (85.0,0.24871677122634128)
            (79.0,0.47124624050445574)
            (87.0,0.3017981172481904)
            (34.0,0.4118665138102874)
            (86.0,0.46110233661130057)
            (81.0,0.34380752518935775)
            (87.0,0.592914605387025)
            (55.0,0.5340532094284938)
            (84.0,0.21982864921620568)
            (86.0,0.12593689360335356)
            (86.0,0.2490899738548067)
            (30.0,0.3888134391760499)
            (149.0,0.155251101357749)
            (131.0,0.055439107403504)
            (155.0,0.12238978551321686)
            (35.0,0.43098325658284026)
            (154.0,0.1394374093998332)
            (152.0,0.2297799184953769)
            (155.0,0.15759694151794004)
            (39.0,0.5057258031699502)
            (154.0,0.3922494485884269)
            (153.0,0.3902229654498584)
            (156.0,0.2773388179874096)
            (43.0,0.5416488514754519)
            (152.0,0.2540652840489718)
            (152.0,0.11832827918668122)
            (154.0,0.11410277669310671)
            (45.0,0.5469697488849031)
            (151.0,0.1870216675213049)
            (127.0,0.16707232055495033)
            (154.0,0.8019823908524971)
            (52.0,0.5113011726127454)
        }
        ;
    \addplot[color={rgb,1:red,1.0;green,0.498;blue,0.0549}, name path={32500e26-f355-48fb-b27a-d77c0e6f6f11}, draw opacity={0.25}, line width={0}, solid, mark={diamond*}, mark size={3.75 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.25}, fill={rgb,1:red,1.0;green,0.498;blue,0.0549}, fill opacity={0.25}, line width={0.75}, rotate={0}, solid}, only marks, forget plot]
        coordinates {
            (75.0,3.147945165083429)
            (73.0,0.7787622330875555)
            (75.0,14.274696485077706)
            (72.0,1.0547043767865791)
            (75.0,3.332024981183407)
            (73.0,0.8054592789691524)
            (75.0,1.9717984455866802)
            (30.0,0.3567713595345774)
            (74.0,1.3257338505548062)
            (71.0,0.454412627271946)
            (75.0,199.32322467686308)
            (75.0,1.0895748631691455)
            (75.0,2.4040986461550835)
            (75.0,30.945783537221924)
            (75.0,1.3655781266539022)
            (72.0,1.7771060355248247)
            (75.0,2.095095365942199)
            (74.0,1.2957150765737162)
            (75.0,10.287194966343153)
            (71.0,23.823930630622364)
            (91.0,2.4310322835821725)
            (90.0,2.03837213281791)
            (93.0,18.48678688820552)
            (18.0,0.1828119186366187)
            (93.0,1.402802143535598)
            (93.0,0.5216804362331351)
            (93.0,344.95675624956914)
            (17.0,0.028392317708999436)
            (93.0,0.5279417818890894)
            (92.0,2.279971972737263)
            (93.0,1.6171895486111396)
            (87.0,0.9929110131500897)
            (92.0,1.6970363177778334)
            (88.0,1.281239828889679)
            (93.0,1.9682814650085763)
            (90.0,1.0443588384128824)
            (93.0,1.4672964427212034)
            (93.0,2.512126815083123)
            (93.0,1.7528157502014407e27)
            (17.0,0.042776379040499156)
            (123.0,292782.19801080116)
            (114.0,0.8319858220508034)
            (122.0,38.36679799718143)
            (119.0,4.247901992170559)
            (123.0,2.1603952895878047)
            (123.0,1.612179389285352)
            (123.0,2.1315469624808055e8)
            (120.0,2.863381885496416)
            (123.0,1.5701579511267307)
            (115.0,1.1995883679712909)
            (122.0,0.8442486879600574)
            (107.0,1.4996647965557675)
            (123.0,43.27286005493181)
            (123.0,0.22240221552099876)
            (123.0,1.724556189521123)
            (123.0,0.7600881434640848)
            (123.0,1.55953539967718)
            (122.0,2.5016970428713385)
            (122.0,125.83729920965449)
            (119.0,1.474402129759871)
            (39.0,1.6787168071085867)
            (38.0,23.286011001150722)
            (39.0,1.8524442120647987e6)
            (39.0,1.1819811023887494)
            (38.0,25.653816244212006)
            (39.0,7.724620004876016)
            (39.0,1.5998738392072849)
            (39.0,230.55843153298235)
            (38.0,35.384317652871445)
            (39.0,18.021070189844696)
            (39.0,195.47077720096976)
            (39.0,160.86609736256958)
            (39.0,3.0592725712776643)
            (39.0,4.398153803012362)
            (39.0,1.1590218432565333)
            (17.0,0.035424442595674274)
            (38.0,4162.440925088575)
            (39.0,40.27926776330599)
            (39.0,2.6373813625877043)
            (39.0,9.740619004230942)
            (57.0,0.8097482769396408)
            (57.0,0.8683241511330079)
            (57.0,0.6548577323997611)
            (57.0,18.271264624639596)
            (57.0,0.8110250229754907)
            (57.0,1.0118191812875524e19)
            (57.0,1166.0668083720273)
            (54.0,24.255595170101138)
            (57.0,2.4197291464377434e17)
            (57.0,25.939711745446342)
            (57.0,411.43443310327984)
            (54.0,25.852674031372572)
            (57.0,1.0362054731778492)
            (57.0,1.0072691225003283e14)
            (56.0,62.4551625376836)
            (47.0,0.3358689620078998)
            (57.0,2.1657544482083853)
            (57.0,1.253110778534678)
            (57.0,2.6027300344473447)
            (57.0,26.29584591974179)
        }
        ;
    \addplot[color={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, name path={17fa3149-1072-43c8-8c21-8a953ad9b789}, draw opacity={1.0}, line width={2}, dashed]
        coordinates {
            (26.0,0.5107297023521244)
            (30.0,0.3888134391760499)
            (70.0,0.04461548817109118)
            (76.0,0.032150726839285076)
            (172.0,0.03671331385133575)
            (348.0,0.04576725492168219)
            (563.0,0.07034107539784748)
        }
        ;
    \addlegendentry {Dense}
    \addplot[color={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, name path={92814b74-5dc8-4049-b104-86ec2005b545}, draw opacity={1.0}, line width={2}, solid]
        coordinates {
            (57.0,2.4305662054492216e9)
            (18.0,0.13408208779207065)
            (20.0,0.0863532735177328)
            (57.0,0.027468464787432298)
            (109.0,0.01674682323492209)
            (136.0,0.015348260495236497)
            (179.0,0.021032926937894693)
        }
        ;
    \addlegendentry {NPU}
    \addplot[color={rgb,1:red,1.0;green,0.498;blue,0.0549}, name path={01e229a2-0f53-4a30-b602-5c368ec01212}, draw opacity={1.0}, line width={2}, dashdotted]
        coordinates {
            (39.0,1.8524442120647987e6)
            (17.0,0.042776379040499156)
            (17.0,0.028392317708999436)
            (123.0,0.22240221552099876)
        }
        ;
    \addlegendentry {NPU (real)}
\end{axis}
\begin{axis}[point meta max={nan}, point meta min={nan}, legend cell align={left}, title={SIR Model}, title style={at={{(0.5,1)}}, anchor={south}, font={{\fontsize{14 pt}{18.2 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, legend style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid, fill={rgb,1:red,1.0;green,1.0;blue,1.0}, fill opacity={1.0}, text opacity={1.0}, font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, at={(0.98, 0.5)}, anchor={east}}, axis background/.style={fill={rgb,1:red,1.0;green,1.0;blue,1.0}, opacity={1.0}}, anchor={north west}, xshift={115.3mm}, yshift={-1.0mm}, width={112.3mm}, height={74.2mm}, scaled x ticks={false}, xlabel={Time}, x tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, x tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, xlabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, xmajorgrids={true}, xmin={-6.0}, xmax={206.0}, xtick={{0.0,50.0,100.0,150.0,200.0}}, xticklabels={{$0$,$50$,$100$,$150$,$200$}}, xtick align={inside}, xticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, x grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis x line*={left}, x axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}, scaled y ticks={false}, ylabel={}, y tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, y tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, ylabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, ymajorgrids={true}, ymin={-3.0}, ymax={103.0}, ytick={{0.0,25.0,50.0,75.0,100.0}}, yticklabels={{$0$,$25$,$50$,$75$,$100$}}, ytick align={inside}, yticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, y grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis y line*={left}, y axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}]
    \addplot[color={rgb,1:red,0.502;green,0.502;blue,0.502}, name path={2c7c1a19-783e-45b8-ba0c-5f0d47ee61d7}, draw opacity={0.8}, line width={4}, solid]
        coordinates {
            (0.0,100.0)
            (5.128205128205129,97.46721309713212)
            (10.256410256410257,91.07411529978752)
            (15.384615384615385,81.85822003827998)
            (20.512820512820515,70.93406989207153)
            (25.641025641025642,59.36171599653322)
            (30.76923076923077,48.05121932732702)
            (35.8974358974359,37.70386572153941)
            (41.02564102564103,28.786661655619767)
            (46.15384615384615,21.536458098202502)
            (51.282051282051285,15.984367444258964)
            (56.41025641025641,12.000464352759552)
            (61.53846153846154,9.344211354396093)
            (66.66666666666667,7.730064928992786)
            (71.7948717948718,6.871778028659456)
            (76.92307692307692,6.531712440790295)
            (82.05128205128206,6.527846168986343)
            (87.17948717948718,6.732261015727868)
            (92.3076923076923,7.058906461697017)
            (97.43589743589743,7.448852247665159)
            (102.56410256410257,7.8621381580828835)
            (107.6923076923077,8.271957039163652)
            (112.82051282051282,8.660383314615434)
            (117.94871794871794,9.015599814052901)
            (123.07692307692308,9.330728378580337)
            (128.2051282051282,9.603063253817359)
            (133.33333333333334,9.832194944069075)
            (138.46153846153845,10.019480104740795)
            (143.5897435897436,10.168236969594094)
            (148.71794871794873,10.282830242207533)
            (153.84615384615384,10.367552891075434)
            (158.97435897435898,10.42665962038892)
            (164.10256410256412,10.464984481530161)
            (169.23076923076923,10.487122611260277)
            (174.35897435897436,10.496809113024415)
            (179.48717948717947,10.49696822418185)
            (184.6153846153846,10.490486949159731)
            (189.74358974358975,10.479876278697317)
            (194.87179487179486,10.467010848152167)
            (200.0,10.453187053405765)
        }
        ;
    \addlegendentry {True $S,I,R$}
    \addplot[color={rgb,1:red,0.502;green,0.502;blue,0.502}, name path={1bd494f5-4860-4f91-bdd7-b6e623424164}, draw opacity={0.8}, line width={4}, solid, forget plot]
        coordinates {
            (0.0,0.01)
            (5.128205128205129,2.326002254590468)
            (10.256410256410257,7.535412858135904)
            (15.384615384615385,14.122344350839555)
            (20.512820512820515,20.861212946319004)
            (25.641025641025642,26.852061199698944)
            (30.76923076923077,31.52079010396936)
            (35.8974358974359,34.589940517583635)
            (41.02564102564103,36.03247808932137)
            (46.15384615384615,36.0106783095002)
            (51.282051282051285,34.81461042142043)
            (56.41025641025641,32.799670718853136)
            (61.53846153846154,30.321886606977262)
            (66.66666666666667,27.70444740533231)
            (71.7948717948718,25.186917212993873)
            (76.92307692307692,22.920167986169474)
            (82.05128205128206,20.97478194912876)
            (87.17948717948718,19.361879697078066)
            (92.3076923076923,18.06136663645284)
            (97.43589743589743,17.0351828644295)
            (102.56410256410257,16.243460467487697)
            (107.6923076923077,15.64716970581006)
            (112.82051282051282,15.209576700999039)
            (117.94871794871794,14.900102701702954)
            (123.07692307692308,14.692768418941395)
            (128.2051282051282,14.564262720391902)
            (133.33333333333334,14.495696710475123)
            (138.46153846153845,14.472242253795276)
            (143.5897435897436,14.480798749993546)
            (148.71794871794873,14.510674957112856)
            (153.84615384615384,14.553801666023665)
            (158.97435897435898,14.60424306180992)
            (164.10256410256412,14.656998699052162)
            (169.23076923076923,14.708526692892267)
            (174.35897435897436,14.75644891382746)
            (179.48717948717947,14.799483648325703)
            (184.6153846153846,14.836795847017735)
            (189.74358974358975,14.868211842226707)
            (194.87179487179486,14.893874068806547)
            (200.0,14.91412562301017)
        }
        ;
    \addplot[color={rgb,1:red,0.502;green,0.502;blue,0.502}, name path={99fd42b1-24fe-476a-9976-bd874af9786a}, draw opacity={0.8}, line width={4}, solid, forget plot]
        coordinates {
            (0.0,0.0)
            (5.128205128205129,0.21678464827744337)
            (10.256410256410257,1.4004718420766002)
            (15.384615384615385,4.029435610880507)
            (20.512820512820515,8.214717161609485)
            (25.641025641025642,13.796222803767884)
            (30.76923076923077,20.43799056870365)
            (35.8974358974359,27.71619376087699)
            (41.02564102564103,35.19086025505889)
            (46.15384615384615,42.462863592297325)
            (51.282051282051285,49.21102213432063)
            (56.41025641025641,55.20986492838734)
            (61.53846153846154,60.34390203862667)
            (66.66666666666667,64.57548766567494)
            (71.7948717948718,67.95130475834671)
            (76.92307692307692,70.55811957304027)
            (82.05128205128206,72.50737188188494)
            (87.17948717948718,73.9158592871941)
            (92.3076923076923,74.88972690185018)
            (97.43589743589743,75.52596488790537)
            (102.56410256410257,75.90440137442945)
            (107.6923076923077,76.09087325502632)
            (112.82051282051282,76.14003998438557)
            (117.94871794871794,76.09429748424418)
            (123.07692307692308,75.9865032024783)
            (128.2051282051282,75.84267402579079)
            (133.33333333333334,75.68210834545584)
            (138.46153846153845,75.51827764146397)
            (143.5897435897436,75.36096428041239)
            (148.71794871794873,75.21649480067964)
            (153.84615384615384,75.08864544290094)
            (158.97435897435898,74.97909731780119)
            (164.10256410256412,74.8880168194177)
            (169.23076923076923,74.81435069584748)
            (174.35897435897436,74.75674197314815)
            (179.48717948717947,74.71354812749247)
            (184.6153846153846,74.68271720382256)
            (189.74358974358975,74.661911879076)
            (194.87179487179486,74.64911508304131)
            (200.0,74.6426873235841)
        }
        ;
    \addplot[color={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, name path={78950b23-4587-48e7-ac69-7a173b42d7ff}, draw opacity={1.0}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, fill={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, fill opacity={1.0}, line width={0.75}, rotate={0}, solid}, only marks]
        coordinates {
            (0.0,100.0)
            (5.128205128205129,97.06371891032103)
            (10.256410256410257,91.16684462650328)
            (15.384615384615385,82.31860705364566)
            (20.512820512820515,71.37328028612147)
            (25.641025641025642,59.56655329185587)
            (30.76923076923077,48.02982853680665)
            (35.8974358974359,37.56283706154292)
            (41.02564102564103,28.637211640920665)
            (46.15384615384615,21.450945359433096)
            (51.282051282051285,15.991646351608207)
            (56.41025641025641,12.091156352995037)
            (61.53846153846154,9.484490451837605)
            (66.66666666666667,7.875556914992195)
            (71.7948717948718,6.990870233379205)
            (76.92307692307692,6.607983321954687)
            (82.05128205128206,6.5600222783518465)
            (87.17948717948718,6.726996153400294)
            (92.3076923076923,7.024919064760524)
            (97.43589743589743,7.39470727063654)
            (102.56410256410257,7.794775985610217)
            (107.6923076923077,8.196178604628553)
            (112.82051282051282,8.579336543097728)
            (117.94871794871794,8.931747895191842)
            (123.07692307692308,9.246307992466145)
            (128.2051282051282,9.520025067810243)
            (133.33333333333334,9.752717909881044)
            (138.46153846153845,9.946211973122255)
            (143.5897435897436,10.103649973188396)
            (148.71794871794873,10.228936301333658)
            (153.84615384615384,10.326310541375907)
            (158.97435897435898,10.400033334390523)
            (164.10256410256412,10.454186099682712)
            (169.23076923076923,10.492511634963721)
            (174.35897435897436,10.518286052520692)
            (179.48717948717947,10.534341485628904)
            (184.6153846153846,10.543067590956252)
            (189.74358974358975,10.546434143372755)
            (194.87179487179486,10.546027918810093)
            (200.0,10.54309740549285)
        }
        ;
    \addlegendentry {$\hat S$}
    \addplot[color={rgb,1:red,1.0;green,0.498;blue,0.0549}, name path={55448a83-940d-42d2-bfa5-a69e99f44840}, draw opacity={1.0}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, fill={rgb,1:red,1.0;green,0.498;blue,0.0549}, fill opacity={1.0}, line width={0.75}, rotate={0}, solid}, only marks]
        coordinates {
            (0.0,0.01)
            (5.128205128205129,2.7125599630590216)
            (10.256410256410257,7.66090322551522)
            (15.384615384615385,14.05992089552267)
            (20.512820512820515,20.853377037596527)
            (25.641025641025642,26.949263303743713)
            (30.76923076923077,31.643268521967897)
            (35.8974358974359,34.65445060429321)
            (41.02564102564103,36.00248493995587)
            (46.15384615384615,35.89734765592843)
            (51.282051282051285,34.65263524249474)
            (56.41025641025641,32.62658545846643)
            (61.53846153846154,30.171255479960887)
            (66.66666666666667,27.588258250205744)
            (71.7948717948718,25.101967545018532)
            (76.92307692307692,22.854404251300224)
            (82.05128205128206,20.916574933981376)
            (87.17948717948718,19.306505476039106)
            (92.3076923076923,18.00963924091414)
            (97.43589743589743,16.993337294186258)
            (102.56410256410257,16.217140779474875)
            (107.6923076923077,15.639502083735772)
            (112.82051282051282,15.2216338588409)
            (117.94871794871794,14.929362607150622)
            (123.07692307692308,14.733677548787432)
            (128.2051282051282,14.610599644370984)
            (133.33333333333334,14.541013265661315)
            (138.46153846153845,14.509771044572922)
            (143.5897435897436,14.505057091871647)
            (148.71794871794873,14.517816285691135)
            (153.84615384615384,14.541245312235125)
            (158.97435897435898,14.570351813286242)
            (164.10256410256412,14.601580037074164)
            (169.23076923076923,14.632505354378589)
            (174.35897435897436,14.661561456708021)
            (179.48717948717947,14.687819457461144)
            (184.6153846153846,14.710818905225636)
            (189.74358974358975,14.730432472745509)
            (194.87179487179486,14.746759324518035)
            (200.0,14.760042741576434)
        }
        ;
    \addlegendentry {$\hat I$}
    \addplot[color={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, name path={7029124d-f96e-4c96-8ccc-df7e7adb01de}, draw opacity={1.0}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, fill={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, fill opacity={1.0}, line width={0.75}, rotate={0}, solid}, only marks]
        coordinates {
            (0.0,0.0)
            (5.128205128205129,0.50693326871289)
            (10.256410256410257,1.417679355799354)
            (15.384615384615385,3.8182491876122566)
            (20.512820512820515,7.962302503151513)
            (25.641025641025642,13.649388710326537)
            (30.76923076923077,20.427370387367066)
            (35.8974358974359,27.787946129597962)
            (41.02564102564103,35.263551206919445)
            (46.15384615384615,42.46863602460634)
            (51.282051282051285,49.116287047058584)
            (56.41025641025641,55.02090402143257)
            (61.53846153846154,60.09164848079044)
            (66.66666666666667,64.31440131855449)
            (71.7948717948718,67.72832791710991)
            (76.92307692307692,70.40495950573064)
            (82.05128205128206,72.43348328533506)
            (87.17948717948718,73.91170893256104)
            (92.3076923076923,74.93627783745409)
            (97.43589743589743,75.5987646759572)
            (102.56410256410257,75.98223718673248)
            (107.6923076923077,76.15882412766837)
            (112.82051282051282,76.18868881450685)
            (117.94871794871794,76.12017219498782)
            (123.07692307692308,75.99077303726688)
            (128.2051282051282,75.8285172837301)
            (133.33333333333334,75.65344697694208)
            (138.46153846153845,75.47937800364895)
            (143.5897435897436,75.31528402015716)
            (148.71794871794873,75.16647568233809)
            (153.84615384615384,75.03557984442344)
            (158.97435897435898,74.92332819239051)
            (164.10256410256412,74.82915576306749)
            (169.23076923076923,74.75168343757129)
            (174.35897435897436,74.68913253538693)
            (179.48717948717947,74.63952887626489)
            (184.6153846153846,74.60087490919402)
            (189.74358974358975,74.57126520497009)
            (194.87179487179486,74.54895766923063)
            (200.0,74.53241178440281)
        }
        ;
    \addlegendentry {$\hat R$}
\end{axis}
\end{tikzpicture}

### 2020-06-02 papers/main.tex
hyperparams

@@
 \end{align}
-where starting and
-ending values $s_{i,\text{start}},s_{i,\text{end}}$ of the summations are chosen
-such that $a$ and $b$ come from subsets of the input vector $\bm x$ with a
-given overlap.  Specifics of the used models are defined in
-Tab.~\ref{tab:models_large_task}.  \cite{madsen_neural_2020} perform an
+where starting and ending values $s_{i,\text{start}},s_{i,\text{end}}$ of the
+summations are chosen such that $a$ and $b$ come from subsets of the input
+vector $\bm x$ with a given overlap.  The training objective is standard MSE,
+regularized with L1:
+\begin{equation}
+  \mathcal{L} = \text{MSE}(\text{model}(\bm x), t) + \beta||\bm\theta||_1,
+\end{equation}
+where $\beta$ is scheduled to be low in the beginning of training and stronger
+towards the end.  Specifics of the used models and their hyper-parameters are defined in
+Tab.~\ref{tab:models_large_task} \& \ref{tab:training_large_scale}.  \cite{madsen_neural_2020} perform an
 extensive analysis of this task with different subset and overlap ratios,
@@
 
-Fig.~\ref{fig:pareto} plots training and testing errors over the number of
-non-zero parameters for all models and tasks.
-The addition column shows that all models except NaiveNPU learn ($+$) on the
-training set, with the NMU converging to the sparsest models. The NMU also
-performs best on the testing set, with the NPU as a close second.\\
-On ($\times$), the best NMU models also outperform the NPU, but some of
-them do not converge at all, which is why the NPU has a better testing MSE on
-average (see also Tab.~\ref{tab:arithmetic100_val}). The testing MSE of the
-NALU is so large that is excluded from the plot.\\
+Fig.~\ref{fig:pareto} plots testing errors over the number of non-zero
+parameters for all models and tasks.  The addition plot shows only NMU and NPU
+can extrapolate on ($+$) with the NMU converging to the sparsest models.\\
+On ($\times$), the best NMU models outperform the NPU, but some of them do not
+converge at all, which is why the NPU has a better testing MSE on average (see
+also Tab.~\ref{tab:arithmetic100_val}). The testing MSE of the NALU is so large
+that is excluded from the plot.\\
 On ($\div,\sqrt{\cdot}$) the NPU clearly outperforms all other layers
@@
 main competitor (NALU) and reaches performance that is on par with the
-multiplication specialist NMU.  For tasks that are known to contain only
-addition and multiplication a stack of NAU and NMU can be a better choice than
-the NPU, because they might be easier to train. For more complicated problems
-that involve division or power functions, the NPU is the better choice.
-
-Additionally we have demonstrated how the NPU can be used as an interpretable
-model that can recover governing equations of dynamical systems purely from
-data.
+multiplication specialist NMU (Sec.~\ref{sub:simple_arithmetic_task} \&
+\ref{sub:large_scale_arithmetic_task}).\\
+Additionally we have demonstrated that the NPU converges consistently, even on
+sequential tasks and that can be used as a highly interpretable by recovering
+the  governing equations of dynamical systems purely from data
+(Sec.~\ref{sub:fractional_sir_model}).
 
@@
 
+\newpage
 \appendix
@@
   \centering
-  \caption{Validation error of the different models (i.e. mean of each heatmap
-  in Fig.~\ref{fig:simple_err}). Each value is obtained by averaging the error
-  of 20 models.
-  }
+  \caption{Model definitions for the fSIR task.}
+  \label{tab:fsir_models}
+  \begin{tabular}{llll}
+    \toprule
+    Model & Layer 1 & Layer 2 & Layer 3 \\
+    \midrule
+    NPU & $\npu(3,\,h)$ & $\nau(h,\,3)$ & -- \\
+    NPU & NPU$_{\text{real}}(3,\,h)$ & $\nau(h,\,3)$ & -- \\
+    Dense & $\dense(2,\,h,\sigma)$ & $\dense(h,\,h,\,\sigma)$ & $\dense(h,\,3)$ \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\begin{table}[h]
+  \centering
+  \caption{Testing error on the simple arithmetic task for the different models
+  (i.e. mean of each heatmap in Fig.~\ref{fig:simple_err}). Each value is
+  obtained by averaging the error of 20 models.}
   \label{tab:simple_err}
@@
   \centering
-  \caption{Model definitions for the simple arithmetic task}
+  \caption{Model definitions for the simple arithmetic task.}
   \label{tab:models_simple_task}
@@
 \begin{table}[h]
-  \caption{Model definitions for the large scale arithmetic task}
+  \centering
+  \caption{Model definitions for the large scale arithmetic task.}
   \label{tab:models_large_task}
@@
   \centering
-  \caption{fSIR model definitions}
-  \label{tab:fsir_models}
-  \begin{tabular}{llll}
+  \caption{Training parameters for the large scale arithmetic task. The
+  $\beta$-parameters define the stepwise exponential growth of the L1
+  regularization with start, step, growth, and end.}
+  \label{tab:training_large_scale}
+  \begin{tabular}{lcccccc}
     \toprule
-    Model & Layer 1 & Layer 2 & Layer 3 \\
+    Task & Learning rate & Iterations & $\beta_{\text{start}}$ &
+      $\beta_{\text{end}}$ & $\beta_{\text{step}}$  & $\beta_{\text{growth}}$ \\
     \midrule
-    NPU & $\npu(3,\,h)$ & $\nau(h,\,3)$ & -- \\
-    NPU & NPU$_{\text{real}}(3,\,h)$ & $\nau(h,\,3)$ & -- \\
-    Dense & $\dense(2,\,h,\sigma)$ & $\dense(h,\,h,\,\sigma)$ & $\dense(h,\,3)$ \\
+    Add  & 1e-2 & 1e5 & 1e-5 & 1e-4 & 10\,000 & 10 \\
+    Mult & 5e-3 & 1e5 & 1e-5 & 1e-7 & 10\,000 & 10 \\
+    Div  & 5e-3 & 1e5 & 1e-9 & 1e-7 & 10\,000 & 10 \\
+    Sqrt & 5e-3 & 1e5 & 1e-6 & 1e-4 & 10\,000 & 10 \\
     \bottomrule

### 2020-06-04 scripts/arithmetic/add_l1_runs.jl
inalu

@@ -55,7 +55,7 @@ end
 config = AddL1SearchConfig()
 @progress name="All runs: " for i in 1:10
     @info config
-    for m in ["gatednpux","nalu","nmu","npux"]
+    for m in ["gatednpux","nalu","nmu","npux","inalu"]
         config = if m == "nmu"
             AddL1SearchConfig(run=i, model=m, βstart=1f-7, niters=10000)
         else

### 2020-06-04 scripts/arithmetic/invx_l1_runs.jl

@@ -56,7 +56,7 @@ end
 config = DivL1SearchConfig()
 @progress name="All runs: " for i in 1:10
     @info config
-    for m in ["gatednpux","nalu","nmu","npux"]
+    for m in ["gatednpux","nalu","nmu","npux","inalu"]
         config = DivL1SearchConfig(run=i, model=m)
         res, fname = produce_or_load(datadir(basename(splitext(@__FILE__)[1])),
                                      config, run, digits=10)

### 2020-06-04 scripts/arithmetic/mult_l1_runs.jl

@@ -55,7 +55,7 @@ end
 config = MultL1SearchConfig()
 @progress name="All runs: " for i in 1:20
     @info config
-    for m in ["gatednpux","nalu","nmu","npux"]
+    for m in ["gatednpux","nalu","nmu","npux","inalu"]
         config = if m == "nmu"
             MultL1SearchConfig(run=i, model=m, βstart=1f-9, niters=20000)
         else

### 2020-06-04 scripts/arithmetic/sqrt_l1_runs.jl

@@ -56,7 +56,7 @@ end
 config = SqrtL1SearchConfig()
 @progress name="All runs: " for i in 1:10
     @info config
-    for m in ["gatednpux","nalu","nmu","npux"]
+    for m in ["gatednpux","nalu","nmu","npux","inalu"]
         config = SqrtL1SearchConfig(run=i, model=m)
         res, fname = produce_or_load(datadir(basename(splitext(@__FILE__)[1])),
                                      config, run, digits=10)

### 2020-06-04 scripts/simple/plots.jl

@@ -24,7 +24,7 @@ end
 folder = datadir("simple")
 run = 19
 npu = load(joinpath(folder, "pos-gatednpux_lr=0.005_niters=20000_run=10_βl1=0.bson"))[:model]
-run = 1
+run = 11
 realnpu = load(joinpath(folder, "pos-realnpu_lr=0.005_niters=20000_run=$(run)_βl1=0.bson"))[:model]
 run = 8
 nalu = load(joinpath(folder, "pos-nalu_lr=0.005_niters=20000_run=$(run).bson"))[:model]

### 2020-06-04 scripts/simple/results_table.jl

@@ -135,7 +135,7 @@ function latex_table(results::DataFrame)
 raw"""
 \begin{tabular}{lccccc}
 \toprule
-Task & GatedNPU & NMU & NALU & iNALU & Dense\\
+Task & NPU & NMU & NALU & iNALU & Dense\\
 \midrule
 """ *
 "Add  & $(r1[1,:GatedNPU]) & $(r1[1,:NMU]) & $(r1[1,:NALU]) & $(r1[1,:iNALU]) & $(r1[1,:Dense]) \\\\\n" *

### 2020-06-04 scripts/arithmetic/revalidate.jl
RealNPU testing

@@ -47,7 +47,8 @@ nrparams(m::GatedNPUX, thresh) = sum(map(x->nrparams(x,thresh), [m.Re,m.Im,m.g])
 nrparams(m::GatedNPU, thresh) = sum(map(x->nrparams(x,thresh), [m.W,m.g]))
 nrparams(m::NAC, thresh) = sum(map(x->nrparams(x,thresh), [m.W,m.M]))
 nrparams(m::NALU, thresh) = sum(map(x->nrparams(x,thresh), [m.nac,m.G,m.b]))
-nrparams(m::Chain, thres) = sum(map(x->nrparams(x,thres), m))
+nrparams(m::iNALU, thresh) = sum(map(x->nrparams(x,thresh), [m.m_nac,m.a_nac,m.G]))
+nrparams(m::Chain, thresh) = sum(map(x->nrparams(x,thresh), m))
 
 task(x::Array,c::SqrtL1SearchConfig) = sqrt(x,c.subset)
 task(x::Array,c::DivL1SearchConfig) = invx(x,c.subset)
@@ -66,9 +67,11 @@ function create_table(df, key)
     table = DataFrame()
     table.task = unique(df.task)
     table.gatednpux = Vector{}(undef, 4)
+    table.gatednpu = Vector{}(undef, 4)
     table.nalu = Vector{}(undef, 4)
     table.nmu = Vector{}(undef, 4)
     table.npux = Vector{}(undef, 4)
+    table.inalu = Any[missing for i=1:4]
     
     for gdf in groupby(μdf, ["model","task"])
         row = gdf[1,:]
@@ -125,15 +128,15 @@ function latex_table(results::DataFrame)
 
     latex_str = (
 raw"""
-\begin{tabular}{lcccc}
+\begin{tabular}{lccccc}
 \toprule
-Task & NPU & NALU & NMU & NaiveNPU\\
+Task & NPU & RealNPU & NALU & NMU & NaiveNPU\\
 \midrule
 """ *
-"Add  & $(r1[1,:gatednpux]) & $(r1[1,:nalu]) & $(r1[1,:nmu]) & $(r1[1,:npux]) \\\\\n" *
[…]

### 2020-06-04 scripts/simple/plots.jl
plot update

@@ -24,7 +24,7 @@ end
 folder = datadir("simple")
 run = 19
 npu = load(joinpath(folder, "pos-gatednpux_lr=0.005_niters=20000_run=10_βl1=0.bson"))[:model]
-run = 11
+run = 9
 realnpu = load(joinpath(folder, "pos-realnpu_lr=0.005_niters=20000_run=$(run)_βl1=0.bson"))[:model]
 run = 8
 nalu = load(joinpath(folder, "pos-nalu_lr=0.005_niters=20000_run=$(run).bson"))[:model]
@@ -45,7 +45,7 @@ plotsize = (1000,200)
 layout = grid(1,5)
 cmap = cgrad(:inferno, rev=true)
 
-clim = (-3,2)
+clim = (-4,2)
 clip(x) = max(min(x,clim[2]),clim[1])
 levels = range(clim..., length=10)
 rminvalid = clip ∘ nantozero ∘ inftoextreme

### 2020-06-04 scripts/simple/results_table.jl

@@ -53,6 +53,7 @@ function delete_from_savename(path,key)
 end
 
 name(m::GatedNPUX) = "NPU"
+name(m::GatedNPU) = "RealNPU"
 name(m::Dense) = "Dense"
 name(m::NALU) = "NALU"
 name(m::NMU) = "NMU"
@@ -74,9 +75,8 @@ Creates table like this:
 | task | npu | npux | ... |
 """
 function table_models_tasks(df::DataFrame)
-    result = DataFrame(Union{Measurement,Missing}, 4, length(df.model)+1)
-    rename!(result, vcat(["task"], df.model))
-    result[!,1] = ["Add", "Mult", "Div", "Sqrt"]
+    result = DataFrame()
+    result.task = ["Add", "Mult", "Div", "Sqrt"]
 
     for m in df.model
         mdf = filter(:model=>model->model==m, df)
@@ -133,15 +133,15 @@ function latex_table(results::DataFrame)
 
     latex_str = (
 raw"""
-\begin{tabular}{lccccc}
+\begin{tabular}{lcccccc}
 \toprule
-Task & NPU & NMU & NALU & iNALU & Dense\\
+Task & NPU & RealNPU & NMU & NALU & iNALU & Dense\\
 \midrule
 """ *
-"Add  & $(r1[1,:GatedNPU]) & $(r1[1,:NMU]) & $(r1[1,:NALU]) & $(r1[1,:iNALU]) & $(r1[1,:Dense]) \\\\\n" *
-"Mult & $(r2[1,:GatedNPU]) & $(r2[1,:NMU]) & $(r2[1,:NALU]) & $(r2[1,:iNALU]) & $(r2[1,:Dense]) \\\\\n" *
-"Div  & $(r3[1,:GatedNPU]) & $(r3[1,:NMU]) & $(r3[1,:NALU]) & $(r3[1,:iNALU]) & $(r3[1,:Dense]) \\\\\n" *
-"Sqrt & $(r4[1,:GatedNPU]) & $(r4[1,:NMU]) & $(r4[1,:NALU]) & $(r4[1,:iNALU]) & $(r4[1,:Dense]) \\\\\n" *
[…]

### 2020-06-04 plots/pareto.tex
update plots

@@
 \begin{tikzpicture}[/tikz/background rectangle/.style={fill={rgb,1:red,1.0;green,1.0;blue,1.0}, draw opacity={1.0}}, show background rectangle]
-\begin{axis}[point meta max={nan}, point meta min={nan}, legend cell align={left}, title={}, title style={at={{(0.5,1)}}, anchor={south}, font={{\fontsize{14 pt}{18.2 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, legend style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid, fill={rgb,1:red,1.0;green,1.0;blue,1.0}, fill opacity={1.0}, text opacity={1.0}, font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, at={(1.02, 1)}, anchor={north west}}, axis background/.style={fill={rgb,1:red,1.0;green,1.0;blue,1.0}, opacity={1.0}}, anchor={north west}, xshift={1.0mm}, yshift={-1.0mm}, width={55.15mm}, height={48.8mm}, scaled x ticks={false}, xlabel={Nr.
+\begin{axis}[point meta max={nan}, point meta min={nan}, legend cell align={left}, title={Addition +}, title style={at={{(0.5,1)}}, anchor={south}, font={{\fontsize{14 pt}{18.2 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, legend style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid, fill={rgb,1:red,1.0;green,1.0;blue,1.0}, fill opacity={1.0}, text opacity={1.0}, font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, at={(1.02, 1)}, anchor={north west}}, axis background/.style={fill={rgb,1:red,1.0;green,1.0;blue,1.0}, opacity={1.0}}, anchor={north west}, xshift={1.0mm}, yshift={-1.0mm}, width={53.9mm}, height={48.8mm}, scaled x ticks={false}, xlabel={Nr.
 Parameters}, x tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, x tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, xlabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, xmode={log}, log basis x={10}, xmajorgrids={true}, xmin={76.74464101797544}, xmax={14403.350974579345}, xtick={{100.0,316.22776601683796,1000.0,3162.2776601683795,10000.0}}, xticklabels={{$10^{2.0}$,$10^{2.5}$,$10^{3.0}$,$10^{3.5}$,$10^{4.0}$}}, xtick align={inside}, xticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, x grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis x line*={left}, x axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}, scaled y ticks={false}, ylabel={Testing MSE}, y tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, y tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, ylabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, ymode={log}, log basis y={10}, ymajorgrids={true}, ymin={0.0005672734950819899}, ymax={291455.14136474277}, ytick={{0.01,1.0,100.0,10000.0}}, yticklabels={{$10^{-2}$,$10^{0}$,$10^{2}$,$10^{4}$}}, ytick align={inside}, yticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, y grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis y line*={left}, y axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}]
-    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={8432bdbe-b384-493b-a894-2ca9aed19dd4}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={4e00da13-c81a-470c-a3b8-db36919bcc4d}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={19c422f2-2c28-4773-bff4-dbd0b472008a}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={17424e8b-9d66-41d4-9342-6596addcfe97}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={2a7cf6d3-80f4-4533-929d-ea31232589ab}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={919a0304-361e-43fb-8e22-2dd0aa37e393}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={b82a4fdf-f8e3-4a56-bc52-e5e1e40eaa88}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={8a503cae-0298-4a7f-9779-9cdbb9c372ab}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
+    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={bf5fbc96-bfd6-4b9c-b7c4-ae90124f2ed9}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+        coordinates {
+            (1548.0,0.0018769886)
+            (710.0,0.03349527)
+            (700.0,0.046460856)
+            (293.0,0.054348093)
+            (1789.0,0.061003357)
+            (852.0,0.06593462)
+            (1782.0,0.07093585)
+            (1283.0,0.07464155)
+            (1837.0,0.0866325)
+            (695.0,0.15184522)
+        }
+        ;
 \end{axis}
-\begin{axis}[point meta max={nan}, point meta min={nan}, legend cell align={left}, title={}, title style={at={{(0.5,1)}}, anchor={south}, font={{\fontsize{14 pt}{18.2 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, legend style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid, fill={rgb,1:red,1.0;green,1.0;blue,1.0}, fill opacity={1.0}, text opacity={1.0}, font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, at={(1.02, 1)}, anchor={north west}}, axis background/.style={fill={rgb,1:red,1.0;green,1.0;blue,1.0}, opacity={1.0}}, anchor={north west}, xshift={58.15mm}, yshift={-1.0mm}, width={55.15mm}, height={48.8mm}, scaled x ticks={false}, xlabel={Nr.
+\begin{axis}[point meta max={nan}, point meta min={nan}, legend cell align={left}, title={Multiplication $\times$}, title style={at={{(0.5,1)}}, anchor={south}, font={{\fontsize{14 pt}{18.2 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, legend style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid, fill={rgb,1:red,1.0;green,1.0;blue,1.0}, fill opacity={1.0}, text opacity={1.0}, font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, at={(1.02, 1)}, anchor={north west}}, axis background/.style={fill={rgb,1:red,1.0;green,1.0;blue,1.0}, opacity={1.0}}, anchor={north west}, xshift={56.9mm}, yshift={-1.0mm}, width={53.9mm}, height={48.8mm}, scaled x ticks={false}, xlabel={Nr.
 Parameters}, x tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, x tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, xlabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, xmode={log}, log basis x={10}, xmajorgrids={true}, xmin={89.49402359104843}, xmax={35417.024208050476}, xtick={{100.0,316.22776601683796,1000.0,3162.2776601683795,10000.0,31622.776601683792}}, xticklabels={{$10^{2.0}$,$10^{2.5}$,$10^{3.0}$,$10^{3.5}$,$10^{4.0}$,$10^{4.5}$}}, xtick align={inside}, xticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, x grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis x line*={left}, x axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}, scaled y ticks={false}, ylabel={}, y tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, y tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, ylabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, ymode={log}, log basis y={10}, ymajorgrids={true}, ymin={0.1}, ymax={100000.0}, ytick={{0.1,1.0,10.0,100.0,1000.0,10000.0,100000.0}}, yticklabels={{$10^{-1}$,$10^{0}$,$10^{1}$,$10^{2}$,$10^{3}$,$10^{4}$,$10^{5}$}}, ytick align={inside}, yticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, y grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis y line*={left}, y axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}]
-    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={ca743fe9-f865-4257-9e33-032174efb577}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={1194bc33-0414-403c-af71-4325d2088744}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={718cbf1c-0e6b-42da-8705-e6a8efb5b5de}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={349954f1-76cd-4bca-8826-e8c5478cb8f6}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={3adb2d3b-7fa3-4ded-a575-cc69f8a5d964}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={6f792b56-8565-4a9c-a0b1-e1b34a960cf1}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
             (383.0,27781.611)
-            (385.0,27991.143)
+            (382.0,27806.723)
         }
         ;
-    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={1b311080-2e2a-4c14-b593-bbd939282850}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={1f1b30b7-99b6-4839-b4db-6b81b5c207a6}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
             (9938.0,687.11816)
+            (9952.0,750.4087)
             (9950.0,1251.8556)
@@
             (10056.0,4618.8584)
-            (9946.0,5408.8984)
+        }
+        ;
+    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={983c27c4-9507-442e-832b-e279e315fb14}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+        coordinates {
+            (1225.0,1.842417)
+            (1782.0,2.1201491)
+            (2933.0,2.320873)
+            (2546.0,2.38704)
+            (2534.0,2.942488)
+            (2345.0,3.2445307)
+            (2640.0,3.3460565)
+            (1463.0,3.474382)
+            (2661.0,6.0047293)
+            (2411.0,6.7132235)
         }
@@
 \end{axis}
-\begin{axis}[point meta max={nan}, point meta min={nan}, legend cell align={left}, title={}, title style={at={{(0.5,1)}}, anchor={south}, font={{\fontsize{14 pt}{18.2 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, legend style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid, fill={rgb,1:red,1.0;green,1.0;blue,1.0}, fill opacity={1.0}, text opacity={1.0}, font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, at={(1.02, 1)}, anchor={north west}}, axis background/.style={fill={rgb,1:red,1.0;green,1.0;blue,1.0}, opacity={1.0}}, anchor={north west}, xshift={115.3mm}, yshift={-1.0mm}, width={55.15mm}, height={48.8mm}, scaled x ticks={false}, xlabel={Nr.
+\begin{axis}[point meta max={nan}, point meta min={nan}, legend cell align={left}, title={Division $\div$}, title style={at={{(0.5,1)}}, anchor={south}, font={{\fontsize{14 pt}{18.2 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, legend style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid, fill={rgb,1:red,1.0;green,1.0;blue,1.0}, fill opacity={1.0}, text opacity={1.0}, font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, at={(1.02, 1)}, anchor={north west}}, axis background/.style={fill={rgb,1:red,1.0;green,1.0;blue,1.0}, opacity={1.0}}, anchor={north west}, xshift={112.8mm}, yshift={-1.0mm}, width={53.9mm}, height={48.8mm}, scaled x ticks={false}, xlabel={Nr.
 Parameters}, x tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, x tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, xlabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, xmode={log}, log basis x={10}, xmajorgrids={true}, xmin={43.480244741743846}, xmax={24215.503069354898}, xtick={{100.0,316.22776601683796,1000.0,3162.2776601683795,10000.0}}, xticklabels={{$10^{2.0}$,$10^{2.5}$,$10^{3.0}$,$10^{3.5}$,$10^{4.0}$}}, xtick align={inside}, xticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, x grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis x line*={left}, x axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}, scaled y ticks={false}, ylabel={}, y tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, y tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, ylabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, ymode={log}, log basis y={10}, ymajorgrids={true}, ymin={3.003128636465643e-10}, ymax={1.0476863806782078e31}, ytick={{1.0,1.0e10,1.0e20,1.0e30}}, yticklabels={{$10^{0}$,$10^{10}$,$10^{20}$,$10^{30}$}}, ytick align={inside}, yticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, y grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis y line*={left}, y axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}]
-    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={25c6bfe2-b14c-4d58-812c-34611c63a621}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={0a7d34a8-6b04-46e4-b7a2-2c8a7956881d}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={35cbff1c-ba07-48c9-bd21-cbf564ba8620}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={3724c949-7487-474b-a429-7a1c21964e1f}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={364b3eb2-628a-44de-a4b5-f6fca4d5743c}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={a7b35447-2ba9-4fe1-be36-40d73f215c37}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={e362d5ba-5d53-4952-9528-3385a563c01a}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={7eeeb8c6-938a-4e4e-9520-d0fc3dae8e83}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
+    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={d678c89e-2af9-43ff-a744-cae1280ce438}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+        coordinates {
+            (102.0,9.266123e-7)
+            (102.0,9.790781e-7)
+            (52.0,1.0640675e-6)
+            (155.0,1.1229005e-6)
+            (204.0,1.3309487e-6)
+            (204.0,1.4702264e-6)
+            (102.0,1.7236525e-6)
+            (102.0,2.1293297e-6)
+            (102.0,2.2655001e-6)
+            (199.0,4.1704498e-6)
+        }
+        ;
 \end{axis}
-\begin{axis}[point meta max={nan}, point meta min={nan}, legend cell align={left}, title={}, title style={at={{(0.5,1)}}, anchor={south}, font={{\fontsize{14 pt}{18.2 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, legend style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid, fill={rgb,1:red,1.0;green,1.0;blue,1.0}, fill opacity={1.0}, text opacity={1.0}, font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, at={(1.02, 1)}, anchor={north west}}, axis background/.style={fill={rgb,1:red,1.0;green,1.0;blue,1.0}, opacity={1.0}}, anchor={north west}, xshift={172.45mm}, yshift={-1.0mm}, width={55.15mm}, height={48.8mm}, scaled x ticks={false}, xlabel={Nr.
-Parameters}, x tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, x tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, xlabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, xmode={log}, log basis x={10}, xmajorgrids={true}, xmin={86.16627370302126}, xmax={33416.29939718559}, xtick={{100.0,316.22776601683796,1000.0,3162.2776601683795,10000.0,31622.776601683792}}, xticklabels={{$10^{2.0}$,$10^{2.5}$,$10^{3.0}$,$10^{3.5}$,$10^{4.0}$,$10^{4.5}$}}, xtick align={inside}, xticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, x grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis x line*={left}, x axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}, scaled y ticks={false}, ylabel={}, y tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, y tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, ylabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, ymode={log}, log basis y={10}, ymajorgrids={true}, ymin={0.0014075044814322237}, ymax={2.162048835278372e21}, ytick={{1.0,100000.0,1.0e10,1.0e15,1.0e20}}, yticklabels={{$10^{0}$,$10^{5}$,$10^{10}$,$10^{15}$,$10^{20}$}}, ytick align={inside}, yticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, y grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis y line*={left}, y axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}]
-    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={ebdc7105-4d92-4a3f-95d2-02699858279c}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+\begin{axis}[point meta max={nan}, point meta min={nan}, legend cell align={left}, title={Square root $\sqrt\cdot$}, title style={at={{(0.5,1)}}, anchor={south}, font={{\fontsize{14 pt}{18.2 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, legend style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid, fill={rgb,1:red,1.0;green,1.0;blue,1.0}, fill opacity={1.0}, text opacity={1.0}, font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, at={(1.02, 0.5)}, anchor={west}}, axis background/.style={fill={rgb,1:red,1.0;green,1.0;blue,1.0}, opacity={1.0}}, anchor={north west}, xshift={168.7mm}, yshift={-1.0mm}, width={53.9mm}, height={48.8mm}, scaled x ticks={false}, xlabel={Nr.
+Parameters}, x tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, x tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, xlabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, xmode={log}, log basis x={10}, xmajorgrids={true}, xmin={86.16627370302126}, xmax={33416.29939718559}, xtick={{100.0,316.22776601683796,1000.0,3162.2776601683795,10000.0,31622.776601683792}}, xticklabels={{$10^{2.0}$,$10^{2.5}$,$10^{3.0}$,$10^{3.5}$,$10^{4.0}$,$10^{4.5}$}}, xtick align={inside}, xticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, x grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis x line*={left}, x axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}, scaled y ticks={false}, ylabel={}, y tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, y tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, ylabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, ymode={log}, log basis y={10}, ymajorgrids={true}, ymin={0.0001}, ymax={1.0e10}, ytick={{0.0001,0.01,1.0,100.0,10000.0,1.0e6,1.0e8,1.0e10}}, yticklabels={{$10^{-4}$,$10^{-2}$,$10^{0}$,$10^{2}$,$10^{4}$,$10^{6}$,$10^{8}$,$10^{10}$}}, ytick align={inside}, yticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, y grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis y line*={left}, y axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}]
+    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={25f20392-b69f-49bd-a635-0be03c74c855}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={554d6241-181a-4734-8d6d-49428305bc1c}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addlegendentry {NPU}
+    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={68d53f2f-7b24-4ac4-b8a2-c2ec04d25fe9}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={55056117-138d-4bdc-a592-4d4fe5a3384e}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addlegendentry {NALU}
+    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={4a827bf3-4301-46d5-8b87-27d268d54885}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={f886d280-b26f-49cb-9603-d33a459d2008}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addlegendentry {NMU}
+    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={3b8108b1-72e4-46dd-9625-3954f74836c5}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
+    \addlegendentry {NaiveNPU}
+    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={98b1028a-bf3d-423a-ba40-eda339d793e0}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+        coordinates {
+            (102.0,0.0059641865)
+            (103.0,0.0059833615)
+            (102.0,0.006018219)
+            (104.0,0.006055212)
+            (102.0,0.0060669794)
+            (206.0,0.027170373)
+            (104.0,0.051722735)
+            (103.0,0.051742423)
+            (104.0,0.051764812)
+            (102.0,0.051804516)
+        }
+        ;
+    \addlegendentry {RealNPU}
 \end{axis}

### 2020-06-04 scripts/arithmetic/pareto.jl

@@ -17,7 +17,8 @@ pgfplotsx()
 include(joinpath(@__DIR__, "sobolconfigs.jl"))
 include(srcdir("arithmetic_dataset.jl"))
 
-res = load(datadir("pareto","thresh=1e-5.bson"))
+#res = load(datadir("pareto","thresh=1e-5.bson"))
+res = load("/home/niklas/repos/npu/data/pareto/thresh=1e-5.bson")
 df = combine(groupby(res[:df], ["model","task"])) do gdf
     gdf = sort(DataFrame(gdf),"val")
     gdf[1:min(10,size(gdf,1)),:]
@@ -31,15 +32,20 @@ end
 models = Dict("npux"=>"NaiveNPU",
               "gatednpux"=>"NPU",
               "nalu"=>"NALU",
-              "nmu"=>"NMU")
+              "nmu"=>"NMU",
+              "gatednpu"=>"RealNPU")
 ms     = 4
 alpha  = 0.7
 xscale = :log10
 yscale = :log10
-plotmodels = [(:circle,"gatednpux"),(:pentagon,"nalu"),(:diamond,"nmu"),(:utriangle,"npux")]
+plotmodels = [(:circle,"gatednpux"),(:pentagon,"nalu"),(:diamond,"nmu"),
+              (:utriangle,"npux"),(:rect,"gatednpu")]
 #plotmodels = ["gatednpux","nalu","nmu"]
 
-s1,s2,s3,s4=plot(),plot(),plot(),plot()
+s1 = plot(title="Addition +")
+s2 = plot(title="Multiplication \$\\times\$")
+s3 = plot(title="Division \$\\div\$")
+s4 = plot(title="Square root \$\\sqrt\\cdot\$")
 pdf  = filter(row->row.task=="add", df)
 for (marker,model) in plotmodels
     mdf = filter(row->row.model==model, pdf)
@@ -69,7 +75,7 @@ for (marker,model) in plotmodels
     mdf = filter(row->row.model==model, pdf)
     scatter!(s4, mdf.nrps, mdf.val, marker=marker,
              label=models[model], yscale=yscale, xscale=xscale, alpha=alpha, ms=ms,
-             legend=false, xlabel="Nr. Parameters")
+             legend=:outerright, xlabel="Nr. Parameters", ylim=(1e-4,1e10))
 end
 
 p1 = plot(s1,s2,s3,s4,layout=(1,4), size=(900,200))
[…]

### 2020-06-04 scripts/simple/plots.jl

@@ -81,88 +81,90 @@ pyplot()
 @info "Plotting NPU..."
 npuadd = contour(posnegx, posnegy, (x,y)->npu_addloss(x,y),
              c=cmap, clim=clim,
-             levels=levels, fill=true, colorbar=false, aspect_ratio=:equal)
+             levels=levels, fill=true, colorbar=false)
 npumult = contour(posnegx, posnegy, (x,y)->npu_multloss(x,y),
              c=cmap, clim=clim,
-             levels=levels, fill=true, colorbar=false, aspect_ratio=:equal)
+             levels=levels, fill=true, colorbar=false)
 npudiv = contour(posnegx, posnegy, (x,y)->npu_divloss(x,y),
              c=cmap, clim=clim,
-             levels=levels, fill=true, colorbar=false, aspect_ratio=:equal)
+             levels=levels, fill=true, colorbar=false)
 npusqrt = contour(posx, posy, (x,y)->npu_sqrtloss(x,y),
              c=cmap, clim=clim,
-             levels=levels, fill=true, colorbar=false, aspect_ratio=:equal)
+             levels=levels, fill=true, colorbar=false)
 
 @info "Plotting RealNPU..."
 realnpuadd = contour(posnegx, posnegy, (x,y)->realnpu_addloss(x,y),
              c=cmap, clim=clim,
-             levels=levels, fill=true, colorbar=false, aspect_ratio=:equal)
+             levels=levels, fill=true, colorbar=false)
 realnpumult = contour(posnegx, posnegy, (x,y)->realnpu_multloss(x,y),
              c=cmap, clim=clim,
-             levels=levels, fill=true, colorbar=false, aspect_ratio=:equal)
+             levels=levels, fill=true, colorbar=false)
 realnpudiv = contour(posnegx, posnegy, (x,y)->realnpu_divloss(x,y),
              c=cmap, clim=clim,
-             levels=levels, fill=true, colorbar=false, aspect_ratio=:equal)
+             levels=levels, fill=true, colorbar=false)
 realnpusqrt = contour(posx, posy, (x,y)->realnpu_sqrtloss(x,y),
              c=cmap, clim=clim,
-             levels=levels, fill=true, colorbar=false, aspect_ratio=:equal)
+             levels=levels, fill=true, colorbar=false)
 
 @info "Plotting NALU..."
 naluadd = contour(posnegx, posnegy, (x,y)->nalu_addloss(x,y),
[…]

### 2020-06-04 scripts/arithmetic/revalidate.jl
use median and mad

@@ -144,6 +144,7 @@ raw"""\bottomrule
    
 end
 
+mad(x) = median(abs.(x .- median(x)))
 
 
 (res,fname) = produce_or_load(datadir("pareto"),
@@ -168,14 +169,14 @@ end
 
 # average runs
 μdf = combine(groupby(df,["model","task"])) do gdf
-    σmse = std(gdf.mse)
-    σval = std(gdf.val)
+    σmse = mad(gdf.mse)
+    σval = mad(gdf.val)
     σmse = isinf(σmse) ? 1e20 : σmse
     σval = isinf(σval) ? 1e20 : σval
     (task = gdf.task[1],
      model = gdf.model[1],
-     mse = measurement(mean(gdf.mse), σmse),
-     val = measurement(mean(gdf.val), σval),
+     mse = measurement(median(gdf.mse), σmse),
+     val = measurement(median(gdf.val), σval),
     )
 end
 

### 2020-06-04 plots/pareto.tex
plots update

@@
 Parameters}, x tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, x tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, xlabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, xmode={log}, log basis x={10}, xmajorgrids={true}, xmin={76.74464101797544}, xmax={14403.350974579345}, xtick={{100.0,316.22776601683796,1000.0,3162.2776601683795,10000.0}}, xticklabels={{$10^{2.0}$,$10^{2.5}$,$10^{3.0}$,$10^{3.5}$,$10^{4.0}$}}, xtick align={inside}, xticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, x grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis x line*={left}, x axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}, scaled y ticks={false}, ylabel={Testing MSE}, y tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, y tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, ylabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, ymode={log}, log basis y={10}, ymajorgrids={true}, ymin={0.0005672734950819899}, ymax={291455.14136474277}, ytick={{0.01,1.0,100.0,10000.0}}, yticklabels={{$10^{-2}$,$10^{0}$,$10^{2}$,$10^{4}$}}, ytick align={inside}, yticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, y grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis y line*={left}, y axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}]
-    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={4e00da13-c81a-470c-a3b8-db36919bcc4d}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={e3f051b4-a68e-486f-b608-6a13dc46bdb0}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={17424e8b-9d66-41d4-9342-6596addcfe97}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={ef39af70-0a29-4a15-8e65-bca546ca9489}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+        coordinates {
+            (1548.0,0.0018769886)
+            (710.0,0.03349527)
+            (700.0,0.046460856)
+            (293.0,0.054348093)
+            (1789.0,0.061003357)
+            (852.0,0.06593462)
+            (1782.0,0.07093585)
+            (1283.0,0.07464155)
+            (1837.0,0.0866325)
+            (695.0,0.15184522)
+        }
+        ;
+    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={8a5e683d-9b46-406e-a65b-a3ed6d04efe6}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={919a0304-361e-43fb-8e22-2dd0aa37e393}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={7779a9b0-66f9-4007-96f4-e6d2ec265c78}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={8a503cae-0298-4a7f-9779-9cdbb9c372ab}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={3b6a467a-a7d8-40ea-8aae-58982e4c7813}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={bf5fbc96-bfd6-4b9c-b7c4-ae90124f2ed9}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
-        coordinates {
-            (1548.0,0.0018769886)
-            (710.0,0.03349527)
-            (700.0,0.046460856)
-            (293.0,0.054348093)
-            (1789.0,0.061003357)
-            (852.0,0.06593462)
-            (1782.0,0.07093585)
-            (1283.0,0.07464155)
-            (1837.0,0.0866325)
-            (695.0,0.15184522)
-        }
-        ;
 \end{axis}
@@
 Parameters}, x tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, x tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, xlabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, xmode={log}, log basis x={10}, xmajorgrids={true}, xmin={89.49402359104843}, xmax={35417.024208050476}, xtick={{100.0,316.22776601683796,1000.0,3162.2776601683795,10000.0,31622.776601683792}}, xticklabels={{$10^{2.0}$,$10^{2.5}$,$10^{3.0}$,$10^{3.5}$,$10^{4.0}$,$10^{4.5}$}}, xtick align={inside}, xticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, x grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis x line*={left}, x axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}, scaled y ticks={false}, ylabel={}, y tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, y tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, ylabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, ymode={log}, log basis y={10}, ymajorgrids={true}, ymin={0.1}, ymax={100000.0}, ytick={{0.1,1.0,10.0,100.0,1000.0,10000.0,100000.0}}, yticklabels={{$10^{-1}$,$10^{0}$,$10^{1}$,$10^{2}$,$10^{3}$,$10^{4}$,$10^{5}$}}, ytick align={inside}, yticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, y grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis y line*={left}, y axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}]
-    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={1194bc33-0414-403c-af71-4325d2088744}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={514f4e34-2ec4-404f-bee4-1e7a5c8c498c}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={349954f1-76cd-4bca-8826-e8c5478cb8f6}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={03945ca4-8958-4986-865f-d38ba070b814}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+        coordinates {
+            (1225.0,1.842417)
+            (1782.0,2.1201491)
+            (2933.0,2.320873)
+            (2546.0,2.38704)
+            (2534.0,2.942488)
+            (2345.0,3.2445307)
+            (2640.0,3.3460565)
+            (1463.0,3.474382)
+            (2661.0,6.0047293)
+            (2411.0,6.7132235)
+        }
+        ;
+    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={0254ada2-8a05-4689-957e-8d313f86842e}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={6f792b56-8565-4a9c-a0b1-e1b34a960cf1}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={7be7d6c0-d826-4b63-85c8-4a37a5605e4a}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={1f1b30b7-99b6-4839-b4db-6b81b5c207a6}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={526a97fb-2f22-43d3-b7f0-3f08966037a5}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={983c27c4-9507-442e-832b-e279e315fb14}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
-        coordinates {
-            (1225.0,1.842417)
-            (1782.0,2.1201491)
-            (2933.0,2.320873)
-            (2546.0,2.38704)
-            (2534.0,2.942488)
-            (2345.0,3.2445307)
-            (2640.0,3.3460565)
-            (1463.0,3.474382)
-            (2661.0,6.0047293)
-            (2411.0,6.7132235)
-        }
-        ;
 \end{axis}
@@
 Parameters}, x tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, x tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, xlabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, xmode={log}, log basis x={10}, xmajorgrids={true}, xmin={43.480244741743846}, xmax={24215.503069354898}, xtick={{100.0,316.22776601683796,1000.0,3162.2776601683795,10000.0}}, xticklabels={{$10^{2.0}$,$10^{2.5}$,$10^{3.0}$,$10^{3.5}$,$10^{4.0}$}}, xtick align={inside}, xticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, x grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis x line*={left}, x axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}, scaled y ticks={false}, ylabel={}, y tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, y tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, ylabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, ymode={log}, log basis y={10}, ymajorgrids={true}, ymin={3.003128636465643e-10}, ymax={1.0476863806782078e31}, ytick={{1.0,1.0e10,1.0e20,1.0e30}}, yticklabels={{$10^{0}$,$10^{10}$,$10^{20}$,$10^{30}$}}, ytick align={inside}, yticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, y grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis y line*={left}, y axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}]
-    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={0a7d34a8-6b04-46e4-b7a2-2c8a7956881d}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={605dd1b6-3f1f-4def-9001-5889c2aae37a}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={3724c949-7487-474b-a429-7a1c21964e1f}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={0681bacc-1cbd-445a-b429-713421b04a3e}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+        coordinates {
+            (102.0,9.266123e-7)
+            (102.0,9.790781e-7)
+            (52.0,1.0640675e-6)
+            (155.0,1.1229005e-6)
+            (204.0,1.3309487e-6)
+            (204.0,1.4702264e-6)
+            (102.0,1.7236525e-6)
+            (102.0,2.1293297e-6)
+            (102.0,2.2655001e-6)
+            (199.0,4.1704498e-6)
+        }
+        ;
+    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={8ca4234d-2529-43fa-b313-caba4a4b1641}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={a7b35447-2ba9-4fe1-be36-40d73f215c37}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={c6756010-4794-44a7-a667-e80dd9f7fbf9}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={7eeeb8c6-938a-4e4e-9520-d0fc3dae8e83}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={305430f0-f2b7-45bc-a66e-638719c98bcd}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={d678c89e-2af9-43ff-a744-cae1280ce438}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
-        coordinates {
-            (102.0,9.266123e-7)
-            (102.0,9.790781e-7)
-            (52.0,1.0640675e-6)
-            (155.0,1.1229005e-6)
-            (204.0,1.3309487e-6)
-            (204.0,1.4702264e-6)
-            (102.0,1.7236525e-6)
-            (102.0,2.1293297e-6)
-            (102.0,2.2655001e-6)
-            (199.0,4.1704498e-6)
-        }
-        ;
 \end{axis}
@@
 Parameters}, x tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, x tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, xlabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, xmode={log}, log basis x={10}, xmajorgrids={true}, xmin={86.16627370302126}, xmax={33416.29939718559}, xtick={{100.0,316.22776601683796,1000.0,3162.2776601683795,10000.0,31622.776601683792}}, xticklabels={{$10^{2.0}$,$10^{2.5}$,$10^{3.0}$,$10^{3.5}$,$10^{4.0}$,$10^{4.5}$}}, xtick align={inside}, xticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, x grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis x line*={left}, x axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}, scaled y ticks={false}, ylabel={}, y tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, y tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, ylabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, ymode={log}, log basis y={10}, ymajorgrids={true}, ymin={0.0001}, ymax={1.0e10}, ytick={{0.0001,0.01,1.0,100.0,10000.0,1.0e6,1.0e8,1.0e10}}, yticklabels={{$10^{-4}$,$10^{-2}$,$10^{0}$,$10^{2}$,$10^{4}$,$10^{6}$,$10^{8}$,$10^{10}$}}, ytick align={inside}, yticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, y grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis y line*={left}, y axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}]
-    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={25f20392-b69f-49bd-a635-0be03c74c855}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={49d3470e-a697-49bc-b9f1-e8f2595862d3}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
     \addlegendentry {NPU}
-    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={68d53f2f-7b24-4ac4-b8a2-c2ec04d25fe9}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={bd4058bd-1bb7-4bcd-9b9c-64e487eca27b}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+        coordinates {
+            (102.0,0.0059641865)
+            (103.0,0.0059833615)
+            (102.0,0.006018219)
+            (104.0,0.006055212)
+            (102.0,0.0060669794)
+            (206.0,0.027170373)
+            (104.0,0.051722735)
+            (103.0,0.051742423)
+            (104.0,0.051764812)
+            (102.0,0.051804516)
+        }
+        ;
+    \addlegendentry {RealNPU}
+    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={a1423905-57ce-45da-ad9e-17ca96b4b8bf}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
     \addlegendentry {NALU}
-    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={4a827bf3-4301-46d5-8b87-27d268d54885}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={44f25ebe-f0eb-4342-beb6-60ddae64c4a9}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
     \addlegendentry {NMU}
-    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={3b8108b1-72e4-46dd-9625-3954f74836c5}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={a509524e-d232-4fc8-bcdb-3b60f960fed8}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
     \addlegendentry {NaiveNPU}
-    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={98b1028a-bf3d-423a-ba40-eda339d793e0}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
-        coordinates {
-            (102.0,0.0059641865)
-            (103.0,0.0059833615)
-            (102.0,0.006018219)
-            (104.0,0.006055212)
-            (102.0,0.0060669794)
-            (206.0,0.027170373)
-            (104.0,0.051722735)
-            (103.0,0.051742423)
-            (104.0,0.051764812)
-            (102.0,0.051804516)
-        }
-        ;
-    \addlegendentry {RealNPU}
 \end{axis}

### 2020-06-04 plots/pareto_sir.tex
plots update

@@
 Paramters}, x tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, x tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, xlabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, xmode={log}, log basis x={10}, xmajorgrids={true}, xmin={15.305486448632008}, xmax={625.3313171144225}, xtick={{15.848931924611142,25.11886431509581,39.810717055349734,63.09573444801933,100.0,158.48931924611142,251.18864315095823,398.1071705534973}}, xticklabels={{$10^{1.2}$,$10^{1.4}$,$10^{1.6}$,$10^{1.8}$,$10^{2.0}$,$10^{2.2}$,$10^{2.4}$,$10^{2.6}$}}, xtick align={inside}, xticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, x grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis x line*={left}, x axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}, scaled y ticks={false}, ylabel={MSE}, y tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, y tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, ylabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, ymode={log}, log basis y={10}, ymajorgrids={true}, ymin={0.005}, ymax={10000.0}, ytick={{0.01,0.1,1.0,10.0,100.0,1000.0,10000.0}}, yticklabels={{$10^{-2}$,$10^{-1}$,$10^{0}$,$10^{1}$,$10^{2}$,$10^{3}$,$10^{4}$}}, ytick align={inside}, yticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, y grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis y line*={left}, y axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}]
-    \addplot[color={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, name path={c6416611-1574-49a0-9ea4-91e50a33118b}, draw opacity={0.25}, line width={0}, solid, mark={*}, mark size={3.75 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.25}, fill={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, fill opacity={0.25}, line width={0.75}, rotate={0}, solid}, only marks, forget plot]
+    \addplot[color={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, name path={089ee56b-6822-4377-827c-374155ed22b5}, draw opacity={0.25}, line width={0}, solid, mark={*}, mark size={3.75 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.25}, fill={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, fill opacity={0.25}, line width={0.75}, rotate={0}, solid}, only marks, forget plot]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, name path={0b6b36d8-c846-4873-8ad0-9609ab2cf7aa}, draw opacity={0.25}, line width={0}, solid, mark={pentagon*}, mark size={3.75 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.25}, fill={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, fill opacity={0.25}, line width={0.75}, rotate={0}, solid}, only marks, forget plot]
+    \addplot[color={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, name path={fb8ade92-3de5-4181-955a-9068086f05cd}, draw opacity={0.25}, line width={0}, solid, mark={pentagon*}, mark size={3.75 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.25}, fill={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, fill opacity={0.25}, line width={0.75}, rotate={0}, solid}, only marks, forget plot]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,1.0;green,0.498;blue,0.0549}, name path={32500e26-f355-48fb-b27a-d77c0e6f6f11}, draw opacity={0.25}, line width={0}, solid, mark={diamond*}, mark size={3.75 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.25}, fill={rgb,1:red,1.0;green,0.498;blue,0.0549}, fill opacity={0.25}, line width={0.75}, rotate={0}, solid}, only marks, forget plot]
+    \addplot[color={rgb,1:red,1.0;green,0.498;blue,0.0549}, name path={a4a2407a-9d13-4d5f-9806-f4dc789913ff}, draw opacity={0.25}, line width={0}, solid, mark={diamond*}, mark size={3.75 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.25}, fill={rgb,1:red,1.0;green,0.498;blue,0.0549}, fill opacity={0.25}, line width={0.75}, rotate={0}, solid}, only marks, forget plot]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, name path={17fa3149-1072-43c8-8c21-8a953ad9b789}, draw opacity={1.0}, line width={2}, dashed]
+    \addplot[color={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, name path={6fca2f50-6519-44f2-b9d9-640264e75dcd}, draw opacity={1.0}, line width={2}, dashed]
         coordinates {
@@
     \addlegendentry {Dense}
-    \addplot[color={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, name path={92814b74-5dc8-4049-b104-86ec2005b545}, draw opacity={1.0}, line width={2}, solid]
+    \addplot[color={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, name path={4df2801f-27fe-4ea1-9f00-dbdbe35d4500}, draw opacity={1.0}, line width={2}, solid]
         coordinates {
@@
     \addlegendentry {NPU}
-    \addplot[color={rgb,1:red,1.0;green,0.498;blue,0.0549}, name path={01e229a2-0f53-4a30-b602-5c368ec01212}, draw opacity={1.0}, line width={2}, dashdotted]
+    \addplot[color={rgb,1:red,1.0;green,0.498;blue,0.0549}, name path={23f3a274-9dd0-40ba-b4c3-9bf7970f58c1}, draw opacity={1.0}, line width={2}, dashdotted]
         coordinates {
@@
         ;
-    \addlegendentry {NPU (real)}
+    \addlegendentry {RealNPU}
 \end{axis}
 \begin{axis}[point meta max={nan}, point meta min={nan}, legend cell align={left}, title={SIR Model}, title style={at={{(0.5,1)}}, anchor={south}, font={{\fontsize{14 pt}{18.2 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, legend style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid, fill={rgb,1:red,1.0;green,1.0;blue,1.0}, fill opacity={1.0}, text opacity={1.0}, font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, at={(0.98, 0.5)}, anchor={east}}, axis background/.style={fill={rgb,1:red,1.0;green,1.0;blue,1.0}, opacity={1.0}}, anchor={north west}, xshift={115.3mm}, yshift={-1.0mm}, width={112.3mm}, height={74.2mm}, scaled x ticks={false}, xlabel={Time}, x tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, x tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, xlabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, xmajorgrids={true}, xmin={-6.0}, xmax={206.0}, xtick={{0.0,50.0,100.0,150.0,200.0}}, xticklabels={{$0$,$50$,$100$,$150$,$200$}}, xtick align={inside}, xticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, x grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis x line*={left}, x axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}, scaled y ticks={false}, ylabel={}, y tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, y tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, ylabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, ymajorgrids={true}, ymin={-3.0}, ymax={103.0}, ytick={{0.0,25.0,50.0,75.0,100.0}}, yticklabels={{$0$,$25$,$50$,$75$,$100$}}, ytick align={inside}, yticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, y grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis y line*={left}, y axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}]
-    \addplot[color={rgb,1:red,0.502;green,0.502;blue,0.502}, name path={2c7c1a19-783e-45b8-ba0c-5f0d47ee61d7}, draw opacity={0.8}, line width={4}, solid]
+    \addplot[color={rgb,1:red,0.502;green,0.502;blue,0.502}, name path={4d2d32cf-0078-477b-aca5-ac47612e3b35}, draw opacity={0.8}, line width={4}, solid]
         coordinates {
@@
     \addlegendentry {True $S,I,R$}
-    \addplot[color={rgb,1:red,0.502;green,0.502;blue,0.502}, name path={1bd494f5-4860-4f91-bdd7-b6e623424164}, draw opacity={0.8}, line width={4}, solid, forget plot]
+    \addplot[color={rgb,1:red,0.502;green,0.502;blue,0.502}, name path={b32b3689-d920-4aa7-9895-f3013f9b1a1b}, draw opacity={0.8}, line width={4}, solid, forget plot]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.502;green,0.502;blue,0.502}, name path={99fd42b1-24fe-476a-9976-bd874af9786a}, draw opacity={0.8}, line width={4}, solid, forget plot]
+    \addplot[color={rgb,1:red,0.502;green,0.502;blue,0.502}, name path={d04156b5-29d1-4f76-8661-f226866e6ee2}, draw opacity={0.8}, line width={4}, solid, forget plot]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, name path={78950b23-4587-48e7-ac69-7a173b42d7ff}, draw opacity={1.0}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, fill={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, fill opacity={1.0}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, name path={daf90f21-20cf-4381-9c0f-30de95c3d54b}, draw opacity={1.0}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, fill={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, fill opacity={1.0}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
     \addlegendentry {$\hat S$}
-    \addplot[color={rgb,1:red,1.0;green,0.498;blue,0.0549}, name path={55448a83-940d-42d2-bfa5-a69e99f44840}, draw opacity={1.0}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, fill={rgb,1:red,1.0;green,0.498;blue,0.0549}, fill opacity={1.0}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,1.0;green,0.498;blue,0.0549}, name path={d719ac49-0b45-4546-885d-0971ecba6177}, draw opacity={1.0}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, fill={rgb,1:red,1.0;green,0.498;blue,0.0549}, fill opacity={1.0}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
     \addlegendentry {$\hat I$}
-    \addplot[color={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, name path={7029124d-f96e-4c96-8ccc-df7e7adb01de}, draw opacity={1.0}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, fill={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, fill opacity={1.0}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, name path={209e1cdb-c150-414a-bfc5-63b07ba91f51}, draw opacity={1.0}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, fill={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, fill opacity={1.0}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {

### 2020-06-04 scripts/arithmetic/pareto.jl

@@ -38,8 +38,8 @@ ms     = 4
 alpha  = 0.7
 xscale = :log10
 yscale = :log10
-plotmodels = [(:circle,"gatednpux"),(:pentagon,"nalu"),(:diamond,"nmu"),
-              (:utriangle,"npux"),(:rect,"gatednpu")]
+plotmodels = [(:circle,"gatednpux"),(:rect,"gatednpu"),(:pentagon,"nalu"),(:diamond,"nmu"),
+              (:utriangle,"npux")]
 #plotmodels = ["gatednpux","nalu","nmu"]
 
 s1 = plot(title="Addition +")

### 2020-06-04 scripts/fracode/pareto-sir.jl

@@ -22,6 +22,7 @@ function delete_from_savename(path,key)
     joinpath(dir, savename(dict,digits=20))
 end
 
+#@unpack df = load("/home/niklas/repos/npu/data/results_fracsir.bson")
 @unpack df = load(datadir("results_fracsir.bson"))
 df.hash = delete_from_savename.(df.path, "run")
 
@@ -92,7 +93,7 @@ plot!(p1, dense_nrps[dense_idx], dense_mse[dense_idx],
 plot!(p1, npux_nrps[npux_idx], npux_mse[npux_idx],
       c=cmap[3], label="NPU", lw=2)
 plot!(p1, npu_nrps[npu_idx], npu_mse[npu_idx],
-      c=cmap[2], label="NPU (real)", lw=2, ls=:dashdot)
+      c=cmap[2], label="RealNPU", lw=2, ls=:dashdot)
 
 plot!(p1, yscale=:log10, xscale=:log10, xlabel="Nr. Paramters", ylabel="MSE",
       ylim=(5e-3,1e4))
@@ -106,6 +107,7 @@ plot!(p2, t, x[3,:], lw=4, c=:gray, alpha=0.8, label=false)
 
 sort!(df,"mse")
 x̂ = load(datadir("fracsir", basename(df[1,"path"])))[:pred]
+#x̂ = load(joinpath("/home/niklas/repos/npu/data","fracsir", basename(df[1,"path"])))[:pred]
 scatter!(p2, t, x̂[1,:], label=L"$\hat S$", lw=2, c=cmap[1])
 scatter!(p2, t, x̂[2,:], label=L"$\hat I$", lw=2, c=cmap[2])
 scatter!(p2, t, x̂[3,:], label=L"$\hat R$", lw=2, c=cmap[3])

### 2020-06-04 plots/pareto.tex
pareto

@@
 Parameters}, x tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, x tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, xlabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, xmode={log}, log basis x={10}, xmajorgrids={true}, xmin={76.74464101797544}, xmax={14403.350974579345}, xtick={{100.0,316.22776601683796,1000.0,3162.2776601683795,10000.0}}, xticklabels={{$10^{2.0}$,$10^{2.5}$,$10^{3.0}$,$10^{3.5}$,$10^{4.0}$}}, xtick align={inside}, xticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, x grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis x line*={left}, x axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}, scaled y ticks={false}, ylabel={Testing MSE}, y tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, y tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, ylabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, ymode={log}, log basis y={10}, ymajorgrids={true}, ymin={0.0005672734950819899}, ymax={291455.14136474277}, ytick={{0.01,1.0,100.0,10000.0}}, yticklabels={{$10^{-2}$,$10^{0}$,$10^{2}$,$10^{4}$}}, ytick align={inside}, yticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, y grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis y line*={left}, y axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}]
-    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={e3f051b4-a68e-486f-b608-6a13dc46bdb0}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={120a2d09-4f86-42f7-a853-273920608e0b}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={ef39af70-0a29-4a15-8e65-bca546ca9489}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={3748f5d3-7b27-499e-9e79-84581d4b88de}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={8a5e683d-9b46-406e-a65b-a3ed6d04efe6}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={6ab26a97-21d5-4709-ad8b-4254e44384c1}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={7779a9b0-66f9-4007-96f4-e6d2ec265c78}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={9e1c25f8-c2f1-47f1-b941-01b1825010ad}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={3b6a467a-a7d8-40ea-8aae-58982e4c7813}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={dfa0d04c-341b-4a96-b094-20e10bc19841}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
 Parameters}, x tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, x tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, xlabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, xmode={log}, log basis x={10}, xmajorgrids={true}, xmin={89.49402359104843}, xmax={35417.024208050476}, xtick={{100.0,316.22776601683796,1000.0,3162.2776601683795,10000.0,31622.776601683792}}, xticklabels={{$10^{2.0}$,$10^{2.5}$,$10^{3.0}$,$10^{3.5}$,$10^{4.0}$,$10^{4.5}$}}, xtick align={inside}, xticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, x grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis x line*={left}, x axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}, scaled y ticks={false}, ylabel={}, y tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, y tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, ylabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, ymode={log}, log basis y={10}, ymajorgrids={true}, ymin={0.1}, ymax={100000.0}, ytick={{0.1,1.0,10.0,100.0,1000.0,10000.0,100000.0}}, yticklabels={{$10^{-1}$,$10^{0}$,$10^{1}$,$10^{2}$,$10^{3}$,$10^{4}$,$10^{5}$}}, ytick align={inside}, yticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, y grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis y line*={left}, y axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}]
-    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={514f4e34-2ec4-404f-bee4-1e7a5c8c498c}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={2979e0a6-bd20-4d44-93c0-5e1e5c514909}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={03945ca4-8958-4986-865f-d38ba070b814}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={3aefcca2-3c95-4a3b-b659-cb86356c953f}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={0254ada2-8a05-4689-957e-8d313f86842e}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={dd44268f-eb15-4c34-bde0-a081f9b06ca1}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={7be7d6c0-d826-4b63-85c8-4a37a5605e4a}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={bd796cda-7735-4ffd-bb8b-eb77ae77cba1}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={526a97fb-2f22-43d3-b7f0-3f08966037a5}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={f7a0af30-9047-4fa7-b207-2272899a498a}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
 Parameters}, x tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, x tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, xlabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, xmode={log}, log basis x={10}, xmajorgrids={true}, xmin={43.480244741743846}, xmax={24215.503069354898}, xtick={{100.0,316.22776601683796,1000.0,3162.2776601683795,10000.0}}, xticklabels={{$10^{2.0}$,$10^{2.5}$,$10^{3.0}$,$10^{3.5}$,$10^{4.0}$}}, xtick align={inside}, xticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, x grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis x line*={left}, x axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}, scaled y ticks={false}, ylabel={}, y tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, y tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, ylabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, ymode={log}, log basis y={10}, ymajorgrids={true}, ymin={3.003128636465643e-10}, ymax={1.0476863806782078e31}, ytick={{1.0,1.0e10,1.0e20,1.0e30}}, yticklabels={{$10^{0}$,$10^{10}$,$10^{20}$,$10^{30}$}}, ytick align={inside}, yticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, y grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis y line*={left}, y axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}]
-    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={605dd1b6-3f1f-4def-9001-5889c2aae37a}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={521e2bcb-fd9e-4c58-9112-a65567cedfcc}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={0681bacc-1cbd-445a-b429-713421b04a3e}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={7ec702db-2560-4f9e-9cd3-941184e16cc3}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={8ca4234d-2529-43fa-b313-caba4a4b1641}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={b9ccb8f0-74da-462a-8d58-b897ea8ac2d2}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={c6756010-4794-44a7-a667-e80dd9f7fbf9}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={54c1af77-4060-4716-afbd-68d3b20bc973}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
         ;
-    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={305430f0-f2b7-45bc-a66e-638719c98bcd}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={3853f9fd-185d-4d50-ac77-e5c60aa46406}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
 Parameters}, x tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, x tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, xlabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, xmode={log}, log basis x={10}, xmajorgrids={true}, xmin={86.16627370302126}, xmax={33416.29939718559}, xtick={{100.0,316.22776601683796,1000.0,3162.2776601683795,10000.0,31622.776601683792}}, xticklabels={{$10^{2.0}$,$10^{2.5}$,$10^{3.0}$,$10^{3.5}$,$10^{4.0}$,$10^{4.5}$}}, xtick align={inside}, xticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, x grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis x line*={left}, x axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}, scaled y ticks={false}, ylabel={}, y tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, y tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, ylabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, ymode={log}, log basis y={10}, ymajorgrids={true}, ymin={0.0001}, ymax={1.0e10}, ytick={{0.0001,0.01,1.0,100.0,10000.0,1.0e6,1.0e8,1.0e10}}, yticklabels={{$10^{-4}$,$10^{-2}$,$10^{0}$,$10^{2}$,$10^{4}$,$10^{6}$,$10^{8}$,$10^{10}$}}, ytick align={inside}, yticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, y grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis y line*={left}, y axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}]
-    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={49d3470e-a697-49bc-b9f1-e8f2595862d3}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.0;green,0.6056;blue,0.9787}, name path={811141d8-12d4-4843-bc39-0aeb4997e193}, draw opacity={0.7}, line width={0}, solid, mark={*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.0;green,0.6056;blue,0.9787}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
     \addlegendentry {NPU}
-    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={bd4058bd-1bb7-4bcd-9b9c-64e487eca27b}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, name path={7dbf443c-0480-4f97-ac81-2993dd1aa359}, draw opacity={0.7}, line width={0}, solid, mark={square*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.8889;green,0.4356;blue,0.2781}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
     \addlegendentry {RealNPU}
-    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={a1423905-57ce-45da-ad9e-17ca96b4b8bf}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, name path={5ec66b6b-cdcf-406a-aec0-41cfd920df3a}, draw opacity={0.7}, line width={0}, solid, mark={pentagon*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.2422;green,0.6433;blue,0.3044}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
     \addlegendentry {NALU}
-    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={44f25ebe-f0eb-4342-beb6-60ddae64c4a9}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, name path={7733a081-9332-4307-826b-4b9cd4dee297}, draw opacity={0.7}, line width={0}, solid, mark={diamond*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.7644;green,0.4441;blue,0.8243}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {
@@
     \addlegendentry {NMU}
-    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={a509524e-d232-4fc8-bcdb-3b60f960fed8}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
+    \addplot[color={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, name path={05ed5fec-1fd5-4ba5-920a-604a99cedb30}, draw opacity={0.7}, line width={0}, solid, mark={triangle*}, mark size={3.0 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.7}, fill={rgb,1:red,0.6755;green,0.5557;blue,0.0942}, fill opacity={0.7}, line width={0.75}, rotate={0}, solid}, only marks]
         coordinates {

### 2020-06-04 scripts/arithmetic/plot_npu.jl
fuzz ufzz

@@ -1,0 +1,84 @@
+using DrWatson
+@quickactivate "NIPS_2020_NPU"
+
+using Flux
+using NeuralArithmetic
+using ValueHistories
+using Plots
+pyplot()
+
+include(srcdir("arithmetic_dataset.jl"))
+include(joinpath(@__DIR__, "sobolconfigs.jl"))
+
+fname = "batch=128_fstinit=rand_inlen=100_lowlim=0_lr=0.005_model=gatednpux_niters=100000_overlap=0.25_run=1_sampler=sobol_sndinit=rand_subset=0.5_uplim=0.5_βend=1e-7_βgrowth=10_βstart=1e-9_βstep=10000.bson"
+fname = datadir("invx_l1_runs", fname)
+
+dir = "/home/niklas/repos/NIPS_2020_NPU/data"
+realnpuadd    = load(joinpath(dir, "add_l1_runs/batch=128_fstinit=rand_inlen=100_lowlim=-1_lr=0.01_model=gatednpu_niters=100000_overlap=0.25_run=7_sampler=sobol_sndinit=rand_subset=0.5_uplim=1_βend=0.0001_βgrowth=10_βstart=1e-5_βstep=10000.bson"))[:model]
+npuadd        = load(joinpath(dir, "add_l1_runs/batch=128_fstinit=rand_inlen=100_lowlim=-1_lr=0.01_model=gatednpux_niters=100000_overlap=0.25_run=14_sampler=sobol_sndinit=rand_subset=0.5_uplim=1_βend=0.0001_βgrowth=10_βstart=1e-5_βstep=10000.bson"))[:model]
+naluadd       = load(joinpath(dir, "add_l1_runs/batch=128_fstinit=rand_inlen=100_lowlim=-1_lr=0.01_model=nalu_niters=100000_overlap=0.25_run=8_sampler=sobol_sndinit=rand_subset=0.5_uplim=1_βend=0.0001_βgrowth=10_βstart=1e-5_βstep=10000.bson"))[:model]
[…]

### 2020-06-04 scripts/arithmetic/revalidate.jl

@@ -161,9 +161,10 @@ df = res[:df]
 
 df = combine(groupby(df, ["model","task"])) do gdf
     gdf = sort(DataFrame(gdf),"val")
-    if gdf.model[1]=="nmu" && gdf.task[1]=="mult"
-        display(gdf[!,["model","task","mse","val","βstart","run"]])
-    end
+    println( gdf[1,"path"])
+    #if gdf.model[1]=="nmu" && gdf.task[1]=="mult"
+    #     display(gdf[!,["model","task","mse","val","βstart","run"]])
+    # end
     gdf[1:min(10,size(gdf,1)),:]
 end
 

### 2020-06-05 papers/main.tex
submitted to nips

@@
 \usepackage{mathtools} 
+\usepackage{amsthm}
+
+\newtheorem*{remark}{Remark}
 
 \newtheorem*{definition}{Definition}
-
-\usepackage{todonotes}
 
@@
 \begin{abstract}
-  Conventional Neural Networks can approximate simple arithmetic operations, but fail
-  to generalize beyond the range of numbers that were seen during training.
-  \emph{Neural Arithmetic Units} aim to overcome this difficulty, but current
-  arithmetic units are either limited to operate on positive numbers or can
-  only represent a subset of arithmetic operations. We introduce the \emph{Neural
-  Power Unit} (NPU) that operates on the
-  \emph{full domain of real numbers} and is capable of \emph{learning
-  arbitrary power functions} in a single layer.
-  The NPU thus fixes the shortcomings of existing arithmetic units and extends
-  their expressivity. This is achieved by using formulas from complex arithmetics
-  without requiring a conversion of the network to complex numbers.
-  We show where the NPU outperforms its
-  competitors in terms of accuracy and sparsity on artificial arithmetic
-  datasets. Additionally, we demonstrate how the NPU can be used as a highly
-  interpretable model to discover the generating equation of a dynamical system
-  purely from the data.
+  Conventional Neural Networks can approximate simple arithmetic operations,
+  but fail to generalize beyond the range of numbers that were seen during
+  training.  \emph{Neural Arithmetic Units} aim to overcome this difficulty,
+  but current arithmetic units are either limited to operate on positive
+  numbers or can only represent a subset of arithmetic operations. We introduce
+  the \emph{Neural Power Unit} (NPU) that operates on the \emph{full domain of
+  real numbers} and is capable of \emph{learning arbitrary power functions} in
+  a single layer.  The NPU thus fixes the shortcomings of existing arithmetic
+  units and extends their expressivity. We achieve this by using
+  complex arithmetic without requiring a conversion of the network to complex
+  numbers. A simplification of the unit to the \emph{RealNPU} yields a highly interpretable model.
+  We show that the NPUs outperform their competitors in terms of
+  accuracy and sparsity on artificial arithmetic datasets, and that the RealNPU can discover
+  the governing equations of a dynamical systems only from data.
 \end{abstract}
@@
 species~\citep{dehaene_number_2011,gallistel_finding_2018}. A successful,
-intelligent agent should therefore be able to perform simple arithmetic.  State
+intelligent agent should, therefore, be able to perform simple arithmetic.  State
 of the art neural networks are capable of learning arithmetic, but they
@@
 numerical extrapolation on simple arithmetic tasks has been shown
-by~\cite{trask_neural_2018}, who also introduce a new class of \emph{Neural
-Arithmetic Units} that show good extrapolation performance on some arithmetic
+by~\cite{trask_neural_2018}, who also introduced a new class of \emph{Neural
+Arithmetic Units} with good extrapolation performance on some arithmetic
 tasks.
 
-Including Neural Arithmetic Units in common neural networks, promises to
+Including Neural Arithmetic Units in standard neural networks, promises to
 significantly increase their extrapolation capabilities due to their inductive
 bias towards numerical computation. This is especially true for tasks in which
-the data contains mathematical relationships.  Additionally, they promise to
-reduce the amount of parameters that are needed for a given task, and can
-therefore drastically improve the explainability of the model.  We demonstrate
-how neural arithmetic units as part of a \emph{Neural Ordinary Differential
-Equation} (NODE, \cite{chen_neural_2019}) can outperform a dense network with
-significantly fewer parameters in Sec.~\ref{sub:fractional_sir_model}.  In
-fact, our NPU can be used to directly read out the correct generating ODE from
-the fitted model.  This is inline with recent efforts to build
-\emph{interpretable} models instead of \emph{explaining} black box models
+the data generating process contains mathematical relationships.  Additionally,
+they promise to reduce the number of parameters that are needed for a given
+task, and can therefore drastically improve the explainability of the model.
+We demonstrate how a \emph{Neural Ordinary Differential Equation} (NODE,
+\cite{chen_neural_2019}) composed of small neural arithmetic units can
+outperform a much larger NODE built from dense layers (Sec.~\ref{sub:fractional_sir_model}).
+In fact, our new unit can be used to directly read out the correct generating ODE
+from the fitted model.  This is in line with recent efforts to build
+\emph{interpretable} models instead of \emph{explaining} black-box models
 \citep{rudin_stop_2019}, like conventional neural networks.
@@
 small inputs.  Recently, \cite{schlor_inalu_2020} introduced the \emph{improved NALU} (iNALU,
-to fix the NALU's shortcomings. However, it significantly increases its complexity and we
-observe only a slight improvement in performance.\\
+to fix the NALU's shortcomings. However, it significantly increases its complexity, and we
+observe only a slight improvement in performance.
 \cite{madsen_neural_2020} solve ($+,\times$) with two new units: the
@@
 (NMU). Instead of gating between addition and multiplication paths, they are
-separate units that can be stacked. They can work with the full range real
-numbers, converge much more reliably, but are not capable of representing
+separate units that can be stacked. They can work with the full range of real
+numbers, converge much more reliably, but cannot represent
 division.
@@
 \textbf{Neural Power Unit.}
-We introduce a new arithmetic layer (NPU,
-Sec.~\ref{sec:neural_power_unit}) which is capable of learning power
-functions $(\prod x_{i}^{w_i})$ for arbitrary real input $x_i$ and power $w_i$ thus including multiplication ($x_1\times x_2 = x_1^1 x_2^1$) as well as division $(x_1\div x_2=x_1^{1}x_2^{-1})$ .
-This is achieved by using formulas from complex arithmetics (Sec.~\ref{sub:naive_npu}).
-Stacks of NAUs and NPUs can thus learn the full spectrum of simple arithmetic operations.
+We introduce a new arithmetic layer (NPU, Sec.~\ref{sec:neural_power_unit})
+which is capable of learning products of power functions $(\prod x_{i}^{w_i})$ of
+arbitrary real inputs $x_i$ and power $w_i$, thus including multiplication
+($x_1\times x_2 = x_1^1 x_2^1$) as well as division $(x_1\div
+x_2=x_1^{1}x_2^{-1})$. This is achieved by using formulas from complex
+arithmetic (Sec.~\ref{sub:naive_npu}).  Stacks of NAUs and NPUs can thus learn
+the full spectrum of simple arithmetic operations.
 
 \textbf{Convergence improvement.}
-We address the known convergence issues of neural arithmetic units by introducing a
-\emph{relevance gate} that smooths out the loss surface of the NPU
-(Sec.~\ref{sub:npu}). With the relevance gate the NPU reaches extrapolation and
-sparsity errors that are on par with the NMU on ($\times$) and outperform NALU
-on ($\div,\sqrt{\cdot}$).
+We address the known convergence issues of neural arithmetic units by
+introducing a \emph{relevance gate} that smooths out the loss surface of the
+NPU (Sec.~\ref{sub:npu}). With the relevance gate, which helps to learn to
+ignore variables, the NPU reaches extrapolation error and sparsity that is on
+par with the NMU on ($\times$) and outperform NALU on ($\div,\sqrt{\cdot}$).
 
 \textbf{Interpretability.}
-We show how the NPU can be used as a highly interpretable model for discovery of epidemiological models. 
-Specifically, we demontrate its ability to provide a model that can be interpreted as fractional SIR model (Sec.~\ref{sub:fractional_sir_model})
-that was used to fit the COVID-19 outbreak in various countries
-\citep{taghvaei_fractional_2020}.
+We show how a power unit can be used as a highly interpretable model for equation discovery
+of dynamical systems. Specifically, we demonstrate its ability to identify
+a model that can be interpreted as a SIR model with fractional powers
+(Sec.~\ref{sub:fractional_sir_model}) that was used to fit the COVID-19
+outbreak in various countries \citep{taghvaei_fractional_2020}.
 
@@
 
-A number of different approaches to automatically solve arithmetic tasks have
-been studied in the recent years. Approaches include Neural GPUs
+Several different approaches to automatically solve arithmetic tasks have
+been studied in recent years. Approaches include Neural GPUs
 \citep{kaiser_neural_2016}, Grid LSTMs \citep{kalchbrenner_grid_2016}, Neural
@@
 \citep{kurach_neural_2016}. They solve tasks like binary addition and
-multiplication, or single digit arithmetic. The Neural Status Register
+multiplication, or single-digit arithmetic. The Neural Status Register
 \citep{faber_neural_2020} focusses on control flow.  The Neural Arithmetic
 Expression Calculator \citep{chen_neural_2018}, a hierarchical reinforcement
-learner is the only method that solves the division problem, but it operates on
+learner, is the only method that solves the division problem, but it operates on
 character sequences of arithmetic expressions. Related is symbolic integration
@@
 designed with an inductive bias towards systematic, arithmetic computation.
-However, currently they are limited in their capabilities of expressing the full
+However, currently, they are limited in their capabilities of expressing the full
 range of simple arithmetic operations ($+,\times,\div$).
-In the following two sections we briefly describe the currently available
-arithmetic layers including their advantages and drawbacks.
+In the following two sections, we briefly describe the currently available
+arithmetic layers, including their advantages and drawbacks.
 
@@
 summing or multiplying two numbers.  In order to increase the power of
-abstraction to for arithmetic tasks they propose the \emph{Neural Arithmetic
-Logic Unit} (NALU) which is capable of learning ($+,\times,\div$).  However,
+abstraction for arithmetic tasks, they propose the \emph{Neural Arithmetic
+Logic Unit} (NALU), which is capable of learning ($+,\times,\div$).  However,
 the NALU cannot handle negative inputs correctly due to the logarithm in
@@
 \end{definition}
-Additionally, the logarithm destabilizes training to an extent that the chance of success
+Additionally, the logarithm destabilizes training to the extent that the chance of success
 can drop below 20\% for ($+,\times$), it becomes practically impossible to
-learn ($\div$), and difficult to learn from small inputs in general
+learn ($\div$) and difficult to learn from small inputs in general
 \citep{madsen_measuring_2019}.
 \cite{schlor_inalu_2020} provide a detailed description of the shortcomings of
-the NALU and they suggest an \emph{improved NALU} (iNALU).  The iNALU addresses
-the NALU's problems through a number of mechanisms.  It has independent
+the NALU, and they suggest an \emph{improved NALU} (iNALU).  The iNALU addresses
+the NALU's problems through several mechanisms.  It has independent
 addition and multiplication weights for Eq.~\ref{eq:nalu_add} and
@@
 
-Instead of trying to fix the NALU's convergence issues
+Instead of trying to fix the NALU's convergence issues,
 \cite{madsen_neural_2020} propose a new unit for ($\times$) only.
@@
 Both NMU and NAU are regularized with $\mathcal{R} = \sum_{ij} \min(|W_{ij}|,
-|1-W_{ij}|)$ and their weights are clipped, which biases them towards learning
+|1-W_{ij}|)$, and their weights are clipped, which biases them towards learning
 an operation or pruning it completely.  The combination of NAU and NMU can thus
@@
 To fix the deficiencies of current arithmetic units, we propose a new
-arithmetic unit (inspired by NALU) that can learn arbitrary power functions $(x^w)$ (including
+arithmetic unit (inspired by NALU) that can learn arbitrary products of power functions $(\prod x_{i}^{w_i})$ (including
 $\times,\div$) for positive and negative numbers, and still train well.
-Combined with the NAU we solve the full range of arithmetic operations.
+Combined with the NAU, we solve the full range of arithmetic operations.
 This is possible through a simple modification of the ($\times$)-path of the
-NALU (Eq.~\ref{eq:nalu_mult_2}).  We suggest to use the complex logarithm and
-to allow $\bm W$ to become complex.  The complex logarithm is also defined for
-negative inputs and a complex $\bm W$ aides convergence (see
+NALU (Eq.~\ref{eq:nalu_mult_2}). 
+We suggest to replace the logarithm of the absolute value by the complex logarithm and
+to allow $\bm W$ to be complex as well. Since the complex logarithm is defined for
+negative inputs, the NPU does not have a problem with negative numbers. A complex $\bm W$ 
+improves convergence at the expense of explainability (see
 Sec.~\ref{sub:fractional_sir_model}). The improvement during training might be
@@
     \label{eq:naivenpu_def}
-    \bm z = \exp(\Wre \log\bm r - \Wim\bm k) \odot \cos(\Wim\log \bm r + \Wre\bm k), \text{ where }\\
+    \bm z = \exp(\Wre \log\bm r - \pi\Wim\bm k) \odot \cos(\Wim\log \bm r + \pi\Wre\bm k), \text{ where }\\
     \nonumber
@@
        0 & x_i \leq 0 \\
-       \pi & x_i > 0
+       1 & x_i > 0
     \end{cases}
@@
     (hatched background) in front of the input to the actual unit to prevent
-    vanishing gradients.}
+    zero gradients.}
     \label{fig:gatednpu_diagram}
@@
 \end{align}
-The left plot in Fig.~\ref{fig:id_loss} depicts
-the the norm of gradient of a batch of two dimensional inputs, one of which is small and
-irrelevant. It is clearly visible that even for this simple example, a large
-part of the gradient surface of the NaiveNPU is zero.  This vanishing gradient can be explained
-as follows. One row of NaiveNPU weights effectively raises each input to a power and
+The left plot in Fig.~\ref{fig:id_loss} depicts the gradient norm of NPU and
+NaiveNPU for a batch of two-dimensional inputs. One input is small and
+irrelevant. Even in this simple example, gradient of the NaiveNPU is close to
+zero in large parts of the parameter space This can be explained as follows.
+One row of NaiveNPU weights effectively raises each input to a power and
 multiplies them: $x_1^{w_1} x_2^{w_2} \dots x_n^{w_n}$. If a single input $x_i$
@@
 matter what its weights are and the gradient information on all other weights
-is lost.  We therefore introduce a gate on the input of the NPU that can turn
+is lost.  Therefore, we introduce a gate on the input of the NPU that can turn
 irrelevant inputs into 1s.
@@
     \label{eq:gatednpu_def}
-    \bm z = \exp(\Wre \log\bm r - \Wim\bm k) 
-          \odot \cos(\Wim\log \bm r + \Wre\bm k), \text{ where } \\
+    \bm z = \exp(\Wre \log\bm r - \pi\Wim\bm k) 
+          \odot \cos(\Wim\log \bm r + \pi\Wre\bm k), \text{ where } \\
     \bm r = \bm{\hat g} \odot |\bm x| + (1-\bm{\hat g}),
@@
        0  & x_i \leq 0 \\
-      \hat g_i\pi & x_i > 0
+      \hat g_i & x_i > 0
     \end{cases},
@@
   \end{minipage}
-  \caption{Absolute value of a gradient of NaiveNPU and NPU for the task
+  \caption{Norm of the gradient of NaiveNPU and NPU for the task
   of learning the identity on $x_1$. Inputs and
@@
 
-\subsection{Initialization}%
+\textbf{Initialization}%
 \label{sub:initialization}
-We recommend to initialize the NPU with a Glorot Uniform distribution on the
+We recommend initializing the NPU with a Glorot Uniform distribution on the
 real weights $\Wre$. The imaginary weights $\Wim$ can be initialized to zeros,
@@
 the NPU can choose to output 1.
-\todo{should this be longer? or not a section at all?}
+
+\begin{definition}[\textbf{RealNPU}]
+  In many practical tasks, such as multiplication or division, the final value
+  of $\bm W_i$ should be equal to zero. We will denote NPU with removed
+  parameters for the imaginary part as RealNPU and study the impact of this
+  change on convergence in Sec.~\ref{sec:experiments}.
+\end{definition}
 
@@
 
-In Sec.~\ref{sub:fractional_sir_model} we show how the NPU can be used as a
-highly interpretable model which can extract the generating equation of an ODE
-that contains fractional powers.
-In Sec.~\ref{sub:simple_arithmetic_task}\,\&\,\ref{sub:large_scale_arithmetic_task}
-we provide experiments on standard arithmetic tasks in which the NPU outperforms
-the NALU in all tasks.
+In Sec.~\ref{sub:fractional_sir_model}, we show how the NPU can help to build
+better NODE models. Additionally, we use the RealNPU as a highly interpretable
+model, from which we can directly recover the generating equation of an ODE
+containing fractional powers.  Subsequent
+Secs.~\ref{sub:simple_arithmetic_task}\,\&\,\ref{sub:large_scale_arithmetic_task}
+compare the NPU to prior art (NALU and NMU) on arithmetic tasks typically used
+to benchmark arithmetic units.
 
@@
 \label{sub:fractional_sir_model}
-\todo{other titles: Discovering the Equations of an Epidemic}
 
@@
 data-driven models with physically informed differential equations to maximize
-explainability of the resulting models.
-NODEs and UDEs can be tricky to fit, because they run into the same
-difficulties as RNNs like vanishing gradients and bifurcations. With this
-experiment we want to demonstrate that the NPU works reliably in such settings,
-despite the convergence issues that its predecessor (the NALU) has -
-even for non-sequential tasks.
-If an ODE contains parameters that cannot easily be modelled by dense layers,
-the NPU can be a good choice because of its ability to learn any power
-function.  Additionally, if interpretability of the result is important, the
-NPU can be used recover the generating ODE because of its interpretable design,
-instead of trying to explain a black box model in retrospect.
+interpretability/explainability of the resulting models.
 
-An example of an ODE that contains powers is the fractional SIR model (fSIR,
-\cite{taghvaei_fractional_2020}).  The classical SIR model is built from three
-quantities of interest: $S$ (susceptible), $I$ (infectious), and $R$
+If an ODE model is composed of dense layers, its direct interpretation is
+problematic and has to be performed retrospectively. The class of models based on
+SINDy is interpretable by design, however it can only provide explanation
+within a linear combination of predefined set of basis functions. Thus, it
+cannot learn models with unknown fractional powers. We will demonstrate that the NPU
+is capable to do so.
+An example of an ODE that contains powers is a modification of the classical
+epidemiological SIR model \citep{kermack1927contribution} to fractional powers
+(fSIR, \cite{taghvaei_fractional_2020}), which was shown to be a beneficial
+modification for modelling the COVID-19 outbreak.  The classical SIR model is
+built from three variables: $S$ (susceptible), $I$ (infectious), and $R$
 (recovered/removed).  Arguably the most important part of the model is the
@@
 \end{align}
-We solve the fSIR model numerically with the parameters $\alpha=0.05$,
-$\beta=0.06$, $\eta=0.01$, $\gamma=\kappa=0.5$, and 40 datapoints that are
-equally spaced in the time interval $T=(0,200)$. The initial conditions are set
-to $S_0=100$, $I_0=0.01$, and $R_0=0$.
 
-We fit the fSIR model with three different model types: a dense network, the
-NPU, and an NPU with imaginary weights fixed to zero (further referred to as
-\emph{real NPU}). An exemplary model is: $\npu=\chain(\npu(3,h),\nau(h,3))$
-with variable hidden size $h$.  The detailed models are defined in
+We have numerically simulated one realization of the fSIR model with the
+parameters $\alpha=0.05$, $\beta=0.06$, $\eta=0.01$, $\gamma=\kappa=0.5$, in 40
+time steps that are equally spaced in the time interval $T=(0,200)$, such that
+the training data $\bm X = [S_t,I_t,R_t]_{t=1}^{40}$
+contains one time series each for $S$, $I$, and $R$.  The initial conditions
+$\bm u_0=[S_0,I_0,R_0]$ are set to $S_0=100$, $I_0=0.01$, and $R_0=0$, Figure
+\ref{fig:pareto_sir} right.
+We fit the data with three
+different NODEs composed of different model types: a dense network, the NPU, and
+the RealNPU. An exemplary model is: $\npu=\chain(\npu(3,h),\nau(h,3))$ with
+variable hidden size $h$.  The detailed models are defined in
 Tab.~\ref{tab:fsir_models}. The training objective is the loss $\mathcal{L}$
@@
   \label{eq:sir_loss}
-  \mathcal{L} = \text{MSE}(\bm t,\text{model}(\bm u_0)) + \beta||\bm\theta||_1.
+  \mathcal{L} = \text{MSE}(\bm X,\text{NODE}_\theta(\bm u_0)) + \beta||\bm\theta||_1.
 \end{align}
 We train each model for 3000 steps with the ADAM optimizer and a learning rate
-of 0.005, and after that with LBFGS until convergence (or for maximum 1000
-steps).  For each model type we run a small grid search to build a Pareto front
+of 0.005, and subsequently with LBFGS until convergence (or for maximum 1000
+steps).  For each model type, we run a small grid search to build a Pareto front
 with $h\in \{6,9,12,15,20\}$ and $\beta\in\{0,0.01,0.1,1\}$, where each
 hyper-parameter pair is run five times. The resulting Pareto front is shown on
-the left of Fig.~\ref{fig:pareto_sir}. The NPU clearly reaches much sparser and
+the left of Fig.~\ref{fig:pareto_sir}. The NPU reaches much sparser and
 better solutions than the dense network.
-The real NPU has problems to converge in the majority of cases.
+The RealNPU has problems to converge in the majority of cases.
 However, there are a few models in the bottom left that
-reach a very low MSE and have very few parameters. The best these models is
+reach a very low MSE and have very few parameters. The best of these models is
 shown in Fig.~\ref{fig:sir_gatednpu_modelps}.  It looks strikingly similar to
-the fSIR model in matrix from:
+the fSIR model in matrix form:
 \renewcommand*{\arraystretch}{1.3}
@@
 Reading Fig.~\ref{fig:sir_gatednpu_modelps} from right to left, we can extract
-the ODE that the real NPU represents.  It identified the transmission rate
-correctly as a product of two fractional powers $r = I^\gamma S^\kappa$ with
-$\kappa=0.57$ and $\gamma=0.62$, which is close to the true values
-$\gamma=\kappa=0.5$.  In the second layer the NAU combines the correct hidden
-outputs from the NPU such that $\dot S$ is composed of the negative
-transmission rate $r$ and positive $R$.  $\dot I$ and $\dot R$ are also
-composed from the correct hidden variables, with the parameters
-$\alpha,\beta,\eta$ being not far off from the truth.
-We conclude that even with this very naive approach the real NPU is able to
-recover a fractional SIR model.
+the ODE that the RealNPU represents.  The first hidden variable correctly
+identified the transmission rate as a product of two fractional powers $r =
+I^\gamma S^\kappa$ with $\kappa=0.57$ and $\gamma=0.62$, which is close to the
+true values $\gamma=\kappa=0.5$. The second, third and the last hidden variable
+were found to be irrelevant (the relevance gate returns 1). The fourth hidden
+variable is a selector of the second input $I$, and the fifth hidden variable
+is selector of a power of $R$, $R^{0.64}$ In the second layer, the NAU combines
+the correct hidden outputs from the NPU such that $\dot S$ is composed of the
+negative transmission rate $r$ and positive $R$.  $\dot I$ and $\dot R$ are
+also composed of the correct hidden variables, with the parameters
+$\alpha,\beta,\eta$ being not far off from the truth.  We conclude that even
+with this very naive approach, the RealNPU can recover a SIR model that
+contains fractional powers. 
 \begin{figure}
@@
   \resizebox{.7\textwidth}{!}{\input{../plots/pareto_sir.tex}}
-  \caption{Pareto fronts of the dense network, the NPU, and the NPU
-  with imaginary weights fixed to zero. The NPU reaches solutions with lower
-  MSE and fewer parameters than the dense net. The real NPU mostly yields
-  worse results than the NPU, just in a few cases it converges to very sparse
-  models with good MSE.}%
+  \caption{Pareto fronts of the dense network, the NPU, and the RealNPU. The
+  NPU reaches solutions with lower  MSE and fewer parameters than the dense
+  net. The RealNPU mostly yields   worse results than the NPU, just in a few
+  cases it converges to very sparse models with good MSE.}%
   \label{fig:pareto_sir}
@@
   \includegraphics[width=.6\linewidth]{../plots/sir_gatednpu_modelps.pdf}
-  \captionof{figure}{Visualization of the best real NPU. Reading from right
+  \captionof{figure}{Visualization of the best RealNPU. Reading from right
   to left, it takes the SIR variables as an input, then applies the NPU and
@@
 \\
-In summary, the NPU clearly works well in sequential tasks, and we have shown
-that we can reach highly interpretable results with the real NPU, but in practice,
-using the real NPU might be difficult due to its lower success rate. With a more
-elaborate analysis it might be possible to reach the same solutions with the
-full NPU and e.g. a strong regularization of its imaginary parameters.
+In summary, the NPU can work well in sequential tasks, and we have shown
+that we can reach highly interpretable results with the RealNPU, but in practice,
+using the RealNPU might be difficult due to its lower success rate. With a more
+elaborate analysis, it should be possible to reach the same solutions with the
+full NPU and e.g. a strong regularization of its imaginary parameters, because
 
@@
 
-In this experiment we demonstrate the capabilities of five different
-layers (NPU, NMU, NALU, iNALU, Dense) on a small problem with two inputs
-and four outputs. The objective is to learn the function $f: \mathbb{R}^2
+In this experiment we compare six different layers (NPU, RealNPU, NMU, NALU,
+iNALU, Dense) on a small problem with two inputs and four outputs. The
+objective is to learn the function $f: \mathbb{R}^2
 \rightarrow \mathbb{R}^4$ with a standard MSE loss:
@@
 \end{align}
-Each model has two layers with a hidden dimension $h=6$.  E.g. the NPU model is
-defined by $\npu=\chain(\npu(2,6),\nau(6,4))$.  The remaining models that are
+Each model has two layers with a hidden dimension $h$.  E.g. the NPU model is
+defined by $\npu=\chain(\npu(2,h=6),\nau(b=6,4))$.  The remaining models that are
 used in the tables and plots are given in Tab.~\ref{tab:models_simple_task}.
@@
 
-The NPU successfully learns ($+,\times,\div,\sqrt{\cdot}$) and clearly
-outperforms NALU and iNALU on all tasks.  The NPU is on par with the NMU for
+Both NPUs successfully learn ($+,\times,\div,\sqrt{\cdot}$) and clearly
+outperform NALU and iNALU on all tasks.  The NPUs are on par with the NMU for
 ($+$), but the NMU is better at ($\times$) due to its inductive bias. The NMU
-cannot learn ($\div,\sqrt{\cdot}$). The NPU excels at extrapolation on all tasks.
+cannot learn ($\div,\sqrt{\cdot}$). The fact that the RealNPU performs slightly better
+than the NPU indicates that the task is easy enough to not require the
+imaginary parameters to help convergence. In such a case, the RealNPU
+generalizes better because it corresponds to the task it
+is trying to learn.
 \begin{figure}
@@
   \includegraphics[width=0.7\linewidth]{simple_err.pdf}
-  \caption{Comparison of different models learning Eq.~\ref{eq:simple_f}. Each
-  column represents the best model of 20 runs.  The dense network learns all
-  tasks, but fails to extrapolate. NALU and iNALU are better at extrapolating
-  to positive numbers, but fail if one of the inputs is negative.  The NMU
-  successfully learns ($+,\times$), but not ($\div,\sqrt{\cdot}\,$). Only the NPU
-  learns all tasks and can extrapolate both to positive and negative numbers.
-  }%
+  \caption{Comparison of extrapolation quality of different models learning Eq.~\ref{eq:simple_f}. Each
+  column represents the best model of 20 runs that were trained on the range
+  $\mathcal{U}(0.1,2)$.  Lighter color implies lower error.}%
   \label{fig:simple_err}
@@
 works reliably on many-input tasks that are heavily over-parametrized.  In this
-section we compare NALU, NMU, NPU, and the NaiveNPU on a task that is identical
+section we compare NALU, NMU, NPU, RealNPU, and the NaiveNPU on a task that is identical
 to the `arithmetic task' that \cite{madsen_neural_2020} and
@@
   b = \sum_{i=s_{2,\text{start}}}^{s_{2,\text{end}}} x_i, &&
-  t_{\text{add}} = a + b, && t_{\text{mul}} = a \times b, &&
-  t_{\text{div}} = 1 / a, && t_{\text{sqrt}} = \sqrt{a},
+  y_{\text{add}} = a + b, && y_{\text{mul}} = a \times b, &&
+  y_{\text{div}} = 1 / a, && y_{\text{sqrt}} = \sqrt{a},
 \end{align}
@@
 \begin{equation}
-  \mathcal{L} = \text{MSE}(\text{model}(\bm x), t) + \beta||\bm\theta||_1,
+  \mathcal{L} = \text{MSE}(\text{model}(\bm x), y) + \beta||\bm\theta||_1,
 \end{equation}
@@
 of NAU/NMU outperforms the NALU. We focus on the
-comparison of NPU, NMU, and NALU on the default parameters of
+comparison of NPU, RealNPU, NMU, and NALU on the default parameters of
 \cite{madsen_neural_2020} which sets the subset ratio to 0.5 and the overlap
 ratio to 0.25 (details in Tab.~\ref{tab:dataset_params_large_scale}).
-We also compare to the NaiveNPU (without the relevance gate) to show
+We include the NaiveNPU (without the relevance gate) to show
 how important the gating mechanism is for both sparsity and overall
@@
 Fig.~\ref{fig:pareto} plots testing errors over the number of non-zero
-parameters for all models and tasks.  The addition plot shows only NMU and NPU
-can extrapolate on ($+$) with the NMU converging to the sparsest models.\\
-On ($\times$), the best NMU models outperform the NPU, but some of them do not
-converge at all, which is why the NPU has a better testing MSE on average (see
-also Tab.~\ref{tab:arithmetic100_val}). The testing MSE of the NALU is so large
-that is excluded from the plot.\\
+parameters for all models and tasks.  The addition plot shows that NMU, NPU,
+and RealNPU successfully learn and extrapolate on ($+$) with the NMU converging
+to the sparsest and most accurate models.
+On ($\times$), the best NMU models outperform the NPU and RealNPU, but some
+NMUs do not converge at all. The testing MSE of the NALU is so large that it is
+excluded from the plot.
 On ($\div,\sqrt{\cdot}$) the NPU clearly outperforms all other layers
-in MSE and sparsity. Generally, the difference between the NaiveNPU and the NPU
-is very significant and demonstrates how important the relevance gate is both
-for convergence and sparsity. The NPU effectively converts irrelevant inputs
-to 1s, while the NaiveNPU is stuck on the zero gradient plateau.
+in MSE and sparsity. Generally, the difference between the NaiveNPU and the other NPUs
+is huge and demonstrates how important the relevance gate is both
+for convergence and sparsity. The NPUs with relevance gates effectively convert
+irrelevant inputs to 1s, while the NaiveNPU is stuck on the zero gradient
+plateau.
 
@@
   \resizebox{\textwidth}{!}{\input{../plots/pareto.tex}}
-  \caption{Validation MSE over number of non-zero parameters ($w_i > 0.001$) of the large scale
+  \caption{Testing MSE over number of non-zero parameters ($w_i > 0.001$) of the large scale
   arithmetic task.  Again, the NMU outperforms the NPU on its
@@
   \centering
-  \caption{Testing errors of the large scale arithmetic task.}
+  \caption{Testing errors of the large scale arithmetic task. Each value is
+  obtained by computing median (and median absolute deviation) of 10 runs.}
   \label{tab:arithmetic100_val}
+  \small
   \input{../plots/arithmetic100_val.tex}
@@
 
-We introduced the \emph{Neural Arithmetic Unit} that addresses the deficiencies
+We introduced the \emph{Neural Power Unit} that addresses the deficiencies
 of current arithmetic units: it can learn arbitrary power functions for
@@
 \ref{sub:large_scale_arithmetic_task}).\\
-Additionally we have demonstrated that the NPU converges consistently, even on
-sequential tasks and that can be used as a highly interpretable by recovering
-the  governing equations of dynamical systems purely from data
-(Sec.~\ref{sub:fractional_sir_model}).
+Additionally, we have demonstrated that the NPU converges consistently, even on
+sequential tasks. The RealNPU can be used as a highly interpretable model that
+is capable of recovering the governing equations of dynamical systems purely
+from the data (Sec.~\ref{sub:fractional_sir_model}).
 
@@
 
-Current neural network architectures can be problematic because they are black
-box models that are difficult to interpret. This becomes highly problematic if
+Current neural network architectures are often perceived as black box models
+that are difficult to explain or interpret. This becomes highly problematic if
 ML models are involved in high stakes decisions in e.g. criminal justice,
-healthcare, or control systems that affect lives.  With the NPU we hope to
-contribute to the broad topic of interpretable machine learning, with a focus
-on scientific applications.
+healthcare, or control systems.  With the NPU, we hope to contribute to the
+broad topic of interpretable machine learning, with a focus on scientific
+applications.
 
@@
   (i.e. mean of each heatmap in Fig.~\ref{fig:simple_err}). Each value is
-  obtained by averaging the error of 20 models.}
+  obtained by computing median (and median absolute deviation) of the error of
+  20 models.}
   \label{tab:simple_err}
+  \small
   \input{../plots/simple_err.tex}
@@
     NPU & NAU(2,\,6) & NPU(6,\,2) & -- \\
+    RealNPU & NAU(2,\,6) & RealNPU(6,\,2) & -- \\
     NMU & NAU(2,\,6) & NMU(6,\,2) & -- \\

### 2020-06-05 scripts/simple/results_table.jl
rename plot for arxiv

@@ -159,7 +159,7 @@ print_table(best[!,["model",key,"add_val","mult_val","div_val","sqrt_val","path"
 r = table_models_tasks(adf)
 print_table(r, :row)
 
-fname = plotsdir("simple_err.tex")
+fname = plotsdir("simple_err_table.tex")
 open(fname, "w") do file
     @info "Writing dataframe to $fname"
     write(file, latex_table(r))

### 2020-06-05 papers/main.tex
rename plot for arxiv
arxiv branch

@@
 % [preprint] option:
-\usepackage{neurips_2020}
+\usepackage[preprint]{neurips_2020}
 
@@
   numbers or can only represent a subset of arithmetic operations. We introduce
-  the \emph{Neural Power Unit} (NPU) that operates on the \emph{full domain of
+  the \emph{Neural Power Unit} (NPU\footnote{Implementation of all used neural arithmetic units: \url{https://github.com/nmheim/NeuralArithmetic.jl} }) that operates on the \emph{full domain of
   real numbers} and is capable of \emph{learning arbitrary power functions} in
@@
   \small
-  \input{../plots/simple_err.tex}
+  \input{../plots/simple_err_table.tex}
 \end{table}

### 2020-06-05 papers/main.tex
fix link

@@
   numbers or can only represent a subset of arithmetic operations. We introduce
-  the \emph{Neural Power Unit} (NPU\footnote{Implementation of all used neural arithmetic units: \url{https://github.com/nmheim/NeuralArithmetic.jl} }) that operates on the \emph{full domain of
+  the \emph{Neural Power Unit} (NPU\footnote{Implementation of all used arithmetic units: \url{https://github.com/nmheim/NeuralArithmetic.jl} }) that operates on the \emph{full domain of
   real numbers} and is capable of \emph{learning arbitrary power functions} in

### 2020-06-05 papers/main.tex
pevnak fixes

--- 2020-06-05 papers/main.tex
@@
 \title{Neural Power Units}
-\author{
-  Niklas Heim,
-  Tom\'a\v s Pevn\'y,
-  V\'aclav \v Sm\'idl\\
-  Artificial Intelligence Center\\
-  Czech Technical University\\
-  Prague, CZ 120 00\\
-  \texttt{\{niklas.heim, vasek.smidl, tomas.pevny\}@aic.fel.cvut.cz}\\
-}
+\author{Anonymous Authors}
 
@@
 significantly increase their extrapolation capabilities due to their inductive
-bias towards numerical computation. This is especially true for tasks in which
-the data generating process contains mathematical relationships.  Additionally,
-they promise to reduce the number of parameters that are needed for a given
-task, and can therefore drastically improve the explainability of the model.
-We demonstrate how a \emph{Neural Ordinary Differential Equation} (NODE,
-\cite{chen_neural_2019}) composed of small neural arithmetic units can
-outperform a much larger NODE built from dense layers (Sec.~\ref{sub:fractional_sir_model}).
-In fact, our new unit can be used to directly read out the correct generating ODE
+bias towards numerical computation. This is especially important for tasks in which
+the data generating process contains mathematical relationships.  They also
+promise to reduce the number of parameters needed for a given
+task, which can improve the explainability of the model.
+We demonstrate this in a \emph{Neural Ordinary Differential Equation} (NODE,
+\cite{chen_neural_2019}), where a handful of neural arithmetic units can
+outperform a much bigger network built from dense layers (Sec.~\ref{sub:fractional_sir_model}).
+Moreover, our new unit can be used to directly read out the correct generating ODE
 from the fitted model.  This is in line with recent efforts to build
@@
 small inputs.  Recently, \cite{schlor_inalu_2020} introduced the \emph{improved NALU} (iNALU,
-to fix the NALU's shortcomings. However, it significantly increases its complexity, and we
+to fix the NALU's shortcomings. It significantly increases its complexity, and we
 observe only a slight improvement in performance.
@@
 sparse results in cases where the input to a given row is small. We
-demonstrate this on a toy example of learning the identity on one of two inputs
-(neglecting the second one):
+demonstrate this on a toy example of learning the identity on one of two inputs and neglecting the second one, $f(x_1,x_2) = x_1$:
 \begin{align}
@@
 cannot learn models with unknown fractional powers. We will demonstrate that the NPU
-is capable to do so.
+is capable of doing so.
 An example of an ODE that contains powers is a modification of the classical
@@
 better solutions than the dense network.
-The RealNPU has problems to converge in the majority of cases.
-However, there are a few models in the bottom left that
+The RealNPU has problems to converge in the majority of cases, however, 
+there are a few models in the bottom left that
 reach a very low MSE and have very few parameters. The best of these models is

### 2020-06-05 papers/main.tex

@@
   numbers or can only represent a subset of arithmetic operations. We introduce
-  the \emph{Neural Power Unit} (NPU) that operates on the \emph{full domain of
+  the \emph{Neural Power Unit} (NPU\footnote{Implementation of all used arithmetic units: \url{https://github.com/nmheim/NeuralArithmetic.jl} }) that operates on the \emph{full domain of
   real numbers} and is capable of \emph{learning arbitrary power functions} in

### 2020-09-30 papers/main.tex
add authors
fix definitions

--- 2020-06-05 papers/main.tex
@@
 % [preprint] option:
-\usepackage{neurips_2020}
+\usepackage[final]{neurips_2020}
 
@@
 \usepackage{amsthm}         % definitions
+\usepackage{amssymb}
 \usepackage{nicefrac}       % compact symbols for 1/2, etc.
@@
 \title{Neural Power Units}
-\author{Anonymous Authors}
+\author{
+    Niklas Heim, Tom\'a\v s Pevn\'y, V\'aclav \v Sm\'idl \\
+    Artificial Intelligence Center\\
+    Czech Technical University\\
+    Prague, Czechia\\
+    \texttt{heimnikl@fel.cvut.cz}
+}
 
@@
 \begin{definition}[{\bf NALU}]
-  The NALU consits of a ($+$) and a ($\times$) path that share their weights $\bm{\hat{W}}$ and $\bm{\hat{M}}$.
+  The NALU consists of a ($+$) and a ($\times$) path that share their weights $\bm{\hat{W}}$ and $\bm{\hat{M}}$.
 \begin{align}
   \label{eq:nalu_add}
-  \text{Addition: }       & \bm a = \bm W \bm x
-                          & \bm{\hat W}& = \tanh(\bm{W}) \odot \sigma(\bm{M}) \\
+  \text{Addition: }       & \bm a = \bm W \bm x,
+                          & \bm{\hat W}& = \tanh(\bm{W}) \odot \sigma(\bm{M}), \\
   \label{eq:nalu_mult}
-  \text{Multiplication: } & \bm m = \exp \bm{\hat W}(\log(|\bm x|+\epsilon)) & &\\
-  \text{Output: }         & \bm y = \bm a \odot \bm g + \bm m \odot (1-\bm g) 
-                          & \bm g& = \sigma(\bm G\bm x)
+  \text{Multiplication: } & \bm m = \exp \bm{\hat W}(\log(|\bm x|+\epsilon)), & &\\
+  \text{Output: }         & \bm y = \bm a \odot \bm g + \bm m \odot (1-\bm g),
+                          & \bm g& = \sigma(\bm G\bm x),
 \end{align}
 \end{definition}
+with inputs $\bm x$ and learnt parameters $\bm W$, $\bm M$, and $\bm G$.
 Additionally, the logarithm destabilizes training to the extent that the chance of success
@@
   \label{eq:nmu}
-  \text{NMU: } &y_j = \prod_i \hat M_{ij} z_{i} + 1 - \hat M_{ij}  & \hat M_{ij}=\min(\max(M_{ij}, 0), 1)\\
+  \text{NMU: } &y_j = \prod_i \hat M_{ij} x_{i} + 1 - \hat M_{ij}, & \hat M_{ij}=\min(\max(M_{ij}, 0), 1),\\
   \label{eq:nau}
-  \text{NAU: } &\bm y = \bm{\hat{A}} \bm x & \hat A_{ij}=\min(\max(A_{ij}, -1), 1)
+  \text{NAU: } &\bm y = \bm{\hat{A}} \bm x, & \hat A_{ij}=\min(\max(A_{ij}, -1), 1),
 \end{align}
 \end{definition}
+with inputs $\bm x$, and learnt parameters $\bm M$, and $\bm A$.
 Both NMU and NAU are regularized with $\mathcal{R} = \sum_{ij} \min(|W_{ij}|,
@@
 Above we have used Euler's formula\footnote{Euler's formula states that for any
-real number $x$: $e^{ix} = \cos x + i\sin x$} and the fact that the complex
-logarithm for real valued inputs is
+real number $x$: $e^{ix} = \cos x + i\sin x$} and that the complex
+logarithm for real valued inputs $x$ is
 \begin{align}
@@
 \end{align}
-where $k=0$ if $r\geq0$ and $k=1$ if $r<0$.
+where $k=0$ if $x\geq0$ and $k=1$ if $x<0$.
 A diagram of the NaiveNPU is shown in Fig.~\ref{fig:npu_diagram}.
@@
   The Naive Neural Power Unit with matrices $\Wre$ and
-  $\Wim$ representing real and imaginary part of the complex numbers defined as
+  $\Wim$ representing real and imaginary part of the complex numbers is defined as
   \begin{gather}
@@
     k_i = \begin{cases}
-       0 & x_i \leq 0 \\
-       1 & x_i > 0
-    \end{cases}
+       0 & x_i \geq 0 \\
+       1 & x_i < 0
+    \end{cases},
   \end{gather}
 \end{definition}
+with inputs $\bm x$, and learnt parameters $\Wre$, and $\Wim$.
 
@@
           \odot \cos(\Wim\log \bm r + \pi\Wre\bm k), \text{ where } \\
+    \nonumber
     \bm r = \bm{\hat g} \odot |\bm x| + (1-\bm{\hat g}),
@@
     k_i = \begin{cases}
-       0  & x_i \leq 0 \\
-      \hat g_i & x_i > 0
+       0  & x_i \geq 0 \\
+      \hat g_i & x_i < 0
     \end{cases},
@@
 \end{definition}
+with inputs $\bm x$, and learnt parameters $\Wre$, $\Wim$, $\bm g$.
+
 \begin{figure}
@@
 An example of an ODE that contains powers is a modification of the classical
-epidemiological SIR model \citep{kermack1927contribution} to fractional powers
+epidemiological SIR model \citep{kermack_contribution_1927} to fractional powers
 (fSIR, \cite{taghvaei_fractional_2020}), which was shown to be a beneficial

### 2020-10-16 scripts/fracode/naivenpu-sir.jl
camera ready

@@ -1,5 +1,5 @@
 using DrWatson
-@quickactivate
+@quickactivate "NIPS_2020_NPU"
 
 using Logging
 using TerminalLoggers
@@ -32,7 +32,7 @@ end
 
 nrparams(p, thresh) = sum(abs.(p) .> thresh)
 
-function run_npu(d::Dict)
+function run_naivenpu(d::Dict)
     idim = 3
     @unpack hdim, αinit, βps, βim, niters, lr = d
 
@@ -40,7 +40,7 @@ function run_npu(d::Dict)
 
     ode_data,u0,t,tspan = fracsir_data()
     dudt = FastChain(
-        FastNPU(idim,hdim, initRe=init,initIm=zeros),
+        FastNaiveNPU(idim,hdim, initRe=init,initIm=zeros),
         FastNAU(hdim,idim,init=init))
     node = NeuralODE(dudt,tspan,Euler(),saveat=t,dt=1)
     predict(p) = node(u0,p)
@@ -66,13 +66,13 @@ function run_npu(d::Dict)
         UnicodePlots.heatmap(cat(Re,Im,W',dims=2))
     end
 
-    function cb(p,l,pred;doplot=false)
+    function cb(p,l,pred;doplot=true)
         @info l mse_loss(pred) reg_loss(p) img_loss(p)
         if doplot
             display(plot_cb(t,ode_data,pred))
             println("\n")
-            display(plot_chain(p))
-            println("\n")
+            #display(plot_chain(p))
+            #println("\n")
         end
         return false
     end
@@ -104,21 +104,21 @@ function run_npu(d::Dict)
     return d
 end
 
-# @progress for nr in 1:10
-#     produce_or_load(datadir("fracsir"),
-#                     Dict{Symbol,Any}(
-#                          :hdim=>9,
-#                          :βim=>0,
-#                          :βps=>0,
-#                          :lr=>0.005,
-#                          :niters=>3000,
-#                          :αinit=>0.2,
-#                          :run=>nr),
-#                     run,
-#                     prefix="npu",
-#                     digits=10,
-#                     force=false)
-# end
+@progress for nr in 1:10
+    produce_or_load(datadir("fracsir"),
+                    Dict{Symbol,Any}(
+                         :hdim=>2,
+                         :βim=>0,
+                         :βps=>0,
+                         :lr=>0.005,
+                         :niters=>3000,
+                         :αinit=>0.2,
+                         :run=>nr),
+                    run_npu,
[…]

### 2020-10-16 scripts/fracode/realnpu-sir.jl

@@ -32,7 +32,7 @@ end
 
 nrparams(p, thresh) = sum(abs.(p) .> thresh)
 
-function run_gatednpu(d::Dict)
+function run_realnpu(d::Dict)
     idim = 3
     @unpack hdim, αinit, βps, βim, niters, lr = d
 
@@ -40,7 +40,7 @@ function run_gatednpu(d::Dict)
 
     ode_data,u0,t,tspan = fracsir_data()
     dudt = FastChain(
-        FastGatedNPU(idim,hdim,init=init),
+        FastRealNPU(idim,hdim,initRe=init),
         FastNAU(hdim,idim,init=init))
     node = NeuralODE(dudt,tspan,Euler(),saveat=t,dt=1)
     predict(p) = node(u0,p)
@@ -115,7 +115,7 @@ end
 #                          :αinit=>0.2,
 #                          :run=>nr),
 #                     run,
-#                     prefix="gatednpu",
+#                     prefix="realnpu",
 #                     digits=10,
 #                     force=false)
 # end

### 2020-10-16 scripts/fracode/run-sir.jl

@@ -1,15 +1,14 @@
 using DrWatson
-@quickactivate
+@quickactivate "NIPS_2020_NMUX"
 
-include(joinpath(@__DIR__, "npu-sir.jl"))
-include(joinpath(@__DIR__, "realnpu-sir.jl"))
+include(joinpath(@__DIR__, "gated-npux-sir.jl"))
+include(joinpath(@__DIR__, "gated-npu-sir.jl"))
 include(joinpath(@__DIR__, "dense-sir.jl"))
 
 @progress for nr in 1:5
     hdims = [6,9,12,15,20]
     βpss  = [0., 1e-2, 1e-1, 1.]
     @progress for (hdim,βps) in Iterators.product(hdims, βpss)
-
         produce_or_load(datadir("fracsir"),
                         Dict{Symbol,Any}(
                              :hdim=>hdim,
@@ -19,8 +18,8 @@ include(joinpath(@__DIR__, "dense-sir.jl"))
                              :niters=>3000,
                              :αinit=>0.2,
                              :run=>nr),
-                        run_npu,
-                        prefix="npu",
+                        run_gatednpux,
+                        prefix="gatednpux",
                         digits=10,
                         force=false)
 
@@ -33,8 +32,8 @@ include(joinpath(@__DIR__, "dense-sir.jl"))
                              :niters=>3000,
                              :αinit=>0.2,
                              :run=>nr),
-                        run_realnpu,
-                        prefix="realnpu",
+                        run_gatednpu,
+                        prefix="gatednpu",
                         digits=10,
                         force=false)
 

### 2020-10-16 scripts/simple/dataset.jl

@@ -9,7 +9,7 @@ generate_pos() = generate_range(umin=0.1f0, umax=2)
 
 function generate_range(;umin=-2, umax=2)
     a = umax - umin
-    x = rand(Float32, 2, 100) .* a .+ umin
+    x = rand(Float32, 2, 1000) .* a .+ umin
     y = f(x)
     (x,y)
 end

### 2020-10-16 scripts/simple/results_table.jl

@@ -142,7 +142,7 @@ raw"""\bottomrule
 end
 
 umin = 0.01
-umax = 1
+umax = 2
 data_directory = datadir("simple_umin=$(umin)_umax=$(umax)")
 df = collect_folder!(data_directory)
 sort!(df,"model")

### 2020-10-16 scripts/simple/run.jl

@@ -1,5 +1,5 @@
 using DrWatson
-@quickactivate "NIPS_2020_NPU"
+@quickactivate
 
 using Logging
 using TerminalLoggers
@@ -57,6 +57,7 @@ end
 function run_npu(c::Dict)
     @unpack umin, umax = c
     hdim = 6
+    #model = Chain(NPU(2,hdim),NAU(hdim,4))
     model = Chain(NPU(2,hdim),NAU(hdim,4))
     ps = params(model)
     opt = ADAM(c[:lr])
@@ -154,7 +155,8 @@ function run_dense(c::Dict)
     return result_dict(model,c)
 end
 
-train_ranges = [(0.01f0,1), (0.1f0, 0.2f0), (1,2), (1.1f0,1.2f0), (10,20)]
+#train_ranges = [(0.01f0,1), (0.1f0, 0.2f0), (1,2), (1.1f0,1.2f0), (10,20)]
+train_ranges = [(0.01f0,2)]
 nr_runs = 20
 
 for (umin,umax) in train_ranges
@@ -163,30 +165,30 @@ for (umin,umax) in train_ranges
 
     @progress for run in 1:nr_runs
         res, _ = produce_or_load(data_directory,
-                                 Dict(:niters=>20000, :βl1=>0, :lr=>0.005, :run=>run, :umin=>umin, :umax=>umax),
+                                 Dict(:niters=>20000, :βl1=>0, :lr=>0.001, :run=>run, :umin=>umin, :umax=>umax),
                                  run_npu,
                                  prefix="npu",
                                  force=false, digits=6)
         res, _ = produce_or_load(data_directory,
-                                 Dict(:niters=>20000, :βl1=>0, :lr=>0.005, :run=>run, :umin=>umin, :umax=>umax),
+                                 Dict(:niters=>20000, :βl1=>0, :lr=>0.001, :run=>run, :umin=>umin, :umax=>umax),
                                  run_realnpu,
                                  prefix="realnpu",
                                  force=false, digits=6)
-        # res, _ = produce_or_load(data_directory,
-        #                          Dict(:niters=>20000, :lr=>0.005, :run=>run, :umin=>umin, :umax=>umax),
-        #                          run_nalu,
-        #                          prefix="nalu", force=false, digits=6)
         res, _ = produce_or_load(data_directory,
-                                 Dict(:niters=>20000, :lr=>0.005, :run=>run, :umin=>umin, :umax=>umax),
[…]

### 2020-10-16 src/NeuralArithmetic.jl

@@ -1,21 +1,0 @@
-module NeuralArithmetic
-
-using Flux
-using Zygote
-using Flux: glorot_uniform, destructure
-using Requires
-
-include("nau.jl")
-include("nmu.jl")
-include("npu.jl")
-
-function __init__()
-    @require DiffEqFlux="aae7a2af-3d4f-5e19-a356-7da93b79d9d0" include("fast_nau.jl")
-    @require DiffEqFlux="aae7a2af-3d4f-5e19-a356-7da93b79d9d0" include("fast_npu.jl")
-end
-
-include("nac.jl")
-include("nalu.jl")
-include("inalu.jl")
-
-end # module

### 2020-10-16 src/fast_nau.jl

@@ -1,21 +1,0 @@
-export FastNAU
-
-struct FastNAU{F} <: DiffEqFlux.FastLayer
-    in::Int
-    out::Int
-    initial_params::F
-    function FastNAU(in::Int, out::Int; init=Flux.glorot_uniform)
-        initial_params() = vec(init(out,in))
-        new{typeof(initial_params)}(in, out, initial_params)
-    end
-end
-
-DiffEqFlux.paramlength(f::FastNAU) = f.out * f.in
-DiffEqFlux.initial_params(f::FastNAU) = f.initial_params()
-
-(f::FastNAU)(x,p) = reshape(p, f.out, f.in) * x
-
-Zygote.@adjoint function (f::FastNAU)(x,p)
-    W = reshape(p, f.out, f.in)
-    f(x,p), ȳ -> (nothing, W'ȳ, vec(ȳ * x'))
-end

### 2020-10-16 src/nau.jl

@@ -1,19 +1,0 @@
-export NAU
-
-"""
-    NAU(in::Int, out::Int; init=glorot_uniform)
-
-Neural addition unit.
-
-Lacks the regularization suggested in https://openreview.net/pdf?id=H1gNOeHKPS
-as it is intended to be used with ARD (automatic relevance determination)
-"""
-struct NAU
-    W::AbstractMatrix
-end
-
-NAU(in::Int, out::Int; init=glorot_uniform) = NAU(init(out,in))
-
-(m::NAU)(x) = m.W * x
-
-Flux.@functor NAU

### 2020-10-16 src/npu.jl

@@ -1,112 +1,0 @@
-export NPUX, NPU, GatedNPU, GatedNPUX
-
-"""
-    NPU(in::Int, out::Int; initRe=glorot_uniform, initIm=zeros)
-
-Neural Power Unit that can learn any power function by using a complex
-multiplication matrix.
-"""
-
-struct NPUX
-    Re::AbstractMatrix
-    Im::AbstractMatrix
-end
-
-function NPUX(in::Int, out::Int; initRe=glorot_uniform, initIm=Flux.zeros)
-    Re = initRe(out, in)
-    Im = initIm(out, in)
-    NPUX(Re, Im)
-end
-
-Flux.@functor NPUX
-
-function mult(Re::AbstractMatrix{T}, Im::AbstractMatrix{T}, x::AbstractArray{T}) where T
-    r = abs.(x) .+ eps(T)
-    k = max.(-sign.(x), 0) .* T(pi)
-    exp.(Re*log.(r) - Im*k) .* cos.(Re*k + Im*log.(r))
-end
-
-(l::NPUX)(x) = mult(l.Re, l.Im, x)
-
-
-struct GatedNPUX{M<:AbstractMatrix,V<:AbstractVector}
-    Re::M
-    Im::M
-    g::V
-end
-
-function GatedNPUX(in::Int, out::Int;
-                   initRe=glorot_uniform, initIm=Flux.zeros)
-   Re = initRe(out, in) 
-   Im = initIm(out, in)
-   g  = Flux.ones(in)/2
-   GatedNPUX(Re,Im,g)
-end
-
-Flux.@functor GatedNPUX
-
-function mult(Re::AbstractMatrix{T}, Im::AbstractMatrix{T}, g::AbstractVector{T}, x::AbstractArray{T}) where T
-    g = min.(max.(g, 0), 1)
-
-    r = abs.(x) .+ eps(T)
-    r = g .* r .+ (1 .- g)
-
-    k = max.(-sign.(x), 0) .* T(pi)
-    k = g .* k
-
-    exp.(Re*log.(r) - Im*k) .* cos.(Re*k + Im*log.(r))
-end
-(l::GatedNPUX)(x) = mult(l.Re, l.Im, l.g, x)
-
-
-struct NPU
-    W::AbstractMatrix
-end
-
-NPU(in::Int, out::Int; init=glorot_uniform) = NPU(init(out,in))
-Flux.@functor NPU
-
[…]

### 2020-10-16 paper/main.tex

--- 2020-04-22 paper/main.tex
@@
 % [preprint] option:
-\usepackage[preprint]{neurips_2020}
+\usepackage[final]{neurips_2020}
 
@@
 \usepackage{amsfonts}       % blackboard math symbols
+\usepackage{amsthm}         % definitions
 \usepackage{nicefrac}       % compact symbols for 1/2, etc.
 \usepackage{microtype}      % microtypography
+\usepackage{caption}
+\usepackage{mathtools}
 
-\usepackage{todonotes}
+\newtheorem*{remark}{Remark}
+
+\newtheorem*{definition}{Definition}
 
@@
 \usepackage{amsmath}
+\usepackage{amssymb}
 \usepackage{graphicx}
 
-\graphicspath{{./../../plots/}}
-\newcommand{\real}{\text{real}}
+% tikz
+\usepackage{tikz}
+\usetikzlibrary{%
+  arrows,%
+  backgrounds,
+  intersections,
+  shapes,
+  shapes.misc,% wg. rounded rectangle
+  shapes.arrows,%
+  chains,%
+  matrix,%
+  positioning,% wg. " of "
+  scopes,%
+  decorations.pathmorphing,% /pgf/decoration/random steps | erste Graphik
+  shadows,%
+  patterns% for hatched rect
+}
 
-\title{Bayesian Neural Arithmetic Units -- Leveraging The Complex Plane}
+% plots
+\graphicspath{{./../plots/}}
+\usepackage{pgfplots}
+\pgfplotsset{compat=newest}
+\usepgfplotslibrary{groupplots}
+\usepgfplotslibrary{polar}
+\usepgfplotslibrary{smithchart}
+\usepgfplotslibrary{statistics}
+\usepgfplotslibrary{dateplot}
+
+\newcommand{\real}{\text{Re}}
+\newcommand{\imag}{\text{Im}}
+\newcommand{\wre}{w_{r}}
+\newcommand{\wim}{w_{i}}
+\newcommand{\Wre}{\bm W_{r}}
+\newcommand{\Wim}{\bm W_{i}}
+\newcommand{\npu}{\text{NPU}}
+\newcommand{\naivenpu}{\text{NaiveNPU}}
+\newcommand{\nau}{\text{NAU}}
+\newcommand{\nmu}{\text{NMU}}
+\newcommand{\nalu}{\text{NALU}}
+\newcommand{\inalu}{\text{iNALU}}
+\newcommand{\dense}{\text{Dense}}
+\newcommand{\chain}{\text{Chain}}
+\newcommand{\norm}[1]{\left\lVert #1 \right\rVert}
+
+% tables
+\usepackage{booktabs}
+\renewcommand{\arraystretch}{1.2}
+
+\title{Neural Power Units}
 \author{
   Niklas Heim,
-  V\'aclav \v Sm\'idl,
-  Tom\'a\v s Pevn\'y \\
+  Tom\'a\v s Pevn\'y,
+  V\'aclav \v Sm\'idl\\
   Artificial Intelligence Center\\
@@
   Prague, CZ 120 00\\
-  \texttt{\{niklas.heim, vasek.smidl, tomas.pevny\}@aic.fel.cvut.cz}\\
+  \texttt{\{niklas.heim, tomas.pevny, vasek.smidl\}@aic.fel.cvut.cz}\\
 }
@@
 \begin{abstract}
-  Common Neural Networks poorly approximate simple arithmetic operations.  The
-  new Neural Arithmetic Units aim to overcome this difficulty, but are limited
-  either limited to operate on positive numbers (NALU by
-  \citet{trask_neural_2018}), or can only represent simple addition and
-  multiplication (NAU \& NMU by \citet{madsen_neural_2020}).
-  We present the first Neural Arithmetic Unit that operates on the full domain
-  of real numbers and is capable of learning arbitrary power functions.
-  For a theoretically grounded sparsification of the units we employ Bayesian
-  compression on the model weights via Automatic Relevance Determination.
+  Conventional Neural Networks can approximate simple arithmetic operations,
+  but fail to generalize beyond the range of numbers that were seen during
+  training.  \emph{Neural Arithmetic Units} aim to overcome this difficulty,
+  but current arithmetic units are either limited to operate on positive
+  numbers or can only represent a subset of arithmetic operations. We introduce
+  the \emph{Neural Power Unit} (NPU)\footnote{
+    Implementation of Neural Arithmetic Units: \url{github.com/nmheim/NeuralArithmetic.jl}.
+    The code to reproduce our experiments is available at \url{github.com/nmheim/NeuralPowerUnits}.
+  }
+  that operates on the \emph{full domain of
+  real numbers} $\mathbb{R}$ and is capable of \emph{learning arbitrary power functions} in
+  a single layer.  The NPU thus fixes the shortcomings of existing arithmetic
+  units and extends their expressivity. We achieve this by using
+  complex arithmetic without requiring a conversion of the network to complex
+  numbers $\mathbb{C}$.
+  A simplification of the unit to the \emph{RealNPU} yields a highly transparent model.
+  We show that the NPUs outperform their competitors in terms of
+  accuracy and sparsity on artificial arithmetic datasets, and that the RealNPU can discover
+  the governing equations of a dynamical system only from data.
 \end{abstract}
@@
 
-It is known that Neural Networks can approximate functions arbitrarily
-well\todo{cite universal approx}.  However, this strength of approximation
-often comes at the cost of generalization beyond the training data manifold.
-\todo{mention ODEs as use case}
+Numbers and simple algebra are essential not only to human intelligence but
+also to the survival of many other
+species~\citep{dehaene_number_2011,gallistel_finding_2018}. A successful,
+intelligent agent should, therefore, be able to perform simple arithmetic.  State
+of the art neural networks are capable of learning arithmetic, but they
+fail to extrapolate beyond the ranges seen during
+training~\citep{suzgun_evaluating_2018,lake_generalization_2018}.  The
+inability to generalize to unseen inputs is a fundamental problem that hints at
+a lack of \emph{understanding} of the given task. The model merely memorizes
+the seen inputs and fails to abstract the true learning task.  The failure of
+numerical extrapolation on simple arithmetic tasks has been shown
+by~\cite{trask_neural_2018}, who also introduced a new class of \emph{Neural
+Arithmetic Units} with good extrapolation performance on some arithmetic
+tasks.
+
+Including Neural Arithmetic Units in standard neural networks promises to
+significantly increase their extrapolation capabilities due to their inductive
+bias towards numerical computation. This is especially important for tasks in which
+the data generating process contains mathematical relationships.  They also
+promise to reduce the number of parameters needed for a given
+task, which can improve the explainability of the model.
+We demonstrate this in a \emph{Neural Ordinary Differential Equation} (NODE,
+\cite{chen_neural_2019}), where a handful of neural arithmetic units can
+outperform a much bigger network built from dense layers (Sec.~\ref{sub:fractional_sir_model}).
+Moreover, our new unit can be used to directly read out the correct generating ODE
+from the fitted model.  This is in line with recent efforts to build
+\emph{transparent} models instead of attempting to explain black-box models
+\citep{rudin_stop_2019}, like conventional neural networks.
+We refer to the terminology by \cite{lipton_mythos_2017} which defines the
+potential of understanding the parameters of a given model as \emph{transparency by decomposability}.
+
+The currently available arithmetic units all have different strengths and
+weaknesses, but none of them solve simple arithmetic completely.
+The \emph{Neural Arithmetic Logic Unit} (NALU) by \cite{trask_neural_2018},
+chronologically, was the first arithmetic unit. It can solve
+addition ($+$, including subtraction), multiplication ($\times$), and division
+($\div$), but is limited to positive inputs. The convergence of the
+NALU is quite fragile due to an internal gating mechanism between addition and
+multiplication paths as well as the use of a logarithm which is problematic for
+small inputs.  Recently, \cite{schlor_inalu_2020} introduced the \emph{improved NALU} (iNALU,
+to fix the NALU's shortcomings. It significantly increases its complexity, and we
+observe only a slight improvement in performance.
+\cite{madsen_neural_2020} solve ($+,\times$) with two new units: the
+\emph{Neural Addition Unit} (NAU), and the \emph{Neural Multiplication Unit}
+(NMU). Instead of gating between addition and multiplication paths, they are
+separate units that can be stacked. They can work with the full range of real
+numbers, converge much more reliably, but cannot represent
+division.
+
+\subsection*{Our Contributions}%
+\label{sub:our_contribution}
+
+\textbf{Neural Power Unit.}
+We introduce a new arithmetic layer (NPU, Sec.~\ref{sec:neural_power_unit})
+which is capable of learning products of power functions $(\prod x_{i}^{w_i})$ of
+arbitrary real inputs $x_i$ and power $w_i$, thus including multiplication
+($x_1\times x_2 = x_1^1 x_2^1$) as well as division $(x_1\div
+x_2=x_1^{1}x_2^{-1})$. This is achieved by using formulas from complex
+arithmetic (Sec.~\ref{sub:naive_npu}).  Stacks of NAUs and NPUs can thus learn
+the full spectrum of simple arithmetic operations.
+
+\textbf{Convergence improvement.}
+We address the known convergence issues of neural arithmetic units by
+introducing a \emph{relevance gate} that smooths out the loss surface of the
+NPU (Sec.~\ref{sub:npu}). With the relevance gate, which helps to learn to
+ignore variables, the NPU reaches extrapolation errors and sparsities that are on
+par with the NMU on ($\times$) and outperforms NALU on ($\div,\sqrt{\cdot}$).
+
+\textbf{Transparency.}
+We show how a power unit can be used as a highly transparent\footnote{as defined by
+\cite{lipton_mythos_2017}} model for equation discovery
+of dynamical systems. Specifically, we demonstrate its ability to identify
+a model that can be interpreted as a SIR model with fractional powers
+(Sec.~\ref{sub:fractional_sir_model}) that was used to fit the COVID-19
+outbreak in various countries \citep{taghvaei_fractional_2020}.
 
@@
 
-\citet{trask_neural_2018} have demonstrated how severe this problem is even for
-the simplest arithmetic operations, such as summing or multiplying two numbers.
-In order to increase the power of abstraction of Neural Networks they propose a
-\emph{Neural Arithmetic Logic Unit} (NALU) which can help to overcome this
-problem \cite{trask_neural_2018} and is capable of learning the arithmetic
-addition, subtraction, multiplication, and division
-$\{+,-,\times,\div\}$ with stunning extrapolation accuracy.  However,
-the NALU comes with the severe limitation not being able to handle negative
-inputs due to the logarithm in the multiplication part of the NALU:
+Several different approaches to automatically solve arithmetic tasks have
+been studied in recent years. Approaches include Neural GPUs
+\citep{kaiser_neural_2016}, Grid LSTMs \citep{kalchbrenner_grid_2016}, Neural
+Turing Machines \citep{graves_neural_2014}, and Neural Random Access Machines
+\citep{kurach_neural_2016}. They solve tasks like binary addition and
+multiplication, or single-digit arithmetic. The Neural Status Register
+\citep{faber_neural_2020} focuses on control flow.  The Neural Arithmetic
+Expression Calculator \citep{chen_neural_2018}, a hierarchical reinforcement
+learner, is the only method that solves the division problem, but it operates on
+character sequences of arithmetic expressions. Related is symbolic integration
+with transformers \citep{lample_deep_2019}. Unfortunately, most of the named models
+have severe problems with extrapolation \citep{madsen_measuring_2019,saxton_analysing_2019}.
+A solution to the extrapolation problem could be Neural Arithmetic Units. They are
+designed with an inductive bias towards systematic, arithmetic computation.
+However, currently, they are limited in their capability of expressing the full
+range of simple arithmetic operations ($+,\times,\div$).
+In the following two sections, we briefly describe the currently available
+arithmetic layers, including their advantages and drawbacks.
 
+\subsection{Neural Arithmetic Logic Units}%
+\label{sub:neural_arithmetic_logic_unit}
+
+\citet{trask_neural_2018} have demonstrated the severity of the extrapolation
+problem of dense networks for even the simplest arithmetic operations, such as
+summing or multiplying two numbers.  To increase the power of
+abstraction for arithmetic tasks, they propose the \emph{Neural Arithmetic
+Logic Unit} (NALU), which is capable of learning ($+,\times,\div$).  However,
+the NALU cannot handle negative inputs correctly due to the logarithm in
+Eq.~\ref{eq:nalu_mult}:
+
+\begin{definition}[{\bf NALU}]
+  The NALU consists of a ($+$) and a ($\times$) path with shared weights $\bm W$ and $\bm M$.
   \begin{align}
     \label{eq:nalu_add}
-  \text{Addition: }       & \bm a = \bm W \bm x
-                          & \bm W& = \tanh(\hat{\bm W}) \odot \sigma(\hat{\bm M}) \\
+    \text{Addition: }       & \bm a = \bm{\hat W} \bm x
+                            & \bm{\hat W}& = \tanh(\bm{W}) \odot \sigma(\bm{M}) \\
     \label{eq:nalu_mult}
-  \text{Multiplication: } & \bm m = \exp \bm W(\log(|\bm x|+\epsilon)) & &\\
+    \text{Multiplication: } & \bm m = \exp (\bm{\hat W}\log(|\bm x|+\epsilon)) & &\\
     \text{Output: }         & \bm y = \bm a \odot \bm g + \bm m \odot (1-\bm g) 
@@
   \end{align}
+  with inputs $\bm x$ and learnt parameters $\bm W$, $\bm M$, and $\bm G$.
+\end{definition}
 
-A multiplication layer that can handle negative inputs was introduced by \citet{madsen_neural_2020}.
-The \emph{Neural Multiplication Unit} (NMU) is defined by Eq.~\ref{eq:nmu} and is typically used in
-conjunction with the so-called \emph{Neural Addition Unit} (NAU) in Eq.~\ref{eq:nau}.
+Additionally, the logarithm destabilizes training to the extent that the chance of success
+can drop below 20\% for ($+,\times$), it becomes practically impossible to
+learn ($\div$) and difficult to learn from small inputs in general
+\citep{madsen_measuring_2019}.
+\cite{schlor_inalu_2020} provide a detailed description of the shortcomings of
+the NALU, and they suggest an \emph{improved NALU} (iNALU).  The iNALU addresses
+the NALU's problems through several mechanisms.  It has independent
+addition and multiplication weights for Eq.~\ref{eq:nalu_add} and
+Eq.~\ref{eq:nalu_mult}, clips weights and gradients to improve training
+stability, regularizes the weights to push them away from zero, and, most
+importantly, introduces a mechanism to recover the sign that is lost due to the
+absolute value in the logarithm. Additionally, the authors propose to
+reinitialize the network if its loss is not improving during training.  We
+include the iNALU in one of our experiments and find that it only slightly
+improves the NALU's performance (Sec.~\ref{sub:simple_arithmetic_task}) at the
+cost of a significantly more complicated unit. Our NPU avoids all these mechanisms
+by internally using complex arithmetic.
+
+\subsection{Neural Multiplication Unit \& Neural Addition Unit}%
+\label{sub:neural_multiplication_unit}
+
+Instead of trying to fix the NALU's convergence issues,
+\cite{madsen_neural_2020} propose a new unit for ($\times$) only.
+The \emph{Neural Multiplication Unit} (NMU) uses explicit multiplications and learns
+to gate between identity and ($\times$) of inputs. The NMU is
+defined by Eq.~\ref{eq:nmu} and is typically used in conjunction with the
+so-called \emph{Neural Addition Unit} (NAU) in Eq.~\ref{eq:nau}.
+
+\begin{definition}[{\bf NMU \& NAU}]
+  NMU and NAU are two units that can be stacked to model ($+,\times$).
   \begin{align}
     \label{eq:nmu}
-  \text{NMU: } &y_j = \prod_i M_{ij} z_{i} + 1 - M_{ij}  &M_{ij}=\min(\max(M_{ij}, 0), 1)\\
+    \text{NMU: } &y_j = \prod_i \hat M_{ij} x_{i} + 1 - \hat M_{ij}  & \hat M_{ij}=\min(\max(M_{ij}, 0), 1)\\
     \label{eq:nau}
-  \text{NAU: } &\bm y = \bm A \bm x &A_{ij}=\min(\max(A_{ij}, 0), 1)
+    \text{NAU: } &\bm y = \bm{\hat{A}} \bm x & \hat A_{ij}=\min(\max(A_{ij}, -1), 1)
   \end{align}
-In both NMU and NAU the weights are clipped to $[0,1]$, and typically regularized
-with $\mathcal{R}$:
+  with inputs $\bm x$, and learnt parameters $\bm M$ and $\bm A$.
+\end{definition}
+
+Both NMU and NAU are regularized with $\mathcal{R} = \sum_{ij} \min(|W_{ij}|,
+|1-W_{ij}|)$, and their weights are clipped, which biases them towards learning
+an operation or pruning it completely.  The combination of NAU and NMU can thus
+learn $(+,\times)$ for both positive and negative inputs. Training NAU and NMU
+is stable and succeeds much more frequently than with the NALU, but they cannot
+represent ($\div$), which we address with our NPU.
+
+\section{Neural Power Units}%
+\label{sec:neural_power_unit}
+
+To fix the deficiencies of current arithmetic units, we propose a new
+arithmetic unit (inspired by NALU) that can learn arbitrary products of power functions $(\prod x_{i}^{w_i})$ (including
+$\times,\div$) for positive and negative numbers, and still train well.
+Combined with the NAU, we solve the full range of arithmetic operations.
+This is possible through a simple modification of the ($\times$)-path of the
+NALU (Eq.~\ref{eq:nalu_mult_2}). 
+We suggest to replace the logarithm of the absolute value by the complex logarithm and
+to allow $\bm W$ to be complex as well. Since the complex logarithm is defined for
+negative inputs, the NPU does not have a problem with negative numbers. A complex $\bm W$ 
+improves convergence at the expense of transparency (see
+Sec.~\ref{sub:fractional_sir_model}). The improvement during training might be
+explained by the additional imaginary parameters that make it possible to avoid
+regions with an uninformative gradient signal.
+
+\subsection{Naive Neural Power Unit -- NaiveNPU}%
+\label{sub:naive_npu}
+
+With the modifications introduced above we can extend the multiplication path
+of the NALU from
 \begin{align}
-  \label{eq:rsparse}
-  \mathcal{R} = \sum_{ij} \min(W_{ij}, 1-W_{ij})
+  \label{eq:nalu_mult_2}
+  \bm m = \exp (\bm W\log_{\text{real}}(|\bm x|+\epsilon))
+\end{align}
+to use the complex logarithm ($\log\coloneqq\log_{\text{complex}}$) and a
+complex weight $\bm W$ to
+\begin{align}
+  \label{eq:1}
+  \bm y = \exp(\bm W\log \bm x) = \exp\left((\Wre + i\Wim) \log\bm x\right),
+\end{align}
+where the input $\bm x$ is still a vector of real numbers.
+With the polar form for a complex number $z=re^{i\theta}$ the complex log applied
+to a real number $x=re^{ik\pi}$ is
+\begin{align}
+  \log x = \log r + ik\pi,
+\end{align}
+where $k=0$ if $x\geq0$ and $k=1$ if $x<0$.
+Using the complex log in Eq.~\ref{eq:1} lifts the positivity constraint on $\bm x$,
+resulting in a layer that can process both positive and negative numbers correctly.
+A complex weight matrix $\bm W$ somewhere in a larger network would result in complex
+gradients in other layers.  This would effectively result in doubling the
+number of parameters of the whole network. As we are only interested in real
+outputs, we can avoid this doubling by considering only the real part
+of the output $\bm y$:
+\begin{align}
+  \real(\bm y) &= \real(\exp((\Wre + i\Wim)(\log\bm r + i\pi\bm k))) \\
+    \label{eq:npumult}
+    &= \exp(\Wre\log\bm r - \pi\Wim\bm k) \odot \cos(\Wim\log\bm r + \pi\Wre\bm k).
+\end{align}
+Above we have used Euler's formula $e^{ix} = \cos x + i\sin x$.
+A diagram of the NaiveNPU is shown in Fig.~\ref{fig:npu_diagram}.
+
+\begin{definition}[{\bf NaiveNPU}]
+  The Naive Neural Power Unit, with matrices $\Wre$ and
+  $\Wim$ representing real and imaginary part of the complex numbers, is defined as
+  \begin{gather}
+    \label{eq:naivenpu_def}
+    \bm y = \exp(\Wre \log\bm r - \pi\Wim\bm k) \odot \cos(\Wim\log \bm r + \pi\Wre\bm k), \text{ where }\\
+    \nonumber
+    \bm r = |\bm x| + \epsilon,
+    \quad
+    k_i = \begin{cases}
+       0 & x_i \geq 0 \\
+       1 & x_i < 0
+    \end{cases},
+  \end{gather}
+  with inputs $\bm x$, machine epsilon $\epsilon$, and learnt parameters $\Wre$ and $\Wim$.
+\end{definition}
+
+\begin{figure}
+  \begin{minipage}{.45\textwidth}
+      \resizebox{0.9\textwidth}{!}{\input{../tikz/npu-diagram.tex}}
+      \captionof{figure}{NaiveNPU diagram, with input $\bm x$ and output $\bm y$.
+      Vectors in green, trainables in orange, functions in blue.}
+      \label{fig:npu_diagram}
+  \end{minipage}
+  \hspace{0.01\textwidth}
+  \begin{minipage}{0.54\textwidth}
+    \resizebox{\textwidth}{!}{\input{../tikz/gatednpu-diagram.tex}}
+    \captionof{figure}{NPU diagram. The NPU has a relevance gate $\bm g$
+    (hatched background) in front of the input to the unit to prevent
+    zero gradients.}
+    \label{fig:gatednpu_diagram}
+  \end{minipage}
+\end{figure}
+
+\subsection{The Relevance Gate -- NPU}%
+\label{sub:npu}
+
+The NaiveNPU has difficulties to converge on large scale tasks, and to reach
+sparse results in cases where the input to a given row is small. We
+demonstrate this on a toy example of learning the function
+$f:\mathbb{R}^2 \rightarrow \mathbb{R}$,
+which is the identity on one of two inputs. The task is defined by the loss $\mathcal L$:
+\begin{gather}
+  \mathcal{L} = \sum_i |m(x_1,x_2) - f(x_1,x_2)| = \sum_i |m(x_1,x_2) - x_{1,i}|,\nonumber\\
+  \label{eq:grad_surf}
+  \text{where } m = \naivenpu \text{ with } (\Wre,\Wim) \in \mathbb{R}^{1\times 2} \\
+  \text{and } x_1 \sim \mathcal U(0,2), x_2 \sim \mathcal U(0,0.05). \nonumber
+\end{gather}
+The left plot in Fig.~\ref{fig:id_loss} depicts the gradient norm $\mathcal{G}$
+\begin{equation}
+  \mathcal{G}(\Wre) = \norm{\frac{\partial\mathcal{L}}{\partial\Wre}}_2
+\end{equation}
+of the NaiveNPU for a batch of two-dimensional inputs.
+Even in this simple example, the gradient of the NaiveNPU is close to
+zero in large parts of the parameter space. This can be explained as follows.
+One row of NaiveNPU weights effectively raises each input to a power and
+multiplies them: $x_1^{w_1} x_2^{w_2} \dots x_n^{w_n}$. If a single input $x_i$
+is constantly close to zero (i.e. irrelevant), the whole row will be zero, no
+matter what its weights are and the gradient information on all other weights
+is lost.  Therefore, we introduce a gate on the input of our layer that can turn
+irrelevant inputs into 1s.
+A diagram of the NPU is shown in Fig.~\ref{fig:gatednpu_diagram}.
+
+\begin{definition}[{\bf NPU}]
+  The NPU extends the NaiveNPU by the relevance gate $\bm g$ on the input $\bm x$.
+   \begin{gather}
+    \label{eq:gatednpu_def}
+    \bm y = \exp(\Wre \log\bm r - \pi\Wim\bm k) 
+          \odot \cos(\Wim\log \bm r + \pi\Wre\bm k), \text{ where } \\
+    \bm r = \bm{\hat g} \odot (|\bm x|+\epsilon) + (1-\bm{\hat g}),
+    \quad
+    k_i = \begin{cases}
+       0  & x_i \geq 0 \\
+      \hat g_i & x_i < 0
+    \end{cases},
+    \quad
+    \hat g_i = \min(\max(g_i,0),1),
+  \end{gather}
+  with inputs $\bm x$, and learnt parameters $\Wre$, $\Wim$ and $\bm g$.
+\end{definition}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=.6\textwidth]{npu_gatednpu_id_grad.pdf}
+  \caption{Gradient norm $\mathcal G$ of NaiveNPU and NPU for the task of learning
+  the identity on $x_1$ (black areas are beyond the color scale). Inputs and
+  loss are defined in Eq.~\ref{eq:grad_surf}. The correct solution is
+  $w_1=1$ and $w_2=0$.  The NaiveNPU has a large zero gradient region for
+  $w_2>0.75$, while the NPU's surface is much more informative. The gates
+  in the central plot are fixed at $g_1=g_2=0.5$ which corresponds to the initial
+  gate parameters. During training they adjust as needed, in this case to
+  $g_1=1$ and $g_2=0$. $\bm W_i$ is set to zero in all plots.
+  }%
+  \label{fig:id_loss}
+\end{figure}
+The central plot of Fig.~\ref{fig:id_loss} shows the gradient norm $\mathcal G$ of the NPU
+on the identity task with its initial gate setting of $g_1=g_2=0.5$. The
+large zero-gradient region of the NaiveNPU is gone. The last plot shows the
+same for $g_1=1$ and $g_2=0$, which corresponds to the correct gates at
+the end of NPU training. The gradient is independent of $w_2$, which
+means that it can easily be pruned by a simple regularization such as $L_1$. In
+Sec.~\ref{sub:large_scale_arithmetic_task} we show how important the relevance
+gating mechanism is for the convergence and sparsity of large models.  Sparsity
+is especially important in order to use the NPU as a transparent model.
+
+\textbf{Initialization}%
+\label{sub:initialization}
+We recommend initializing the NPU with a Glorot Uniform distribution on the
+real weights $\Wre$. The imaginary weights $\Wim$ can be initialized to zeros,
+so they will only be used where necessary, and the gate $\bm g$ with 0.5, so
+the NPU can choose to output 1.
+
+\begin{definition}[\textbf{RealNPU}]
+  In many practical tasks, such as multiplication or division, the final value
+  of $\bm W_i$ should be equal to zero. We will denote NPU with removed
+  parameters for the imaginary part as RealNPU and study the impact of this
+  change on convergence in Sec.~\ref{sec:experiments}.
+\end{definition}
+
+\section{Experiments}%
+\label{sec:experiments}
+
+In Sec.~\ref{sub:fractional_sir_model}, we show how the NPU can help to build
+better NODE models. Additionally, we use the RealNPU as a highly transparent
+model, from which we can directly recover the generating equation of an ODE
+containing fractional powers.  Subsequent
+Secs.~\ref{sub:simple_arithmetic_task} and \ref{sub:large_scale_arithmetic_task}
+compare the NPU to prior art (NALU and NMU) on arithmetic tasks typically used
+to benchmark arithmetic units.
+
+\subsection{A Step Towards Equation Discovery of an Epidemiological Model}%
+\label{sub:fractional_sir_model}
+
+Data-driven models such as \emph{SINDy}~\citep{champion_data-driven_2019} or
+\emph{Neural Ordinary Differential Equations} (NODE, \cite{chen_neural_2019})
+are used more and more in scientific applications.
+Recently, \emph{Universal Differential Equations} (UDEs,
+\cite{rackauckas_universal_2020}) were introduced which aim to combine
+data-driven models with physically informed differential equations to maximize
+interpretability/explainability of the resulting models.
+
+If an ODE model is composed of dense layers, its direct interpretation is
+problematic and has to be performed retrospectively. The class of models based on
+SINDy is transparent by design, however it can only provide explanation
+within a linear combination of predefined set of basis functions. Thus, it
+cannot learn models with unknown fractional powers. 
+With this experiment we aim to show that the NPU can \emph{potentially} discover
+exact ODE models\footnote{The demonstration given here is not intended to be
+used in practice. For real-world predictions in such a sensitive area much more
+post-processing is needed to ensure safe predictions.}.
+An example of an ODE that contains powers is a modification of the well-known
+epidemiological SIR model \citep{kermack_contribution_1927} to fractional powers
+(fSIR, \cite{taghvaei_fractional_2020}), which was shown to be a beneficial
+modification for modelling the COVID-19 outbreak.  The SIR model is
+built from three variables: $S$ (susceptible), $I$ (infectious), and $R$
+(recovered/removed).  Arguably the most important part of the model is the
+transmission rate $r$, which is typically taken to be proportional to the
+product of $S$ and $I$.  \citet{taghvaei_fractional_2020} argue that,
+especially in the initial phase of an epidemic, the boundary areas of infected
+and susceptible cells scale with a fractional power, which leads to
+Eq.~\ref{eq:fracsir_r}:
+\begin{align}
+  \label{eq:fracsir}
+  \frac{dS}{dt} &= -r(t) + \eta R(t), &
+  \frac{dI}{dt} &=  r(t) - \alpha I(t), &
+  \frac{dR}{dt} &= \alpha I(t) - \eta R(t),\\
+  \label{eq:fracsir_r}
+  & & r(t) &= \beta I(t)^\gamma S(t)^\kappa,
 \end{align}
 
-The combination of NAU and NMU can thus learn $\{+,-,\times\}$, but no division.
+We have numerically simulated one realization of the fSIR model with the
+parameters $\alpha=0.05$, $\beta=0.06$, $\eta=0.01$, $\gamma=\kappa=0.5$, in 40
+time steps that are equally spaced in the time interval $T=(0,200)$, such that
+the training data $\bm X = [S_t,I_t,R_t]_{t=1}^{40}$
+contains one time series each for $S$, $I$, and $R$.  The initial conditions
+$\bm u_0=[S_0,I_0,R_0]$ are set to $S_0=100$, $I_0=0.01$, and $R_0=0$, as shown in Figure
+\ref{fig:pareto_sir} (right).
+We fit the data with three
+different NODEs composed of different model types: a dense network, the NPU, and
+the RealNPU. An exemplary model is: $\npu=\chain(\npu(3,h),\nau(h,3))$ with
+variable hidden size $h$.  The detailed models are defined in
+Tab.~\ref{tab:fsir_models}. The training objective is the loss $\mathcal{L}$
+with $L_1$ regularization.
+\begin{align}
+  \label{eq:sir_loss}
+  \mathcal{L} = \text{MSE}(\bm X,\text{NODE}_\theta(\bm u_0)) + \beta||\bm\theta||_1.
+\end{align}
+We train each model for 3000 steps with the ADAM optimizer and a learning rate
+of 0.005, and subsequently with LBFGS until convergence (or for maximum 1000
+steps).  For each model type, we run a small grid search to build a Pareto front
+with $h\in \{6,9,12,15,20\}$ and $\beta\in\{0,0.01,0.1,1\}$, where each
+hyper-parameter pair is run five times. The resulting Pareto front is shown on
+the left of Fig.~\ref{fig:pareto_sir}. The NPU reaches much sparser and
+better solutions than the dense network.
+\begin{figure}
+  \centering
+  \resizebox{.9\textwidth}{!}{\input{../plots/pareto_sir.tex}}
+  \caption{Pareto fronts of the dense network, NPU, and RealNPU. The
+  NPU reaches solutions with lower MSE and fewer parameters than the dense
+  net. The RealNPU mostly yields worse results than the NPU. Just in a few
+  cases it converges to very sparse models with good MSE.}%
+  \label{fig:pareto_sir}
+\end{figure}
+The RealNPU has problems to converge in the majority of cases, however, 
+there are a few models in the bottom left that
+reach a very low MSE and have very few parameters. The best of these models is
+shown in Fig.~\ref{fig:sir_gatednpu_modelps}.  It looks strikingly similar to
+the fSIR model in matrix form:
+\renewcommand*{\arraystretch}{1.3}
+\begin{equation}
+  \begin{bmatrix}
+    \dot S \\ \dot I \\ \dot R
+  \end{bmatrix}
+  =
+  \begin{bmatrix}
+    -\beta & 0 & \eta \\
+    \beta & -\alpha & 0 \\
+    0 & \alpha & \eta
+  \end{bmatrix}
+  \begin{bmatrix}
+    I^\gamma S^\kappa \\ I \\ R
+  \end{bmatrix}.
+\end{equation}
+Reading Fig.~\ref{fig:sir_gatednpu_modelps} from right to left, we can extract
+the ODE that the RealNPU represents.  The first hidden variable correctly
+identified the transmission rate as a product of two fractional powers $r =
+I^\gamma S^\kappa$ with $\kappa=0.57$ and $\gamma=0.62$, which is close to the
+true values $\gamma=\kappa=0.5$. The second, third, and the last hidden variable
+were found to be irrelevant (the relevance gate returns 1). The fourth hidden
+variable is a selector of the second input $I$, and the fifth hidden variable
+is selector of a power of $R$, $R^{0.64}$. In the second layer, the NAU combines
+the correct hidden outputs from the NPU such that $\dot S$ is composed of the
+negative transmission rate $r$ and positive $R$.  $\dot I$ and $\dot R$ are
+also composed of the correct hidden variables, with the parameters
+$\alpha,\beta,\eta$ being not far off from the truth.  We conclude that even
+with this very naive approach, the RealNPU can recover something close to the
+true fractional SIR model.
+\begin{figure}
+  \centering
+  \includegraphics[width=.8\linewidth]{../plots/sir_gatednpu_modelps.pdf}
+  \captionof{figure}{Visualization of the best RealNPU. Reading from right
+  to left, it takes the SIR variables as an input, then applies the NPU and
+  the NAU.  It correctly identifies $r$ as a fractional product in the NPU,
+  and gets the rest of the fSIR parameters almost right in the NAU.}%
+  \label{fig:sir_gatednpu_modelps}
+\end{figure}
+\\
+In summary, the NPU can work well in sequential tasks, and we have shown
+that we can reach highly transparent results with the RealNPU, but in practice,
+using the RealNPU might be difficult due to its lower success rate. With a more
+elaborate analysis, it should be possible to reach the same solutions with the
+full NPU and e.g. a strong regularization of its imaginary parameters.
 
-\todo{put this in acknowledgements
-all the results in this paper were create with the help of the following Julia
-packages: \cite{rackauckas_differentialequationsjl_2017} + (Flux.jl)}
+\subsection{Simple Arithmetic Task}%
+\label{sub:simple_arithmetic_task}
 
-\section{Neural Power Unit}%
-\label{sec:neural_power_unit}
+In this experiment we compare six different layers (NPU, RealNPU, NMU, NALU,
+iNALU, Dense) on a small problem with two inputs and four outputs. The
+objective is to learn the function $f: \mathbb{R}^2
+\rightarrow \mathbb{R}^4$ with a standard MSE loss:
+\begin{align}
+  \label{eq:simple_f}
+  f(x,y) &= (x+y,\, xy,\, x/y,\, \sqrt{x} \text{  })^T \eqqcolon \bm t, \\
+  \mathcal L &= \frac{1}{4} \sum_{i=1}^{4}\left(\text{model}(x,y)_i - f(x,y)_i\right)
+             = \text{MSE}(\bm{\hat t}, \bm t).
+\end{align}
+Learning the function $f$ includes not only learning the correct arithmetic operation,
+but also to separate them cleanly, which tests the gating mechanisms of the layers.
+Each model has two layers with a hidden dimension $h$.  E.g. the NPU model is
+defined by $\npu=\chain(\npu(2,h=6),\nau(h=6,4))$.  The remaining models that are
+used in the tables and plots are given in Tab.~\ref{tab:models_simple_task}.
+To obtain valid results in case of division we train on positive, non-zero
+inputs, but test on negative, non-zero numbers (except for test inputs to the
+square-root):
+\begin{align}
+  \label{eq:simple_train}
+  (x_{\text{train}}, y_{\text{train}}) &\sim \mathcal{U}(0.1,2) &
+  (x_{\text{test}}, y_{\text{test}}) &\sim \mathcal{R}(\text{-4.1:0.2:4}) &
+  (x_{\text{test,\,sqrt}}, y_{\text{test,\,sqrt}}) &\sim \mathcal{R}(\text{0.1:0.1:4})
+\end{align}
+where $\mathcal{R}$ denotes a \emph{range} with start, step, and end.
+We train each model for 20\,000 steps with the ADAM optimizer, a learning rate of
+0.001, and a batch size of 100. The input samples are generated on the fly
+during training. Fig.~\ref{fig:simple_err} shows the error surface of the best
+of 20 models on each task. Tab.~\ref{tab:simple_err} lists the corresponding
+averaged testing errors of all 20 models.
 
-Our \emph{Neural Power Unit} (NPU) can learn arbitrary power functions (which
-includes division) while still being able to correctly deal with negative
-inputs.  The NPU layer is defined by
+Both NPUs successfully learn ($+,\times,\div,\sqrt{\cdot}$) and clearly
+outperform NALU and iNALU on all tasks.
+Surprisingly, the NALU has problems extrapolating in this task, which as
+\cite{schlor_inalu_2020} suggest, might be due to its gating mechanism.
+The NPUs are on par with the NMU for
+($+$), but the NMU is better at ($\times$) due to its inductive bias. The NMU
+cannot learn ($\div,\sqrt{\cdot}$). The fact that the RealNPU performs slightly better
+than the NPU indicates that the task is easy enough to not require the
+imaginary parameters to help convergence. In such a case, the RealNPU
+generalizes better because it corresponds to the task it
+is trying to learn.
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{simple_err.pdf}
+  \caption{Comparison of extrapolation quality of different models learning Eq.~\ref{eq:simple_f}. Each
+  column represents the best model of 20 runs that were trained on the range
+  $\mathcal{U}(0.1,2)$.  Lighter color implies lower error.}%
+  \label{fig:simple_err}
+\end{figure}
+
+\subsection{Large Scale Arithmetic Task}%
+\label{sub:large_scale_arithmetic_task}
+
+One of the most important properties of a layer in a neural network is its
+ability to scale. With the large scale arithmetic task we show that the NPU
+works reliably on many-input tasks that are heavily over-parametrized.  In this
+section we compare NALU, NMU, NPU, RealNPU, and the NaiveNPU on a task that is identical
+to the `arithmetic task' that \cite{madsen_neural_2020} and
+\cite{trask_neural_2018} analyse as well.
+The goal is to sum two subsets of a 100 dimensional vector and
+apply an operation (like $\times$) to the two summed subsets.  The dataset
+generation is defined in the set of Eq.~\ref{eq:large_scale_def}, with the
+parameters from Tab.~\ref{tab:dataset_params_large_scale}.
 \begin{align}
-  k_i &= \begin{cases}
-     0  & x_i \leq 0 \\
-    \pi & x_i > 0
-  \end{cases} \\
-  \bm r &= |\bm x| \\
-  \bm m &= \exp(\bm M \log(\bm r)) \odot \cos(\bm M \bm k)
+  \label{eq:large_scale_def}
+  a = \sum_{i=s_{1,\text{start}}}^{s_{1,\text{end}}} x_i, &&
+  b = \sum_{i=s_{2,\text{start}}}^{s_{2,\text{end}}} x_i, &&
+  y_{\text{add}} = a + b, && y_{\text{mul}} = a \times b, &&
+  y_{\text{div}} = 1 / a, && y_{\text{sqrt}} = \sqrt{a},
 \end{align}
-where $\bm k$ is a vector that is zero where $\bm x$ is positive and $\pi$
-where it is negative, $\bm r$ is the elementwise absolute value, and $\bm M$
-the multiplication matrix that we want to learn.
+where starting and ending values $s_{i,\text{start}},s_{i,\text{end}}$ of the
+summations are chosen such that $a$ and $b$ come from subsets of the input
+vector $\bm x$ with a given overlap.  The training objective is standard MSE,
+regularized with $L_1$:
+\begin{equation}
+  \mathcal{L} = \text{MSE}(\text{model}(\bm x), y) + \beta\norm{\bm\theta}_1,
+\end{equation}
+where $\beta$ is scheduled to be low in the beginning of training and stronger
+towards the end.  Specifics of the used models and their hyper-parameters are defined in
+Tab.~\ref{tab:models_large_task} \& \ref{tab:training_large_scale}.  \cite{madsen_neural_2020} perform an
+extensive analysis of this task with different subset and overlap ratios,
+varying model and input sizes, and much more, establishing that the combination
+of NAU/NMU outperforms the NALU. We focus on the
+comparison of NPU, RealNPU, NMU, and NALU on the default parameters of
+\cite{madsen_neural_2020} which sets the subset ratio to 0.5 and the overlap
+ratio to 0.25 (details in Tab.~\ref{tab:dataset_params_large_scale}).
+We include the NaiveNPU (without the relevance gate) to show
+how important the gating mechanism is for both sparsity and overall
+performance.
 
-The NPU is inspired by the multiplication part of the NALU
-Eq.~\ref{eq:nalu_mult}, extended to negative inputs by taking advantage of the
-complex logarithm. In general, for any complex number $z$\footnote{Note that
-complex numbers can be represented in the polar, complex plane where
-$z=re^{i\varphi}$ with $r>0$ and $\varphi \in (0,2\pi)$.}
-\begin{align}
-  \log(z) = \log\left(r\cdot e^{i\varphi}\right)
-     = \log(r) + i\varphi.
-\end{align}
-However, as $z$ is assumed to be real, we can simplify as follows:
-\begin{align}
-  \log(z) = \log(r) + ik\pi,
-\end{align}
-where $k \in [0,1]$ is zero for positive inputs and one for negative inputs $z$.
+Fig.~\ref{fig:pareto} plots testing errors over the number of non-zero
+parameters for all models and tasks.  The addition plot shows that NMU, NPU,
+and RealNPU successfully learn and extrapolate on ($+$) with the NMU converging
+to the sparsest and most accurate models.
+On ($\times$), the best NMU models outperform the NPU and RealNPU, but some
+NMUs do not converge at all. The testing MSE of the NALU is so large that it is
+excluded from the plot.
+On ($\div,\sqrt{\cdot}$) the NPU clearly outperforms all other layers
+in MSE and sparsity. Generally, the difference between the NaiveNPU and the other NPUs
+is huge and demonstrates how important the relevance gate is both
+for convergence and sparsity. The NPUs with relevance gates effectively convert
+irrelevant inputs to 1s, while the NaiveNPU is stuck on the zero gradient
+plateau.
 
-\begin{align}
-  \bm m &= \exp(\bm M \log(\bm x)) \\
-    &= \exp(\bm M ( \log(\bm r) + i\pi\bm k ))
-\end{align}
+\begin{figure}
+  \centering
+  \resizebox{\textwidth}{!}{\input{../plots/pareto.tex}}
+  \caption{Testing MSE over number of non-zero parameters ($w_i > 0.001$) of the large scale
+  arithmetic task. The NMU outperforms the NPU on its
+  native tasks, addition and multiplication. The NPU is the best at division
+  and square-root.  The NaiveNPU without the relevance gate is far off, because
+  it does not have the necessary gradient signal to converge, as discussed in
+  Sec.~\ref{sub:npu}}%
+  \label{fig:pareto}
+\end{figure}
 
-\begin{align}
-  \bm m_{\text{re}} &= \real(\exp(\bm M \log \bm r + i\pi\bm M\bm k)) \\
-    &= \real(\exp(\bm M \log \bm r) \odot (\cos(\pi \bm M \bm k) + i \sin(\pi \bm M \bm k))) \\
-    &= \exp(\bm M \log \bm r) \odot \cos(\pi \bm M \bm k)
-\end{align}
+\begin{table}
+  \centering
+  \caption{Testing errors of the large scale arithmetic task. Each value is
+  obtained by computing median (and median absolute deviation) of 10 runs.}
+  \label{tab:arithmetic100_val}
+  \small
+  \input{../plots/arithmetic100_val.tex}
+\end{table}
 
-\section{Experimetns}%
-\label{sec:experimetns}
+\section{Conclusion}%
+\label{sec:conclusion}
 
-\subsection{10 param func}%
-\label{sub:10_param_func}
+We introduced the \emph{Neural Power Unit} which addresses the deficiencies
+of current arithmetic units: it can learn multiplication, division, and arbitrary power functions for
+positive, negative, and small numbers. We showed that the NPU outperforms its
+main competitor (NALU) and reaches performance that is on par with the
+multiplication specialist NMU (Sec.~\ref{sub:simple_arithmetic_task} and
+\ref{sub:large_scale_arithmetic_task}).\\
+Additionally, we have demonstrated that the NPU converges consistently, even on
+sequential tasks. The RealNPU can be used as a transparent model that
+is capable of recovering the governing equations of dynamical systems purely
+from the data (Sec.~\ref{sub:fractional_sir_model}).
 
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.8\linewidth]{10-param-func-task-nmu-paper.pdf}
-%   \caption{MSE optimization result}%
-%   \label{fig:10-param-func-task-nmu-paper}
-% \end{figure}
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.8\linewidth]{10-param-func-bayes-task-nmu-paper.pdf}
-%   \caption{ARD result with MSE starting point}%
-%   \label{fig:10-param-func-bayes-task-nmu-paper}
-% \end{figure}
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.8\linewidth]{10-param-func-bayes-task-nmu-paper-history.pdf}
-%   \caption{ARD history}%
-%   \label{fig:history}
-% \end{figure}
-% 
-% \subsection{10 param func with sqrt and power}%
-% \label{sub:10_param_func_with_sqrt_and_power}
-% 
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.8\linewidth]{10-param-func-task-sqrt-power.pdf}
-%   \caption{10-param-func-task-sqrt-Power}%
-%   \label{fig:10-param-func-task-sqrt-power}
-% \end{figure}
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.8\linewidth]{10-param-func-bayes-task-sqrt-power.pdf}
-%   \caption{10-param-func-bayes-task-sqrt-Power}%
-%   \label{fig:10-param-func-bayes-task-sqrt-power}
-% \end{figure}
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.8\linewidth]{10-param-func-bayes-task-sqrt-power-history.pdf}
-%   \caption{10-param-func-bayes-task-sqrt-Power-history}%
-%   \label{fig:10-param-func-bayes-task-sqrt-power-history}
-% \end{figure}
+\section{Statement of Broader Impact}%
+\label{sec:statement_of_broader_impact}
 
-\subsection{Gradient surfaces}%
-\label{sub:gradient_surfaces}
+Current neural network architectures are often perceived as black box models
+that are difficult to explain or interpret. This becomes highly problematic if
+ML models are involved in high stakes decisions in e.g. criminal justice,
+healthcare, or control systems.  With the NPU, we hope to contribute to the
+broad topic of interpretable machine learning, with a focus on scientific
+applications.
+Additionally, learning to abstract (mathematical) ideas and extrapolating is a
+fundamental goal that might contribute to more reliable machine learning
+systems.
+
+However, the inductive biases that are used to increase transparency in the NPU
+can cause the model to ignore subgroups in the data. This is not an issue for learning
+arithmetic operations, but could lead to biased models in more general use cases.
+
+The methodology presented in the experiments in Sec.~\ref{sub:fractional_sir_model}
+is not indented to be used for real-world epidemiological predictions.
+They are merely demonstrating that the NPU can learn an ODE with fractional powers.
+For an application of the NPU much more post-processing has to be done to ensure
+the reliability of the results.
+
+\section{Acknowledgements}%
+\label{sec:acknowledgements}
+
+The research presented in this work has been supported by the Grant Agency of
+Czech Republic no. 18-21409S. The authors also acknowledge the support of the
+OP VVV MEYS funded project CZ.02.1.01/0.0/0.0/16\_019/0000765 ``Research Center
+for Informatics''.
+
+We thank the authors of the Julia packages
+Flux.jl~\citep{innes_fashionable_2018} and
+DifferentialEquations.jl~\citep{rackauckas_differentialequationsjl_2017}).
 
@@
 
+\newpage
+\appendix
+\section*{Appendix}%
+\label{sec:appendix}
+
+\setcounter{table}{0}
+\renewcommand{\thetable}{A\arabic{table}}
+
+\begin{table}[h]
+  \centering
+  \caption{Model definitions for the fSIR task.}
+  \label{tab:fsir_models}
+  \begin{tabular}{llll}
+    \toprule
+    Model & Layer 1 & Layer 2 & Layer 3 \\
+    \midrule
+    NPU & $\npu(3,\,h)$ & $\nau(h,\,3)$ & -- \\
+    NPU & NPU$_{\text{real}}(3,\,h)$ & $\nau(h,\,3)$ & -- \\
+    Dense & $\dense(2,\,h,\sigma)$ & $\dense(h,\,h,\,\sigma)$ & $\dense(h,\,3)$ \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\begin{table}[h]
+  \centering
+  \caption{Testing error on the simple arithmetic task for the different models
+  (i.e. mean of each heatmap in Fig.~\ref{fig:simple_err}). Each value is
+  obtained by computing median (and median absolute deviation) of the error of
+  20 models.}
+  \label{tab:simple_err}
+  \small
+  \input{../plots/simple_err.tex}
+\end{table}
+
+\begin{table}[h]
+  \centering
+  \caption{Model definitions for the simple arithmetic task.}
+  \label{tab:models_simple_task}
+  \begin{tabular}{llll}
+    \toprule
+    Model & Layer 1 & Layer 2 & Layer 3 \\
+    \midrule
+    NPU & NAU(2,\,6) & NPU(6,\,2) & -- \\
+    RealNPU & NAU(2,\,6) & RealNPU(6,\,2) & -- \\
+    NMU & NAU(2,\,6) & NMU(6,\,2) & -- \\
+    NALU & NALU(2,\,6) & NALU(6,\,2) & -- \\
+    iNALU & iNALU(2,\,6) & iNALU(6,\,2) & -- \\
+    Dense & Dense(2,\,10,\,$\sigma$) & Dense(10,\,10,\,$\sigma$) & Dense(10,\,2) \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\begin{table}[h]
+  \centering
+  \caption{Model definitions for the large scale arithmetic task.}
+  \label{tab:models_large_task}
+  \begin{tabular}{llll}
+    \toprule
+    Model & Layer 1 & Layer 2\\
+    \midrule
+    NPU & NAU(100,\,100) & NPU(100,\,1) \\
+    NPU & NAU(100,\,100) & NPU(100,\,1) \\
+    NMU & NAU(100,\,100) & NMU(100,\,1) \\
+    NALU & NALU(100,\,100) & NALU(100,\,1) \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\begin{table}[h]
+  \centering
+  \caption{Dataset parameters for the large scale arithmetic task.}
+  \label{tab:dataset_params_large_scale}
+  \begin{tabular}{lccccc}
+    \toprule
+    Task & Input size & Subset ratio & Overlap ratio & Training range  & Validation range\\
+    \midrule
+    Add  & 100        & 0.5          & 0.25          & Sobol(-1,1)     & Sobol(-4,4) \\
+    Mult & 100        & 0.5          & 0.25          & Sobol(-1,1)     & Sobol(-4,4)\\
+    Div  & 100        & 0.5          & --            & Sobol(0,0.5)    & Sobol(-0.5,0.5) \\
+    Sqrt & 100        & 0.5          & --            & Sobol(0,2)      & Sobol(0,4) \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\begin{table}[h]
+  \centering
+  \caption{Training parameters for the large scale arithmetic task. The
+  $\beta$-parameters define the stepwise exponential growth of the $L_1$
+  regularization with start, step, growth, and end.}
+  \label{tab:training_large_scale}
+  \begin{tabular}{lcccccc}
+    \toprule
+    Task & Learning rate & Iterations & $\beta_{\text{start}}$ &
+      $\beta_{\text{end}}$ & $\beta_{\text{step}}$  & $\beta_{\text{growth}}$ \\
+    \midrule
+    Add  & 1e-2 & 1e5 & 1e-5 & 1e-4 & 10\,000 & 10 \\
+    Mult & 5e-3 & 1e5 & 1e-5 & 1e-7 & 10\,000 & 10 \\
+    Div  & 5e-3 & 1e5 & 1e-9 & 1e-7 & 10\,000 & 10 \\
+    Sqrt & 5e-3 & 1e5 & 1e-6 & 1e-4 & 10\,000 & 10 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
 \end{document}

### 2020-12-17 slides_short/fsir.tex
more slides

--- 2020-06-04 plots/pareto_sir.tex
@@
 \begin{tikzpicture}[/tikz/background rectangle/.style={fill={rgb,1:red,1.0;green,1.0;blue,1.0}, draw opacity={1.0}}, show background rectangle]
-\begin{axis}[point meta max={nan}, point meta min={nan}, legend cell align={left}, title={Pareto}, title style={at={{(0.5,1)}}, anchor={south}, font={{\fontsize{14 pt}{18.2 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, legend style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid, fill={rgb,1:red,1.0;green,1.0;blue,1.0}, fill opacity={1.0}, text opacity={1.0}, font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, at={(0.98, 0.98)}, anchor={north east}}, axis background/.style={fill={rgb,1:red,1.0;green,1.0;blue,1.0}, opacity={1.0}}, anchor={north west}, xshift={1.0mm}, yshift={-1.0mm}, width={112.3mm}, height={74.2mm}, scaled x ticks={false}, xlabel={Nr.
-Paramters}, x tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, x tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, xlabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, xmode={log}, log basis x={10}, xmajorgrids={true}, xmin={15.305486448632008}, xmax={625.3313171144225}, xtick={{15.848931924611142,25.11886431509581,39.810717055349734,63.09573444801933,100.0,158.48931924611142,251.18864315095823,398.1071705534973}}, xticklabels={{$10^{1.2}$,$10^{1.4}$,$10^{1.6}$,$10^{1.8}$,$10^{2.0}$,$10^{2.2}$,$10^{2.4}$,$10^{2.6}$}}, xtick align={inside}, xticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, x grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis x line*={left}, x axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}, scaled y ticks={false}, ylabel={MSE}, y tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, y tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, ylabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, ymode={log}, log basis y={10}, ymajorgrids={true}, ymin={0.005}, ymax={10000.0}, ytick={{0.01,0.1,1.0,10.0,100.0,1000.0,10000.0}}, yticklabels={{$10^{-2}$,$10^{-1}$,$10^{0}$,$10^{1}$,$10^{2}$,$10^{3}$,$10^{4}$}}, ytick align={inside}, yticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, y grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis y line*={left}, y axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}]
-    \addplot[color={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, name path={089ee56b-6822-4377-827c-374155ed22b5}, draw opacity={0.25}, line width={0}, solid, mark={*}, mark size={3.75 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.25}, fill={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, fill opacity={0.25}, line width={0.75}, rotate={0}, solid}, only marks, forget plot]
-        coordinates {
-            (105.0,0.05584966441816506)
-            (102.0,0.04975238296092152)
-            (109.0,0.05940020202500067)
-            (89.0,2.294967031333799)
-            (109.0,0.01674682323492209)
-            (103.0,0.10720479779621425)
-            (111.0,0.047378610574098125)
-            (91.0,0.10379493048125163)
-            (110.0,2.513624607833005)
-            (104.0,0.05086478924822935)
-            (109.0,0.11351618280207543)
-            (108.0,0.4020253123624037)
-            (110.0,0.07446102987541804)
-            (105.0,0.11535032606585913)
-            (111.0,0.18480906070431535)
-            (98.0,0.20276032629175944)
-            (107.0,0.08951349573643062)
-            (102.0,0.04128707134536484)
-            (111.0,0.08564751808207169)
-            (101.0,0.3024196229705965)
-            (134.0,0.0625994120602839)
-            (123.0,0.07725887987692295)
-            (137.0,0.0446213228734711)
-            (133.0,0.3084188318399655)
-            (133.0,0.01962266981062221)
-            (134.0,0.10146607016990984)
-            (138.0,0.06814314041036643)
-            (126.0,0.1400125295960749)
-            (138.0,467.4741755918939)
-            (127.0,1.1166477896146412)
-            (138.0,0.17714972309111646)
-            (19.0,0.11922132709056152)
-            (133.0,0.08769252229223219)
-            (130.0,0.07793316024608679)
-            (137.0,0.1718723416265335)
-            (125.0,0.33914255094342527)
-            (136.0,0.015348260495236497)
-            (131.0,0.14565843998621403)
-            (137.0,0.19446231157170504)
-            (123.0,0.26589194567164826)
-            (178.0,0.13602372744489552)
-            (164.0,1.3096147548790622)
-            (183.0,1.2001412178607553)
-            (20.0,0.13777438440294185)
-            (181.0,0.8479907542370899)
-            (183.0,0.0950066129025234)
-            (182.0,0.0973834969835291)
-            (140.0,4.6045371868841265)
-            (181.0,0.08489426529555413)
-            (171.0,1.434207428800683)
-            (182.0,0.03715339077893962)
-            (172.0,0.22976469267521113)
-            (179.0,0.021032926937894693)
-            (174.0,0.12032695402812911)
-            (183.0,0.1184679992516246)
-            (167.0,0.19684607920197908)
-            (179.0,0.07686867922650574)
-            (173.0,2.5546282892181007)
-            (182.0,2.568218715361108)
-            (20.0,0.14201835288630793)
-            (57.0,0.034130835764939665)
-            (57.0,0.08573571106663361)
-            (57.0,0.027468464787432298)
-            (53.0,0.1845821255465333)
-            (57.0,0.3145059229030894)
-            (50.0,0.03924953982860379)
-            (57.0,0.06856875980583756)
-            (18.0,0.13408208779207065)
-            (57.0,0.246120844440766)
-            (57.0,0.04960174895763792)
-            (57.0,2.4305662054492216e9)
-            (49.0,0.19845525108383108)
-            (57.0,0.10124427200601582)
-            (57.0,723.2519398047787)
-            (57.0,0.04868286562065639)
-            (21.0,0.09182349525167144)
-            (57.0,2.72184197085509)
-            (57.0,0.02883792885224287)
-            (57.0,0.05463115607163071)
-            (47.0,3.4065463877724946)
-            (83.0,0.0897939767464811)
-            (73.0,0.13931869624662485)
-            (82.0,0.2953775450777107)
-            (78.0,0.18845400004232993)
-            (83.0,0.03326786171772812)
-            (81.0,0.03346088666911155)
-            (84.0,0.021920164977564584)
-            (29.0,0.13107584979633108)
-            (83.0,0.025448977666601213)
-            (83.0,0.052182247335789286)
-            (84.0,0.03318537664315938)
-            (19.0,0.11324273930491076)
-            (83.0,0.049563710942017516)
-            (82.0,0.05229073956836107)
-            (84.0,0.936285586965232)
-            (79.0,0.36352072822414827)
-            (84.0,0.06743210142176875)
-            (83.0,0.06069929189699635)
-            (84.0,1.0402239808527012)
-            (20.0,0.0863532735177328)
-        }
-        ;
-    \addplot[color={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, name path={fb8ade92-3de5-4181-955a-9068086f05cd}, draw opacity={0.25}, line width={0}, solid, mark={pentagon*}, mark size={3.75 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.25}, fill={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, fill opacity={0.25}, line width={0.75}, rotate={0}, solid}, only marks, forget plot]
-        coordinates {
-            (235.0,0.13357198945321846)
-            (70.0,0.04461548817109118)
-            (240.0,0.27826514621649645)
-            (55.0,0.40610599113961626)
-            (231.0,0.16842724844486784)
-            (183.0,0.053126061241543406)
-            (243.0,0.09279724868377123)
-            (44.0,0.6219680679576621)
-            (224.0,0.14673187421056033)
-            (222.0,0.17126303810452492)
-            (242.0,0.26732925740823366)
-            (72.0,0.40406046468282036)
-            (239.0,0.27881283308599)
-            (215.0,0.08349271759735011)
-            (242.0,0.2125101399226415)
-            (32.0,0.5513286633867127)
-            (235.0,0.22568337408398828)
-            (206.0,0.09258343306049661)
-            (243.0,0.20454040997137593)
-            (26.0,0.5107297023521244)
-            (323.0,0.3667902032609065)
-            (106.0,0.04378510564953422)
-            (346.0,0.16065746518529136)
-            (41.0,0.4591112638861731)
-            (338.0,0.16645620302038866)
-            (329.0,0.0837772625628679)
-            (343.0,0.14366152756083547)
-            (43.0,0.6024946038819587)
-            (331.0,0.18929036413010172)
-            (287.0,0.33185148527249725)
-            (348.0,0.04576725492168219)
-            (40.0,0.5307735589972514)
-            (333.0,0.25561466836673213)
-            (267.0,0.08139063563463969)
-            (348.0,0.2603533867117459)
-            (42.0,0.485145599462851)
-            (324.0,0.06458173214154204)
-            (150.0,0.03822594080269291)
-            (346.0,0.22772148021684693)
-            (38.0,0.5349911168200644)
-            (529.0,0.09246980203670312)
-            (76.0,0.032150726839285076)
-            (561.0,0.2953731709925806)
-            (42.0,0.42435150858456305)
-            (551.0,0.5658710399734437)
-            (172.0,0.03671331385133575)
-            (562.0,0.2247420272307935)
-            (39.0,0.6093866677344313)
-            (552.0,0.42285681275210707)
-            (338.0,0.07585812329891815)
-            (561.0,0.16916001531239544)
-            (39.0,0.4801687797714871)
-            (536.0,0.1460284576306947)
-            (519.0,0.1674664372593216)
-            (563.0,0.07034107539784748)
-            (36.0,0.6153149633129895)
-            (538.0,0.2901270824759899)
-            (314.0,0.0894523538965804)
-            (561.0,0.9493069230558913)
-            (43.0,0.45231290229037063)
-            (86.0,0.19904079876071654)
-            (86.0,0.2474597369029254)
-            (87.0,0.9661924012140722)
-            (52.0,0.5183448216596367)
-            (83.0,0.41163416709756745)
-            (86.0,0.2018533637471545)
-            (87.0,0.7338740990737738)
-            (29.0,0.502255804939499)
-            (85.0,0.24871677122634128)
-            (79.0,0.47124624050445574)
-            (87.0,0.3017981172481904)
-            (34.0,0.4118665138102874)
-            (86.0,0.46110233661130057)
-            (81.0,0.34380752518935775)
-            (87.0,0.592914605387025)
-            (55.0,0.5340532094284938)
-            (84.0,0.21982864921620568)
-            (86.0,0.12593689360335356)
-            (86.0,0.2490899738548067)
-            (30.0,0.3888134391760499)
-            (149.0,0.155251101357749)
-            (131.0,0.055439107403504)
-            (155.0,0.12238978551321686)
-            (35.0,0.43098325658284026)
-            (154.0,0.1394374093998332)
-            (152.0,0.2297799184953769)
-            (155.0,0.15759694151794004)
-            (39.0,0.5057258031699502)
-            (154.0,0.3922494485884269)
-            (153.0,0.3902229654498584)
-            (156.0,0.2773388179874096)
-            (43.0,0.5416488514754519)
-            (152.0,0.2540652840489718)
-            (152.0,0.11832827918668122)
-            (154.0,0.11410277669310671)
-            (45.0,0.5469697488849031)
-            (151.0,0.1870216675213049)
-            (127.0,0.16707232055495033)
-            (154.0,0.8019823908524971)
-            (52.0,0.5113011726127454)
-        }
-        ;
-    \addplot[color={rgb,1:red,1.0;green,0.498;blue,0.0549}, name path={a4a2407a-9d13-4d5f-9806-f4dc789913ff}, draw opacity={0.25}, line width={0}, solid, mark={diamond*}, mark size={3.75 pt}, mark options={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.25}, fill={rgb,1:red,1.0;green,0.498;blue,0.0549}, fill opacity={0.25}, line width={0.75}, rotate={0}, solid}, only marks, forget plot]
-        coordinates {
-            (75.0,3.147945165083429)
-            (73.0,0.7787622330875555)
-            (75.0,14.274696485077706)
-            (72.0,1.0547043767865791)
-            (75.0,3.332024981183407)
-            (73.0,0.8054592789691524)
-            (75.0,1.9717984455866802)
-            (30.0,0.3567713595345774)
-            (74.0,1.3257338505548062)
-            (71.0,0.454412627271946)
-            (75.0,199.32322467686308)
-            (75.0,1.0895748631691455)
-            (75.0,2.4040986461550835)
-            (75.0,30.945783537221924)
-            (75.0,1.3655781266539022)
-            (72.0,1.7771060355248247)
-            (75.0,2.095095365942199)
-            (74.0,1.2957150765737162)
-            (75.0,10.287194966343153)
-            (71.0,23.823930630622364)
-            (91.0,2.4310322835821725)
-            (90.0,2.03837213281791)
-            (93.0,18.48678688820552)
-            (18.0,0.1828119186366187)
-            (93.0,1.402802143535598)
-            (93.0,0.5216804362331351)
-            (93.0,344.95675624956914)
-            (17.0,0.028392317708999436)
-            (93.0,0.5279417818890894)
-            (92.0,2.279971972737263)
-            (93.0,1.6171895486111396)
-            (87.0,0.9929110131500897)
-            (92.0,1.6970363177778334)
-            (88.0,1.281239828889679)
-            (93.0,1.9682814650085763)
-            (90.0,1.0443588384128824)
-            (93.0,1.4672964427212034)
-            (93.0,2.512126815083123)
-            (93.0,1.7528157502014407e27)
-            (17.0,0.042776379040499156)
-            (123.0,292782.19801080116)
-            (114.0,0.8319858220508034)
-            (122.0,38.36679799718143)
-            (119.0,4.247901992170559)
-            (123.0,2.1603952895878047)
-            (123.0,1.612179389285352)
-            (123.0,2.1315469624808055e8)
-            (120.0,2.863381885496416)
-            (123.0,1.5701579511267307)
-            (115.0,1.1995883679712909)
-            (122.0,0.8442486879600574)
-            (107.0,1.4996647965557675)
-            (123.0,43.27286005493181)
-            (123.0,0.22240221552099876)
-            (123.0,1.724556189521123)
-            (123.0,0.7600881434640848)
-            (123.0,1.55953539967718)
-            (122.0,2.5016970428713385)
-            (122.0,125.83729920965449)
-            (119.0,1.474402129759871)
-            (39.0,1.6787168071085867)
-            (38.0,23.286011001150722)
-            (39.0,1.8524442120647987e6)
-            (39.0,1.1819811023887494)
-            (38.0,25.653816244212006)
-            (39.0,7.724620004876016)
-            (39.0,1.5998738392072849)
-            (39.0,230.55843153298235)
-            (38.0,35.384317652871445)
-            (39.0,18.021070189844696)
-            (39.0,195.47077720096976)
-            (39.0,160.86609736256958)
-            (39.0,3.0592725712776643)
-            (39.0,4.398153803012362)
-            (39.0,1.1590218432565333)
-            (17.0,0.035424442595674274)
-            (38.0,4162.440925088575)
-            (39.0,40.27926776330599)
-            (39.0,2.6373813625877043)
-            (39.0,9.740619004230942)
-            (57.0,0.8097482769396408)
-            (57.0,0.8683241511330079)
-            (57.0,0.6548577323997611)
-            (57.0,18.271264624639596)
-            (57.0,0.8110250229754907)
-            (57.0,1.0118191812875524e19)
-            (57.0,1166.0668083720273)
-            (54.0,24.255595170101138)
-            (57.0,2.4197291464377434e17)
-            (57.0,25.939711745446342)
-            (57.0,411.43443310327984)
-            (54.0,25.852674031372572)
-            (57.0,1.0362054731778492)
-            (57.0,1.0072691225003283e14)
-            (56.0,62.4551625376836)
-            (47.0,0.3358689620078998)
-            (57.0,2.1657544482083853)
-            (57.0,1.253110778534678)
-            (57.0,2.6027300344473447)
-            (57.0,26.29584591974179)
-        }
-        ;
-    \addplot[color={rgb,1:red,0.1216;green,0.4667;blue,0.7059}, name path={6fca2f50-6519-44f2-b9d9-640264e75dcd}, draw opacity={1.0}, line width={2}, dashed]
-        coordinates {
-            (26.0,0.5107297023521244)
-            (30.0,0.3888134391760499)
-            (70.0,0.04461548817109118)
-            (76.0,0.032150726839285076)
-            (172.0,0.03671331385133575)
-            (348.0,0.04576725492168219)
-            (563.0,0.07034107539784748)
-        }
-        ;
-    \addlegendentry {Dense}
-    \addplot[color={rgb,1:red,0.1725;green,0.6275;blue,0.1725}, name path={4df2801f-27fe-4ea1-9f00-dbdbe35d4500}, draw opacity={1.0}, line width={2}, solid]
-        coordinates {
-            (57.0,2.4305662054492216e9)
-            (18.0,0.13408208779207065)
-            (20.0,0.0863532735177328)
-            (57.0,0.027468464787432298)
-            (109.0,0.01674682323492209)
-            (136.0,0.015348260495236497)
-            (179.0,0.021032926937894693)
-        }
-        ;
-    \addlegendentry {NPU}
-    \addplot[color={rgb,1:red,1.0;green,0.498;blue,0.0549}, name path={23f3a274-9dd0-40ba-b4c3-9bf7970f58c1}, draw opacity={1.0}, line width={2}, dashdotted]
-        coordinates {
-            (39.0,1.8524442120647987e6)
-            (17.0,0.042776379040499156)
-            (17.0,0.028392317708999436)
-            (123.0,0.22240221552099876)
-        }
-        ;
-    \addlegendentry {RealNPU}
-\end{axis}
-\begin{axis}[point meta max={nan}, point meta min={nan}, legend cell align={left}, title={SIR Model}, title style={at={{(0.5,1)}}, anchor={south}, font={{\fontsize{14 pt}{18.2 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, legend style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid, fill={rgb,1:red,1.0;green,1.0;blue,1.0}, fill opacity={1.0}, text opacity={1.0}, font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, at={(0.98, 0.5)}, anchor={east}}, axis background/.style={fill={rgb,1:red,1.0;green,1.0;blue,1.0}, opacity={1.0}}, anchor={north west}, xshift={115.3mm}, yshift={-1.0mm}, width={112.3mm}, height={74.2mm}, scaled x ticks={false}, xlabel={Time}, x tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, x tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, xlabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, xmajorgrids={true}, xmin={-6.0}, xmax={206.0}, xtick={{0.0,50.0,100.0,150.0,200.0}}, xticklabels={{$0$,$50$,$100$,$150$,$200$}}, xtick align={inside}, xticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, x grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis x line*={left}, x axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}, scaled y ticks={false}, ylabel={}, y tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, y tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, ylabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, ymajorgrids={true}, ymin={-3.0}, ymax={103.0}, ytick={{0.0,25.0,50.0,75.0,100.0}}, yticklabels={{$0$,$25$,$50$,$75$,$100$}}, ytick align={inside}, yticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, y grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis y line*={left}, y axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}]
+\begin{axis}[point meta max={nan}, point meta min={nan}, legend cell align={left}, title={fSIR Model}, title style={at={{(0.5,1)}}, anchor={south}, font={{\fontsize{14 pt}{18.2 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, legend style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid, fill={rgb,1:red,1.0;green,1.0;blue,1.0}, fill opacity={1.0}, text opacity={1.0}, font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, at={(0.98, 0.5)}, anchor={east}}, axis background/.style={fill={rgb,1:red,1.0;green,1.0;blue,1.0}, opacity={1.0}}, anchor={north west}, xshift={115.3mm}, yshift={-1.0mm}, width={112.3mm}, height={74.2mm}, scaled x ticks={false}, xlabel={Time}, x tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, x tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, xlabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, xmajorgrids={true}, xmin={-6.0}, xmax={206.0}, xtick={{0.0,50.0,100.0,150.0,200.0}}, xticklabels={{$0$,$50$,$100$,$150$,$200$}}, xtick align={inside}, xticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, x grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis x line*={left}, x axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}, scaled y ticks={false}, ylabel={}, y tick style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}}, y tick label style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, opacity={1.0}, rotate={0}}, ylabel style={at={(ticklabel cs:0.5)}, anchor=near ticklabel, font={{\fontsize{11 pt}{14.3 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, ymajorgrids={true}, ymin={-3.0}, ymax={103.0}, ytick={{0.0,25.0,50.0,75.0,100.0}}, yticklabels={{$0$,$25$,$50$,$75$,$100$}}, ytick align={inside}, yticklabel style={font={{\fontsize{8 pt}{10.4 pt}\selectfont}}, color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, rotate={0.0}}, y grid style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={0.1}, line width={0.5}, solid}, axis y line*={left}, y axis line style={color={rgb,1:red,0.0;green,0.0;blue,0.0}, draw opacity={1.0}, line width={1}, solid}]
     \addplot[color={rgb,1:red,0.502;green,0.502;blue,0.502}, name path={4d2d32cf-0078-477b-aca5-ac47612e3b35}, draw opacity={0.8}, line width={4}, solid]

### 2020-12-17 slides_long/julia/1d-extrapolation.jl

@@ -1,0 +1,163 @@
+using Distributions
+using DrWatson
+using Flux
+using NeuralArithmetic
+
+function dense_abs(config)
+    @unpack hdim = config
+
+    task(x) = abs(x)
+    xs = rand(Uniform(-1,1), 1, 100, 10000)
+    data = [(xs[:,:,i],task.(xs[:,:,i])) for i in 1:size(xs,3)]
+
+    model = Chain(Dense(1,hdim,σ), Dense(hdim,hdim,σ), Dense(hdim,1))
+    trainmodel(model, data, config)
+end
+function dense_square(config)
+    @unpack hdim = config
+
+    task(x) = x^2
+    xs = rand(Uniform(-1,1), 1, 100, 10000)
+    data = [(xs[:,:,i],task.(xs[:,:,i])) for i in 1:size(xs,3)]
+
+    model = Chain(Dense(1,hdim,σ), Dense(hdim,1))
+    trainmodel(model, data, config)
+end
+function dense_sin(config)
+    @unpack hdim = config
+
+    task(x) = sin(x)
+    xs = rand(Uniform(-3,3), 1, 100, 10000)
+    data = [(xs[:,:,i],task.(xs[:,:,i])) for i in 1:size(xs,3)]
+
+    model = Chain(Dense(1,hdim,σ), Dense(hdim,1))
+    trainmodel(model, data, config)
+end
+
+
+
+function npu_abs(config)
+    @unpack hdim = config
+
+    task(x) = abs(x)
+    xs = Float32.(rand(Uniform(-1,1), 1, 100, 10000))
+    data = [(xs[:,:,i],task.(xs[:,:,i])) for i in 1:size(xs,3)]
+
+    model = Chain(NPU(1,hdim), NAU(hdim,1))
+    trainmodel(model, data, config)
+end
+function npu_square(config)
+    @unpack hdim = config
+
+    task(x) = x^2
+    xs = Float32.(rand(Uniform(-1,1), 1, 100, 10000))
+    data = [(xs[:,:,i],task.(xs[:,:,i])) for i in 1:size(xs,3)]
+
+    model = Chain(NPU(1,hdim), NAU(hdim,1))
+    trainmodel(model, data, config)
+end
+function npu_sin(config)
+    @unpack hdim = config
+
+    task(x) = sin(x)
+    xs = Float32.(rand(Uniform(-3,3), 1, 100, 10000))
[…]

### 2020-12-17 paper/main.tex
rename table...
Merge arxiv branch
Includes slides / fixed references

@@
   numbers or can only represent a subset of arithmetic operations. We introduce
-  the \emph{Neural Power Unit} (NPU)\footnote{
-    Implementation of Neural Arithmetic Units: \url{github.com/nmheim/NeuralArithmetic.jl}.
+  the \emph{Neural Power Unit} (NPU).\footnote{
+    Implementation of Neural Arithmetic Units: \url{github.com/nmheim/NeuralArithmetic.jl}
     The code to reproduce our experiments is available at \url{github.com/nmheim/NeuralPowerUnits}.
@@
 With this experiment we aim to show that the NPU can \emph{potentially} discover
-exact ODE models\footnote{The demonstration given here is not intended to be
+exact ODE models.\footnote{The demonstration given here is not intended to be
 used in practice. For real-world predictions in such a sensitive area much more
-post-processing is needed to ensure safe predictions.}.
+post-processing is needed to ensure safe predictions.}
 An example of an ODE that contains powers is a modification of the well-known
@@
 
-\section{Statement of Broader Impact}%
+\section*{Broader Impact}%
 \label{sec:statement_of_broader_impact}
@@
 
-\section{Acknowledgements}%
+\section*{Acknowledgements and Disclosure of Funding}%
 \label{sec:acknowledgements}

### 2020-12-17 slides_long/julia/interpolate.jl

@@ -1,0 +1,23 @@
+using DrWatson
+using Flux
+
+model = load(datadir("dense-square_hdim=5_lr=0.01.bson"))[:model]
+predict(m,x::Real) = m([x])[1]
+
+using Plots
+using LaTeXStrings
+pgfplotsx()
+#pyplot()
+theme(:default, lw=2, legend=false)
+
+x = -1:0.1:1
+f(x) = x^2
+p1 = plot(x, f, label="Truth", color="black", size=(200,200)) 
+plot!(p1, x, x->predict(model,x), label="Dense", ls=:dash)
+savefig(p1, "x2-interp.tikz")
+
+x = -2:0.1:2
+p2 = plot(x, f, label="Truth", color="black", size=(200,200)) 
+vline!(p2, [-1,1], color="black", lw=1, alpha=0.5)
+plot!(p2, x, x->predict(model,x), label="Dense", ls=:dash, color=2)
+savefig(p2, "x2-extrap.tikz")

### 2021-01-06 scripts/id-loss.jl
updated simple arithmetic task plot

@@ -1,9 +1,9 @@
 using DrWatson
-@quickactivate "NIPS_2020_NPU"
 
 using Plots
 using Distributions
 using LaTeXStrings
+using NeuralArithmetic
 using Random
 Random.seed!(2)
 #pgfplotsx()

### 2021-01-06 scripts/simple/plots.jl

@@ -21,19 +21,28 @@ function inftoextreme(z)
     end
 end
 
-folder = datadir("simple")
-run = 19
-npu = load(joinpath(folder, "pos-gatednpux_lr=0.005_niters=20000_run=10_βl1=0.bson"))[:model]
-run = 9
-realnpu = load(joinpath(folder, "pos-realnpu_lr=0.005_niters=20000_run=$(run)_βl1=0.bson"))[:model]
+umin = 0.01
+umax = 2
+folder = datadir("simple_lr005_umin=$(umin)_umax=$(umax)")
+
+run  = 2
+file = "npu_lr=0.005_niters=20000_run=$(run)_umax=2_umin=0.01_βl1=0.bson"
+npu = load(joinpath(folder, file))[:model]
+run = 37
+file = "realnpu_lr=0.005_niters=20000_run=$(run)_umax=2_umin=0.01_βl1=0.bson"
+realnpu = load(joinpath(folder, file))[:model]
+run = 15
+file = "nalu_lr=0.005_niters=20000_run=$(run)_umax=2_umin=0.01.bson"
+nalu = load(joinpath(folder, file))[:model]
+run = 36
+file = "inalu_lr=0.005_niters=20000_run=$(run)_t=20_umax=2_umin=0.01.bson"
+inalu = load(joinpath(folder, file))[:model]
 run = 8
-nalu = load(joinpath(folder, "pos-nalu_lr=0.005_niters=20000_run=$(run).bson"))[:model]
-run = 4
-inalu = load(joinpath(folder, "pos-inalu_lr=0.001_niters=20000_run=$(run).bson"))[:model]
-run = 8
-nmu = load(joinpath(folder, "pos-nmu_lr=0.005_niters=20000_run=$(run).bson"))[:model]
-run = 1
-dense = load(joinpath(folder, "pos-dense_lr=0.005_niters=20000_run=$(run).bson"))[:model]
+file = "nmu_lr=0.005_niters=20000_run=$(run)_umax=2_umin=0.01.bson"
+nmu = load(joinpath(folder, file))[:model]
+run = 12
+file = "dense_lr=0.005_niters=20000_run=$(run)_umax=2_umin=0.01.bson"
+dense = load(joinpath(folder, file))[:model]
 
 
 posnegx = Float32.(collect(-4.1:0.2:4))
[…]

### 2021-01-06 scripts/simple/results_table.jl

@@ -143,7 +143,7 @@ end
 
 umin = 0.01
 umax = 2
-data_directory = datadir("simple_umin=$(umin)_umax=$(umax)")
+data_directory = datadir("simple_lr005_umin=$(umin)_umax=$(umax)")
 df = collect_folder!(data_directory)
 sort!(df,"model")
 adf = aggregateruns(df)

### 2021-01-06 scripts/simple/run.jl

@@ -161,33 +161,33 @@ nr_runs = 20
 
 for (umin,umax) in train_ranges
     @info "Running training range: ($umin,$umax)"
-    data_directory = datadir("simple_umin=$(umin)_umax=$(umax)")
+    data_directory = datadir("simple_lr005_umin=$(umin)_umax=$(umax)")
 
     @progress for run in 1:nr_runs
         res, _ = produce_or_load(data_directory,
-                                 Dict(:niters=>20000, :βl1=>0, :lr=>0.001, :run=>run, :umin=>umin, :umax=>umax),
+                                 Dict(:niters=>20000, :βl1=>0, :lr=>0.005, :run=>run, :umin=>umin, :umax=>umax),
                                  run_npu,
                                  prefix="npu",
                                  force=false, digits=6)
         res, _ = produce_or_load(data_directory,
-                                 Dict(:niters=>20000, :βl1=>0, :lr=>0.001, :run=>run, :umin=>umin, :umax=>umax),
+                                 Dict(:niters=>20000, :βl1=>0, :lr=>0.005, :run=>run, :umin=>umin, :umax=>umax),
                                  run_realnpu,
                                  prefix="realnpu",
                                  force=false, digits=6)
         res, _ = produce_or_load(data_directory,
-                                 Dict(:niters=>20000, :lr=>0.001, :run=>run, :umin=>umin, :umax=>umax),
+                                 Dict(:niters=>20000, :lr=>0.005, :run=>run, :umin=>umin, :umax=>umax),
                                  run_nalu,
                                  prefix="nalu", force=false, digits=6)
         res, _ = produce_or_load(data_directory,
-                                 Dict(:niters=>20000, :lr=>0.001, :run=>run, :umin=>umin, :umax=>umax),
+                                 Dict(:niters=>20000, :lr=>0.005, :run=>run, :umin=>umin, :umax=>umax),
                                  run_nmu,
                                  prefix="nmu", force=false, digits=6)
         res, _ = produce_or_load(data_directory,
-                                 Dict(:niters=>20000, :lr=>0.001, :run=>run, :umin=>umin, :umax=>umax),
+                                 Dict(:niters=>20000, :lr=>0.005, :run=>run, :umin=>umin, :umax=>umax),
                                  run_dense,
                                  prefix="dense", force=false, digits=6)
         res, _ = produce_or_load(data_directory,
[…]

### 2021-01-06 slides_long/naive-npu.tex

% \documentclass[tikz,14pt,border=10pt]{standalone}
% 
% \usepackage{verbatim}
% \usepackage{bm}
% 
% \usetikzlibrary{%
%   arrows,%
%   shapes.misc,% wg. rounded rectangle
%   shapes.arrows,%
%   chains,%
%   matrix,%
%   positioning,% wg. " of "
%   scopes,%
%   decorations.pathmorphing,% /pgf/decoration/random steps | erste Graphik
%   shadows%
% }
% \begin{document}

\definecolor{c1}{HTML}{8097e9}
\definecolor{c2}{HTML}{c6dea2}
\definecolor{c3}{HTML}{ffb200}
\definecolor{c4}{HTML}{b6b6b6}

\tikzset{
  function/.style={
    % The shape:
    rectangle,
    rounded corners=3,
    % The size:
    minimum height=6mm,
    % The border:
    thick,
    draw=black,
    % The filling:
    top color=c1,
    bottom color=c1,
    % Font
    font=\tt
  },
  vector/.style={
    % The shape:
    rounded rectangle,
    minimum size=6mm,
    % The rest
    thick,draw=black,
    top color=c2!80,
    bottom color=c2!80,
    font=\ttfamily
  },
  trainable/.style={
    % The shape:
    diamond,
    rounded corners=3,
    minimum size=6mm,
    % The rest
    thick,draw=black,
    top color=c3!80,
    bottom color=c3!80,
    font=\ttfamily
  },
  skip loop/.style={to path={-- ++(0,#1) -| (\tikztotarget)}}
}

{
  \tikzset{vector/.append style={text height=1.5ex,text depth=.25ex}}
  \tikzset{function/.append style={text height=1.5ex,text depth=.25ex}}
}

\begin{tikzpicture}[
        point/.style={coordinate},>=stealth',thick,draw=black!90,
        tip/.style={->,shorten >=0.007pt},every join/.style={rounded corners},
        fat/.style={-, ultra thick, opacity=0.5},every join/.style={rounded corners},
        path/.style={to path={-- (\tikztotarget)}},
        hv path/.style={to path={-| (\tikztotarget)}},
        vh path/.style={to path={|- (\tikztotarget)}},
        text height=1.5ex,text depth=.25ex]

  \matrix[column sep=3mm, row sep=3mm] {
    & \node (abs) [function] {$\mathrm{abs}$}; &
    \node (r) [vector] {$\bm r$}; & &
    \node (mult) [function] {$\mathrm{mult}$}; \\

    \node (x) [vector] {$\bm x$}; & & & &
    \node (wr) [trainable] {$\bm W_r$}; & \node (wi) [trainable] {$\bm W_i$}; &
    \node (odot) [function] {$\odot$}; &
    \node (y) [vector] {$\bm y$};\\

    & \node (bin) [function] {$\mathrm{bin}$}; &
    \node (k) [vector] {$\bm k$}; & &
    \node (sign) [function] {$\mathrm{sign}$}; \\
  };

  { [start chain]
    \chainin (x);
    \chainin (abs) [join=by {tip, vh path}];
    \chainin (r) [join=by path];
    \chainin (mult) [join=by tip];
    \chainin (odot) [join=by {hv path, tip}];
    \chainin (y) [join=by tip];
  }
  { [start chain]
    \chainin (x);
    \chainin (bin) [join=by {tip, vh path}];
    \chainin (k) [join=by path];
    \chainin (sign) [join=by tip];
    \chainin (odot) [join=by {tip, hv path}];
  }
  { [start chain] \chainin (wr); \chainin (mult) [join=by tip]; }
  { [start chain] \chainin (wr); \chainin (sign) [join=by tip]; }
  { [start chain] \chainin (wi); \chainin (mult) [join=by tip]; }
  { [start chain] \chainin (wi); \chainin (sign) [join=by tip]; }
  { [start chain] \chainin (r); \chainin (sign) [join=by tip]; }
  { [start chain] \chainin (k); \chainin (mult) [join=by tip]; }

\end{tikzpicture}

% \end{document}

### 2021-01-06 slides_long/npu.tex

--- 2021-01-06 slides_long/naive-npu.tex
@@
         fat/.style={-, ultra thick, opacity=0.5},every join/.style={rounded corners},
-        path/.style={to path={-- (\tikztotarget)}},
         hv path/.style={to path={-| (\tikztotarget)}},
@@
   \matrix[column sep=3mm, row sep=3mm] {
-    & \node (abs) [function] {$\mathrm{abs}$}; &
+    & &
     \node (r) [vector] {$\bm r$}; & &
@@
 
-    \node (x) [vector] {$\bm x$}; & & & &
+    \node (x) [vector] {$\bm x$}; &
+    \node (gate) [function] {$\mathrm{gate}$}; &
+    \node (g) [trainable] {$\bm g$}; & &
     \node (wr) [trainable] {$\bm W_r$}; & \node (wi) [trainable] {$\bm W_i$}; &
@@
 
-    & \node (bin) [function] {$\mathrm{bin}$}; &
+    & &
     \node (k) [vector] {$\bm k$}; & &
@@
     \chainin (x);
-    \chainin (abs) [join=by {tip, vh path}];
-    \chainin (r) [join=by path];
+    \chainin (gate) [join=by tip];
+    \chainin (r) [join=by {vh path}];
     \chainin (mult) [join=by tip];
@@
   { [start chain]
-    \chainin (x);
-    \chainin (bin) [join=by {tip, vh path}];
-    \chainin (k) [join=by path];
+    \chainin (gate);
+    \chainin (k) [join=by {vh path}];
     \chainin (sign) [join=by tip];
@@
   { [start chain] \chainin (k); \chainin (mult) [join=by tip]; }
+  { [start chain] \chainin (g); \chainin (gate) [join=by tip]; }
 

### 2021-01-26 poster/main.tex
poster

\documentclass[30pt]{tikzposter}

% design based on https://twitter.com/mikemorrison/status/1110191245035479041?lang=en
% and https://github.com/SimonLarsen/tikzpostersdu

\input{preamble.tex}

\hyphenation{RealNPU}

\begin{document}

% remove offset that would otherwise be fixed by \maketitle
\makeatletter
\setlength{\TP@blocktop}{.47\textheight}
\makeatother

\begin{columns}

  \column{0.53}
    \nobackgroundblock{
      {\fontseries{l}\fontsize{60}{80}\selectfont
        \textbf{\emph{Neural Power Units}} -
        Learning to \textbf{extrapolate} functions composed of
        \textbf{arithmetic operations}.
      }
    }

  \column{0.17}
    \nobackgroundblock{
      \begin{center}
        {\fontseries{l}\fontsize{35}{40}\selectfont
          Niklas Heim\\
          V\'aclav \v Sm\'idl\\
          Tom\'a\v s Pevn\'y}
      \end{center}
    }

  \column{0.30}
  \block{}{
    \begin{minipage}{0.18\textwidth}
      \includegraphics[width=\textwidth]{div-logo.png}
    \end{minipage}
    \hfill
    \begin{minipage}{0.08\textwidth}
      \begin{flushleft}
      Czech Technical University\\
      Prague
      \end{flushleft}
    \end{minipage}
  }

\end{columns}

\begin{columns}

  \column{0.53}
  \block{}{
    \centering
    \begin{minipage}{0.1\textwidth}
      \centering
      \textbf{Neural Power Unit}\\
      schematic with the \textbf{relevance gate}\\
      shaded in grey
    \end{minipage}
    \hspace{2cm}
    \begin{minipage}{0.33\columnwidth}
      \includegraphics[width=\textwidth]{npu.png}
    \end{minipage}
  }

  \begin{subcolumns}
    \subcolumn{0.5}
    \block{Neural Arithmetic}{
      \emph{Neural Arithmetic} (or \emph{Arithmetic Extrapolation}) uses
      inductive biases to increase the extrapolation performance of neural
      networks on tasks in which the underlying function is \emph{partially}
      composed of arithmetic operations.
    }
    \block{Neural Power Unit (NPU)}{
      The NPU (inspired by NALU; Trask et al.) uses complex arithmetic to correctly
      process negative numbers and contains a relevance gate $g$ for
      more consistent convergence and sparser solutions.
      \begin{align*}
        y &= \exp(\Wre \log r - \pi\Wim k) \\
          &\odot \cos(\Wim\log  r + \pi\Wre k),
      \end{align*}
      where
      \begin{align*}
        \label{eq:gatednpu_def}
        r &= {\hat g} \odot (| x|+\epsilon) + (1-{\hat g}), \\
        k_i &= \begin{cases}
           0  & x_i \geq 0 \\
          \hat g_i & x_i < 0
        \end{cases},\\
        \hat g_i &= \min(\max(g_i,0),1),
      \end{align*}
      with inputs $ x$, and trainable parameters $\Wre$, $\Wim$, $g$.\\
      In the \textbf{RealNPU} we fix $\Wim$ to zero to
      obtain a highly transparent model.
    }

    \block{Prior art}{
      \begin{itemize}
        \item \emph{NALU} (Trask et al.): Can perform $(+,\times,\div)$,
          but cannot handle negative numbers and has convergence problems.
        \item \emph{NMU \& NAU} (Madsen \& Johansen): Can perform addition and multiplication,
          but no division.
      \end{itemize}
    }

    \subcolumn{0.5}
    \block{Our Contributions}{
      \begin{itemize}
        \item Learning \textbf{multiplication}, \textbf{division} and
          fractional \textbf{power functions} 
        \item Correct processing of \textbf{negative inputs}  
        \item \textbf{Relevance gating} for reliable convergence and sparse solutions
        \item A \textbf{transparent} model for applications like equation discovery (RealNPU)
      \end{itemize}
    }

    \block{Relevance gate}{
      On a toy task of learning $f(x,y) = x$ we demonstrate that
      the \emph{NaiveNPU} (without the relevance gate) has a zero gradient norm
      in large parts of parameter space (left plot).
      In the NPU (with the gate) the gradient surface becomes much more informative.
      \vspace{1cm}

      \includegraphics[width=0.235\textwidth]{../plots/npu_gatednpu_id_grad.pdf}
    }
    \block{}{
      Find all the details in our paper or contact us via
      \texttt{heimnikl@fel.cvut.cz}.

      \vspace{1.5cm}
      \begin{center}
        \begin{minipage}{0.07\textwidth}
          \centering
          Paper\\
          \vspace{0.3cm}
          \includegraphics[height=4.5cm]{qr-paper.png}
        \end{minipage}
        \hspace{2cm}
        \begin{minipage}{0.07\textwidth}
          \centering
          Code\\
          \vspace{0.3cm}
          \includegraphics[height=4.5cm]{qr-code.png}
        \end{minipage}
      \end{center}
      \vspace{1.05cm}
    }
  \end{subcolumns}

  \column{0.47}
  \block{Extrapolation experiment}{
    %\begin{multicols}{2}
      Prediction error for different models trained to learn $f$ on training
      samples $(x,y) \sim U(0.01,2)$.
      \begin{equation*}
        f(x,y) = (x+y,\, xy,\, \frac{x}{y},\, \sqrt{x} \text{  })^T
      \end{equation*}
      Bright colors indicate low error. All models learn the problem within the
      training range, but only the NPU manages to learn all operations including
      the fractional power $\sqrt{x}$.
    %\end{multicols}
    \begin{center}
      \includegraphics[width=0.4\textwidth]{../plots/simple_err.pdf}
    \end{center}
  }
  \block{Towards Equation Discovery}{
    %\begin{multicols}{2}
      Our paper sketches how to use the \textbf{RealNPU} for equation discovery
      of ODEs with fractional powers.  The RealNPU (Layer 1) on the right
      discovers a product of fractional powers in the first row of weights.
      The NAU (Layer 2) looks very similar to the parameter matrix of the
      \emph{fSIR} model (Taghvaei et al.) on the left.
    %\end{multicols}

    \begin{center}
      \begin{minipage}{.14\textwidth}
        \begin{equation*}
          \begin{bmatrix}
            \dot S \\ \dot I \\ \dot R
          \end{bmatrix}
          =
          \begin{bmatrix}
            \text{-}\beta & 0 & \eta \\
            \beta & \text{-}\alpha & 0 \\
            0 & \alpha & \eta
          \end{bmatrix}
          \begin{bmatrix}
            I^\gamma S^\kappa \\ I \\ R
          \end{bmatrix}
        \end{equation*}
      \end{minipage}
      \hspace{2cm}
      \begin{minipage}{.25\textwidth}
        \includegraphics[width=\textwidth]{../plots/sir_gatednpu_modelps.pdf}
      \end{minipage}
    \end{center}
    \vspace{0.5cm}
  }

\end{columns}

\end{document}
